### 2019-12-10 paper/draft.tex
Add tex file

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

\usepackage{tikz}
\usepackage{amsmath}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Formatting Submissions for a USENIX Conference:\\
  An (Incomplete) Example}

%for single author (just remove % characters)
\author{
{\rm Grigoris Ntousakis}\\
Technical University of Crete
\and
{\rm Nikos Vasilakis}\\
Massachusetts Institute of Technology
}

\maketitle

\begin{abstract}
  One two three
\end{abstract}

\section{Introduction}

Intro

% \section*{Acknowledgments}
% 
% \section*{Availability}

\bibliographystyle{plain}
\bibliography{\jobname}

\end{document}

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks

### 2019-12-10 paper/draft.tex
Update stuff

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Formatting Submissions for a USENIX Conference:\\
-  An (Incomplete) Example}
+\title{\Large \bf Module-aware Fracture and Recombination for Dynamic Analysis}
 
@@
 
-Intro
+Some citations to ensure we can see them~\cite{Christophe:2015:DAU:2819009.2819180, Keil:2013:EDA:2508168.2508176, Lehmann:2019:WFD:3297858.3304068, Sun:2018:EDA:3178372.3179527}.
 
@@
 \bibliographystyle{plain}
-\bibliography{\jobname}
+\bibliography{bib}
 

### 2019-12-19 paper/draft.tex
Update packages

@@
 
-\usepackage{tikz}
-\usepackage{amsmath}
+\usepackage{soul}
+\usepackage{xspace}
+\usepackage{color}
+\newcommand{\eg}{{\em e.g.}, }
+\newcommand{\ie}{{\em i.e.}, }
+\newcommand{\etc}{{\em etc.}\xspace}
+\newcommand{\vs}{{\em vs.} }
 
+\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
+\newcommand{\sx}[1]{(\S\ref{#1})}
+\newcommand{\sys}{{\scshape Lya}\xspace}
+\newcommand{\toy}{{\tt lya.js}\xspace}
 %-------------------------------------------------------------------------------
@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Module-aware Fracture and Recombination for Dynamic Analysis}
+\title{\Large \bf Module-level Dynamic Analysis}
 
@@
 \begin{abstract}
-  One two three
+We introduce \emph{module-level dynamic analysis}, a new dynamic analysis abstraction that supports dynamic fracture and recombination at the level of individual modules.
+By leveraging the ubiquity of third-party modules in today's applications, this analysis provides 
+Our implementation, \sys, simplifies the analysis
+
 \end{abstract}

### 2019-12-19 paper/draft.tex
Update Lya

@@
 \section{Introduction}
+\label{intro}
 
+Dynamic analysis is a type of program analysis performed by (and while) executing a program with the goal of identifying information about the program.
+Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics (multiple citations).
+
+% Where dynamic analysis shines is
+Dynamic analysis occupies a clear spot in the space of analysis has clear strengths and weaknesses.
+  (i) involve current runtime information, such as the workload patterns
+  (ii) have full visibility into the current execution (no path explosion),
+  (iii) is the only viable option in dynamic programming languages---such as Ruby, Python, 
+Examples of information not analyzable statically include runtime code evaluation, runtime introspection and reflection, as well as multi-lingual support.
+Dynamic analysis is a particularly good fit for the analysis of dynamic languages.
+
+Unfortunately, however, reaping these benefits comes with significant overheads in terms of developer effort and runtime performance.
+One approach is to instrument the program requires an in-depth understanding of its internals and associated tools (\eg instruction set \etc).
+Another approach is to modify the runtime environment of the program---\eg JavaScript's V8 engine.
+Problem-specific solutions require significant investment outside the language's mental model and
+
+This paper proposes a novel approach to dynamic analysis, termed \emph{module-aware dynamic analysis} and implemented in \sys.
+(i) at a somewhat coarser granularity, but still offering insights---and in a semantics-aware way tailored to the programming language.
+(ii) bolt on
+Our approach is applicable to any language that supports some notion of modularity, runtime introspection, and .
+It plugs into the module-loading capability of the runtime system to insert key hooks for inserting 
+After the parsing and interpretation phases of module loading complete, 
+ which are then parsed and interpreted and 
+Surprisingly, as we show in this paper, this architecture requires \emph{no} modifications to the language runtime---that is, it is backward-compatible with vanilla unmodified language runtime environments.
+
+Its key strategy is to fracture applications at the boundaries of modules, instrument their interfaces (including direct accesses) using meta-programming capabilities, and recombine them 
+By combining visiiblity into both built-in and third-party modules, \sys can get gather important information for 
+at a much lower cost---both in terms of runtime performance and developer effort.
+
+% to enable module-aware dynamic analysis are general
+To achieve this, module-aware dynamic analysis leverages several techniques.
+It plugs into the module manager;
+wraps interfaces
+(i) bolt on, meaning
+(ii) high-performance, and 
+(iii) low effort
+
+As shown later, these capabilities are generally available in all dynamic programming languages---\eg
+
+To demonstrate the effectiveness of our techniques, we
+  (i) build a prototype of module-aware dynamic analysis for server-side JavaScript, called \sys; and
+  (ii) develop a diverse set of analyses---including an allow/deny security analysis, a profiling analysis showing hot modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
+  (iii)  and use \sys to evaluate these analyses on three levels:
+    synthetic micro-benchmarks, that highlight certain features;
+    single-module meso-benchmarks, that allow comparison with other dynamic analysis tools; and
+    end-to-end full-application macro-benchmarks, that shows \sys's behavior of the system on realistic workloads. 
+\sys's implementation and evaluation drives the design requirements for \sys and highlights the benefits of bolt-on module-aware dynamic analysis.
+
+Our contributions, presented in \S\ref{bg}--\ref{impl} include:
+\begin{itemize}
+\item We characterize the shared needs of four case-study analyses~\sx{bg} for which an implementation from scratch would require a significant investment in terms of developer effort.
+\item We present the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
+\item We describe designs of four 
+\item We discuss our prototype implementation, \sys, as a pluggable library for the JavaScript ecosystem~\sx{impl}; our evaluation shows that \sys incurs minimal performance overheads over the respective baseline runtime.
+\end{itemize}
+
+Aside from the sections corresponding to these contributions (\S\ref{bg}--\ref{impl}), the paper discusses \sys's limitations and its application to other environments~\sx{diss};
+   it compares \sys with related prior work in the literature~\sx{rw}; and draws appropriate conclusions~\sx{end}.
+
+\section{Background, Examples, and Goals}
+\label{bg}
+
+\section{Module-aware Dialysis}
+\label{design}
+
+\section{Applications of Analysis}
+\label{apps}
+
+\section{Implementation}
+\label{impl}
+
+\section{Evaluation}
+\label{eval}
+
+\subsection{Micro-benchmarks}
+\label{micro}
+
+\subsection{Single-module Benchmarks}
+\label{meso}
+
+\subsection{End-to-End Benchmarks}
+\label{macro}
+
+\section{Discussion and Limitations}
+\label{diss}
+
+\section{Related Work}
+\label{rw}
 Some citations to ensure we can see them~\cite{Christophe:2015:DAU:2819009.2819180, Keil:2013:EDA:2508168.2508176, Lehmann:2019:WFD:3297858.3304068, Sun:2018:EDA:3178372.3179527}.
+
+\section{Conclusion}
+\label{end}
 

### 2019-12-19 paper/draft.tex
Update prelude and intro

@@
+% TODO: tempted to term this "Module-aware dynamic fracture, analysis, and reassembly" as Dialysis or refracture
 \documentclass[letterpaper,twocolumn,10pt]{article}
@@
 \usepackage{color}
-\newcommand{\eg}{{\em e.g.}, }
-\newcommand{\ie}{{\em i.e.}, }
-\newcommand{\etc}{{\em etc.}\xspace}
-\newcommand{\vs}{{\em vs.} }
+
+\def\omit#1{}
+\def\eg{{\em e.g.}, }
+\def\ie{{\em i.e.}, }
+\def\etc{{\em etc.}\xspace}
+\def\vs{{\em vs.}\xspace}
+% \newcommand{\heading}[1]{\vspace{4pt}\noindent\textbf{#1}\enspace}
+% No vspace, coz Usenix class already has paragraph space
+\newcommand{\heading}[1]{\vspace{2pt}\noindent\textbf{#1}\enspace}
+\newcommand{\ttt}[1]{\texttt{#1}}
+\newcommand{\ttiny}[1]{\texttt{\scriptsize #1}}
+\newcommand{\tcn}[1]{}
 
@@
 \newcommand{\toy}{{\tt lya.js}\xspace}
+
+\newcommand{\nv}[1]{[{\color{cyan}#1 --- Nikos}]}
+\newcommand{\review}[1]{{\color{red}#1}}
+\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
+\newcommand{\todo}[1]{\hl{#1}\xspace}
+\newcommand{\fixme}[1]{{\color{red}#1}}
+\newcommand{\tc}{(\todo{cite})\xspace}
 %-------------------------------------------------------------------------------
@@
 \author{
-{\rm Grigoris Ntousakis}\\
-Technical University of Crete
-\and
-{\rm Nikos Vasilakis}\\
-Massachusetts Institute of Technology
+{\rm Anonymous Author(s)}\\
+Submission \#323, 12 pages; Additional Material:
+% {\rm Grigoris Ntousakis}\\
+% Technical University of Crete
+% \and
+% {\rm Nikos Vasilakis}\\
+% Massachusetts Institute of Technology
 }
@@
 \begin{abstract}
-We introduce \emph{module-level dynamic analysis}, a new dynamic analysis abstraction that supports dynamic fracture and recombination at the level of individual modules.
-By leveraging the ubiquity of third-party modules in today's applications, this analysis provides 
+Modern software relies extensive on third-party libraries:
+  recent studies on several ecosystems show that code written by an application's nominal developers is only a small fraction of its total line count.
+Such over-reliance creates many challenges that appear later in the development process, exactly because developers have little knowledge and understanding of the module's internals.
+For example, security auditing and performance profiling large applications in the presence of deeply-nested third-party code becomes cumbersome.
+
+We introduce \emph{module dialysis}, a technique for dynamic analysis specifically tailored to module boundaries.
+Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion, and enables module-aware application fracture, analysis, and reassembly at runtime.
+Dialysis supports dynamic application fragmentation, analysis, and re-assembly at the level of individual modules.
+Tailored at providing information at the (recursive) boundaries of third-party modules.
+Such modules can be part of third-party packages or of the language's standard library;
+  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
+By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k
+
+We use a series of case-study analyses to motivate \sys's design and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values
+
+, all with minimal developer effort.
+The key feature is that module-level analysis can be bolted onto existing runtime environments as a library, without requiring low-level intsrumentation and maintaing the semantics of..
+Measurements of two COWL implementations, one in Firefox and one in Chromium, demonstrate a virtually imperceptible increase in page-load latency.
+
 Our implementation, \sys, simplifies the analysis

### 2019-12-19 paper/draft.tex
More on intro

@@
 
-\section{Module-aware Dialysis}
+A single application today often incorporates multiple libraries\footnote{We use the terms ``library'', ``package'', and ``module'' interchangeably.} written and published by several different authors.
+The emerging development process should (and to a certain extent, does) simplify the development and testing process;
+  unfortunately, good abstractions are sealed (\ie they do not leak between abstraction layers), which makes the inspection of a library difficult.
+
+\subsection{Modularity Today}
+
+languages provide module systems
+
+closely coupled with the runtime
+
+A module uses a \ttt{import} function and returns an export .
+Intuitively a map
+
+Several details:
+  same module at multiple levels, and the module cache
+  sometime it's the same, some times it;s not
+  module resolution algorithm
+
+\subsection{Motivating Examples}
+
+Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions.
+These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
+
+\subsection{Design Goals}
+
+We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
+While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses systems as these
+
+require highly specialized solutions often outside the core language,
+do not leverage or offer semantic information at the level of module boundaries,
+or lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
+These applications clearly illustrate the need for a system 
+To summarize, these applications would appear to be served well by a system that:
+\begin{itemize}
+  \item Operates at the level of modules, both semantics and performance-wise
+  \item Does not require learning a new tool or language---on the contrary,
+    developers
+  \item can be bolt onto an existing runtime as a library, regardless of whether 
+  \item supports programmable analyses
+\end{itemize}
+
+In the next section we describe the design \sys, a new dynamic analyses
+framework that satisfies these goals
+
+\section{Module-aware Dynamic Analysis}
 \label{design}

### 2019-12-19 paper/draft.tex
Add implementation details

@@
 
-\section{Implementation}
+\section{Implementation: Lya}
 \label{impl}
+
+We implemented \sys for version 
+We show where other implementations would diverge in table 1
+
+The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
+It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+
+(1) why node.js
+(2) Create a table of compatibility and show individual aspects
+
+\heading{Module System}
+Node.js' module system is implemented entirely in JavaScript.
+It exposes \ttt{require}, a global-looking function for importing modules.
+\fixme{Figure} above demonstrates the use of \ttt{require}.
+
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% // -------------- [./main.js] -------------
+% // importing point
+% let Point = require("./point.js");
+% Point.create(1, 1).print(); // => [1, 1]
+% 
+% // -------------- [./point.js] ------------
+% let Point = function Point (x, y) {
+%     this.x = x; this.y = y;
+% };
+% Point.prototype.print = function print () {
+%   console.log([this.x, this.y]);
+% };
+% module.exports = {
+%     create:  function create (x, y) {
+%         return new Point(x, y);
+%     }
+% };
+% \end{lstlisting}
+
+In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
+Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
+  the rest is module-private functionality.
+Files and modules are in one-to-one correspondence (each file is treated as a separate module).
+Method \ttt{require} is synchronous (\ie blocking):
+  it will block execution until the module specified is loaded.
+% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
+The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.
+
+\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).
+
+\subsection{Implementation of the Module System}
+\label{c}
+
+At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+
+\begin{enumerate}
+% \def\labelenumi{\arabic{enumi}.}
+\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+\end{enumerate}
+
+% The resolution algorithm is somewhat convoluted, because it depends on several different facts (including the type of the file requested, whether it is a globally installed, whether it is a directory \etc).
+% It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
+\sys interposes on all of these steps to facilitate transformations.
+Wrapping (3) and evaluation (4) are particularly interesting, because they allow \sys to interpose at the module boundary during runtime.
+Before a module's code is evaluated, the Node.js module loader wraps the module so that
+  (i) it keeps top-level variables (defined with \ttt{var}, \ttt{const} or \ttt{let}) scoped to the module rather than the global object; and
+  (ii) it provides some global-looking variables that are actually specific to the module, such as the \ttt{module} and \ttt{exports} objects that the implementor can use to export values from the module and convenience variables---such as \ttt{\_\_filename} and \ttt{\_\_dirname}  containing the module's absolute filename and directory path, respectively.
+True globals remaining are
+  (i) the global objects as defined by the EcmaScript standard (\eg \ttt{Object}, \ttt{Function}, \ttt{Math}); and
+  (ii) Node.js-specific globals (\eg \ttt{console}, \ttt{process}, \ttt{timer}).
+These globals require further interposition.
+
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% // Node.js will wrap a module with a function,
+% // so as to bring certain names into scope
+% // before compiling/evaluating code.
+% let wrapped = "function (" +
+%         "exports, require, module, " +
+%         "__filename, __dirname, CTX) {" +
+%     "let Math = CTX.Math" +
+%     "let console = CTX.console" +
+%     //...[more definitions]
+%     moduleSource +
+%   "});"
+% \end{lstlisting}
+
+\sys hooks into the wrapper function (the last variable in the function definition, \ttt{CTX}).
+This trivial source-to-source transformation re-defines global variables as module-locals and initializes them with \sys-augmented values.
+For example, \ttt{console} in the context of the module will be an \sys-created object that allows \sys to interpose on it.
+Evaluation of the module passes an additional value to this function, which is the modified context.
+As a result, any changes to the top-level objects and any global variables are accessible from the within the module.
+
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% //Input: module ID e.g., absolute filepath
+% let load = function (ID) {
+%   if (cache[ID]) {
+%      return cache[ID];
+%   }
+%   let m = {
+%     exports: {}, id: ID, dir: path.resolve(ID)
+%   };
+%   let cm = v8.compile(wrapped);
+%   let ii = iris.getImplicit(ID);
+%   let c = iris.freshContext(ii);
+%   cm(m.exports, this.require, m, ID, m.dir, c);
+%   let ei = iris.getExplicit(ID);
+%   m.exports = iris.wrap(m.exports, [ei] );
+%   cache[ID] = m;
+%   return m.exports;
+% }
+% \end{lstlisting}
+
+The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
+After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
+\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
+Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
+Finally, the results of the entire process are placed into the module cache for later use.
+
+\
 

### 2019-12-20 paper/draft.tex
Update abstract

@@
-% TODO: tempted to term this "Module-aware dynamic fracture, analysis, and reassembly" as Dialysis or refracture
+% TODO: tempted to term this "Module-aware dynamic fragmentation, analysis, and reassembly" as Dialysis or refracture
 \documentclass[letterpaper,twocolumn,10pt]{article}
@@
 
+\newcommand{\fra}{fragmentation\xspace} % fracture
+\newcommand{\ana}{analysis\xspace}      % 
+\newcommand{\ass}{reassembly\xspace}    % 
+\newcommand{\dia}{\fra, \ana, and \ass}
+
 \newcommand{\nv}[1]{[{\color{cyan}#1 --- Nikos}]}
@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Module-level Dynamic Analysis}
+\title{\Large \bf Module Dialysis with Lya}
 
@@
 {\rm Anonymous Author(s)}\\
-Submission \#323, 12 pages; Additional Material:
+Submission \#225, 12 pages; Additional Material:
 % {\rm Grigoris Ntousakis}\\
@@
 \begin{abstract}
-Modern software relies extensive on third-party libraries:
-  recent studies on several ecosystems show that code written by an application's nominal developers is only a small fraction of its total line count.
-Such over-reliance creates many challenges that appear later in the development process, exactly because developers have little knowledge and understanding of the module's internals.
-For example, security auditing and performance profiling large applications in the presence of deeply-nested third-party code becomes cumbersome.
 
-We introduce \emph{module dialysis}, a technique for dynamic analysis specifically tailored to module boundaries.
-Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion, and enables module-aware application fracture, analysis, and reassembly at runtime.
-Dialysis supports dynamic application fragmentation, analysis, and re-assembly at the level of individual modules.
-Tailored at providing information at the (recursive) boundaries of third-party modules.
+This paper introduces \emph{module dialysis}, a novel technique for dynamic analysis specifically tailored to module boundaries. % to applications with many modules
+Modules are becoming the cornerstone of modern software engineering:
+  applications today use hundreds of modules, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
+On the surface, such code reuse is beneficial, as it lowers development costs, software testing, encapsulation; 
+  however, such over-reliance creates many challenges later in the development process, exactly because developers have little knowledge and understanding of module's internals.
+For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
+
+% Turn such over-reliance on its head
+To address these challenges, module dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
+One of its highlights is ease of deployment and use:
+  (i) bolted onto existing runtime environments as a library, by wrapping and transforming the underlying module system
+  (ii) allowing developers to extract information using the same abstractions as the host language---eschewing low-level instrumentation.
+Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis has the potential of low performance overheads while still providing important information.
+
+Our dialysis prototype, \sys, targets the JavaScript ecosystem through the V8 runtime.
+We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly low developer effort.
+Experiments with \sys show that it adds a virtually imperceptible increase in the load latency of individual modules and that it scales well to real applications with hundreds of modules.
+
+module-level analysis
+
+ and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values
+
+Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
+% By leveraging the ubiquity of third-party modules in today's applications
 Such modules can be part of third-party packages or of the language's standard library;

### 2019-12-20 paper/draft.tex
Update abstract

@@
 
-This paper introduces \emph{module dialysis}, a novel technique for dynamic analysis specifically tailored to module boundaries. % to applications with many modules
-Modules are becoming the cornerstone of modern software engineering:
-  applications today use hundreds of modules, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
-On the surface, such code reuse is beneficial, as it lowers development costs, software testing, encapsulation; 
-  however, such over-reliance creates many challenges later in the development process, exactly because developers have little knowledge and understanding of module's internals.
+This paper introduces \emph{library dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
+The proliferation of third party libraries in applications is a recent trend in software engineering:
+Libraries are becoming the cornerstone of modern 
+  applications today rely on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
+% On the surface, such reliance is beneficial, as it lowers development costs, aids targeted software testing, and enables code reuse;
+Despite its benefits, such over-reliance creates many challenges down the road, exactly because developers have little knowledge and understanding of each library's internals.
 For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
 
-% Turn such over-reliance on its head
-To address these challenges, module dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
+To address these challenges, library dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
 One of its highlights is ease of deployment and use:
@@
   the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
-By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k
-
-We use a series of case-study analyses to motivate \sys's design and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values
 
 , all with minimal developer effort.
-The key feature is that module-level analysis can be bolted onto existing runtime environments as a library, without requiring low-level intsrumentation and maintaing the semantics of..
-Measurements of two COWL implementations, one in Firefox and one in Chromium, demonstrate a virtually imperceptible increase in page-load latency.
+As a result,
 

### 2019-12-20 paper/draft.tex
Nailed the abstract:-)

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Module Dialysis with Lya}
+\title{\Large \bf Library Dialysis with Lya}
 
@@
 {\rm Anonymous Author(s)}\\
-Submission \#225, 12 pages; Additional Material:
+\normalsize{Submission \#225, 12 pages}\\
+\normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
 % {\rm Grigoris Ntousakis}\\
@@
 This paper introduces \emph{library dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
-The proliferation of third party libraries in applications is a recent trend in software engineering:
-Libraries are becoming the cornerstone of modern 
-  applications today rely on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
+Such library over-reliance is a recent trend in software engineering:
+  applications today rely recursively on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
 % On the surface, such reliance is beneficial, as it lowers development costs, aids targeted software testing, and enables code reuse;
-Despite its benefits, such over-reliance creates many challenges down the road, exactly because developers have little knowledge and understanding of each library's internals.
-For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
+Despite its benefits, such over-reliance creates many challenges for developers, exactly because their little knowledge of and visibility in the internals of these libraries:
+  for example, security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
 
-To address these challenges, library dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
-One of its highlights is ease of deployment and use:
-  (i) bolted onto existing runtime environments as a library, by wrapping and transforming the underlying module system
-  (ii) allowing developers to extract information using the same abstractions as the host language---eschewing low-level instrumentation.
-Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis has the potential of low performance overheads while still providing important information.
+To address these challenges, library dialysis is a general technique that allows extracting meaningful insights with only a few lines of analysis-specific code.
+This feature is achieved by automating dynamic \fra, \ana, and \ass of applications at the level of individual modules and during program execution, by wrapping and transforming the underlying dependency graph.
+Operating at this level of granularity has several benefits:
+  (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
+  (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and %developers can use their tools
+  (iii) it features low performance overheads, to the point that has the potential to be used online.
+% FIXME: It depends on the analysis
+% Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis 
+% Operating at the granularity of library has several benefits: (i) ease (ii) performance (iii) while still getting 
+%In a sense, modules are the right level of abstraction
 
-Our dialysis prototype, \sys, targets the JavaScript ecosystem through the V8 runtime.
-We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly   low developer effort.
-Experiments with \sys show that it adds a virtually imperceptible increase in the load latency of individual modules and that it scales well to real applications with hundreds of modules.
+Our dialysis prototype, \sys, targets the JavaScript ecosystem, which counts over 1M libraries and is used on the web, server, and mobile.
+We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly   low developer effort and performance overhead:
+  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual modules, and scale to real applications with hundreds of modules.
 
-module-level analysis
-
- and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values
-
-Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
-% By leveraging the ubiquity of third-party modules in today's applications
-Such modules can be part of third-party packages or of the language's standard library;
-  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
-
-, all with minimal developer effort.
-As a result,
-
-Our implementation, \sys, simplifies the analysis
+% Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
+% % By leveraging the ubiquity of third-party modules in today's applications
+% Such modules can be part of third-party packages or of the language's standard library;
+%   the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
 
@@
 \label{design}
+
+\subsection{Overview}
+
+At a high level, dialysis works at three stages:
+
+: Fracture the programs into shards — pieces
+of the programs that implement a computation or functionality. The granularity of the fracture determines
+the size of the shards. Potentially useful granularities
+include functions, procedures, classes, abstract data
+types, modules, loops, and program slices. Program
+fracture typically includes the encapsulation of each
+shard into its own separately invocable program for
+testing, analysis, and exploration.
 

### 2019-12-20 paper/draft.tex
Update analysis

@@
 % TODO: tempted to term this "Module-aware dynamic fragmentation, analysis, and reassembly" as Dialysis or refracture
+% CFP: https://www.usenix.org/conference/atc20/call-for-papers
 \documentclass[letterpaper,twocolumn,10pt]{article}
@@
 \newcommand{\ass}{reassembly\xspace}    % 
+\newcommand{\Fra}{Fragmentation\xspace} % fracture
+\newcommand{\Ana}{Analysis\xspace}      % 
+\newcommand{\Ass}{Reassembly\xspace}    % 
 \newcommand{\dia}{\fra, \ana, and \ass}
@@
 
-Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions.
+Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
+  (i) an allow/deny security analysis,
+  (ii) a profiling analysis showing hot modules,
+  (iii) a synthesis-oriented analysis on input-output data, and
+  (iv) an analysis enforcing a static union-based type system at runtime.
 These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
+
+\heading{Security Analysis}
+Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
+Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
+As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
+The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
+Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
+Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.
+
+Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
+The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
+% and is exploitable.
+Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
+Other functionality is \emph{implicitly} provided by the programming language;
+  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
+Both explicitly and implicitly provided functionality is exploitable by third-party code.
+While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
+% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
+MLC shows great promise, as it can
+(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
+(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
+(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).
+
+To make this concrete, we are introducing
+
+\heading{Performance Diagnosis}
+Developers use various techniques to understand such problems.
+For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
+These techniques, however, require some degree of \emph{manual} effort:
+  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
+Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.
+
+Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
+A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
+This allows viewing a series of calls as a stream of messages. % that 
+% at each module boundary 
+Module boundaries can be viewed as (virtual) queues of messages that await processing.
+% and applying windowed average operations on a 
+Overwhelming a module causes its ingress queue to grow.
+% MM: related to the sync vs. async
+% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
+At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
+% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.
+
+To make this concrete, we are introducing
+
+\heading{Type and Invariant Checking}
+Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
+Dynamic analysis can be used to generate type assertions or invariants
+For example
+
+To make this concrete, we are using
+The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
+
+\heading{Learning, Synthesis, and Regeneration}
+Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
+Dynamic analysis can be used to generate type assertions or invariants
+For example
+The approach has been pioneered by systems such as
+
+To make this concrete, we are using
+The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
 

### 2019-12-20 paper/draft.tex
Multiple updates

@@
 \usepackage{color}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{graphicx}
+
+\captionsetup[figure]{font=footnotesize,name={Fig.},labelfont={bf, footnotesize}}
+\captionsetup[table]{font=footnotesize,name={Tab.},labelfont={bf, footnotesize}, skip=2pt, aboveskip=2pt}
+\captionsetup{font=footnotesize,labelfont={bf, footnotesize}, belowskip=2pt}
 
@@
 \newcommand{\ttt}[1]{\texttt{#1}}
-\newcommand{\ttiny}[1]{\texttt{\scriptsize #1}}
+\newcommand{\ttiny}[1]{\texttt{\footnotesize #1}}
 \newcommand{\tcn}[1]{}
@@
 
-Dynamic analysis is a type of program analysis performed by (and while) executing a program with the goal of identifying information about the program.
+Dynamic analysis is a type of program analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
 Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics (multiple citations).
+Contrary to other types of analysis, its key benefits make it primary candidate in a variety of scenarios---for example in scenarios that
+  (i) involve current and accurate runtime information in view of changing workloads or use patterns,
+  (ii) have full visibility into the current execution (no path explosion),
+  (iii) enforce Turing-complete execution policies, where the invariants themselves are arbitrary programs,
+  (iii) involve dynamic or interpreted programming languages---such as Ruby, Python, Lua, or JavaScript.
 
 % Where dynamic analysis shines is
-Dynamic analysis occupies a clear spot in the space of analysis has clear strengths and weaknesses.
-  (i) involve current runtime information, such as the workload patterns
-  (ii) have full visibility into the current execution (no path explosion),
-  (iii) is the only viable option in dynamic programming languages---such as Ruby, Python, 
-Examples of information not analyzable statically include runtime code evaluation, runtime introspection and reflection, as well as multi-lingual support.
-Dynamic analysis is a particularly good fit for the analysis of dynamic languages.
+% Dynamic analysis occupies a clear spot in the space of analysis has clear strengths and weaknesses.
+% Examples of information not analyzable statically include runtime code evaluation, runtime introspection and reflection, as well as multi-lingual support.
+% Dynamic analysis is a particularly good fit for the analysis of dynamic languages.
 
-Unfortunately, however, reaping these benefits comes with significant overheads in terms of developer effort and runtime performance.
+Unfortunately, however, reaping these benefits comes with significant overheads in terms of developer effort or runtime performance.
 One approach is to instrument the program requires an in-depth understanding of its internals and associated tools (\eg instruction set \etc).
@@
 
-This paper proposes a novel approach to dynamic analysis, termed \emph{module-aware dynamic analysis} and implemented in \sys.
+This paper proposes a novel approach to dynamic analysis, termed \emph{module dialysis}\footnote{
+  A method of deconstruction, often for the purposes of removing waste products or component alteration.
+  From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
+} and implemented in \sys.
 (i) at a somewhat coarser granularity, but still offering insights---and in a semantics-aware way tailored to the programming language.
@@
 
-At a high level, dialysis works at three stages:
+FIXME: add user data
+At a high level, module dialysis works at three stages:
 
-: Fracture the programs into shards — pieces
-of the programs that implement a computation or functionality. The granularity of the fracture determines
-the size of the shards. Potentially useful granularities
-include functions, procedures, classes, abstract data
-types, modules, loops, and program slices. Program
-fracture typically includes the encapsulation of each
-shard into its own separately invocable program for
-testing, analysis, and exploration.
+\begin{itemize}
+
+  \item \Fra:
+    It first starts by recursively dis-assembling programs into their library dependencies---pieces of software implement a computation or functionality.
+    This is essentially achieved by instrumenting the import statements and walking the program's recursive dependency structure.
+    Different analysis can operate at different granularities, and has to solve challenges such as multi-module and dedublication.
+
+  \item \Ana:
+It then sets a specific analysis up by wrapping and transforming each module interface, its surrounding environment, as well as the values passing through the module boundary.
+Programmatic transformations walk and transform each one of these values based on their type:
+  the module interface is usually a complex (but singular) object; the surrounding environment treats 
+This phase requires solving several challenges, including enumerating and tracking all points of entry into and exit out of a library.
+It also requires providing 
+ in a backwards compatible fashion.
+
+  \item \Ass:
+  Finally, it re-assembles individual modified modules back into the original structure.
+  This creates several challenges, the most important of which is the treatment of the module cache---a mechanism for avoiding multiple loads of the same module .
+  Since a single library can now correspond to many different wrappers, each modified to capture different  analysis fragments, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
+
+\end{itemize}
+
+% \textbf{Core Language}
+% a few is not the same as 
+Transformations are used pervasively throughout \sys, and are abstracted via a few parametrizable templates.
+Templates map different types of values (List.~\ref{core-tx}) to a generic handler for each type.
+%given a value, a template will transform it using a handler matching its type
+% Templates match, 
+% \hl{match} between different \hl{value} % what are values
+%    \emph{types} and define generic handlers for each type.
+Transformations have these handlers parametrized to achieve concrete goals such as monitoring, serialization, and scale-out.
+Simplified instances are described in the following two sections (\S\ref{profiling}--\ref{core}).
+
+Transformations can be applied to any value in the language, such as an object returned from a module or an exception about to be sent across the network.
+The general case of such a value is a directed acyclic graph (DAG).
+The types of its vertices can be coarsely grouped into primitives, functions, and objects.
+Objects map strings to other values, pointing to other vertices in the DAG.
+% Listing~\ref{core-tx} presents a simplified core of the language.
+Transformations start by walking the DAG from the root vertex and processing component values based on their types.
+They do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+They only partially explore the object graph, as they do not peak through function closure environments.
+Fortunately, this aligns well with our goal of monitoring activity at module boundaries and ignoring module-internal activity.
+
+As an example, consider transforming the \ttt{crypto} module~\sx{solution}.
+\sys traverses the object returned by \ttt{crypto} and replaces functions such as \ttt{pbkdf2} with wrappers whose specifics depend on the intended goal:
+  profiling wrappers call the original function in between statistics collection, and RPC wrappers forward the call to a remote replica.
 
@@
 
+Library dialysis, as implemented in \sys, depends on a few features available in the programming language.
+In this section we describe how to develop the same solution on other environments.
+In the second part of this section, we reflect on some of the current limitations of the system.
+
+\subsection{Applying to Other Environments}
+
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Language features used and their availability in other languages}.
+    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
+\toprule
+                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
+\midrule
+Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
+Walk objects                    &         &             &        &      &      &      &      &         \\
+Shadow variables                &         &             &        &      &      &      &      &         \\
+Wrap values                     &         &             &        &      &      &      &      &         \\
+Global names                    &         &             &        &      &      &      &      &         \\
+\bottomrule
+\end{tabular*}
+\label{tab:compatibility}
+\vspace{-5mm}
+\end{table}
+
+\heading{Dynamic Language Interpretation}
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
+They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
+  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
+
 \section{Related Work}

### 2019-12-20 paper/draft.tex
Update intro

@@
   applications today rely recursively on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
-% On the surface, such reliance is beneficial, as it lowers development costs, aids targeted software testing, and enables code reuse;
+% On the surface, such reliance is beneficial, 
 Despite its benefits, such over-reliance creates many challenges for developers, exactly because their little knowledge of and visibility in the internals of these libraries:
@@
 This feature is achieved by automating dynamic \fra, \ana, and \ass of applications at the level of individual modules and during program execution, by wrapping and transforming the underlying dependency graph.
-Operating at this level of granularity has several benefits:
-  (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
-  (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and %developers can use their tools
-  (iii) it features low performance overheads, to the point that has the potential to be used online.
-% FIXME: It depends on the analysis
-% Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis 
-% Operating at the granularity of library has several benefits: (i) ease (ii) performance (iii) while still getting 
-%In a sense, modules are the right level of abstraction
-
 Our dialysis prototype, \sys, targets the JavaScript ecosystem, which counts over 1M libraries and is used on the web, server, and mobile.
@@
 
+% Operating at this level of granularity has several benefits:
+%   (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
+%   (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and %developers can use their tools
+%   (iii) it features low performance overheads, to the point that has the potential to be used online.
+% % FIXME: It depends on the analysis
+% % Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis 
+% % Operating at the granularity of library has several benefits: (i) ease (ii) performance (iii) while still getting 
+% %In a sense, modules are the right level of abstraction 
 \end{abstract}
@@
 Dynamic analysis is a type of program analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
-Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics (multiple citations).
-Contrary to other types of analysis, its key benefits make it primary candidate in a variety of scenarios---for example in scenarios that
-  (i) involve current and accurate runtime information in view of changing workloads or use patterns,
-  (ii) have full visibility into the current execution (no path explosion),
-  (iii) enforce Turing-complete execution policies, where the invariants themselves are arbitrary programs,
-  (iii) involve dynamic or interpreted programming languages---such as Ruby, Python, Lua, or JavaScript.
+Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
+Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
+  (i) current runtime information, such as profiling information, in view of changing workloads or use patterns~\cite{staticdynamic},
+  (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
+  (iii) Turing-complete policies, where invariants themselves are arbitrary programs~\cite{contracts1, contracts2, contracts3},
+  (iii) dynamic or runtime-reflection features~\cite{jsanalysis1, jsanalysis2}, such as the ones present in Python and JavaScript.
 
@@
 
-Unfortunately, however, reaping these benefits comes with significant overheads in terms of developer effort or runtime performance.
-One approach is to instrument the program requires an in-depth understanding of its internals and associated tools (\eg instruction set \etc).
-Another approach is to modify the runtime environment of the program---\eg JavaScript's V8 engine.
-Problem-specific solutions require significant investment outside the language's mental model and
+Unfortunately, reaping these benefits comes with significant costs in terms of (often, both) developer effort and runtime performance.
+Instrumenting the program often requires a good understanding of its internals.
+Applying associated tools adds to this requirement, such as instrumentation framework, instruction sets, and other underlying primitives~\cite{pin, valgrind}.
+Modifying the runtime environment of the program is also cumbersome, error-prone, and JavaScript's V8 engine.
+Problem-specific solutions require significant investment outside the language's mental model---for example, performance tracing frameworks such as perf and dtrace each feature their own language for specifying tracing programs, different from the application's language.
+---as a case in point, Jalangi reports XX overhed (exact overheads always depend on the specific analysis).
+
+Both overheads are severely compounded by the use of third-party libraries, development-time constructs usually glued together without a full understanding of their internals.
+Libraries are used pervasively nowadays to lower development costs and improve software quality, a recent phenomenon enabled by zero-cost of sharing:
+% This over-reliance to third-party libraries is a recent phenomenon, 
+  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library have essentially dropped to zero.
+As a result, applications today
+  to the point that it is common for thousands of applications to depend on libraries that count only a few dozen lines:
+  for example, leftpad and
 
 This paper proposes a novel approach to dynamic analysis, termed \emph{module dialysis}\footnote{
-  A method of deconstruction, often for the purposes of removing waste products or component alteration.
+  A method of deconstruction, often for the purposes of removing waste products or altering piecewise components.
   From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
 } and implemented in \sys.
-(i) at a somewhat coarser granularity, but still offering insights---and in a semantics-aware way tailored to the programming language.
-(ii) bolt on
-Our approach is applicable to any language that supports some notion of modularity, runtime introspection, and .
-It plugs into the module-loading capability of the runtime system to insert key hooks for inserting 
-After the parsing and interpretation phases of module loading complete, 
- which are then parsed and interpreted and 
-Surprisingly, as we show in this paper, this architecture requires \emph{no} modifications to the language runtime---that is, it is backward-compatible with vanilla unmodified language runtime environments.
+Library dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
+It operates during program execution, automating wrapping and transforming the underlying dependency graph, allowing developers to extract meaningful insights with only a few lines of analysis-specific code
+By operating at the granularity of libraries, module dialysis has several benefits over full-fledged dynamic analysis:
+  (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
+  (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and
+  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.
 
-Its key strategy is to fracture applications at the boundaries of modules, instrument their interfaces (including direct accesses) using meta-programming capabilities, and recombine them 
-By combining visiiblity into both built-in and third-party modules, \sys can get gather important information for 
-at a much lower cost---both in terms of runtime performance and developer effort.
+% (i) at a somewhat coarser granularity, but still offering insights---and in a semantics-aware way tailored to the programming language.
+% (ii) bolt on
+% Our approach is applicable to any language that supports some notion of modularity, runtime introspection, and .
+% It plugs into the module-loading capability of the runtime system to insert key hooks for inserting 
+% After the parsing and interpretation phases of module loading complete, 
+%  which are then parsed and interpreted and 
+% Surprisingly, as we show in this paper, this architecture requires \emph{no} modifications to the language runtime---that is, it is backward-compatible with vanilla unmodified language runtime environments.
+% 
+% Its key strategy is to fracture applications at the boundaries of modules, instrument their interfaces (including direct accesses) using meta-programming capabilities, and recombine them 
+% By combining visiiblity into both built-in and third-party modules, \sys can get gather important information for 
+% at a much lower cost---both in terms of runtime performance and developer effort.
+% 
+% % to enable module-aware dynamic analysis are general
+% To achieve this, module-aware dynamic analysis leverages several techniques.
+% It plugs into the module manager;
+% wraps interfaces
+% (i) bolt on, meaning
+% (ii) high-performance, and 
+% (iii) low effort 
+% 
+% As shown later, these capabilities are generally available in all dynamic programming languages---\eg
 
-% to enable module-aware dynamic analysis are general
-To achieve this, module-aware dynamic analysis leverages several techniques.
-It plugs into the module manager;
-wraps interfaces
-(i) bolt on, meaning
-(ii) high-performance, and 
-(iii) low effort
+To demonstrate the effectiveness of the proposed techniques, we build a prototype of library dialysis, called \sys, targeting the JavaScript ecosystem---featuring more than 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
+We develop a diverse set of four analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing hot modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
+This set of analysis drives the design requirements for \sys and highlights the benefits of bolt-on module-aware dynamic analysis.
+Finally, we we use \sys to evaluate these analyses on three different levels:
+  (i) synthetic micro-benchmarks that highlight certain features and confirm the correctness of our analyses in a controlled environment;
+  (ii) single-module meso-benchmarks that allow comparison with more traditional dynamic analysis frameworks; and
+  (iii) end-to-end full-application macro-benchmarks that show behavior of the \sys system on realistic workloads.
 
-As shown later, these capabilities are generally available in all dynamic programming languages---\eg
-
-To demonstrate the effectiveness of our techniques, we
-  (i) build a prototype of module-aware dynamic analysis for server-side JavaScript, called \sys; and
-  (ii) develop a diverse set of analyses---including an allow/deny security analysis, a profiling analysis showing hot modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
-  (iii)  and use \sys to evaluate these analyses on three levels:
-    synthetic micro-benchmarks, that highlight certain features;
-    single-module meso-benchmarks, that allow comparison with other dynamic analysis tools; and
-    end-to-end full-application macro-benchmarks, that shows \sys's behavior of the system on realistic workloads. 
-\sys's implementation and evaluation drives the design requirements for \sys and highlights the benefits of bolt-on module-aware dynamic analysis.
-
-Our contributions, presented in \S\ref{bg}--\ref{impl} include:
+\S\ref{bg}--\ref{eval} present our key contributions:
 \begin{itemize}
-\item We characterize the shared needs of four case-study analyses~\sx{bg} for which an implementation from scratch would require a significant investment in terms of developer effort.
-\item We present the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
-\item We describe designs of four 
-\item We discuss our prototype implementation, \sys, as a pluggable library for the JavaScript ecosystem~\sx{impl}; our evaluation shows that \sys incurs minimal performance overheads over the respective baseline runtime.
+\item \S\ref{bg} characterizes the shared needs of four case-study analyses for which no prior dynamic analysis framework meets their needs.
+\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
+\item \S\ref{impl} discuss our prototype implementation, \sys, as a pluggable library for the JavaScript ecosystem;
+\item \S\ref{eval} implementation and evaluation of the four analyses, showing \sys can express insightful analyses in 10–20 lines of code, adds a virtually imperceptible increase in the load latency of individual modules, and scales to real applications with hundreds of modules.
 \end{itemize}
 
-Aside from the sections corresponding to these contributions (\S\ref{bg}--\ref{impl}), the paper discusses \sys's limitations and its application to other environments~\sx{diss};
-   it compares \sys with related prior work in the literature~\sx{rw}; and draws appropriate conclusions~\sx{end}.
+Aside from the aforementioned sections (\S\ref{bg}--\ref{impl}), the paper discusses \sys's limitations and its application to other languages~\sx{diss};
+  it compares with related prior work in the literature~\sx{rw};
+  and closes with appropriate conclusions~\sx{end}.
 

### 2019-12-21 paper/draft.tex
More work in related work

@@
 
-\section{Applications of Analysis}
-\label{apps}
+% \section{Applications of Analysis}
+% \label{apps}
 
@@
 \label{rw}
-Some citations to ensure we can see them~\cite{Christophe:2015:DAU:2819009.2819180, Keil:2013:EDA:2508168.2508176, Lehmann:2019:WFD:3297858.3304068, Sun:2018:EDA:3178372.3179527}.
+
+Existing dynamic analysis frameworks can be classified either as coarse- or fine-grained.
+The former analyze interactions at the boundaries of entire components, whereas the latter associate metadata at the level of individual instructions or objects.
+We compare \sys to previously proposed systems in both categories, then contrast the two categories' overall characteristics.
+
+\heading{Heavyweight instrumentation}
+There is a series of heavyweight dynamic analysis frameworks.
+Popular frameworks include
+  Valgrind~\cite{valgrind} and Pin~\cite{pin} for native programs,
+  DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} for JVM byte code,
+  Jalangi~\cite{jalangi} for JavaScript programs, and,
+  most recently, Wasabi~\cite{wasabi} for Web-Assembly.
+
+The approach advocated by \sys is to throw a quick-and-easy analysis at the module boundaries
+
+Jalangi is the most relevant of these frameworks, and served as an inspiration
+
+\heading{Dynamic Analysis for WebAssembly}
+Related to JavaScript is WebAssembly, a standardized subset of JavaScript target ideal as a compilation target.
+Two techniques modify V8
+
+Wasabi is a framework for dynamic analysis of WebAssembly.
+Similar to \sys, it succeeds at lowering the effort required to write analyses, 
+and provides hooks for observation rather than manipulation
+Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.
+
+; even more similarly, it allows expressing analyses in JavaScript.
+Prior work has modified
+
+Some citations to ensure we can see them~\cite{javascript1, javascript2, javascript3}.
+
+\heading{Dynamic Instrumentation}
+Dialysis is related to dynamic binary instrumentation frameworks that wrap parts of the program to extract information.
+Many such frameworks translate basic blocks of the program just before their execution;
+  \sys starts with a phase that wraps (equivalent to instrumenting) a library during import, adding a small overhead at the loading time of each library.
+The overhead of this phase is only a small fraction of the time required to locate and load the module from disk.
+
+\heading{Program Transformations}
+% Add our work
+Module dialysis builds on aspect-oriented programming (AOP), a programming model that maps program points to actions to be taken at these points~\cite{aop}.
+Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
+Moreover, AOP works on languages that were already designed to support it, whereas module dialysis was explicitly designed to bolt onto existing languages and environments.
+
+More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure and which enable a program to access to its own internal structure, including rewriting itself as it executes.
+They are examples of runtime reflection, of which \sys makes extensive use to traverse, understand, wrap, and rewrite interfaces.
+With \sys, however, developers do not need to provide their own metaobjects.
+% self element
+
+\heading{Fracture and Recombination}
+Module dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
+PFR breaks up multiple programs into multiple components (called shards) with the goal of exchanging functionality between donor-donee pairs of programs.
+Module dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries, in the guise of libraries or modules.
 
@@
 
+Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
+Applications today routinely pull together hundreds of libraries, making their analysis difficult
+
+due to the very same abstraction and modularity principles that have benefited software engineering for decades.
+
+security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
+
+This paper introduces \emph{module dialysis}, an approach 
+corser
+approach towards coarse-grained
+This is achieved using a set of programmatic \emph{transformations} parametrizable by optional \emph{distribution recipes}.
+These operate at module boundaries during runtime to collect profiling information, detect bottlenecked components, and dynamically separate and coalesce parts of the application.
+
 % \section*{Acknowledgments}
-% 
+% Martin
 % \section*{Availability}

### 2019-12-21 run_all.sh
Add test for classname,debug,minimist

@@ -1,0 +1,43 @@
+cd ./tst/working/repos
+
+cd ./classnames
+[ -e timebind.txt ] && rm timebind.txt
+
+npm --key=0 test > /dev/null
+npm --key=1 test > /dev/null
+npm --key=5 test > /dev/null
+npm --key=2 test > /dev/null  
+npm --key=3 test > /dev/null 
+npm --key=4 test > /dev/null
+npm --key=6 test > /dev/null
+npm --key=7 test > /dev/null
+echo "We all test for classnames"
+
+cd ../debug/debug-master/
+[ -e timetest.txt ] && rm timetest.txt
+
+npm --key=0  test > /dev/null
+npm --key=1  test > /dev/null
+npm --key=5  test > /dev/null
+npm --key=2  test > /dev/null
+npm --key=3  test > /dev/null
+npm --key=4  test > /dev/null
+npm --key=6  test > /dev/null
+npm --key=7  test > /dev/null
+echo "We finish all test for debug"
+
+cd ../../minimist/t2_repo/
+cd t1 
+[ -e timetest.txt ] && rm timetest.txt
+
+key=0 node  whitespace.js > /dev/null
+key=1 node  whitespace.js > /dev/null
+key=5 node  whitespace.js > /dev/null
+key=2 node  whitespace.js > /dev/null
+key=3 node  whitespace.js > /dev/null
+key=4 node  whitespace.js > /dev/null
+key=6 node  whitespace.js > /dev/null
+key=7 node  whitespace.js > /dev/null
+
+echo "Test 1 from minimist repo is .... ok"
+

### 2019-12-21 tst/working/repos/classnames/tests/bind.js

@@ -1,11 +1,16 @@
 /* global describe, it */
-/* global describe, it */
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
-};
-let lya = require("../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+if (parseInt(process.env.npm_config_key) != 0) {
+	lyaConfig = {
+	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+	analysisCh: parseInt(process.env.npm_config_key),
+ 	POLICY: '../tst/working/repos/classnames/tests/dynamic.json'
+	};
+	let lya = require("../../../../../src/txfm.js");
+	require = lya.configRequire(require, lyaConfig);
+}
+// We start to count time for the tests
+const time = process.hrtime();
+const fs = require('fs');
 
 var assert = require('assert');
 var classNames = require('../bind');
@@ -21,133 +26,144 @@ var cssModulesMock = {
 
 var classNamesBound = classNames.bind(cssModulesMock);
 
-describe('bind', function () {
-	describe('classNames', function () {
-		it('keeps object keys with truthy values', function () {
-			assert.equal(classNames({
-				a: true,
-				b: false,
-				c: 0,
-				d: null,
-				e: undefined,
-				f: 1
-			}), 'a f');
-		});
 
-		it('joins arrays of class names and ignore falsy values', function () {
-			assert.equal(classNames('a', 0, null, undefined, true, 1, 'b'), 'a 1 b');
-		});
+for (var i = 0; i < 10; i++) {
+	describe('bind', function () {
+		describe('classNames', function () {
+			it('keeps object keys with truthy values', function () {
+				assert.equal(classNames({
+					a: true,
+					b: false,
+					c: 0,
+					d: null,
+					e: undefined,
+					f: 1
+				}), 'a f');
+			});	
 
-		it('supports heterogenous arguments', function () {
-			assert.equal(classNames({a: true}, 'b', 0), 'a b');
-		});
+			it('joins arrays of class names and ignore falsy values', function () {
+				assert.equal(classNames('a', 0, null, undefined, true, 1, 'b'), 'a 1 b');
+			});	
 
-		it('should be trimmed', function () {
-			assert.equal(classNames('', 'b', {}, ''), 'b');
-		});
+			it('supports heterogenous arguments', function () {
+				assert.equal(classNames({a: true}, 'b', 0), 'a b');
[…]

### 2019-12-21 tst/working/repos/debug/debug-master/test.js

@@ -1,128 +1,142 @@
 /* eslint-env mocha */
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 7,
-  POLICY: '/home/grigorisntousakis/Dropbox/thesis/lya/tst/working/repos/debug/debug-master/dynamic.json'
-};
-let lya = require("../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+if (parseInt(process.env.npm_config_key) != 0) {
+	lyaConfig = {
+	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+	analysisCh: parseInt(process.env.npm_config_key),
+ 	POLICY: '../tst/working/repos/debug/debug-master/dynamic.json'
+	};
+	let lya = require("../../../../../src/txfm.js");
+	require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 
 const assert = require('assert');
 const debug = require('./src');
 
-describe('debug', () => {
-	it('passes a basic sanity check', () => {
-		const log = debug('test');
-		log.enabled = true;
-		log.log = () => {};
-
-		assert.doesNotThrow(() => log('hello world'));
-	});
-
-	it('allows namespaces to be a non-string value', () => {
-		const log = debug('test');
-		log.enabled = true;
-		log.log = () => {};
-
-		assert.doesNotThrow(() => debug.enable(true));
-	});
-
-	it('honors global debug namespace enable calls', () => {
-		assert.deepStrictEqual(debug('test:12345').enabled, false);
-		assert.deepStrictEqual(debug('test:67890').enabled, false);
-
-		debug.enable('test:12345');
-		assert.deepStrictEqual(debug('test:12345').enabled, true);
-		assert.deepStrictEqual(debug('test:67890').enabled, false);
-	});
-
-	it('uses custom log function', () => {
-		const log = debug('test');
-		log.enabled = true;
-
-		const messages = [];
-		log.log = (...args) => messages.push(args);
-
-		log('using custom log function');
-		log('using custom log function again');
-		log('%O', 12345);
-
-		assert.deepStrictEqual(messages.length, 3);
-	});
-
-	describe('extend namespace', () => {
-		it('should extend namespace', () => {
-			const log = debug('foo');
+for (var i = 0; i < 10; i++) {
+	describe('debug', () => {
+		it('passes a basic sanity check', () => {
[…]

### 2019-12-21 tst/working/repos/minimist/t2_repo/t1/whitespace.js

@@ -1,16 +1,30 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 6,
-  removejson: ['hasOwnProperty'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
+console.log(process.env.key)
+if (parseInt(process.env.key) != 0) {
+	lyaConfig = {
+	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+	analysisCh: parseInt(process.env.key),
+	removejson: ['hasOwnProperty'],
+	};
+	let lya = require("../../../../../../src/txfm.js");
+	require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 var parse = require('minimist');
 var test = require('tape');
-
 test('whitespace should be whitespace' , function (t) {
-    t.plan(1);
-    var x = parse([ '-x', '\t' ]).x;
-    t.equal(x, '\t');
+	for (var ii = 0; ii < 100; ii++) {
+		t.plan(1);
+    	var x = parse([ '-x', '\t' ]).x;
+    	t.equal(x, '\t');
+	};
 });
+
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2019-12-22 paper/draft.tex
Update intro

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Library Dialysis with Lya}
+\title{\Large \bf Dynamic Program Dialysis with Lya}
 
@@
 \normalsize{Submission \#225, 12 pages}\\
-\normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
+% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
 % {\rm Grigoris Ntousakis}\\
@@
 
-This paper introduces \emph{library dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
-Such library over-reliance is a recent trend in software engineering:
-  applications today rely recursively on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
+% Such library over-reliance is a recent trend: % in software engineering:
+Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
 % On the surface, such reliance is beneficial, 
-Despite its benefits, such over-reliance creates many challenges for developers, exactly because their little knowledge of and visibility in the internals of these libraries:
-  for example, security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
+Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge of and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
 
-To address these challenges, library dialysis is a general technique that allows extracting meaningful insights with only a few lines of analysis-specific code.
-This feature is achieved by automating dynamic \fra, \ana, and \ass of applications at the level of individual modules and during program execution, by wrapping and transforming the underlying dependency graph.
-Our dialysis prototype, \sys, targets the JavaScript ecosystem, which counts over 1M libraries and is used on the web, server, and mobile.
-We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly low developer effort and performance overhead:
-  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual modules, and scale to real applications with hundreds of modules.
+To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
+Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
+% is a general technique that
+It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
+Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries used on the web, server, and mobile.
+We develop a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-libraries application programs with low developer effort and performance overhead:
+  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual libraries, and scale to real applications with hundreds of libraries.
 
@@
 Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
-  (i) current runtime information, such as profiling information, in view of changing workloads or use patterns~\cite{staticdynamic},
+  (i) current runtime information, such as profiling information, in view of changing load patterns~\cite{staticdynamic},
   (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
-  (iii) Turing-complete policies, where invariants themselves are arbitrary programs~\cite{contracts1, contracts2, contracts3},
-  (iii) dynamic or runtime-reflection features~\cite{jsanalysis1, jsanalysis2}, such as the ones present in Python and JavaScript.
+  (iii) Turing-complete policies, where policies themselves are programs~\cite{contracts1, contracts2, contracts3},
+  (iv) dynamic or runtime-reflection features, such as the ones present in Python and JavaScript~\cite{jsanalysis1, jsanalysis2}.
 
@@
 
-Unfortunately, reaping these benefits comes with significant costs in terms of (often, both) developer effort and runtime performance.
-Instrumenting the program often requires a good understanding of its internals.
-Applying associated tools adds to this requirement, such as instrumentation framework, instruction sets, and other underlying primitives~\cite{pin, valgrind}.
-Modifying the runtime environment of the program is also cumbersome, error-prone, and JavaScript's V8 engine.
-Problem-specific solutions require significant investment outside the language's mental model---for example, performance tracing frameworks such as perf and dtrace each feature their own language for specifying tracing programs, different from the application's language.
----as a case in point, Jalangi reports XX overhed (exact overheads always depend on the specific analysis).
+Unfortunately, reaping these benefits comes with significant costs in terms of developer effort or runtime performance.
+Manually instrumenting a program requires a good understanding of its internals. % instruction sets?
+External tools such as instrumentation frameworks~\cite{pin, valgrind} and performance tracing tools~\cite{perf, dtrace} only add to the curve, as they feature their own language for specifying analyses.
+% usually different from the application's language.
+Modifying the application's runtime environment such as the interpreter is cumbersome, error-prone, and requires development in a language that is different than that of the program.
+Tools that virtualize execution~\cite{pin, valgrind, jalangi, roadrunner} have high performance costs---for example, Jalangi~\cite{jalangi} and RoadRunner~\cite{roadrunner} report No-Op analysis on the order of 26--32$\times$ and 52$\times$, respectively.
+% Problem-specific solutions require significant investment outside the language's mental model---for example,  each ---as a case in point, Jalangi reports XX overhed (exact overheads always depend on the specific analysis).
 
-Both overheads are severely compounded by the use of third-party libraries, development-time constructs usually glued together without a full understanding of their internals.
-Libraries are used pervasively nowadays to lower development costs and improve software quality, a recent phenomenon enabled by zero-cost of sharing:
+Both effort and performance costs are severely compounded by the use of third-party libraries---development-time constructs usually glued together without a full understanding of their internals.
+Their ubiquity is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}
+% Libraries are used pervasively today to lower development costs and improve software quality, 
 % This over-reliance to third-party libraries is a recent phenomenon, 
-  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library have essentially dropped to zero.
-As a result, applications today
-  to the point that it is common for thousands of applications to depend on libraries that count only a few dozen lines:
-  for example, leftpad and
+  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
+As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{}. % how to say thousands of them depend on a 11-line lib?
+Library-oriented analysis adds to the challenges of prior tools as
+  (i) library boundaries disappear at runtime, and
+  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.
 
-This paper proposes a novel approach to dynamic analysis, termed \emph{module dialysis}\footnote{
-  A method of deconstruction, often for the purposes of removing waste products or altering piecewise components.
+To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
+  A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
   From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
 } and implemented in \sys.
-Library dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
-It operates during program execution, automating wrapping and transforming the underlying dependency graph, allowing developers to extract meaningful insights with only a few lines of analysis-specific code
-By operating at the granularity of libraries, module dialysis has several benefits over full-fledged dynamic analysis:
-  (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
-  (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and
+Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
+It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
+By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
+  (i) it allows bolting library dialysis itself as a library onto existing runtime environments with no dynamic analysis,
+  (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
   (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.
@@
 
-To demonstrate the effectiveness of the proposed techniques, we build a prototype of library dialysis, called \sys, targeting the JavaScript ecosystem---featuring more than 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
-We develop a diverse set of four analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing hot modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
-This set of analysis drives the design requirements for \sys and highlights the benefits of bolt-on module-aware dynamic analysis.
-Finally, we we use \sys to evaluate these analyses on three different levels:
-  (i) synthetic micro-benchmarks that highlight certain features and confirm the correctness of our analyses in a controlled environment;
-  (ii) single-module meso-benchmarks that allow comparison with more traditional dynamic analysis frameworks; and
-  (iii) end-to-end full-application macro-benchmarks that show behavior of the \sys system on realistic workloads.
-
+To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem with over 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
+We develop a diverse set of analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing bottlenecked modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
+This set of analysis drives the design requirements for \sys and highlights the benefits of our approach.
+Finally, we use \sys to evaluate these analyses on three different levels:
+  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
+  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
+  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
 \S\ref{bg}--\ref{eval} present our key contributions:
@@
 \item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
-\item \S\ref{impl} discuss our prototype implementation, \sys, as a pluggable library for the JavaScript ecosystem;
-\item \S\ref{eval} implementation and evaluation of the four analyses, showing \sys can express insightful analyses in 10–20 lines of code, adds a virtually imperceptible increase in the load latency of individual modules, and scales to real applications with hundreds of modules.
+\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
+\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
 \end{itemize}

### 2019-12-22 paper/draft.tex
Fixes

@@
 \usepackage{booktabs}
-\usepackage{caption}
 \usepackage{graphicx}
 
+\usepackage{caption}
 \captionsetup[figure]{font=footnotesize,name={Fig.},labelfont={bf, footnotesize}}
@@
 \captionsetup{font=footnotesize,labelfont={bf, footnotesize}, belowskip=2pt}
+
+\usepackage{enumitem}
+\setlist{noitemsep,leftmargin=10pt,topsep=2pt,parsep=2pt,partopsep=2pt}
 
@@
   with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
-As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{}. % how to say thousands of them depend on a 11-line lib?
+As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
 Library-oriented analysis adds to the challenges of prior tools as
@@
   A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
-  From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
+  From ancient Greek {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
 } and implemented in \sys.
@@
 
-To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem with over 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
-We develop a diverse set of analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing bottlenecked modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
-This set of analysis drives the design requirements for \sys and highlights the benefits of our approach.
-Finally, we use \sys to evaluate these analyses on three different levels:
+To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}).
+% and unusually high code-reuse~\cite{npmstudy:19}.
+%, and a pressing need for usable dynamic analysis~\cite{}.
+We develop a diverse set of analyses that target practical information about a program:
+  an allow/deny security analysis,
+  a profiling analysis showing bottlenecked modules,
+  a synthesis-oriented analysis on input-output data, and
+  an analysis enforcing a static union-based type system at runtime.
+This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
+We evaluate \sys at three different levels:
   (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
@@
 \begin{itemize}
-\item \S\ref{bg} characterizes the shared needs of four case-study analyses for which no prior dynamic analysis framework meets their needs.
+\item \S\ref{bg} characterizes the shared needs of four case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
 \item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
@@
 A single application today often incorporates multiple libraries\footnote{We use the terms ``library'', ``package'', and ``module'' interchangeably.} written and published by several different authors.
-The emerging development process should (and to a certain extent, does) simplify the development and testing process;
-  unfortunately, good abstractions are sealed (\ie they do not leak between abstraction layers), which makes the inspection of a library difficult.
+To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
+These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
+Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.
 
-\subsection{Modularity Today}
+% The emerging development process should (and to a certain extent, does) simplify the development and testing process;
+%   unfortunately, good abstractions are sealed (\ie they do not leak between abstraction layers), which makes the inspection of a library difficult.
+
+\subsection{Background on Modules and Module Systems}
+\label{bg1}
 

### 2019-12-22 run_all.sh
Restructure, add tests, fix things

@@ -30,14 +30,91 @@ cd ../../minimist/t2_repo/
 cd t1 
 [ -e timetest.txt ] && rm timetest.txt
 
-key=0 node  whitespace.js > /dev/null
-key=1 node  whitespace.js > /dev/null
-key=5 node  whitespace.js > /dev/null
-key=2 node  whitespace.js > /dev/null
-key=3 node  whitespace.js > /dev/null
-key=4 node  whitespace.js > /dev/null
-key=6 node  whitespace.js > /dev/null
-key=7 node  whitespace.js > /dev/null
-
+key=0 node whitespace.js > /dev/null
+key=1 node whitespace.js > /dev/null
+key=5 node whitespace.js > /dev/null
+key=2 node whitespace.js > /dev/null
+key=3 node whitespace.js > /dev/null
+key=4 node whitespace.js > /dev/null
+key=6 node whitespace.js > /dev/null
+key=7 node whitespace.js > /dev/null
 echo "Test 1 from minimist repo is .... ok"
+
+cd ../t2
+[ -e timetest.txt ] && rm timetest.txt
+
+key=0 node stop_early.js > /dev/null
+key=1 node stop_early.js > /dev/null
+key=5 node stop_early.js > /dev/null
+key=2 node stop_early.js > /dev/null
+key=3 node stop_early.js > /dev/null
+key=4 node stop_early.js > /dev/null
+key=6 node stop_early.js > /dev/null
+key=7 node stop_early.js > /dev/null
+echo "Test 2 from minimist repo is .... ok"
+
+cd ../t3
+[ -e timetest.txt ] && rm timetest.txt
+
+key=0 node short.js  > /dev/null
+key=1 node short.js  > /dev/null
+key=5 node short.js  > /dev/null
+key=2 node short.js  > /dev/null
+key=3 node short.js  > /dev/null
+key=4 node short.js  > /dev/null
+key=6 node short.js  > /dev/null
+key=7 node short.js  > /dev/null
+echo "Test 3 from minimist repo is .... ok"
+
+cd ../t4
+[ -e timetest.txt ] && rm timetest.txt
+
+key=0 node long.js > /dev/null
+key=1 node long.js > /dev/null
+key=5 node long.js > /dev/null
+key=2 node long.js > /dev/null
+key=3 node long.js > /dev/null
+key=4 node long.js > /dev/null
+key=6 node long.js > /dev/null
+key=7 node long.js > /dev/null
[…]

### 2019-12-22 tst/not working/mkdirp/mkdirp-master/test/chmod.js

@@ -1,0 +1,59 @@
+if (parseInt(process.env.npm_config_key) != 0) {
+    lyaConfig = {
+    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+    analysisCh: parseInt(process.env.npm_config_key),
+    removejson: ['hasOwnProperty','Promise'],
+    };
+    let lya = require("../../../../../../src/txfm.js");
+    require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+
+var mkdirp = require('../').mkdirp;
+var path = require('path');
+var fs = require('fs');
+var test = require('tap').test;
+var _0777 = parseInt('0777', 8);
+var _0755 = parseInt('0755', 8);
+var _0744 = parseInt('0744', 8);
+
+var ps = [ '', 'tmp' ];
+
+for (var i = 0; i < 25; i++) {
+    var dir = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
+    ps.push(dir);
+}
+
+var file = ps.join('/');
+
+test('chmod-pre', function (t) {
+    var mode = _0744
+    mkdirp(file, mode, function (er) {
+        t.ifError(er, 'should not error');
+        fs.stat(file, function (er, stat) {
+            t.ifError(er, 'should exist');
+            t.ok(stat && stat.isDirectory(), 'should be directory');
+            t.equal(stat && stat.mode & _0777, mode, 'should be 0744');
+            t.end();
+        });
+    });
+});
+
+test('chmod', function (t) {
+    var mode = _0755
+    mkdirp(file, mode, function (er) {
+        t.ifError(er, 'should not error');
+        fs.stat(file, function (er, stat) {
+            t.ifError(er, 'should exist');
+            t.ok(stat && stat.isDirectory(), 'should be directory');
+            t.end();
+        });
+    });
+});
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.npm_config_key) + ' is ' + thisTime + ' \n', 'utf-8');

### 2019-12-22 tst/not working/mkdirp/t2_repo/t1/mkdirp.js

@@ -1,0 +1,50 @@
+if (parseInt(process.env.npm_config_key) != 0) {
+    lyaConfig = {
+    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+    analysisCh: parseInt(process.env.npm_config_key),
+    };
+    let lya = require("../../../../../../src/txfm.js");
+    require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+
+var assert = require('assert');
+var mkdirp = require('mkdirp');
+var path = require('path');
+var fs = require('fs');
+
+
+    for (var i = 0; i < 1; i++) {
+        var x = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
+        var y = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
+        var z = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
+    
+        var file = '/tmp/' + [x,y,z].join('/');
+        var to = setTimeout(function () {
+            assert.fail('never called back');
+        }, 1000);
+    
+        mkdirp(file, 0755, function (err) {
+            if (err) assert.fail(err);
+            else path.exists(file, function (ex) {
+                if (!ex) assert.fail('file not created')
+                else fs.stat(file, function (err, stat) {
+                    if (err) assert.fail(err)
+                    else {
+                        clearTimeout(to);
+                        assert.eql(stat.mode & 0777, 0755);
+                        assert.ok(stat.isDirectory(), 'target not a directory');
+                    }
+                })
+            })
+        });
+    }
+
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.npm_config_key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2019-12-22 tst/working/repos/minimist/t2_repo/t1/whitespace.js

@@ -1,4 +1,3 @@
-console.log(process.env.key)
 if (parseInt(process.env.key) != 0) {
 	lyaConfig = {
 	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),

### 2019-12-22 tst/working/repos/minimist/t2_repo/t2/stop_early.js

@@ -1,15 +1,20 @@
-lyaConfig = {
+if (parseInt(process.env.key) != 0) {
+  lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 5,
+  analysisCh: parseInt(process.env.key),
   removejson: ['hasOwnProperty'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+  };
+  let lya = require("../../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 
 var parse = require('minimist');
 var test = require('tape');
 
 test('stops parsing on the first non-option when stopEarly is set', function (t) {
+  for (var i = 0; i < 10; i++) {
     var argv = parse(['--aaa', 'bbb', 'ccc', '--ddd'], {
         stopEarly: true
     });
@@ -19,5 +24,13 @@ test('stops parsing on the first non-option when stopEarly is set', function (t)
         _: ['ccc', '--ddd']
     });
 
-    t.end();
+  }
+  t.end();
 });
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');

### 2019-12-22 tst/working/repos/minimist/t2_repo/t3/short.js

@@ -1,10 +1,14 @@
-lyaConfig = {
+if (parseInt(process.env.key) != 0) {
+  lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
+  analysisCh: parseInt(process.env.key),
   removejson: ['hasOwnProperty'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+  };
+  let lya = require("../../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 
 var parse = require('minimist');
 var test = require('tape');
@@ -73,3 +77,11 @@ test('short and long', function (t) {
     );
     t.end();
 });
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2019-12-22 tst/working/repos/minimist/t2_repo/t4/long.js

@@ -1,10 +1,14 @@
-lyaConfig = {
+if (parseInt(process.env.key) != 0) {
+  lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
+  analysisCh: parseInt(process.env.key),
   removejson: ['hasOwnProperty'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+  };
+  let lya = require("../../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 
 var test = require('tape');
 var parse = require('minimist');
@@ -37,3 +41,11 @@ test('long opts', function (t) {
     );
     t.end();
 });
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2019-12-22 tst/working/repos/minimist/t2_repo/t5/dotted.js

@@ -1,10 +1,15 @@
-lyaConfig = {
+if (parseInt(process.env.key) != 0) {
+  lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 5,
+  analysisCh: parseInt(process.env.key),
   removejson: ['hasOwnProperty'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+  };
+  let lya = require("../../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+
+const time = process.hrtime();
+const fs = require('fs');
 
 var parse = require('minimist');
 var test = require('tape');
@@ -28,3 +33,11 @@ test('dotted default with no alias', function (t) {
     t.equal(argv.a.b, 11);
     t.end();
 });
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2019-12-22 tst/working/repos/mkdirp/t2_repo/t1/mkdirp.js

@@ -1,37 +1,0 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 5,
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
-var assert = require('assert');
-var mkdirp = require('mkdirp');
-var path = require('path');
-var fs = require('fs');
-
-exports.woo = function () {
-    var x = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
-    var y = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
-    var z = Math.floor(Math.random() * Math.pow(16,4)).toString(16);
-    
-    var file = '/tmp/' + [x,y,z].join('/');
-    var to = setTimeout(function () {
-        assert.fail('never called back');
-    }, 1000);
-    
-    mkdirp(file, 0755, function (err) {
-        if (err) assert.fail(err);
-        else path.exists(file, function (ex) {
-            if (!ex) assert.fail('file not created')
-            else fs.stat(file, function (err, stat) {
-                if (err) assert.fail(err)
-                else {
-                    clearTimeout(to);
-                    assert.eql(stat.mode & 0777, 0755);
-                    assert.ok(stat.isDirectory(), 'target not a directory');
-                }
-            })
-        })
-    });
-};

### 2019-12-22 tst/working/repos/moment/main.js

@@ -1,23 +1,23 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 5,
-};
-
-let lya = require("../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
+if (parseInt(process.env.key) != 0) {
+	lyaConfig = {
+	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+	analysisCh: parseInt(process.env.key),
+	removejson: ['hasOwnProperty'],
+	};
+	let lya = require("../../../../src/txfm.js");
+	require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 /// <reference path="../moment.d.ts" />
+
 const moment = require('moment');
-moment.suppressDeprecationWarnings = true;
-
-moment.parseTwoDigitYear("50");
-
-moment().add('hours', 1).fromNow();
-
+moment.suppressDeprecationWarnings = true;	
+moment.parseTwoDigitYear("50");	
+moment().add('hours', 1).fromNow();	
 var day = new Date(2011, 9, 16);
 var dayWrapper = moment(day);
-var otherDay = moment(new Date(2020, 3, 7));
-
+var otherDay = moment(new Date(2020, 3, 7));	
 var day1 = moment(1318781876406);
 var day2 = moment.unix(1318781876);
 var day3 = moment("Dec 25, 1995");
@@ -31,8 +31,7 @@ var day9 = moment([2010, 6]);
 var day10 = moment([2010, 6, 10]);
 var array = [2010, 1, 14, 15, 25, 50, 125];
 var day11 = moment(Date.UTC.apply({}, array));
-var day12 = moment.unix(1318781876);
-
+var day12 = moment.unix(1318781876);	
 // TODO: reenable in 2.0
 // moment(null);
 moment(undefined);
@@ -42,27 +41,23 @@ moment("20140101", "YYYYMMDD", "en");
 moment("20140101", "YYYYMMDD", "en", true);
 moment("20140101", ["YYYYMMDD"], true);
 moment("20140101", ["YYYYMMDD"], "en");
-moment("20140101", ["YYYYMMDD"], "en", true);
-
+moment("20140101", ["YYYYMMDD"], "en", true);	
 moment(day.toISOString(), moment.ISO_8601);
 moment(day.toISOString(), moment.ISO_8601, true);
[…]

### 2019-12-22 tst/working/repos/moment/t1/main.js

@@ -1,9 +1,0 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
-};
-let lya = require("../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
-var moment = require('moment');
-console.log(moment().format());

### 2019-12-22 tst/working/repos/yargs/t1/main.js

@@ -1,13 +1,0 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
-};
-let lya = require("../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-const argv = require('yargs').argv
- 
-if (argv.ships > 3 && argv.distance < 53.5) {
-  console.log('Plunder more riffiwobbles!')
-} else {
-  console.log('Retreat from the xupptumblers!')
-}

### 2019-12-22 tst/working/repos/yargs/t2/main.js

@@ -1,24 +1,0 @@
-lyaConfig = {
-  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
-};
-let lya = require("../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
-require('yargs') // eslint-disable-line
-  .command('serve [port]', 'start the server', (yargs) => {
-    yargs
-      .positional('port', {
-        describe: 'port to bind on',
-        default: 5000
-      })
-  }, (argv) => {
-    if (argv.verbose) console.info(`start server on :${argv.port}`)
-    serve(argv.port)
-  })
-  .option('verbose', {
-    alias: 'v',
-    type: 'boolean',
-    description: 'Run with verbose logging'
-  })
-  .argv

### 2019-12-22 tst/working/repos/yargs/test/yargs.js

@@ -2,12 +2,16 @@
 /* global context, describe, it, beforeEach, afterEach */
 // THIS IS COMMIT ON 1 JAN 2018
 // FIXME: problem with global --> anyway to do this better
-global.lyaConfig = {
+if (parseInt(process.env.npm_config_key) != 0) {
+  global.lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-  analysisCh: 1,
-};
-let lya = require("../../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+  analysisCh: parseInt(process.env.npm_config_key),
+  POLICY: '../tst/working/repos/debug/debug-master/dynamic.json'
+  };
+  let lya = require("../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
 
 const expect = require('chai').expect
 const fs = require('fs')
@@ -2123,3 +2127,10 @@ describe('yargs dsl tests', () => {
     })
   })
 })
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.npm_config_key) + ' is ' + thisTime + ' \n', 'utf-8');

### 2019-12-23 paper/draft.tex
Update related work

@@
 
+\subsection{When to Use Dialysis}
+\label{principles}
+Dynamic analysis is a general analysis technique that discovering facts about programs;
+  dialysis can be thought as a specif
+While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
+
+Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
+By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
+
+Another use is in the existence of multi-language applications---wrappers and FFI.
+
 \section{Related Work}
@@
 
-Existing dynamic analysis frameworks can be classified either as coarse- or fine-grained.
-The former analyze interactions at the boundaries of entire components, whereas the latter associate metadata at the level of individual instructions or objects.
-We compare \sys to previously proposed systems in both categories, then contrast the two categories' overall characteristics.
+In this section, we compare \sys to previously proposed systems in several categories.
+For a comparison between dialysis and dynamic analysis, we refer the reader to the previous section~\sx{principles}.
 
-\heading{Heavyweight instrumentation}
-There is a series of heavyweight dynamic analysis frameworks.
-Popular frameworks include
-  Valgrind~\cite{valgrind} and Pin~\cite{pin} for native programs,
-  DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} for JVM byte code,
-  Jalangi~\cite{jalangi} for JavaScript programs, and,
-  most recently, Wasabi~\cite{wasabi} for Web-Assembly.
+\heading{Dynamic Analysis Systems}
+There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
+The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
+On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
+This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
+  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
+They are also not embeddable in existing applications in a runtime-agnostic manner.
+These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.
 
-The approach advocated by \sys is to throw a quick-and-easy analysis at the module boundaries
+NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
+NodeProf takes a different approach than code-level instrumentation, statically instrumenting the AST, which makes it easier to maintain compared to source changes.
+Similar to \sys, NodeProf 
+is not tied to the source code, has significantly lower overheads, and can be toggled on/off during program execution.
+Requires AST extraction and manipulation to build, which is not available in many languages % it is an additional requirement
+and is in conflict with many dynamic features. 
+It stands at a different point in the design space---more powerful analysis, but with significantly more effort:
+  assumes knowledge of the internal Graal and Truffle APIs and requires recompilation of the Java hooks.
 
-Jalangi is the most relevant of these frameworks, and served as an inspiration
+Similar to NodeProf, \sys
+
+Aran~\cite{javascript1} is presented in a poster to
+
+JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
+It allows users to write 
+It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
+Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.
 
 \heading{Dynamic Analysis for WebAssembly}
-Related to JavaScript is WebAssembly, a standardized subset of JavaScript target ideal as a compilation target.
-Two techniques modify V8
-
-Wasabi is a framework for dynamic analysis of WebAssembly.
-Similar to \sys, it succeeds at lowering the effort required to write analyses, 
-and provides hooks for observation rather than manipulation
+Related to JavaScript is WebAssembly, a standardized subset of JavaScript target, designed to serve as a compilation target.
+The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of the same goals with \sys---\eg lowering the effort required to write analyses, and providing hooks for observation rather than manipulation.
+Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
+  Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
+  whereas our explicit goal is to write analysis in the same language as the program~\sx{goals}---that is, dialysis implemented for Python would be using Python abstractions.
 Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.
 
-; even more similarly, it allows expressing analyses in JavaScript.
-Prior work has modified
+\heading{Dynamic Instrumentation}
+Dialysis is related to dynamic instrumentation frameworks~\cite{pin, valgrind} that wrap incrementally parts of the program to extract information.
+Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
+  \sys starts by wrapping a library during import, adding a small overhead on its loading time.
+This overhead is only a small fraction of the time required to locate and load the module from disk.
+However, these systems operate at a much lower level (binary) than \sys, and are not available to high-level runtime environments as a pluggable library.
 
-Some citations to ensure we can see them~\cite{javascript1, javascript2, javascript3}.
-
-\heading{Dynamic Instrumentation}
-Dialysis is related to dynamic binary instrumentation frameworks that wrap parts of the program to extract information.
-Many such frameworks translate basic blocks of the program just before their execution;
-  \sys starts with a phase that wraps (equivalent to instrumenting) a library during import, adding a small overhead at the loading time of each library.
-The overhead of this phase is only a small fraction of the time required to locate and load the module from disk.
+DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} are systems for instrumenting JVM byte code.
+These too work at a lower level than \sys,
 
@@
 % Add our work
-Module dialysis builds on aspect-oriented programming (AOP), a programming model that maps program points to actions to be taken at these points~\cite{aop}.
+Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
 Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
-Moreover, AOP works on languages that were already designed to support it, whereas module dialysis was explicitly designed to bolt onto existing languages and environments.
+Moreover, AOP works on languages that were already designed to support it, whereas module dialysis is explicitly designed to bolt onto existing languages.
 
-More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure and which enable a program to access to its own internal structure, including rewriting itself as it executes.
-They are examples of runtime reflection, of which \sys makes extensive use to traverse, understand, wrap, and rewrite interfaces.
-With \sys, however, developers do not need to provide their own metaobjects.
+More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
+While \sys makes extensive use of metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
 % self element
@@
 \heading{Fracture and Recombination}
-Module dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
-PFR breaks up multiple programs into multiple components (called shards) with the goal of exchanging functionality between donor-donee pairs of programs.
-Module dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries, in the guise of libraries or modules.
+Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
+PFR breaks up multiple programs into many components with the goal of exchanging functionality between donor-donee pairs of programs.
+Contrary to PFR, dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.
 

### 2019-12-23 src/policy1.js
Add comment

@@ -1,8 +1,5 @@
-// env is {
-//   trueName : trueName,
-//   requireLevel : requireLevel,
-//   accessMatrix: accessMatrix,
-// }
+// This is the policy for true false analysis. Each time we access a variable
+// or a function we write it with true in a export file dynamic.json 
 let locEnv;
 
 // Holds the end of each name store of new assigned global variables

### 2019-12-23 src/policy2.js

@@ -1,8 +1,5 @@
-// env is {
-//   trueName : trueName,
-//   requireLevel : requireLevel,
-//   accessMatrix: accessMatrix,
-// }
+// This is the policy for counter analysis. Each time we access a variable
+// or a function we increment a counter in a export file dynamic.json 
 let locEnv;
 
 // Holds the end of each name store of new assigned global variables

### 2019-12-23 src/txfm.js

@@ -1,6 +1,8 @@
 /* eslint prefer-rest-params: "off", no-global-assign: "off",
 no-shadow-restricted-names: "off" */
-//let lyaConfig= {};
+
+// We use this global value to know if the program has ended or not
+// necessary for enforcement analysis(5, 7) 
 global.end= false;
 
 // We import and declare all the necessary modules
@@ -57,6 +59,8 @@ const env = {
 // 3) Time Analysis
 // 4) Time Analysis2.0
 // 5) Enforcement Analysis
+// 6) RWE Analysis
+// 7) RWE Enforcement
 let userChoice = (lyaConfig.analysisCh && [1, 2, 3, 4, 5, 6, 7].includes(lyaConfig.analysisCh))? lyaConfig.analysisCh : 1
 
 // You import the right policy depenting on the choice
@@ -72,6 +76,7 @@ const mainRequire = (original) => {
   return new Proxy(original, policy.require);
 };
 
+// TOFIX:
 // We incriment and declare the ness things
 // This is for the handlerObjExport
 const exportControl = (storedCalls, truename) => {
@@ -105,14 +110,16 @@ const handlerAddArg= {
   },
 };
 
-// We first wrap the export obj so that we avoid to
-// print functions that are not called by us
-//
+// TODO: 
 // require('fs);
 // fs.openSync(pizza);
 // fs.read(katiAllo);
 //
 // fs.read () => {... fs.resolve(...) ... return...}
+
+// We first wrap the export obj. Every time someone requires 
+// a function or an object from inside export obj we wrap it 
+// in the right handler(in our case handlerExports).
 const handlerObjExport= {
   get: function(target, name, receiver) {
     if (typeof target[name] != 'undefined' && typeof name === 'string') { // + udnefined
@@ -350,6 +357,8 @@ vm.runInThisContext = function(code, options) {
 Module.prototype.require = function(...args) {
   const path = args[0];
   let result = originalRequire.apply(this, args);
+  // If false that means that we pass from here for the 
+  // first time.
   if ( objName.has(result) === false ) {
     objName.set(result, 'require(\'' + path + '\')');
     objPath.set(result, trueName[requireLevel]);
@@ -358,7 +367,6 @@ Module.prototype.require = function(...args) {
       requireLevel--;
       policy.updateCounter(requireLevel);
     }
-    //if (policy.requireLevel !=0) policy.requireLevel--;
   } else {
     result = new Proxy(result, handlerObjExport);
[…]

### 2020-01-05 paper/draft.tex
Update text

@@
 \newcommand{\dia}{\fra, \ana, and \ass}
+
+\newcommand{\goal}[1]{(\textbf{G#1})\xspace}
 
@@
 We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
-While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses systems as these
-
-require highly specialized solutions often outside the core language,
-do not leverage or offer semantic information at the level of module boundaries,
-or lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
-These applications clearly illustrate the need for a system 
+While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
+  these frameworks either require highly specialized solutions often outside the core language,
+  do not leverage or offer semantic information at the level of module boundaries, or
+  lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
 To summarize, these applications would appear to be served well by a system that:
 \begin{itemize}
-  \item Operates at the level of modules, both semantics and performance-wise
-  \item Does not require learning a new tool or language---on the contrary,
-    developers
-  \item can be bolt onto an existing runtime as a library, regardless of whether 
-  \item supports programmable analyses
+  \item \textbf{(G1)} Operates at the level of modules, leveraging both the semantics and performance potential that this level of granularity potentially offers.
+  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses on the same language as the program.
+  \item \textbf{(G3)} Can be implemented as a library that bolts onto an existing language runtime environment.
 \end{itemize}
 
-In the next section we describe the design \sys, a new dynamic analyses
-framework that satisfies these goals
+The next section describes program dialysis, a new program analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
+  the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.
 
-\section{Module-aware Dynamic Analysis}
+\section{The Design of Program Dialysis}
 \label{design}
 
+Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
+  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
+We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
+We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).
+
 \subsection{Overview}
+\label{overview}
 
-FIXME: add user data
-At a high level, module dialysis works at three stages:
+% FIXME: add user data
+At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
+ In more detail, these three phases are as follows:
 
@@
 
-% \textbf{Core Language}
-% a few is not the same as 
-Transformations are used pervasively throughout \sys, and are abstracted via a few parametrizable templates.
-Templates map different types of values (List.~\ref{core-tx}) to a generic handler for each type.
-%given a value, a template will transform it using a handler matching its type
-% Templates match, 
-% \hl{match} between different \hl{value} % what are values
-%    \emph{types} and define generic handlers for each type.
-Transformations have these handlers parametrized to achieve concrete goals such as monitoring, serialization, and scale-out.
-Simplified instances are described in the following two sections (\S\ref{profiling}--\ref{core}).
+Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
 
-Transformations can be applied to any value in the language, such as an object returned from a module or an exception about to be sent across the network.
-The general case of such a value is a directed acyclic graph (DAG).
-The types of its vertices can be coarsely grouped into primitives, functions, and objects.
-Objects map strings to other values, pointing to other vertices in the DAG.
+% , such as an object returned from a module or an exception about to be sent across the network.
+Transformations can be applied to any value in the language. 
+The most general value is an object, a bag of records holding key-value fields;
+  other value types include primitives, functions, and booleans.
 % Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations start by walking the DAG from the root vertex and processing component values based on their types.
-They do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
-They only partially explore the object graph, as they do not peak through function closure environments.
-Fortunately, this aligns well with our goal of monitoring activity at module boundaries and ignoring module-internal activity.
+Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
+More specifically,
+  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
+  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
+  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
+% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
 
-As an example, consider transforming the \ttt{crypto} module~\sx{solution}.
-\sys traverses the object returned by \ttt{crypto} and replaces functions such as \ttt{pbkdf2} with wrappers whose specifics depend on the intended goal:
-  profiling wrappers call the original function in between statistics collection, and RPC wrappers forward the call to a remote replica.
+The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
+These skeletons provide hooks for end-developers writing analyses.
+Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
+These hooks are then extended or rewritten by developers to
+
+For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
+\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
+The wrappers depend on the intended goal:
+  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.
+
+\subsection{Disassembly}
+\label{one}
+
+\subsection{Transformation}
+\label{two}
+
+\subsection{Reassembly}
+\label{three}
 
@@
 
-\heading{Dynamic Analysis Systems}
+% \heading{Dynamic Analysis Systems}
 There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
@@
 NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
-NodeProf takes a different approach than code-level instrumentation, statically instrumenting the AST, which makes it easier to maintain compared to source changes.
-Similar to \sys, NodeProf 
-is not tied to the source code, has significantly lower overheads, and can be toggled on/off during program execution.
-Requires AST extraction and manipulation to build, which is not available in many languages % it is an additional requirement
-and is in conflict with many dynamic features. 
-It stands at a different point in the design space---more powerful analysis, but with significantly more effort:
-  assumes knowledge of the internal Graal and Truffle APIs and requires recompilation of the Java hooks.
+NodeProf stands at a different point in the analysis design space---more powerful than \sys, but with significantly more effort.
+It statically instruments the program's AST (rather than the code), making it easier to maintain compared to source changes but assuming some knowledge of the Graal and Truffle APIs and requiring recompilation of the Java hooks.
+Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
+Nevertheless, NodeProf's approach shares similarities with \sys, including decoupling from the source code, overheads lower than code instrumentation, and can on/off toggling during execution.
+%FIXME: Lya is also limited (i) by dynamic features such as reflection, because they're gonna hit the wrapper and (ii) the equality and other primitive operators
 
-Similar to NodeProf, \sys
-
-Aran~\cite{javascript1} is presented in a poster to
+Aran~\cite{javascript1}, an implementation sketch of proxy-based analysis, leverages JavaScript's \ttt{with} primitive to wrap custom contexts.
+\sys works at the module boundaries (at a potentially coarser granularity) without any special language constructs.
 
 JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
-It allows users to write 
+It allows users to write access control contracts, policies that execute at runtime.
 It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 

### 2020-01-05 paper/draft.tex
More udpates

@@
 
-We implemented \sys for version 
-We show where other implementations would diverge in table 1
+We implemented \sys for version 8.9.4 of the Node.js runtime.
+Node.js is a runtime that bun
+
+in about 1.5K lines of JavaScript.
+We summarize where other implementations would diverge in table 1
+
+Individual analysis are implemented using a set of templates that provide initial constructs (see below).
+The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.
 
@@
 It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+
+In practice, the aforementioned dialysis stages can be implemented in two different ways.
+The first is as a modified version of the runtime, where 
+No-op analyses correspond to the default execution
+  either 
+It is introduced as a backward-compatible, drop-in replacement of the language's module system.
+It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
+
+We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
+However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
+  we expand on these at the end of this section~\sx{opportunities}.
+% get second argument, no need to pass arguments around, tricky to 
+% carefull hardcoding of paths, because \sys's code itself is split into modules
+% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
+% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
+% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
+% This is useful, for example, when...
+% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
 
@@
 
-\
+\subsection{Limitations}
 
-\section{Evaluation}
+% FIXME: Talk about the inability to 
+A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
+This is because \sys cannot transform the context of that file
+As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
+The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
+
+\section{Evaluation and Experience}
 \label{eval}
+
+\sys's  development achieves goals~\goal{1--3}~\sx{goals}, demonstrating that it is indeed feasible to construct a framework that operates at the level of modules, 
+does not force developers to learn a new language, and that it can be implemented as a library around an existing runtime.
+Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
+
+In this section, we are interested in zooming into \sys's performance characteristics~\goal{4}.
+At a high level, we are interested in three questions:
+(i) the overheads of the \sys's underlying building blocks;
+(ii) the overhead of different analysis on real libraries and how this compares with production dynamic analysis frameworks; and
+(iii) evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
+% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
+% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
+% For the third question, we use a combination of real applications~\sx{macro}.
+
+Several takeaways are worth highlighting.
+\fixme{TODO after we have the results.}
+
+Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
+In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu XXX version}, Jalangi \fixme{vXXX}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
+We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.
 
@@
 \label{micro}
+
+\sys's micro-benchmark suite was designed with two goals in mind.
+
+The first goal was to test key properties of each analysis and confirm it outputs the expected results.
+For example, to better understand performance diagnosis policy and confirm it works correctly, we craft a library that contains four other libraries with pre-defined bottlenecks.
+The library can perform one of three operations, depending on its current state:
+  (i) invoke a call to a module it imports,
+  (ii) busy-wait, or
+  (iii) respond to calls by returning a value.
+
+The second goal was to identify understand \sys bottlenecks in a controlled environment, 
+Both of these goals would have been difficult to achieve outside a synthetic environment, as we do not fully understand applications we haven't written ourselves.
+
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Synthetic Micro-benchmarks}.
+    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
+\toprule
+                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
+\midrule
+Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
+Walk objects                    &         &             &        &      &      &      &      &         \\
+Shadow variables                &         &             &        &      &      &      &      &         \\
+Wrap values                     &         &             &        &      &      &      &      &         \\
+Global names                    &         &             &        &      &      &      &      &         \\
+\bottomrule
+\end{tabular*}
+\label{tab:compatibility}
+\vspace{-5mm}
+\end{table}
+
+t1    0.696719      3.433219       3.456324    3.264275    3.225375    3.629768    4.201675    3.786415
+t2    1.307968      4.806233       4.547337    4.631335    4.812661    4.769355    5.197067    4.977848
+t3    5.94999       4.784134       4.245242    4.846751    4.097349    4.38602    4.478904    4.475653
+t4    18.286143     11.202162      10.241839    9.541254    10.435567    10.285686    10.557981    10.68798
+t5    24214.89589   24721.45699    24574.01965    24502.74046    24519.45243    24645.79223    24448.94942    24456.74015
+
+Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
+We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
+Currently, these benchmarks return the results we expect, but they did help with the identification of problems such as 
+These be
+Load is visible at the application level (left), but the lack of detail does not help determine which modules must be scaled out.
+Module-level data, collected by \sys' coordinator (right), reveal that \ttt{m3} receives the majority of the load.
+
+To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
+  unmodified and proxy-wrapped.
+Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
+We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
+The proxy-wrapped version introduces interposition at every level.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+
+We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
 
@@
 
-\section{Discussion and Limitations}
+\section{Discussion}
 \label{diss}

### 2020-01-05 paper/draft.tex
Add figure

@@
 
+\begin{figure*}[t]
+  \centering
+   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
+  \caption{
+    \textbf{Analysis overheads.}
+    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
+		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
+    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
+  }
+  \label{fig:meso}
+  \vspace{-3mm}
+\end{figure*}
+
 \subsection{End-to-End Benchmarks}

### 2020-01-05 paper/draft.tex
Add more measurement tables

@@
     \textbf{Synthetic Micro-benchmarks}.
-    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
+		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
   }
 }
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
 \toprule
-                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
+              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
 \midrule
-Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
-Walk objects                    &         &             &        &      &      &      &      &         \\
-Shadow variables                &         &             &        &      &      &      &      &         \\
-Wrap values                     &         &             &        &      &      &      &      &         \\
-Global names                    &         &             &        &      &      &      &      &         \\
+something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
+something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
+something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
+something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
+something5    &           &  24214  &   24721  &   24574  &   24502   \\
 \bottomrule
 \end{tabular*}
-\label{tab:compatibility}
+\label{tab:synthetic}
 \vspace{-5mm}
@@
 
-t1    0.696719      3.433219       3.456324    3.264275    3.225375    3.629768    4.201675    3.786415
-t2    1.307968      4.806233       4.547337    4.631335    4.812661    4.769355    5.197067    4.977848
-t3    5.94999       4.784134       4.245242    4.846751    4.097349    4.38602    4.478904    4.475653
-t4    18.286143     11.202162      10.241839    9.541254    10.435567    10.285686    10.557981    10.68798
-t5    24214.89589   24721.45699    24574.01965    24502.74046    24519.45243    24645.79223    24448.94942    24456.74015
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Applying \sys to single-library programs}.
+		\fixme{Execution time of four test suites against }
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
+\toprule
+                    & Base   &  SA   & PD     &   TIC   & LSR     \\
+\midrule
+Classnames~\cite{}  &  2.72  & 6.62  &  6.61  &  6.10   & 5.94    \\
+Debug~\cite{}       & 31.39  & 33.54 &  33.94 &  33.96  & 33.04   \\
+% Minimist\\
+~~~-t1              & 31.46  & 60.13 &  60.00 &  56.62  & 56.72   \\
+~~~-t2              & 19.17  & 59.77 &  60.75 &  57.15  & 57.79   \\
+~~~-t3              & 21.64  & 205.2 &  205.53&  132.25 & 137.84  \\
+~~~-t4              & 20.69  & 59.70 &  60.75 &  59.92  & 56.60   \\
+~~~-t5              & 20.49  & 70.48 &  72.20 &  64.71  & 66.03   \\
+Moment~\cite{}      & 31.73  & 48.04 &  49.23 &  44.95  & 46.12   \\
+yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
+\bottomrule
+\end{tabular*}
+\label{tab:meso}
+\vspace{-5mm}
+\end{table}
 
@@
 
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Applying \sys to three large applications}.
+		\fixme{Highlight some things}
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
+\toprule
+                    & Koa    & Moeda   &  Terminalizer \\
+\midrule
+ Size (KB)          & 41M    &  29M    &   262M        \\
+ LoC                & 127K   &  79K    &   39K         \\
+ Top-level modules  &  24    &  7      &    33         \\
+ Total Modules      &  432   &  260    &    1084       \\
+ Lya detects:       &  1507  &   729   &     2355      \\
+ Baseline           &  xx    &         &               \\
+ A1 (TF)            &        &         &               \\
+ A3 (HF)            &        &         &               \\
+ A8 (Types)         &        &         &               \\     
+\bottomrule
+\end{tabular*}
+\label{tab:macro}
+\vspace{-5mm}
+\end{table}
+
+Highly popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
+Applying \sys to these applications generates much larger analayses
+For example, the performance diagnosis analysis hooks reports timing characteristics for
+
+The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few different reasons.
+One is that an analysis does not report accesses if a 
+\sys analyzes modules that are part of the standard library too (some of which have themselves internal dependencies), which are not shown by \ttt{npm}.
+Our post-processing counts by module name (\ie squashes duplicate reports by 
+This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
+For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
+It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{cache}).
+Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
+
 \section{Discussion}
@@
 
-\heading{Dynamic Language Interpretation}
 Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
@@
 
+We want to emphasize that \sys is open source, available to experiment with more applications and analyses
+
 % \section*{Acknowledgments}

### 2020-01-06 tst/nodejs_apps/colorette-master/bench/index.js
Add Colorette for tests

@@ -1,0 +1,75 @@
+const styles = [
+  "reset",
+  "bold",
+  "dim",
+  "italic",
+  "underline",
+  "inverse",
+  "hidden",
+  "strikethrough",
+  "black",
+  "red",
+  "green",
+  "yellow",
+  "blue",
+  "magenta",
+  "cyan",
+  "white",
+  "gray",
+  "bgBlack",
+  "bgRed",
+  "bgGreen",
+  "bgYellow",
+  "bgBlue",
+  "bgMagenta",
+  "bgCyan",
+  "bgWhite"
+]
+const { runBenchmark } = require("./runBenchmark")
+
+runBenchmark(
+  {
+    "# Using Styles": c => styles.map(k => c[k](k)),
+    "# Combining Styles": ({ red, bgWhite, bold, underline, italic }, id) =>
+      id === "colorette"
+        ? red(bgWhite(bold(underline(italic("Engage!")))))
+        : id === "kleur"
+        ? red()
+            .bgWhite()
+            .bold()
+            .underline()
+            .italic("Engage!")
+        : red.bgWhite.bold.underline.italic("Engage!"),
+    "# Nesting Styles": ({
+      red,
+      blue,
+      cyan,
+      white,
+      yellow,
+      magenta,
+      bold,
+      italic,
+      underline
+    }) =>
+      red(
+        `RED, ${blue(
+          `BLUE, ${bold(
+            `BOLD AND ${yellow("YELLOW")}. BACK TO BLUE, ${underline(
+              `UNDERLINE,`
+            )}`
+          )} MORE BLUE, ${magenta(
+            `MAGENTA, ${white("WHITE,")}${cyan(
+              ` CYAN, ${italic(`ITALIC ${bold("BOLD")} ITALIC`)}, CYAN,`
+            )} MAGENTA,`
+          )} BLUE`
+        )} AND BACK TO RED.`
+      )
+  },
+  {
+    chalk: require("chalk"),
+    kleur: require("kleur"),
+    colors: require("colors/safe"),
+    "ansi-colors": require("ansi-colors"),
+    colorette: require("..")
+  }
+)

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/policy1.js

@@ -1,0 +1,192 @@
+// This is the policy for true false analysis. Each time we access a variable
+// or a function we write it with true in a export file dynamic.json 
+let locEnv;
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// @storedCalls it is a table that contains all the analysis data
+// @truename the name of the current function, object etc that we want to add to
+// the table 
+// Given those two inputs we can update the analysis data that are stored in storedCalls
+const updateAnalysisData = (storedCalls, truename) => {
+  if (Object.prototype.hasOwnProperty.
+        call(storedCalls, truename) === false) {
+      storedCalls[truename] = true;
+  }
+};
+
+// This the handler of the require function. Every time a "require" is used to load up a module
+// this handler is called. It updates the analysis data that are stored in the accessMatrix table.
+const requireHandler = {
+  apply: function(target, thisArg, argumentsList) {
+    const currentName = locEnv.trueName[locEnv.requireLevel];
+    const origReqModuleName = argumentsList[0];
+    locEnv.accessMatrix[currentName]['require(\'' + origReqModuleName + '\')'] = true;
+    return Reflect.apply(...arguments);
+  },
+};
+
+// The handler of the global variable.Every time we access the global variabe in order to declare 
+// or call a variable, then we can print it on the export file.
+const globalHandler = {
+  get: function(target, name) {
+    // XXX[target] != 'undefined'
+    if (typeof name === 'string'){
+      if (typeof target[name+endName] != 'undefined') {
+        const currentName = locEnv.trueName[locEnv.requireLevel];
+        const nameToShow = target[name+endName];
+        updateAnalysisData(locEnv.accessMatrix[currentName], nameToShow);
+      }
+    }
+
+    return Reflect.get(target, name);
+  },
+  set: function(target, name, value) {
+    if (typeof value === 'number') {
+      const currentName = locEnv.trueName[locEnv.requireLevel];
+      const nameToStore = 'global.' + name;
+      const result = Reflect.set(target, name, value);
+      // In order to exist a disticton between the values we declared ourselfs
+      // We declare one more field with key value that stores the name
+      Object.defineProperty(target, name+endName, {value: nameToStore});
+      updateAnalysisData(locEnv.accessMatrix[currentName], nameToStore);
+
+      return result;
+    }
+
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/policy2.js

@@ -1,0 +1,189 @@
+// This is the policy for counter analysis. Each time we access a variable
+// or a function we increment a counter in a export file dynamic.json 
+let locEnv;
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// @storedCalls it is a table that contains all the analysis data
+// @truename the name of the current function, object etc that we want to add to
+// the table 
+// Given those two inputs we can update the analysis data that are stored in storedCalls
+const updateAnalysisData = (storedCalls, truename, arguments) => {
+  if (Object.prototype.hasOwnProperty.
+        call(storedCalls, truename) === false) {
+      storedCalls[truename] = 1;
+    } else {
+      storedCalls[truename]++;
+    }
+};
+
+// This the handler of the require function. Every time a "require" is used to load up a module
+// this handler is called. It updates the analysis data that are stored in the accessMatrix table.
+const requireHandler = {
+  apply: function(target) {
+    const currentName = locEnv.trueName[locEnv.requireLevel];
+    const nameReq = target.name + '(\'' + arguments[2][0] +// In arguments[2][0]
+      '\')';// Is the name we use to import
+    locEnv.accessMatrix[currentName][nameReq] = 1;
+
+    return Reflect.apply( ...arguments);
+  },
+};
+
+// The handler of the global variable.Every time we access the global variabe in order to declare 
+// or call a variable, then we can print it on the export file.
+const globalHandler = {
+  get: function(target, name) {
+    // XXX[target] != 'undefined'
+    if (typeof name === 'string'){
+      if (typeof target[name+endName] != 'undefined') {
+        const currentName = locEnv.trueName[locEnv.requireLevel];
+        const nameToShow = target[name+endName];
+        updateAnalysisData(locEnv.accessMatrix[currentName], nameToShow);
+      }
+    }
+    
+    return Reflect.get(target, name);
+  },
+  set: function(target, name, value) {
+    if (typeof value === 'number') {
+      const currentName = locEnv.trueName[locEnv.requireLevel];
+      const nameToStore = 'global.' + name;
+      const result = Reflect.set(target, name, value);
+      // In order to exist a disticton between the values we declared ourselfs
+      // We declare one more field with key value that stores the name
+      Object.defineProperty(target, name+endName, {value: nameToStore});
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/policy6.js

@@ -1,0 +1,200 @@
+// env is {
+//   trueName : trueName,
+//   requireLevel : requireLevel,
+//   accessMatrix: accessMatrix,
+// }
+let locEnv;
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// This the handler of the require function. Every time a "require" is used to load up a module
+// this handler is called. It updates the analysis data that are stored in the accessMatrix table.
+const requireHandler = {
+  apply: function(target, thisArg, argumentsList) {
+    const currentName = locEnv.trueName[locEnv.requireLevel];
+    const origReqModuleName = argumentsList[0];
+    locEnv.accessMatrix[currentName]['require(\'' + origReqModuleName + '\')'] = 'R';
+    return Reflect.apply(...arguments);
+  },
+};
+
+// We add the R or W or E to the existing string
+const addEvent = (event, values, index) => {
+  let storedValue = values[index];
+  if (!storedValue.includes(event)){
+    storedValue += event;
+    values[index] = storedValue;
+  }
+};
+
+// @storedCalls it is a table that contains all the analysis data
+// @truename the name of the current function, object etc that we want to add to
+// the table 
+// @mode the mode of the current access (R,W or E)
+// Given those two inputs we can update the analysis data that are stored in storedCalls
+const updateAnalysisData = (storedCalls, truename, mode) => {
+	if (Object.prototype.hasOwnProperty.
+        call(storedCalls, truename) === false) {
+    storedCalls[truename] = mode;
+  } else {
+    addEvent(mode, storedCalls, truename);
+  }
+};
+
+// The handler of the global variable.Every time we access the global variabe in order to declare 
+// or call a variable, then we can print it on the export file.
+const globalHandler = {
+  get: function(target, name) {
+    // XXX[target] != 'undefined'
+    if (typeof name === 'string') {
+      if (typeof target[name+endName] != 'undefined') {
+        const currentName = locEnv.trueName[locEnv.requireLevel];
+        const nameToShow = target[name+endName];
+        updateAnalysisData(locEnv.accessMatrix[currentName], nameToShow, 'R');
+      }
+    }
+
+    return Reflect.get(target, name);
+  },
+  set: function(target, name, value) {
+    if (typeof value === 'number') {
+      const currentName = locEnv.trueName[locEnv.requireLevel];
+      const nameToStore = 'global.' + name;
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/policy8.js

@@ -1,0 +1,167 @@
+// This is the policy for true false analysis. Each time we access a variable
+// or a function we write it with true in a export file dynamic.json 
+let locEnv;
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// @storedCalls it is a table that contains all the analysis data
+// @truename the name of the current function, object etc that we want to add to
+// the table 
+// Given those two inputs we can update the analysis data that are stored in storedCalls
+const updateAnalysisData = (storedCalls, truename) => {
+  if (Object.prototype.hasOwnProperty.
+        call(storedCalls, truename) === false) {
+      storedCalls[truename] = true;
+    }
+};
+
+// This the handler of the require function. Every time a "require" is used to load up a module
+// this handler is called. It updates the analysis data that are stored in the accessMatrix table.
+const requireHandler = {
+  apply: function(target, thisArg, argumentsList) {
+    const currentName = locEnv.trueName[locEnv.requireLevel];
+    const origReqModuleName = argumentsList[0];
+    locEnv.accessMatrix[currentName]['require(\'' + origReqModuleName + '\')'] = true;
+    return Reflect.apply(...arguments);
+  },
+};
+
+// The handler of the global variable.Every time we access the global variabe in order to declare 
+// or call a variable, then we can print it on the export file.
+const globalHandler= {
+  get: function(target, name) {
+    // XXX[target] != 'undefined'
+    if (typeof name === 'string'){
+      if (typeof target[name+endName] != 'undefined') {
+        const currentName = locEnv.trueName[locEnv.requireLevel];
+        const nameToShow = target[name+endName];
+        updateAnalysisData(locEnv.accessMatrix[currentName], nameToShow);
+      }
+    }
+
+    return Reflect.get(target, name);
+  },
+  set: function(target, name, value) {
+    if (typeof value === 'number') {
+      const currentName = locEnv.trueName[locEnv.requireLevel];
+      const nameToStore = 'global.' + name;
+      const result = Reflect.set(target, name, value);
+      // In order to exist a disticton between the values we declared ourselfs
+      // We declare one more field with key value that stores the name
+      Object.defineProperty(target, name+endName, {value: nameToStore});
+      updateAnalysisData(locEnv.accessMatrix[currentName], nameToStore);
+
+      return result;
+    }
+
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/policy9.js

@@ -1,0 +1,158 @@
+// This is the policy for true false analysis. Each time we access a variable
+// or a function we write it with true in a export file dynamic.json 
+let locEnv;
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// @storedCalls it is a table that contains all the analysis data
+// @truename the name of the current function, object etc that we want to add to
+// the table 
+// @inputType the type of the inputs of the function ~> as a string
+// @outputType the type of the output of the function ~> as a string
+// Update the analysis data that are stored in storedCalls
+const updateAnalysisData = (storedCalls, truename, inputType, outputType) => {
+  const saveData = 'input: ' + inputType + ' => output: ' + outputType; 
+  if (Object.prototype.hasOwnProperty.
+        call(storedCalls, truename) === false) {
+      storedCalls[truename] = saveData;
+  } else {
+    if (!storedCalls[truename].includes(saveData)) {
+      storedCalls[truename] += ' || ' + saveData;
+    }
+  }
+};
+
+// This the handler of the require function. Every time a "require" is used to load up a module
+// this handler is called. It updates the analysis data that are stored in the accessMatrix table.
+const requireHandler = {
+  apply: function(target, thisArg, argumentsList) {
+    const currentName = locEnv.trueName[locEnv.requireLevel];
+    const origReqModuleName = argumentsList[0];
+    //locEnv.accessMatrix[currentName]['require(\'' + origReqModuleName + '\')'] = true;
+    return Reflect.apply(...arguments);
+  },
+};
+
+// The handler of the global variable.Every time we access the global variabe in order to declare 
+// or call a variable, then we can print it on the export file.
+const globalHandler = {
+  get: function(target, name) {
+    return Reflect.get(target, name);
+  },
+  set: function(target, name, value) {
+    return Reflect.set(target, name, value);
+  },
+};
+
+// The handler of the all the function that are called inside a module. Every time we
+// load a module with require it first execute all the code and then prepary and exports 
+// all the export data. We use this handler to catch all the code that is executed on the 
+// module.
+const moduleHandler = {
+  apply: function(target) {
+    return Reflect.apply(...arguments);
+  },
+  get: function(target, name) {
+    return Reflect.get(target, name);
+  },
+};
+
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/lya/txfm.js

@@ -1,0 +1,348 @@
+/* eslint prefer-rest-params: "off", no-global-assign: "off",
+no-shadow-restricted-names: "off" */
+
+// We use this global value to know if the program has ended or not
+// necessary for enforcement analysis(5, 7) 
+global.end= false;
+
+// We import and declare all the necessary modules
+const Module = require('module');
+const vm = require('vm');
+const fs = require('fs');
+
+// All the necessary modules for swap
+const originalWrap = Module.wrap;
+const originalRequire = Module.prototype.require;
+const originalRun = vm.runInThisContext;
+
+// `require` name stack / tree 
+// require( ...require('..')... )
+// main: 0;
+// m1: 1;
+// m2: 2;
+const trueName = [];
+let requireLevel = 0;
+const globalProxies = {};
+const accessMatrix = {};
+
+trueName[0] = 'main';
+accessMatrix[trueName[0]] = {};
+
+// Holds the end of each name store of new assigned global variables
+// suffix for our own metadata
+const endName = '@name';
+
+// This holds the string of the transformations inside modules
+let finalDecl = ' ';
+
+// WeakMaps to store the name and the path for every object value
+const objName = new WeakMap();
+const objPath = new WeakMap();
+
+// @globals.json contains all the functions we want to wrap in a proxy
+// @staticGlobals.json contains all the global variables that contain static functions
+// @constantGlobals.json has all the constants of the static variables 
+// We read and store the data of the json file
+const globals = require('./globals.json');
+const sglobals = require('./staticGlobals.json');
+const cglobals = require('./constantGlobals.json');
+// const jsonPrototypeData = require('./prototypeGlobals.json');
+
+// We make a test on fragment
+const env = {
+  trueName : trueName,
+  requireLevel : requireLevel,
+  accessMatrix: accessMatrix,
+  objName : objName,
+  objPath : objPath,
+};
+
+// We return the choice of the user
+// 1) True - False Analysis
+// 2) Times calling a function
+// 3) Time Analysis
+// 4) Time Analysis2.0
+// 5) Enforcement Analysis
+// 6) RWE Analysis
+// 7) RWE Enforcement
+// 8) Global Object Analysis
+// 9) TypeOf Export Object Analysis
+let userChoice = (lyaConfig.analysisCh && [1, 2, 3, 4, 5, 6, 7, 8, 9].includes(lyaConfig.analysisCh))? lyaConfig.analysisCh : 1
+
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/test/index.js

@@ -1,0 +1,86 @@
+lyaConfig = {
+    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+    analysisCh: 1,
+};
+let lya = require("../lya/txfm.js");
+require = lya.configRequire(require, lyaConfig);
+
+
+const c = require("..")
+const equal = require("testmatrix").equal
+
+const EqualTest = (actual, expected) => ({
+  name: actual,
+  assert: equal,
+  actual,
+  expected
+})
+
+const StyleTest = (name, open, close) =>
+  EqualTest(c[name](name), open + name + close)
+
+exports.default = {
+  "using styles": [
+    ["reset", "\x1b[0m", "\x1b[0m"],
+    ["bold", "\x1b[1m", "\x1b[22m"],
+    ["dim", "\x1b[2m", "\x1b[22m"],
+    ["italic", "\x1b[3m", "\x1b[23m"],
+    ["underline", "\x1b[4m", "\x1b[24m"],
+    ["inverse", "\x1b[7m", "\x1b[27m"],
+    ["hidden", "\x1b[8m", "\x1b[28m"],
+    ["strikethrough", "\x1b[9m", "\x1b[29m"],
+    ["black", "\x1b[30m", "\x1b[39m"],
+    ["red", "\x1b[31m", "\x1b[39m"],
+    ["green", "\x1b[32m", "\x1b[39m"],
+    ["yellow", "\x1b[33m", "\x1b[39m"],
+    ["blue", "\x1b[34m", "\x1b[39m"],
+    ["magenta", "\x1b[35m", "\x1b[39m"],
+    ["cyan", "\x1b[36m", "\x1b[39m"],
+    ["white", "\x1b[37m", "\x1b[39m"],
+    ["gray", "\x1b[90m", "\x1b[39m"],
+    ["bgBlack", "\x1b[40m", "\x1b[49m"],
+    ["bgRed", "\x1b[41m", "\x1b[49m"],
+    ["bgGreen", "\x1b[42m", "\x1b[49m"],
+    ["bgYellow", "\x1b[43m", "\x1b[49m"],
+    ["bgBlue", "\x1b[44m", "\x1b[49m"],
+    ["bgMagenta", "\x1b[45m", "\x1b[49m"],
+    ["bgCyan", "\x1b[46m", "\x1b[49m"],
+    ["bgWhite", "\x1b[47m", "\x1b[49m"],
[…]

### 2020-01-06 tst/nodejs_apps/colorette-master/test/ts/index.ts

@@ -1,0 +1,9 @@
+import { red, green, bold, options, Style } from "colorette"
+
+options.enabled = true
+
+console.log(`
+  Beets are ${red("red")},
+  Cucumbers are ${green("green")},
+  ${bold("Colorette!")}.
+`)

### 2020-01-06 paper/draft.tex
Add base transform

@@
 
+\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue
+
 \newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
 \newcommand{\sx}[1]{(\S\ref{#1})}
+\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
 \newcommand{\sys}{{\scshape Lya}\xspace}
@@
 % Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
+\caption{
+  \textbf{Base transformation.}
+  \textmd{
+  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
+  }
+}
+\label{fig:base}
+\end{figure}
 
@@
 \end{tabular*}
-\label{tab:compatibility}
+\label{tab:compat}
 \vspace{-5mm}
 \end{table}
+
+The techniques presented in this paper are applicable to any programming language.
+We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
+  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
+	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
+In this section, we discuss the requirements for building \sys over other runtime environments.
+% FIXME: All these features have to have been discussed earlier
+
+By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
+All major programming languages can support these five features in a variety of ways, as described below.
+
+First, \sys replaces the implementation of the import statement (\eg \ttt{require});
+  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
+If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+% This is simplified by the fact that the import syntax is trivial.
+
+Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).
 
@@
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
+
+Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
+% used for performance monitoring and replica construction:
+  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
+All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
+% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.
+
+Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
+Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
+Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
+  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
+Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
+Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
 

### 2020-01-06 paper/draft.tex
Add shadowing figure
Add example

@@
 
-\subsection{Transformation}
-\label{two}
+\begin{figure}[t]
+\centering 
+\includegraphics[width=0.45\textwidth]{./figs/lya_shadowing.pdf}
+\caption{
+  \textbf{Shadowing segments.}
+  \textmd{
+  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
+  }
+  \vspace{-4mm}
+}
+\label{fig:shadowing}
+\end{figure}
 
@@
 \label{c}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
+\vspace{-2mm}
+\caption{
+  \textbf{Example transformations.}
+   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
+}
+\label{fig:tx2}
+\vspace{-2mm}
+\end{figure*}
 

### 2020-01-06 paper/draft.tex
Update language features

@@
 Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
-Walk objects                    &         &             &        &      &      &      &      &         \\
+Traverse objects                &         &             &        &      &      &      &      &         \\
+Wrap values                     &         &             &        &      &      &      &      &         \\
+(Weak) Maps                     &         &             &        &      &      &      &      &         \\
 Shadow variables                &         &             &        &      &      &      &      &         \\
-Wrap values                     &         &             &        &      &      &      &      &         \\
-Global names                    &         &             &        &      &      &      &      &         \\
+% Global names                    &         &             &        &      &      &      &      &         \\
 \bottomrule
@@
 
-First, \sys replaces the implementation of the import statement (\eg \ttt{require});
-  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
-If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
-If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
+% This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
+If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
 % This is simplified by the fact that the import syntax is trivial.
 
-Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).
+\sys also needs the ability to interpose on values and transform their components.
+This is relatively easy in languages that provide meta-programming capabilities.
+Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor metaprogramming Ruby.
+Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
+Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
+And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
+% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
+% Static programming languages provide different types of support for
 
-Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
-They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
+\sys makes extensive use of weak maps to support to check for object equality.
+Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
+Hash tables that are indexed by reference are supported in virtually all programming languages.
+An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
+Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
+
+Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
+This is a feature that is universally available in programming languages;\footnote{
+  A notable exception is the scripting language CoffeeScript, which can mimic the same feature using function scope.
+}
+Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
+
+To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
+Runtime transformations conveniently unify module identification with interposition:
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-
-Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
-% used for performance monitoring and replica construction:
-  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
-% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.
-
-Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
-Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
-Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
-  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
-Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
-Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
+Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
+Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
+  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 

### 2020-01-10 tst/nodejs_apps/moeda/bin/index.js
Fix

@@ -14,8 +14,11 @@ const argv = process.argv.slice(2)
 helpers(argv)
 
 const command = {
-  amount: argv[0] || 1,
-  from: argv[1] || 'USD',
-  to: (argv.length > 2) ? process.argv.slice(4) : ['USD', 'EUR', 'GBP', 'BRL']
+  amount: 1,
+  from: 'USD',
+  to: ['USD', 'EUR', 'GBP', 'BRL']
 }
-moeda(command)
+
+//for (i = 0; i < 1000; i++) {
+  moeda(command)
+//}

### 2020-01-10 tst/nodejs_apps/terminalizer-master/lya/policy1.js
Fix

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/terminalizer-master/lya/policy9.js

@@ -100,7 +100,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && type === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy1.js
Problem

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy2.js

@@ -125,7 +125,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy3.js

@@ -91,7 +91,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy4.js

@@ -151,7 +151,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
 

### 2020-01-10 src/policy5.js

@@ -142,7 +142,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
 

### 2020-01-10 src/policy6.js

@@ -136,7 +136,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy7.js

@@ -161,7 +161,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
 

### 2020-01-10 src/policy8.js

@@ -105,7 +105,7 @@ const updateCounter = (counter) => {
 const exportHandler= {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 src/policy9.js

@@ -100,7 +100,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/koajsExamples/lya/policy1.js

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];  
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && type === 'function' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (typeof target[name] === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/moeda/lya/policy1.js

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-      if (type != 'undefined' && type === 'string') { // + udnefined
+      if (type != 'undefined' && typeof name === 'string' && type === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/pokedex-go-master/lya/policy1.js

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-      if (type != 'undefined' && type === 'string') { // + udnefined
+      if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/koajsExamples/lya/policy1.js
Problems

@@ -124,13 +124,18 @@ const readFunction = (myFunc, name) => {
 // This is the handler of the export object. Every time we require a module, and it has
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
+const m = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];  
-    if (type != 'undefined' && type === 'function' && typeof name === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (typeof target[name] === 'object') {
         // FIXME
+        if (m.has(target[name])) {
+          return;
+        }
+        m.set(target[name], true); 
         let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
         if (truename === undefined) {
@@ -143,7 +148,6 @@ const exportHandler = {
         target[name] = new Proxy(localObject, exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
-
       } else if (typeof target[name] === 'function') {
         const localFunction = target[name];
 

### 2020-01-10 tst/nodejs_apps/moeda/lya/policy1.js

@@ -123,11 +123,13 @@ const readFunction = (myFunc, name) => {
 
 // This is the handler of the export object. Every time we require a module, and it has
 // export data we wrap those data in this handler. So this is the first layer of the 
-// export data wraping. 
+// export data wraping.
+const m = new WeakMap();
+const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-      if (type != 'undefined' && typeof name === 'string' && type === 'function') { // + udnefined
+      if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME

### 2020-01-10 tst/nodejs_apps/pokedex-go-master/lya/policy1.js

@@ -124,6 +124,7 @@ const readFunction = (myFunc, name) => {
 // This is the handler of the export object. Every time we require a module, and it has
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
+const m = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
@@ -131,6 +132,12 @@ const exportHandler = {
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME
+        if (m.has(target[name])) {
+          //console.log('fuckme')
+          return Reflect.get(target, name);
+        }
+        //console.log('haha')
+        m.set(target[name], true); 
         let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
         if (truename === undefined) {

### 2020-01-10 tst/nodejs_apps/pokedex-go-master/lya/policy1.js
Problems

@@ -125,6 +125,7 @@ const readFunction = (myFunc, name) => {
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
 const m = new WeakMap();
+const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
@@ -133,10 +134,8 @@ const exportHandler = {
       if (type  === 'object') {
         // FIXME
         if (m.has(target[name])) {
-          //console.log('fuckme')
-          return Reflect.get(target, name);
+          return Reflect.get(target, name);;
         }
-        //console.log('haha')
         m.set(target[name], true); 
         let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
@@ -153,7 +152,12 @@ const exportHandler = {
 
       } else if (type === 'function') {
         const localFunction = target[name];
-
+        //console.log(typeof target[name])
+        if (n.has(target[name])) {
+          readFunction(target[name], locEnv.objName.get(target));
+            return Reflect.get(target, name);;
+        }
+        n.set(target[name], true); 
         Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);

### 2020-01-10 tst/nodejs_apps/koajsExamples/lya/policy1.js
Problem

@@ -125,6 +125,7 @@ const readFunction = (myFunc, name) => {
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
 const m = new WeakMap();
+const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];  
@@ -133,7 +134,7 @@ const exportHandler = {
       if (typeof target[name] === 'object') {
         // FIXME
         if (m.has(target[name])) {
-          return;
+          return Reflect.get(target, name);;
         }
         m.set(target[name], true); 
         let truepath = locEnv.objPath.get(receiver);
@@ -149,8 +150,13 @@ const exportHandler = {
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
       } else if (typeof target[name] === 'function') {
+      	//console.log(typeof target[name])
+      	if (n.has(target[name])) {
+      		readFunction(target[name], locEnv.objName.get(target));
+          	return Reflect.get(target, name);;
+        }
+        n.set(target[name], true); 
         const localFunction = target[name];
-
         Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);

### 2020-01-10 src/policy1.js
Still problems to fix

@@ -139,11 +139,12 @@ const exportHandler = {
         if (truepath === undefined) {
           truepath = locEnv.objPath.get(target);
         }
-        const localObject = target[name];
-        target[name] = new Proxy(localObject, exportHandler);
+        //const localObject = target[name];
+        const localObject = new Proxy(target[name], exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
 
+        return localObject;
       } else if (type === 'function') {
         const localFunction = target[name];
 

### 2020-01-10 src/policy9.js

@@ -112,11 +112,12 @@ const exportHandler = {
         if (truepath === undefined) {
           truepath = locEnv.objPath.get(target);
         }
-        const localObject = target[name];
-        target[name] = new Proxy(localObject, exportHandler);
+        //const localObject = target[name];
+        const localObject = new Proxy(target[name], exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
 
+        return localObject;
       } else if (type === 'function') {
         const localFunction = target[name];
 

### 2020-01-10 tst/nodejs_apps/koajsExamples/lya/policy1.js

@@ -125,17 +125,17 @@ const readFunction = (myFunc, name) => {
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
 const m = new WeakMap();
-const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];  
     if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
-      if (typeof target[name] === 'object') {
+      if (type === 'object') {
         // FIXME
         if (m.has(target[name])) {
           return Reflect.get(target, name);;
         }
+
         m.set(target[name], true); 
         let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
@@ -146,17 +146,12 @@ const exportHandler = {
           truepath = locEnv.objPath.get(target);
         }
         const localObject = target[name];
-        target[name] = new Proxy(localObject, exportHandler);
+        //target[name] = new Proxy(localObject, exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
-      } else if (typeof target[name] === 'function') {
-      	//console.log(typeof target[name])
-      	if (n.has(target[name])) {
-      		readFunction(target[name], locEnv.objName.get(target));
-          	return Reflect.get(target, name);;
-        }
-        n.set(target[name], true); 
+      } else if (type === 'function') {
         const localFunction = target[name];
+
         Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);

### 2020-01-10 tst/nodejs_apps/moeda/bin/index.js

@@ -1,7 +1,7 @@
 #!/usr/bin/env node
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+    analysisCh: 9,
     removejson: ["unescape","Buffer"],	
 };
 let lya = require("../lya/txfm.js");

### 2020-01-10 tst/nodejs_apps/moeda/lya/policy1.js

@@ -124,16 +124,19 @@ const readFunction = (myFunc, name) => {
 // This is the handler of the export object. Every time we require a module, and it has
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping.
-const m = new WeakMap();
 const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-      if (type != 'undefined' && typeof name === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME
-        let truepath = locEnv.objPath.get(receiver);
+        if (n.has(target[name])) {
+          return Reflect.get(target, name);;
+        }
+        n.set(target[name], true); 
+	      let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
         if (truename === undefined) {
           truename = locEnv.objName.get(target);
@@ -141,14 +144,15 @@ const exportHandler = {
         if (truepath === undefined) {
           truepath = locEnv.objPath.get(target);
         }
-        const localObject = target[name];
-        target[name] = new Proxy(localObject, exportHandler);
+        //const localObject = target[name];
+        const localObject = new Proxy(target[name], exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
 
+        return localObject;
+
       } else if (type === 'function') {
         const localFunction = target[name];
-
         Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);

### 2020-01-10 tst/nodejs_apps/moeda/lya/policy9.js

@@ -100,7 +100,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME
@@ -112,11 +112,12 @@ const exportHandler = {
         if (truepath === undefined) {
           truepath = locEnv.objPath.get(target);
         }
-        const localObject = target[name];
-        target[name] = new Proxy(localObject, exportHandler);
+        //const localObject = target[name];
+        const localObject = new Proxy(target[name], exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
-
+        
+        return localObject;
       } else if (type === 'function') {
         const localFunction = target[name];
 

### 2020-01-10 tst/nodejs_apps/pokedex-go-master/lya/policy1.js

@@ -125,7 +125,6 @@ const readFunction = (myFunc, name) => {
 // export data we wrap those data in this handler. So this is the first layer of the 
 // export data wraping. 
 const m = new WeakMap();
-const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
@@ -133,10 +132,7 @@ const exportHandler = {
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME
-        if (m.has(target[name])) {
-          return Reflect.get(target, name);;
-        }
-        m.set(target[name], true); 
+        
         let truepath = locEnv.objPath.get(receiver);
         let truename = locEnv.objName.get(receiver);
         if (truename === undefined) {
@@ -152,12 +148,7 @@ const exportHandler = {
 
       } else if (type === 'function') {
         const localFunction = target[name];
-        //console.log(typeof target[name])
-        if (n.has(target[name])) {
-          readFunction(target[name], locEnv.objName.get(target));
-            return Reflect.get(target, name);;
-        }
-        n.set(target[name], true); 
+
         Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);

### 2020-01-11 paper/draft.tex
Update intro

@@
 
-Both effort and performance costs are severely compounded by the use of third-party libraries---development-time constructs usually glued together without a full understanding of their internals.
-Their ubiquity is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}
+Effort and performance costs are severely compounded by the use of third-party libraries, usually glued together without a full understanding of their internals.
+This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
 % Libraries are used pervasively today to lower development costs and improve software quality, 
 % This over-reliance to third-party libraries is a recent phenomenon, 
-  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
-As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
+  language-specific package repositories eliminate the cost of publishing and using a library.
+As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each often only a few lines long~\cite{leftpad, npmstudy:19}.
+% how to say thousands of them depend on a 11-line lib?
 Library-oriented analysis adds to the challenges of prior tools as
@@
 
-A single application today often incorporates multiple libraries\footnote{We use the terms ``library'', ``package'', and ``module'' interchangeably.} written and published by several different authors.
+A single application today often incorporates multiple libraries written and published by several different authors.
 To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
@@
 
-\subsection{Background on Modules and Module Systems}
+\subsection{Background on Module Systems}
 \label{bg1}
@@
 \subsection{Applying to Other Environments}
+\label{reqs}
 
-\begin{table}[t]
+\begin{table*}[t]
 \center
@@
 }
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
+\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
 \toprule
-                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
+             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
 \midrule
-Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
-Traverse objects                &         &             &        &      &      &      &      &         \\
-Wrap values                     &         &             &        &      &      &      &      &         \\
-(Weak) Maps                     &         &             &        &      &      &      &      &         \\
-Shadow variables                &         &             &        &      &      &      &      &         \\
-% Global names                    &         &             &        &      &      &      &      &         \\
+Lua          &                              &                       &                     &                   &                       \\
+JavaScript   &                              &                       &                     &                   &                       \\
+Python       &                              &                       &                     &                   &                       \\
+Ruby         &                              &                       &                     &                   &                       \\
+Haskell      &                              &                       &                     &                   &                       \\
+OCaml        &                              &                       &                     &                   &                       \\
+Rust         &                              &                       &                     &                   &                       \\
+Java         &                              &                       &                     &                   &                       \\
 \bottomrule
@@
 \vspace{-5mm}
-\end{table}
+\end{table*}
 
@@
 This is relatively easy in languages that provide meta-programming capabilities.
-Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor metaprogramming Ruby.
+Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
 Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
@@
 This is a feature that is universally available in programming languages;\footnote{
-  A notable exception is the scripting language CoffeeScript, which can mimic the same feature using function scope.
+  A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
 }
@@
 \label{principles}
-Dynamic analysis is a general analysis technique that discovering facts about programs;
-  dialysis can be thought as a specif
+Dynamic analysis is a general analysis technique that discovering facts about programs.
 While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
+Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
+Which are these cases exactly?
 
+The first class of  
+It is really a quick-and-dirty 
+As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
+Its availability as a global module makes this trivial.
+% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
+
+The second is when the goal is to understand the behavior of third-party code.
+Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
 Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
+Examples include the 
+N-version programming ---all of which would require a custom tool.
 By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
 
-Another use is in the existence of multi-language applications---wrappers and FFI.
+Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
+These limitations is due to several reasons.
+First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
+An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
+Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
+A related problem is the inability to traverse and wrap objects, due to lack of bounds.
+It is unclear how to wrap values without any kind of size information.\footnote{
+  Recent advances show promise: C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} provide type-aware heap traversal for C programs.
+}
+% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}
+
+That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
+Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
+Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
 

### 2020-01-11 paper/draft.tex
Update module system

@@
 
-languages provide module systems
+A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
+This functionality falls into two categories:
+  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
+  or (ii) is provided by other developers sharing code others might find useful.
+Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
 
-closely coupled with the runtime
+From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
+What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
+This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
+The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
+% , as shown on line \fixme{XX},
+% closely coupled with the runtime
+% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.
 
-A module uses a \ttt{import} function and returns an export .
-Intuitively a map
+From the language's perspective, the loading process is achieved in several steps. 
+In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
+Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
+This process starts by locating the library in the file system or across the network,\footnote{
+  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
+}
+by resolving relative or absolute identifiers.
+% The library is assigned a unique identifier.
+The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
+The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
+Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.
 
-Several details:
-  same module at multiple levels, and the module cache
-  sometime it's the same, some times it;s not
-  module resolution algorithm
+There is significant variation, but a few features are common across many implementations.
+A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
+The library cache serves a dual purpose:
+  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
+Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
+An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
+As a result, a single \ttt{import} \emph{name} does not necessarily resolve to the same library every time
+The dual of this situation is also possible, in which two different library names might resolve to the same identifier (in which case the second will be redirected to the cache).
+
+% Several details:
+%   same module at multiple levels, and the module cache
+%   sometime it's the same, some times it;s not
+%   module resolution algorithm
 

### 2020-01-11 paper/draft.tex
Add details on analysis 1

@@
 An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \emph{name} does not necessarily resolve to the same library every time
-The dual of this situation is also possible, in which two different library names might resolve to the same identifier (in which case the second will be redirected to the cache).
+As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
+The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
+These features complicate library-level analysis, especially in interpreted programming languages.
 
@@
   (i) an allow/deny security analysis,
-  (ii) a profiling analysis showing hot modules,
+  (ii) a profiling analysis showing hot libraries,
   (iii) a synthesis-oriented analysis on input-output data, and
@@
 \heading{Security Analysis}
-Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
-Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
-As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
-The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
+The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
+Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
+As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
+Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
 Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
-Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.
+Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.
 
-Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
-The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
-% and is exploitable.
-Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
-Other functionality is \emph{implicitly} provided by the programming language;
-  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
-Both explicitly and implicitly provided functionality is exploitable by third-party code.
-While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
-% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
-MLC shows great promise, as it can
-(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
-(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
-(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).
+As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
+As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
+At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
+  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
+Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
+% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
 
-To make this concrete, we are introducing
+To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior.
+% FIXME more about the policy, tracking arguments too
+A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
+Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.
+
+\emph{
+This use case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
+}
 

### 2020-01-11 paper/draft.tex
Update analyses

@@
 
-To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior.
+To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
 % FIXME more about the policy, tracking arguments too
@@
 
-\emph{
-This use case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-}
+% \emph{
+% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
+% }
 
 \heading{Performance Diagnosis}
-Developers use various techniques to understand such problems.
-For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
-These techniques, however, require some degree of \emph{manual} effort:
-  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
-Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.
+Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
+Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
+  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
+Maintenance and rewriting can cause performance regressions between two versions of a library.
+% FIXME: Garbage collection
+Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.
 
-Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
-A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
-This allows viewing a series of calls as a stream of messages. % that 
-% at each module boundary 
-Module boundaries can be viewed as (virtual) queues of messages that await processing.
-% and applying windowed average operations on a 
+As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
+Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
+The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).
+
+The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
+An analysis 
+% A key observation is the semantic isomorphism between calling a function and passing a message
+% This allows viewing a series of calls as a stream of messages.
+% Module boundaries can be viewed as (virtual) queues of messages that await processing.
+treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
 Overwhelming a module causes its ingress queue to grow.
-% MM: related to the sync vs. async
-% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
-At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
-% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.
+At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
+Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
+Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
+Profile generation can operate at a high resolution in time and space:
+  (i) at every function call entering a module, and (ii) on thousands of modules across an application.
 
-To make this concrete, we are introducing
+% ATTRIBUTION
+% Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
+% For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency\eat{ is \ttt{A}-internal and how much} comes from \ttt{B}.
+% or \ttt{B}'s dependency, \ttt{C}.
+%
 
-\heading{Type and Invariant Checking}
+% \emph{
+% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
+% }
+
+\heading{Invariant Discovery}
 Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
@@
 For example
+e.
+For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
+This is especially problematic in dynamic programming languages:
+  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.
 
-To make this concrete, we are using
+To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
+Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
+if the type changes, because of a library version change or because of changes in the .
+
 The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
+A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
+The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
+The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
 
-\heading{Learning, Synthesis, and Regeneration}
-Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
-Dynamic analysis can be used to generate type assertions or invariants
-For example
-The approach has been pioneered by systems such as
+% would need to be able 
+% to capture structural subtitling---that is the piecewise
 
-To make this concrete, we are using
-The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
+% \heading{Learning, Synthesis, and Regeneration}
 

### 2020-01-11 paper/draft.tex
Update overview

@@
 \newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
+\newcommand{\rf}[1]{\ref{#1}}
+\newcommand{\se}[1]{\S\ref{#1}}
+\newcommand{\fg}[1]{Fig.~\ref{#1}}
+
 \newcommand{\sys}{{\scshape Lya}\xspace}
@@
 \newcommand{\dia}{\fra, \ana, and \ass}
+
+% FIXME:
+\newcommand{\pc}{PIC\xspace}
+\newcommand{\pcs}{\pc{}s\xspace}
 
@@
 Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
-  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
-We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
-We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).
+  instead of simply locating and loading a library from the file-system, it yields control to \sys, which applies a series of transformations to libraries with the goal of interposing at their boundaries.
+We start with an overview of dialysis~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).
 
@@
 % FIXME: add user data
-At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
- In more detail, these three phases are as follows:
+At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
+ In more detail:
 
@@
 
-  \item \Fra:
-    It first starts by recursively dis-assembling programs into their library dependencies---pieces of software implement a computation or functionality.
-    This is essentially achieved by instrumenting the import statements and walking the program's recursive dependency structure.
-    Different analysis can operate at different granularities, and has to solve challenges such as multi-module and dedublication.
-
-  \item \Ana:
-    It then sets a specific analysis up by wrapping and transforming each module interface, its surrounding environment, as well as the values passing through the module boundary.
-    Programmatic transformations walk and transform each one of these values based on their type:
-      the module interface is usually a complex (but singular) object; the surrounding environment treats 
-    This phase requires solving several challenges, including enumerating and tracking all points of entry into and exit out of a library.
-    It also requires providing 
-     in a backwards compatible fashion.
-
-  \item \Ass:
-    Finally, it re-assembles individual modified modules back into the original structure.
-    This creates several challenges, the most important of which is the treatment of the module cache---a mechanism for avoiding multiple loads of the same module .
-    Since a single library can now correspond to many different wrappers, each modified to capture different  analysis fragments, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
+  \item \textbf{Dismantling:}
+Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
+This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
+During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.
+
+  \item \textbf{Transformation:}
+It then sets up the provided analysis, by transforming each library interface, its surrounding environment, and possibly the values passing through the library boundary.
+Programmatic transformations walk and wrap each one of these values based on their type.
+% the library interface is usually a complex (but singular) object;
+% the surrounding environment provides names to multiple ``implicitely'' imported libraries, functionality provided by the language.
+This phase requires solving several challenges, including enumerating all points of entry into and exit out of a library, 
+and swapping original values externally available to a library with ones that are wrapped with interposition mechanisms.
+
+  \item \textbf{Re-assembly}
+Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
+The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
+  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
 
@@
 
-Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
-
-% , such as an object returned from a module or an exception about to be sent across the network.
-Transformations can be applied to any value in the language. 
-The most general value is an object, a bag of records holding key-value fields;
-  other value types include primitives, functions, and booleans.
-% Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
-More specifically,
-  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
-  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
-  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
 

### 2020-01-11 paper/draft.tex
Dismantling

@@
   The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
+The meta-function $\alpha$ stands for the locations of analysis hooks.
   }
@@
 
-The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
-These skeletons provide hooks for end-developers writing analyses.
-Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
-These hooks are then extended or rewritten by developers to
-
-For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
-\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
-The wrappers depend on the intended goal:
-  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.
-
-\subsection{Disassembly}
+% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
+% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
+% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
+% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
+% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
+% The following subsections detail these steps.
+
+\subsection{Dismantling}
 \label{one}
+
+When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
+Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
+For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
+For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
+
+It then dynamically replaces the implementation of\ttt{import}:
+  rather than simply locating and loading a library, the function yields to \sys.
+
+\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
+If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
+If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
+% \omit{---the common case---}
+Otherwise, \sys first invokes the built-in library loader to locate the library.
+
+The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
+Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
+A series of transformations is applied before and after interpretation~\sx{two}.
+
+Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
+\sys must note not to include these constructs in the ones 
+% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
+Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
+To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
+The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
+  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
 

### 2020-01-11 paper/draft.tex
Update transformations

@@
 
+\subsection{Transformation}
+\label{two}
+
+For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
+This is achieved in three logical steps:
+(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
+(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
+(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
+Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
+
+\heading{Transformations}
+% , such as an object returned from a module or an exception about to be sent across the network.
+Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
+% Listing~\ref{core-tx} presents a simplified core of the language.
+Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
+More specifically,
+  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
+  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
+  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
+To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
+% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+
+% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
+% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
+% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
+% At runtime, $f'$ checks $\sigma$:
+%  if the access is allowed, it forwards the call to $f$;
+%  otherwise, it raises an exception.
+% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
+% 
+% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
+% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
+% 
+% % Listing~\ref{core-tx} presents a simplified core of the language.
+% 
+% \begin{itemize}
+% \item
+%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
+% \item
+%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
+% \item
+%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
+% \end{itemize}
+
+Direct field accesses, such as assignments, require custom detection upon dereference.
+To achieve this, \sys wraps fields with an interposition mechanism;
+  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
+% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
+\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
+For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
+
+\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
+To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
+  the unprocessed value is used to create objects, at runtime, that run a different analysis;
+  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
+
 \subsection{Reassembly}

### 2020-01-11 paper/draft.tex
Update transformations

@@
 
+\heading{Context Transformation}
+To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
+
+To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
+Semantically, the context is a map from variable names to their values.
+Thus, \sys creates an auxiliary hash table mapping names to transformed values.
+Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
+Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
+
+%% FIXME: 
+%% While user-defined global variables are stored in well-known locations,\footnote{
+%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
+%% } traversing the global scope for built-in values is generally not possible.
+%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
+%%   different lists exist for different environments and versions of the language.
+%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.
+
+Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
+These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
+Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
+Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
+\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).
+
+\heading{Context Linking}
+To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
+The closure's body starts with a prologue of the form:
+\begin{verbatim}
+  pint = ctx.print
+  error = ctx.error
+  ...
+\end{verbatim}
+These statements shadow global variable names by redefining them as local ones.
+The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
+The prologue executes before everything else in the library.
+% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
+This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
+Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
+
+Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
+  these names are now bound to the correct library-local values.
+
+\heading{Library Interface Transformation}
+Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
+% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
+The goal of the final transformation is to track activity at the boundary;
+  for some analyses, \sys needs to also augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
+
 \subsection{Reassembly}

### 2020-01-11 paper/draft.tex
Update library

@@
 The goal of the final transformation is to track activity at the boundary;
-  for some analyses, \sys needs to also augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
-
-\subsection{Reassembly}
+  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
+
+The final transformation is applied for every new consumer of the library.
+This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
+
+\subsection{Re-assembly}
 \label{three}
 
-% \section{Applications of Analysis}
-% \label{apps}
-
-\section{Implementation: Lya}
-\label{impl}
-
-We implemented \sys for version 8.9.4 of the Node.js runtime.
-Node.js is a runtime that bun
-
-in about 1.5K lines of JavaScript.
-We summarize where other implementations would diverge in table 1
-
-Individual analysis are implemented using a set of templates that provide initial constructs (see below).
-The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.
+To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
+The central mechanism for resolution is the library cache.
+
+To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
+The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
+A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
+Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
+% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
+For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
+Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
+  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.
+
+% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
+A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
+When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
+It then applies a transformation to the library's return value.
+New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
 

### 2020-01-11 src/policy9.js
Tries to fix obj problem

@@ -112,12 +112,12 @@ const exportHandler = {
         if (truepath === undefined) {
           truepath = locEnv.objPath.get(target);
         }
-        //const localObject = target[name];
-        const localObject = new Proxy(target[name], exportHandler);
+        const localObject = target[name];
+        target[name] = new Proxy(localObject, exportHandler);
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
 
-        return localObject;
+        
       } else if (type === 'function') {
         const localFunction = target[name];
 

### 2020-01-11 tst/nodejs_apps/koajsExamples/blog/app.js

@@ -1,6 +1,6 @@
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+    analysisCh: 9,
     removejson: ["Promise","toString","unescape","Buffer"],
 };
 let lya = require("../lya/txfm.js");

### 2020-01-11 tst/nodejs_apps/koajsExamples/lya/policy9.js

@@ -100,7 +100,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (typeof target[name] === 'object') {
         // FIXME

### 2020-01-11 tst/nodejs_apps/moeda/lya/policy9.js

@@ -117,7 +117,6 @@ const exportHandler = {
         locEnv.objName.set(localObject, truename + '.' + name);
         locEnv.objPath.set(localObject, truepath);
         
-        return localObject;
       } else if (type === 'function') {
         const localFunction = target[name];
 

### 2020-01-11 tst/nodejs_apps/koajsExamples/blog/app.js
Take times with function only for big programs

@@ -1,6 +1,6 @@
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 9,
+    analysisCh: 1,
     removejson: ["Promise","toString","unescape","Buffer"],
 };
 let lya = require("../lya/txfm.js");

### 2020-01-11 tst/nodejs_apps/koajsExamples/lya/policy1.js

@@ -128,7 +128,7 @@ const m = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];  
-    if (type != 'undefined' && typeof name === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string' && type === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-11 tst/nodejs_apps/koajsExamples/templates/test.js

@@ -2,6 +2,7 @@ const app = require('./app');
 const server = app.listen();
 const request = require('supertest').agent(server);
 
+for (var i; i<10; i++) {
 describe('Templates', function() {
   after(function() {
     server.close();
@@ -15,4 +16,4 @@ describe('Templates', function() {
       .expect('<p>Tobi is a 3 year old ferret.</p>', done);
     });
   });
-});
+});}

### 2020-01-11 tst/nodejs_apps/moeda/bin/index.js

@@ -19,6 +19,6 @@ const command = {
   to: ['USD', 'EUR', 'GBP', 'BRL']
 }
 
-//for (i = 0; i < 1000; i++) {
-  moeda(command)
-//}
+for (var i=0; i<1000; i++) {
+moeda(command)
+}

### 2020-01-11 tst/nodejs_apps/moeda/lya/policy1.js

@@ -128,7 +128,7 @@ const n = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && typeof name === 'string') { // + udnefined
+    if (type != 'undefined' && typeof name === 'string' && type === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME
@@ -157,8 +157,8 @@ const exportHandler = {
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);
         locEnv.objName.set(localFunction, locEnv.objName.get(target));
-          
-        // Undefined fix
+        
+	// Undefined fix
         readFunction(localFunction, locEnv.objName.get(target));
 
       }

### 2020-01-11 tst/nodejs_apps/moeda/lya/policy2.js

@@ -125,7 +125,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && type === 'string') { // + udnefined
+    if (type === 'function' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         let truepath = locEnv.objPath.get(receiver);

### 2020-01-11 tst/nodejs_apps/moeda/lya/policy9.js

@@ -100,7 +100,7 @@ const updateCounter = (counter) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && typeof name === 'string') { // + udnefined
+    if (type === 'function' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME

### 2020-01-11 tst/nodejs_apps/pokedex-go-master/lya/policy1.js

@@ -128,7 +128,7 @@ const m = new WeakMap();
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-      if (type != 'undefined' && typeof name === 'string') { // + udnefined
+      if (type != 'undefined' && typeof name === 'string' && type === 'function') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type  === 'object') {
         // FIXME

### 2020-01-11 tst/nodejs_apps/pokedex-go-master/test/database-manager.spec.js

@@ -12,7 +12,7 @@ const _ = require('lodash');
 const databaseManager = require('../src/database-manager');
 const POKEMONS = require('../db/pokemons.json');
 const TYPES = require('../db/types.json');
-
+for (var i=0; i <1000; i++) {
 describe('database manager', () => {
 
     it('should find the right modifiers', () => {
@@ -87,4 +87,4 @@ describe('database manager', () => {
 
 	});
 
-});
+});}

### 2020-01-11 tst/nodejs_apps/terminalizer-master/lya/policy1.js

@@ -127,7 +127,7 @@ const readFunction = (myFunc, name) => {
 const exportHandler = {
   get: function(target, name, receiver) {
     const type = typeof target[name];
-    if (type != 'undefined' && typeof name === 'function') { // + udnefined
+    if (type === 'function' && typeof name === 'string') { // + udnefined
       // If we try to grab an object we wrap it in this proxy
       if (type === 'object') {
         // FIXME
@@ -146,8 +146,8 @@ const exportHandler = {
 
       } else if (type === 'function') {
         const localFunction = target[name];
-
-        Object.defineProperty(localFunction, 'name', {value: name});
+        
+	Object.defineProperty(localFunction, 'name', {value: name});
         target[name] = new Proxy(localFunction, exportsFuncHandler);
         locEnv.objPath.set(localFunction, locEnv.trueName[locEnv.requireLevel]);
         locEnv.objName.set(localFunction, locEnv.objName.get(target));

### 2020-01-12 paper/draft.tex
Update techniques

@@
 \usepackage{graphicx}
+\usepackage{alltt}
+\usepackage{amssymb}
+\usepackage{amsmath}
 
@@
 
-% ATTRIBUTION
-% Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
-% For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency\eat{ is \ttt{A}-internal and how much} comes from \ttt{B}.
-% or \ttt{B}'s dependency, \ttt{C}.
-%
-
 % \emph{
@@
 \begin{verbatim}
-  pint = ctx.print
-  error = ctx.error
+  local pint = ctx.print
+  local error = ctx.error
   ...
@@
 
-The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
-It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
-
-In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is as a modified version of the runtime, where 
-No-op analyses correspond to the default execution
-  either 
-It is introduced as a backward-compatible, drop-in replacement of the language's module system.
-It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
-
-We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
-However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-  we expand on these at the end of this section~\sx{opportunities}.
-% get second argument, no need to pass arguments around, tricky to 
-% carefull hardcoding of paths, because \sys's code itself is split into modules
-% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
-% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
-% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
-% This is useful, for example, when...
-% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
-
-(1) why node.js
-(2) Create a table of compatibility and show individual aspects
-
-\heading{Module System}
-Node.js' module system is implemented entirely in JavaScript.
-It exposes \ttt{require}, a global-looking function for importing modules.
-\fixme{Figure} above demonstrates the use of \ttt{require}.
-
-% \begin{lstlisting}[language=js,mathescape,upquote=true]
-% // -------------- [./main.js] -------------
-% // importing point
-% let Point = require("./point.js");
-% Point.create(1, 1).print(); // => [1, 1]
-% 
-% // -------------- [./point.js] ------------
-% let Point = function Point (x, y) {
-%     this.x = x; this.y = y;
-% };
-% Point.prototype.print = function print () {
-%   console.log([this.x, this.y]);
-% };
-% module.exports = {
-%     create:  function create (x, y) {
-%         return new Point(x, y);
-%     }
-% };
-% \end{lstlisting}
-
-In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
-Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
-  the rest is module-private functionality.
-Files and modules are in one-to-one correspondence (each file is treated as a separate module).
-Method \ttt{require} is synchronous (\ie blocking):
-  it will block execution until the module specified is loaded.
-% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
-The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.
-
-\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).
-
-\subsection{Implementation of the Module System}
-\label{c}
+\section{Implementation of Dialysis for SSJ}
+\label{impl}
 

### 2020-01-12 paper/draft.tex
Update implementation

@@
    Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
+\fixme{No UX!}
 }
@@
 
-At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
-
-\begin{enumerate}
-% \def\labelenumi{\arabic{enumi}.}
-\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
-\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
-\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
-\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
-\end{enumerate}
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
+We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
+We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
+
+In practice, the aforementioned dialysis stages can be implemented in two different ways.
+The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
+The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
+It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
+  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
+  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
+% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
+%   we expand on in the discussion section~\sx{reqs}.
+
+% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+
+\subsection{System Implementation}
+\label{impl1}
+
+Node.js' module system is implemented entirely in JavaScript.
+It exposes \ttt{require}, a global-looking function for importing modules.
+At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
 
@@
 
-% \begin{lstlisting}[language=js,mathescape,upquote=true]
-% // Node.js will wrap a module with a function,
-% // so as to bring certain names into scope
-% // before compiling/evaluating code.
-% let wrapped = "function (" +
-%         "exports, require, module, " +
-%         "__filename, __dirname, CTX) {" +
-%     "let Math = CTX.Math" +
-%     "let console = CTX.console" +
+% \begin{verbatim}
+% let lib = `
+%  function (exports, require, module,
+%            __filename, __dirname, CTX) {
+%    let Math = CTX.Math
+%    let console = CTX.console
 %    //...[more definitions]
-%     moduleSource +
-%   "});"
-% \end{lstlisting}
+%    ${moduleSource}
+%  });`;
+% \end{verbatim}
 

### 2020-01-12 paper/draft.tex
Update implementation

@@
 
-% \begin{lstlisting}[language=js,mathescape,upquote=true]
-% //Input: module ID e.g., absolute filepath
-% let load = function (ID) {
-%   if (cache[ID]) {
-%      return cache[ID];
-%   }
-%   let m = {
-%     exports: {}, id: ID, dir: path.resolve(ID)
-%   };
-%   let cm = v8.compile(wrapped);
-%   let ii = iris.getImplicit(ID);
-%   let c = iris.freshContext(ii);
-%   cm(m.exports, this.require, m, ID, m.dir, c);
-%   let ei = iris.getExplicit(ID);
-%   m.exports = iris.wrap(m.exports, [ei] );
-%   cache[ID] = m;
-%   return m.exports;
-% }
-% \end{lstlisting}
-
-The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
-After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
-\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
-Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
-Finally, the results of the entire process are placed into the module cache for later use.
-
-\subsection{Limitations}
-
-% FIXME: Talk about the inability to 
-A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
-This is because \sys cannot transform the context of that file
-As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
-The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
-
-\section{Evaluation and Experience}
+% get second argument, no need to pass arguments around, tricky to 
+% carefull hardcoding of paths, because \sys's code itself is split into modules
+% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
+% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
+% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
+% This is useful, for example, when...
+% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
+
+%% TODO: implementation
+%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
+%% These skeletons provide hooks for end-developers writing analyses.
+%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
+%% These hooks are then extended or rewritten by developers to
+
+Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
+\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
+The precise wrappers depend on the intended analysis, reviewed next.
+
+\subsection{Individual Analyses}
+\label{impl2}
+
+Individual analysis are implemented using a set of templates that provide initial constructs (see below).
+\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
+As a result, code that is specific to individual analyses averages about 20--30 lines.
+
+\heading{Security Analysis}
+To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
+The language of the analysis is given in the following grammar:
+
+\begin{alltt}
+  str:  <identifier in JS>
+  libs: [ str ]
+  path: str `.` path
+  mode: P{ R | W | X }
+  body: { [ path: mode ]: path \(\in\) mods}
+  analysis:  mods body
+\end{alltt}
+
+\heading{Performance Diagnosis}
+
+\begin{equation}
+\label{eq:2}
+R_{new} =
+\begin{cases}
+  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
+  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
+\end{cases}
+\end{equation}
+
+Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
+However, after scale-in, the system often ends up just scaling out the same module.
+To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.
+
+% ATTRIBUTION
+Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
+For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
+% \eat{ is \ttt{A}-internal and how much}
+comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
+
+\heading{Invariant Discovery}
+Describe specific type system
+
+% \subsection{Limitations}
+% 
+% % FIXME: Talk about the inability to 
+% A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
+% This is because \sys cannot transform the context of that file
+% As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
+% The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
+
+\section{Evaluation}
 \label{eval}

### 2020-01-12 paper/draft.tex
Add an introductory example

@@
 
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
+\caption{
+  \textbf{Example of a library import.}
+  \textmd{
+    The code on the left imports the \ttt{simple-math} library, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
+    Several names resolve to functionality provided by the programming language:
+      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
+  }
+}
+\label{fig:base}
+\end{figure}
+
 A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
@@
   or (ii) is provided by other developers sharing code others might find useful.
-Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
+Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{Math} library provides a set of four elementary operations.
 

### 2020-01-12 paper/draft.tex
Minor corrections

@@
   a profiling analysis showing bottlenecked modules,
-  a synthesis-oriented analysis on input-output data, and
-  an analysis enforcing a static union-based type system at runtime.
+% a synthesis-oriented analysis on input-output data,
+  and an analysis extracting invariants around a static union-based type system at runtime.
 This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
@@
 \begin{itemize}
-\item \S\ref{bg} characterizes the shared needs of four case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
-\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
-\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
+\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
+\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
+\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
 \item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
@@
   \textmd{
-    The code on the left imports the \ttt{simple-math} library, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
+    The program on the left imports the \ttt{simple-math} library, shown right, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
     Several names resolve to functionality provided by the programming language:
@@
 }
-\label{fig:base}
+\label{fig:ex1}
 \end{figure}
 
-A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
+A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
 This functionality falls into two categories:
-  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) is provided by other developers sharing code others might find useful.
-Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{Math} library provides a set of four elementary operations.
-
-From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
-What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
-This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
-The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
-Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
+  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
+  or (ii) provided by other developers sharing code others might find useful.
+Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).
+
+From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
+% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
+This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
+The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
 % , as shown on line \fixme{XX},
@@
 
-From the language's perspective, the loading process is achieved in several steps. 
-In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
-Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
-This process starts by locating the library in the file system or across the network,\footnote{
-  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
-}
+From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
+Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
+Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
+This process starts by locating the library in the file system % or across the network,\footnote{
+%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
+% }
 by resolving relative or absolute identifiers.
@@
 The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
-The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
-Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.
+The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
+Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.
 
 There is significant variation, but a few features are common across many implementations.
-A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
-The library cache serves a dual purpose:
-  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
-Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
+A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
+The cache serves a dual purpose:
+  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
+Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
 An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
-The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
+As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
+The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
 These features complicate library-level analysis, especially in interpreted programming languages.
@@
   (i) an allow/deny security analysis,
-  (ii) a profiling analysis showing hot libraries,
-  (iii) a synthesis-oriented analysis on input-output data, and
-  (iv) an analysis enforcing a static union-based type system at runtime.
+  (ii) a performance-profiling analysis showing bottlenecked libraries, and
+% (iii) a synthesis-oriented analysis on input-output data, and
+  (iii) an analysis extracting runtime type invariants.
 These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
@@
 
-We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
+We have briefly introduced three motivating analyses for extracting information about an application's dependencies.
 While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
@@
     \textbf{Synthetic Micro-benchmarks}.
-		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
+		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
   }
@@
     \textbf{Applying \sys to single-library programs}.
-		\fixme{Execution time of four test suites against }
+		\fixme{Execution time of eight test suites against }
   }
@@
 
-Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
+Table~\ref{} depicts the results of the three analysis applied to these benchmarks.
 We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.

### 2020-01-12 paper/draft.tex

--- 2020-01-12 paper/draft.tex
@@
 \usepackage{graphicx}
-\usepackage{alltt}
-\usepackage{amssymb}
-\usepackage{amsmath}
 
@@
 
-\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue
-
 \newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
 \newcommand{\sx}[1]{(\S\ref{#1})}
-\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
-\newcommand{\rf}[1]{\ref{#1}}
-\newcommand{\se}[1]{\S\ref{#1}}
-\newcommand{\fg}[1]{Fig.~\ref{#1}}
-
 \newcommand{\sys}{{\scshape Lya}\xspace}
@@
 \newcommand{\dia}{\fra, \ana, and \ass}
-
-% FIXME:
-\newcommand{\pc}{PIC\xspace}
-\newcommand{\pcs}{\pc{}s\xspace}
-
-\newcommand{\goal}[1]{(\textbf{G#1})\xspace}
 
@@
 
-Effort and performance costs are severely compounded by the use of third-party libraries, usually glued together without a full understanding of their internals.
-This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
+Both effort and performance costs are severely compounded by the use of third-party libraries---development-time constructs usually glued together without a full understanding of their internals.
+Their ubiquity is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}
 % Libraries are used pervasively today to lower development costs and improve software quality, 
 % This over-reliance to third-party libraries is a recent phenomenon, 
-  language-specific package repositories eliminate the cost of publishing and using a library.
-As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each often only a few lines long~\cite{leftpad, npmstudy:19}.
-% how to say thousands of them depend on a 11-line lib?
+  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
+As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
 Library-oriented analysis adds to the challenges of prior tools as
@@
 
-A single application today often incorporates multiple libraries written and published by several different authors.
+A single application today often incorporates multiple libraries\footnote{We use the terms ``library'', ``package'', and ``module'' interchangeably.} written and published by several different authors.
 To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
@@
 
-\subsection{Background on Module Systems}
+\subsection{Background on Modules and Module Systems}
 \label{bg1}
 
-A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
-This functionality falls into two categories:
-  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) is provided by other developers sharing code others might find useful.
-Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
+languages provide module systems
 
-From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
-What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
-This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
-The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
-Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
-% , as shown on line \fixme{XX},
-% closely coupled with the runtime
-% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.
+closely coupled with the runtime
 
-From the language's perspective, the loading process is achieved in several steps. 
-In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
-Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
-This process starts by locating the library in the file system or across the network,\footnote{
-  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
-}
-by resolving relative or absolute identifiers.
-% The library is assigned a unique identifier.
-The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
-The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
-Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.
+A module uses a \ttt{import} function and returns an export .
+Intuitively a map
 
-There is significant variation, but a few features are common across many implementations.
-A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
-The library cache serves a dual purpose:
-  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
-Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
-An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
-The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
-These features complicate library-level analysis, especially in interpreted programming languages.
-
-% Several details:
-%   same module at multiple levels, and the module cache
-%   sometime it's the same, some times it;s not
-%   module resolution algorithm
+Several details:
+  same module at multiple levels, and the module cache
+  sometime it's the same, some times it;s not
+  module resolution algorithm
 
@@
   (i) an allow/deny security analysis,
-  (ii) a profiling analysis showing hot libraries,
+  (ii) a profiling analysis showing hot modules,
   (iii) a synthesis-oriented analysis on input-output data, and
@@
 \heading{Security Analysis}
-The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
-Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
-As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
-Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
+Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
+Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
+As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
+The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
 Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
-Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.
+Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.
 
-As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
-As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
-At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
-  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
-Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
-% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
+Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
+The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
+% and is exploitable.
+Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
+Other functionality is \emph{implicitly} provided by the programming language;
+  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
+Both explicitly and implicitly provided functionality is exploitable by third-party code.
+While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
+% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
+MLC shows great promise, as it can
+(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
+(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
+(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).
 
-To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
-% FIXME more about the policy, tracking arguments too
-A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
-Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.
-
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
+To make this concrete, we are introducing
 
 \heading{Performance Diagnosis}
-Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
-Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
-  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
-Maintenance and rewriting can cause performance regressions between two versions of a library.
-% FIXME: Garbage collection
-Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.
+Developers use various techniques to understand such problems.
+For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
+These techniques, however, require some degree of \emph{manual} effort:
+  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
+Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.
 
-As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
-Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
-The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).
+Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
+A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
+This allows viewing a series of calls as a stream of messages. % that 
+% at each module boundary 
+Module boundaries can be viewed as (virtual) queues of messages that await processing.
+% and applying windowed average operations on a 
+Overwhelming a module causes its ingress queue to grow.
+% MM: related to the sync vs. async
+% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
+At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
+% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.
 
-The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
-An analysis 
-% A key observation is the semantic isomorphism between calling a function and passing a message
-% This allows viewing a series of calls as a stream of messages.
-% Module boundaries can be viewed as (virtual) queues of messages that await processing.
-treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
-Overwhelming a module causes its ingress queue to grow.
-At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
-Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
-Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
-Profile generation can operate at a high resolution in time and space:
-  (i) at every function call entering a module, and (ii) on thousands of modules across an application.
+To make this concrete, we are introducing
 
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
-
-\heading{Invariant Discovery}
+\heading{Type and Invariant Checking}
 Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
@@
 For example
-e.
-For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
-This is especially problematic in dynamic programming languages:
-  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.
 
-To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
-Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
-if the type changes, because of a library version change or because of changes in the .
+To make this concrete, we are using
+The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
 
+\heading{Learning, Synthesis, and Regeneration}
+Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
+Dynamic analysis can be used to generate type assertions or invariants
+For example
+The approach has been pioneered by systems such as
+
+To make this concrete, we are using
 The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
-A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
-The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
-The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
-
-% would need to be able 
-% to capture structural subtitling---that is the piecewise
-
-% \heading{Learning, Synthesis, and Regeneration}
 
@@
 
-Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
-  instead of simply locating and loading a library from the file-system, it yields control to \sys, which applies a series of transformations to libraries with the goal of interposing at their boundaries.
-We start with an overview of dialysis~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).
+Dialysis detects and scales out bottlenecked components by interposing on the application's module boundaries.
+It is introduced as a backward-compatible, drop-in replacement of the language's module system.
+It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
+Dialysis starts by dynamically modifying the function that imports libraries: \eat{for locating and loading a module.}
+  instead of simply locating and loading a module, the function yields to \sys, which applies a series of transformation steps to modules, with the goal of interposing on their boundaries.
+We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
+We next describe each one of these steps in more detail
 
@@
 
+This section presents the design of 
 % FIXME: add user data
-At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
- In more detail:
+At a high level, module dialysis works at three stages:
 
@@
 
-  \item \textbf{Dismantling:}
-Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
-This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
-During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.
+  \item \Fra:
+    It first starts by recursively dis-assembling programs into their library dependencies---pieces of software implement a computation or functionality.
+    This is essentially achieved by instrumenting the import statements and walking the program's recursive dependency structure.
+    Different analysis can operate at different granularities, and has to solve challenges such as multi-module and dedublication.
 
-  \item \textbf{Transformation:}
-It then sets up the provided analysis, by transforming each library interface, its surrounding environment, and possibly the values passing through the library boundary.
-Programmatic transformations walk and wrap each one of these values based on their type.
-% the library interface is usually a complex (but singular) object;
-% the surrounding environment provides names to multiple ``implicitely'' imported libraries, functionality provided by the language.
-This phase requires solving several challenges, including enumerating all points of entry into and exit out of a library, 
-and swapping original values externally available to a library with ones that are wrapped with interposition mechanisms.
+  \item \Ana:
+It then sets a specific analysis up by wrapping and transforming each module interface, its surrounding environment, as well as the values passing through the module boundary.
+Programmatic transformations walk and transform each one of these values based on their type:
+  the module interface is usually a complex (but singular) object; the surrounding environment treats 
+This phase requires solving several challenges, including enumerating and tracking all points of entry into and exit out of a library.
+It also requires providing 
+ in a backwards compatible fashion.
 
-  \item \textbf{Re-assembly}
-Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
-The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
-  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
+  \item \Ass:
+  Finally, it re-assembles individual modified modules back into the original structure.
+  This creates several challenges, the most important of which is the treatment of the module cache---a mechanism for avoiding multiple loads of the same module .
+  Since a single library can now correspond to many different wrappers, each modified to capture different  analysis fragments, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
 
@@
 
-% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
+% \textbf{Core Language}
+% a few is not the same as 
+Transformations are used pervasively throughout \sys, and are abstracted via a few parametrizable templates.
+Templates map different types of values (List.~\ref{core-tx}) to a generic handler for each type.
+%given a value, a template will transform it using a handler matching its type
+% Templates match, 
+% \hl{match} between different \hl{value} % what are values
+%    \emph{types} and define generic handlers for each type.
+Transformations have these handlers parametrized to achieve concrete goals such as monitoring, serialization, and scale-out.
+Simplified instances are described in the following two sections (\S\ref{profiling}--\ref{core}).
 
-\begin{figure}[t]
-\raggedleft 
-\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
-\caption{
-  \textbf{Base transformation.}
-  \textmd{
-  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
-The meta-function $\alpha$ stands for the locations of analysis hooks.
-  }
-}
-\label{fig:base}
-\end{figure}
+Transformations can be applied to any value in the language, such as an object returned from a module or an exception about to be sent across the network.
+The general case of such a value is a directed acyclic graph (DAG).
+The types of its vertices can be coarsely grouped into primitives, functions, and objects.
+Objects map strings to other values, pointing to other vertices in the DAG.
+% Listing~\ref{core-tx} presents a simplified core of the language.
+Transformations start by walking the DAG from the root vertex and processing component values based on their types.
+They do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+They only partially explore the object graph, as they do not peak through function closure environments.
+Fortunately, this aligns well with our goal of monitoring activity at module boundaries and ignoring module-internal activity.
 
-% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
-% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
-% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
-% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
-% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
-% The following subsections detail these steps.
+As an example, consider transforming the \ttt{crypto} module~\sx{solution}.
+\sys traverses the object returned by \ttt{crypto} and replaces functions such as \ttt{pbkdf2} with wrappers whose specifics depend on the intended goal:
+  profiling wrappers call the original function in between statistics collection, and RPC wrappers forward the call to a remote replica.
 
-\subsection{Dismantling}
-\label{one}
+% \section{Applications of Analysis}
+% \label{apps}
 
-When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
-Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
-For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
-For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
-
-It then dynamically replaces the implementation of\ttt{import}:
-  rather than simply locating and loading a library, the function yields to \sys.
-
-\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
-If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
-If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
-% \omit{---the common case---}
-Otherwise, \sys first invokes the built-in library loader to locate the library.
-
-The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
-Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
-A series of transformations is applied before and after interpretation~\sx{two}.
-
-Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
-\sys must note not to include these constructs in the ones 
-% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
-Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
-To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
-The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
-  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
-
-\begin{figure}[t]
-\centering 
-\includegraphics[width=0.45\textwidth]{./figs/lya_shadowing.pdf}
-\caption{
-  \textbf{Shadowing segments.}
-  \textmd{
-  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
-  }
-  \vspace{-4mm}
-}
-\label{fig:shadowing}
-\end{figure}
-
-\subsection{Transformation}
-\label{two}
-
-For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
-This is achieved in three logical steps:
-(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
-(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
-(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
-Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
-
-\heading{Transformations}
-% , such as an object returned from a module or an exception about to be sent across the network.
-Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
-% Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
-More specifically,
-  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
-  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
-  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
-% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
-
-% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
-% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
-% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
-% At runtime, $f'$ checks $\sigma$:
-%  if the access is allowed, it forwards the call to $f$;
-%  otherwise, it raises an exception.
-% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
-% 
-% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
-% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
-% 
-% % Listing~\ref{core-tx} presents a simplified core of the language.
-% 
-% \begin{itemize}
-% \item
-%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
-% \item
-%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
-% \item
-%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
-% \end{itemize}
-
-Direct field accesses, such as assignments, require custom detection upon dereference.
-To achieve this, \sys wraps fields with an interposition mechanism;
-  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
-% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
-\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
-For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
-
-\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
-To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
-  the unprocessed value is used to create objects, at runtime, that run a different analysis;
-  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
-
-\heading{Context Transformation}
-To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
-
-To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
-Semantically, the context is a map from variable names to their values.
-Thus, \sys creates an auxiliary hash table mapping names to transformed values.
-Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
-Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
-
-%% FIXME: 
-%% While user-defined global variables are stored in well-known locations,\footnote{
-%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
-%% } traversing the global scope for built-in values is generally not possible.
-%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
-%%   different lists exist for different environments and versions of the language.
-%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.
-
-Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
-These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
-Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
-Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
-\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).
-
-\heading{Context Linking}
-To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
-The closure's body starts with a prologue of the form:
-\begin{verbatim}
-  local pint = ctx.print
-  local error = ctx.error
-  ...
-\end{verbatim}
-These statements shadow global variable names by redefining them as local ones.
-The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
-The prologue executes before everything else in the library.
-% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
-This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
-Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
-
-Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
-  these names are now bound to the correct library-local values.
-
-\heading{Library Interface Transformation}
-Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
-% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
-The goal of the final transformation is to track activity at the boundary;
-  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
-
-The final transformation is applied for every new consumer of the library.
-This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
-
-\subsection{Re-assembly}
-\label{three}
-
-To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
-The central mechanism for resolution is the library cache.
-
-To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
-The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
-A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
-Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
-% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
-For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
-Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
-  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.
-
-% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
-A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
-When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
-It then applies a transformation to the library's return value.
-New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
-
-\section{Implementation of Dialysis for SSJ}
+\section{Implementation: Lya}
 \label{impl}
 
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
-\vspace{-2mm}
-\caption{
-  \textbf{Example transformations.}
-   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
-\fixme{No UX!}
-}
-\label{fig:tx2}
-\vspace{-2mm}
-\end{figure*}
+We implemented \sys for version 
+We show where other implementations would diverge in table 1
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
+The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
+It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
 
-In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
-The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+(1) why node.js
+(2) Create a table of compatibility and show individual aspects
 
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
-It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
-  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
-  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
-% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-%   we expand on in the discussion section~\sx{reqs}.
-
-% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
-
-\subsection{System Implementation}
-\label{impl1}
-
+\heading{Module System}
 Node.js' module system is implemented entirely in JavaScript.
 It exposes \ttt{require}, a global-looking function for importing modules.
-At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
-(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
-(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
-(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
-(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+\fixme{Figure} above demonstrates the use of \ttt{require}.
+
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% // -------------- [./main.js] -------------
+% // importing point
+% let Point = require("./point.js");
+% Point.create(1, 1).print(); // => [1, 1]
+% 
+% // -------------- [./point.js] ------------
+% let Point = function Point (x, y) {
+%     this.x = x; this.y = y;
+% };
+% Point.prototype.print = function print () {
+%   console.log([this.x, this.y]);
+% };
+% module.exports = {
+%     create:  function create (x, y) {
+%         return new Point(x, y);
+%     }
+% };
+% \end{lstlisting}
+
+In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
+Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
+  the rest is module-private functionality.
+Files and modules are in one-to-one correspondence (each file is treated as a separate module).
+Method \ttt{require} is synchronous (\ie blocking):
+  it will block execution until the module specified is loaded.
+% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
+The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.
+
+\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).
+
+\subsection{Implementation of the Module System}
+\label{c}
+
+At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+
+\begin{enumerate}
+% \def\labelenumi{\arabic{enumi}.}
+\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+\end{enumerate}
 
@@
 
-% \begin{verbatim}
-% let lib = `
-%  function (exports, require, module,
-%            __filename, __dirname, CTX) {
-%    let Math = CTX.Math
-%    let console = CTX.console
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% // Node.js will wrap a module with a function,
+% // so as to bring certain names into scope
+% // before compiling/evaluating code.
+% let wrapped = "function (" +
+%         "exports, require, module, " +
+%         "__filename, __dirname, CTX) {" +
+%     "let Math = CTX.Math" +
+%     "let console = CTX.console" +
 %     //...[more definitions]
-%    ${moduleSource}
-%  });`;
-% \end{verbatim}
+%     moduleSource +
+%   "});"
+% \end{lstlisting}
 
@@
 
-% get second argument, no need to pass arguments around, tricky to 
-% carefull hardcoding of paths, because \sys's code itself is split into modules
-% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
-% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
-% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
-% This is useful, for example, when...
-% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% //Input: module ID e.g., absolute filepath
+% let load = function (ID) {
+%   if (cache[ID]) {
+%      return cache[ID];
+%   }
+%   let m = {
+%     exports: {}, id: ID, dir: path.resolve(ID)
+%   };
+%   let cm = v8.compile(wrapped);
+%   let ii = iris.getImplicit(ID);
+%   let c = iris.freshContext(ii);
+%   cm(m.exports, this.require, m, ID, m.dir, c);
+%   let ei = iris.getExplicit(ID);
+%   m.exports = iris.wrap(m.exports, [ei] );
+%   cache[ID] = m;
+%   return m.exports;
+% }
+% \end{lstlisting}
 
-%% TODO: implementation
-%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
-%% These skeletons provide hooks for end-developers writing analyses.
-%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
-%% These hooks are then extended or rewritten by developers to
+The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
+After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
+\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
+Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
+Finally, the results of the entire process are placed into the module cache for later use.
 
-Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
-\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
-The precise wrappers depend on the intended analysis, reviewed next.
-
-\subsection{Individual Analyses}
-\label{impl2}
-
-Individual analysis are implemented using a set of templates that provide initial constructs (see below).
-\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
-As a result, code that is specific to individual analyses averages about 20--30 lines.
-
-\heading{Security Analysis}
-To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
-The language of the analysis is given in the following grammar:
-
-\begin{alltt}
-  str:  <identifier in JS>
-  libs: [ str ]
-  path: str `.` path
-  mode: P{ R | W | X }
-  body: { [ path: mode ]: path \(\in\) mods}
-  analysis:  mods body
-\end{alltt}
-
-\heading{Performance Diagnosis}
-
-\begin{equation}
-\label{eq:2}
-R_{new} =
-\begin{cases}
-  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
-  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
-\end{cases}
-\end{equation}
-
-Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
-However, after scale-in, the system often ends up just scaling out the same module.
-To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.
-
-% ATTRIBUTION
-Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
-For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
-% \eat{ is \ttt{A}-internal and how much}
-comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
-
-\heading{Invariant Discovery}
-Describe specific type system
-
-% \subsection{Limitations}
-% 
-% % FIXME: Talk about the inability to 
-% A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
-% This is because \sys cannot transform the context of that file
-% As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
-% The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
+\
 
@@
 
-\sys's  development achieves goals~\goal{1--3}~\sx{goals}, demonstrating that it is indeed feasible to construct a framework that operates at the level of modules, 
-does not force developers to learn a new language, and that it can be implemented as a library around an existing runtime.
-Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
-
-In this section, we are interested in zooming into \sys's performance characteristics~\goal{4}.
-At a high level, we are interested in three questions:
-(i) the overheads of the \sys's underlying building blocks;
-(ii) the overhead of different analysis on real libraries and how this compares with production dynamic analysis frameworks; and
-(iii) evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
-% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
-% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
-% For the third question, we use a combination of real applications~\sx{macro}.
-
-Several takeaways are worth highlighting.
-\fixme{TODO after we have the results.}
-
-Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
-In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu XXX version}, Jalangi \fixme{vXXX}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
-We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.
-
 \subsection{Micro-benchmarks}
 \label{micro}
-
-\sys's micro-benchmark suite was designed with two goals in mind.
-
-The first goal was to test key properties of each analysis and confirm it outputs the expected results.
-For example, to better understand performance diagnosis policy and confirm it works correctly, we craft a library that contains four other libraries with pre-defined bottlenecks.
-The library can perform one of three operations, depending on its current state:
-  (i) invoke a call to a module it imports,
-  (ii) busy-wait, or
-  (iii) respond to calls by returning a value.
-
-The second goal was to identify understand \sys bottlenecks in a controlled environment, 
-Both of these goals would have been difficult to achieve outside a synthetic environment, as we do not fully understand applications we haven't written ourselves.
-
-\begin{table}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{Synthetic Micro-benchmarks}.
-		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
-\toprule
-              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
-\midrule
-something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
-something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
-something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
-something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
-something5    &           &  24214  &   24721  &   24574  &   24502   \\
-\bottomrule
-\end{tabular*}
-\label{tab:synthetic}
-\vspace{-5mm}
-\end{table}
-
-\begin{table}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{Applying \sys to single-library programs}.
-		\fixme{Execution time of four test suites against }
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
-\toprule
-                    & Base   &  SA   & PD     &   TIC   & LSR     \\
-\midrule
-Classnames~\cite{}  &  2.72  & 6.62  &  6.61  &  6.10   & 5.94    \\
-Debug~\cite{}       & 31.39  & 33.54 &  33.94 &  33.96  & 33.04   \\
-% Minimist\\
-~~~-t1              & 31.46  & 60.13 &  60.00 &  56.62  & 56.72   \\
-~~~-t2              & 19.17  & 59.77 &  60.75 &  57.15  & 57.79   \\
-~~~-t3              & 21.64  & 205.2 &  205.53&  132.25 & 137.84  \\
-~~~-t4              & 20.69  & 59.70 &  60.75 &  59.92  & 56.60   \\
-~~~-t5              & 20.49  & 70.48 &  72.20 &  64.71  & 66.03   \\
-Moment~\cite{}      & 31.73  & 48.04 &  49.23 &  44.95  & 46.12   \\
-yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
-\bottomrule
-\end{tabular*}
-\label{tab:meso}
-\vspace{-5mm}
-\end{table}
-
-Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
-We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
-Currently, these benchmarks return the results we expect, but they did help with the identification of problems such as 
-These be
-Load is visible at the application level (left), but the lack of detail does not help determine which modules must be scaled out.
-Module-level data, collected by \sys' coordinator (right), reveal that \ttt{m3} receives the majority of the load.
-
-To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
-  unmodified and proxy-wrapped.
-Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
-We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
-The proxy-wrapped version introduces interposition at every level.
-Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
-
-We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
-  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
-The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
 
@@
 
-\begin{figure*}[t]
-  \centering
-   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
-  \caption{
-    \textbf{Analysis overheads.}
-    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
-		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
-    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
-  }
-  \label{fig:meso}
-  \vspace{-3mm}
-\end{figure*}
-
 \subsection{End-to-End Benchmarks}
@@
 
-\begin{table}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{Applying \sys to three large applications}.
-		\fixme{Highlight some things}
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
-\toprule
-                    & Koa    & Moeda   &  Terminalizer \\
-\midrule
- Size (KB)          & 41M    &  29M    &   262M        \\
- LoC                & 127K   &  79K    &   39K         \\
- Top-level modules  &  24    &  7      &    33         \\
- Total Modules      &  432   &  260    &    1084       \\
- Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  xx    &         &               \\
- A1 (TF)            &        &         &               \\
- A3 (HF)            &        &         &               \\
- A8 (Types)         &        &         &               \\     
-\bottomrule
-\end{tabular*}
-\label{tab:macro}
-\vspace{-5mm}
-\end{table}
-
-Highly popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
-Applying \sys to these applications generates much larger analayses
-For example, the performance diagnosis analysis hooks reports timing characteristics for
-
-The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few different reasons.
-One is that an analysis does not report accesses if a 
-\sys analyzes modules that are part of the standard library too (some of which have themselves internal dependencies), which are not shown by \ttt{npm}.
-Our post-processing counts by module name (\ie squashes duplicate reports by 
-This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
-For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
-It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{cache}).
-Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
-
-\section{Discussion}
+\section{Discussion and Limitations}
 \label{diss}
@@
 \subsection{Applying to Other Environments}
-\label{reqs}
 
-\begin{table*}[t]
+\begin{table}[t]
 \center
@@
 }
-\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
 \toprule
-             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
+                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
 \midrule
-Lua          &                              &                       &                     &                   &                       \\
-JavaScript   &                              &                       &                     &                   &                       \\
-Python       &                              &                       &                     &                   &                       \\
-Ruby         &                              &                       &                     &                   &                       \\
-Haskell      &                              &                       &                     &                   &                       \\
-OCaml        &                              &                       &                     &                   &                       \\
-Rust         &                              &                       &                     &                   &                       \\
-Java         &                              &                       &                     &                   &                       \\
+Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
+Walk objects                    &         &             &        &      &      &      &      &         \\
+Shadow variables                &         &             &        &      &      &      &      &         \\
+Wrap values                     &         &             &        &      &      &      &      &         \\
+Global names                    &         &             &        &      &      &      &      &         \\
 \bottomrule
 \end{tabular*}
-\label{tab:compat}
+\label{tab:compatibility}
 \vspace{-5mm}
-\end{table*}
+\end{table}
 
-The techniques presented in this paper are applicable to any programming language.
-We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
-  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
-	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
-In this section, we discuss the requirements for building \sys over other runtime environments.
-% FIXME: All these features have to have been discussed earlier
-
-By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
-All major programming languages can support these five features in a variety of ways, as described below.
-
-First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
-% This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
-If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
-If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
-% This is simplified by the fact that the import syntax is trivial.
-
-\sys also needs the ability to interpose on values and transform their components.
-This is relatively easy in languages that provide meta-programming capabilities.
-Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
-Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
-Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
-And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
-% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
-% Static programming languages provide different types of support for
-
-\sys makes extensive use of weak maps to support to check for object equality.
-Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
-Hash tables that are indexed by reference are supported in virtually all programming languages.
-An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
-Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
-
-Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
-This is a feature that is universally available in programming languages;\footnote{
-  A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
-}
-Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
-
-To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
-Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
-Runtime transformations conveniently unify module identification with interposition:
+\heading{Dynamic Language Interpretation}
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
+They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
-Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
-  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 
@@
 \label{principles}
-Dynamic analysis is a general analysis technique that discovering facts about programs.
+Dynamic analysis is a general analysis technique that discovering facts about programs;
+  dialysis can be thought as a specif
 While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
-Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
-Which are these cases exactly?
 
-The first class of  
-It is really a quick-and-dirty 
-As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
-Its availability as a global module makes this trivial.
-% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
-
-The second is when the goal is to understand the behavior of third-party code.
-Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
 Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
-Examples include the 
-N-version programming ---all of which would require a custom tool.
 By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
 
-Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
-These limitations is due to several reasons.
-First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
-An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
-Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
-A related problem is the inability to traverse and wrap objects, due to lack of bounds.
-It is unclear how to wrap values without any kind of size information.\footnote{
-  Recent advances show promise: C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} provide type-aware heap traversal for C programs.
-}
-% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}
-
-That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
-Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
-Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
+Another use is in the existence of multi-language applications---wrappers and FFI.
 
@@
 
-We want to emphasize that \sys is open source, available to experiment with more applications and analyses
-
 % \section*{Acknowledgments}

### 2020-01-13 paper/draft.tex

@@
 \newcommand{\sx}[1]{(\S\ref{#1})}
+\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
 \newcommand{\sys}{{\scshape Lya}\xspace}
@@
 
-Dialysis detects and scales out bottlenecked components by interposing on the application's module boundaries.
-It is introduced as a backward-compatible, drop-in replacement of the language's module system.
-It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
-Dialysis starts by dynamically modifying the function that imports libraries: \eat{for locating and loading a module.}
-  instead of simply locating and loading a module, the function yields to \sys, which applies a series of transformation steps to modules, with the goal of interposing on their boundaries.
+Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
+  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
 We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
-We next describe each one of these steps in more detail
+We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).
 
@@
 
-This section presents the design of 
 % FIXME: add user data
-At a high level, module dialysis works at three stages:
+At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
+ In more detail, these three phases are as follows:
 
@@
 
+\sys's micro-benchmark suite was designed with two goals in mind.
+
+The first goal was to test key properties of each analysis and confirm it outputs the expected results.
+For example, to better understand performance diagnosis policy and confirm it works correctly, we craft a library that contains four other libraries with pre-defined bottlenecks.
+The library can perform one of three operations, depending on its current state:
+  (i) invoke a call to a module it imports,
+  (ii) busy-wait, or
+  (iii) respond to calls by returning a value.
+
+The second goal was to identify understand \sys bottlenecks in a controlled environment, 
+Both of these goals would have been difficult to achieve outside a synthetic environment, as we do not fully understand applications we haven't written ourselves.
+
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Synthetic Micro-benchmarks}.
+		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
+\toprule
+              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
+\midrule
+something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
+something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
+something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
+something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
+something5    &           &  24214  &   24721  &   24574  &   24502   \\
+\bottomrule
+\end{tabular*}
+\label{tab:synthetic}
+\vspace{-5mm}
+\end{table}
+
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Applying \sys to single-library programs}.
+		\fixme{Execution time of four test suites against }
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
+\toprule
+                    & Base   &  SA   & PD     &   TIC   & LSR     \\
+\midrule
+Classnames~\cite{}  &  2.72  & 6.62  &  6.61  &  6.10   & 5.94    \\
+Debug~\cite{}       & 31.39  & 33.54 &  33.94 &  33.96  & 33.04   \\
+% Minimist\\
+~~~-t1              & 31.46  & 60.13 &  60.00 &  56.62  & 56.72   \\
+~~~-t2              & 19.17  & 59.77 &  60.75 &  57.15  & 57.79   \\
+~~~-t3              & 21.64  & 205.2 &  205.53&  132.25 & 137.84  \\
+~~~-t4              & 20.69  & 59.70 &  60.75 &  59.92  & 56.60   \\
+~~~-t5              & 20.49  & 70.48 &  72.20 &  64.71  & 66.03   \\
+Moment~\cite{}      & 31.73  & 48.04 &  49.23 &  44.95  & 46.12   \\
+yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
+\bottomrule
+\end{tabular*}
+\label{tab:meso}
+\vspace{-5mm}
+\end{table}
+
+Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
+We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
+Currently, these benchmarks return the results we expect, but they did help with the identification of problems such as 
+These be
+Load is visible at the application level (left), but the lack of detail does not help determine which modules must be scaled out.
+Module-level data, collected by \sys' coordinator (right), reveal that \ttt{m3} receives the majority of the load.
+
+To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
+  unmodified and proxy-wrapped.
+Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
+We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
+The proxy-wrapped version introduces interposition at every level.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+
+We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
+
 \subsection{Single-module Benchmarks}
 \label{meso}
+
+\begin{figure*}[t]
+  \centering
+   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
+  \caption{
+    \textbf{Analysis overheads.}
+    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
+		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
+    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
+  }
+  \label{fig:meso}
+  \vspace{-3mm}
+\end{figure*}
 
@@
 
-\section{Discussion and Limitations}
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Applying \sys to three large applications}.
+		\fixme{Highlight some things}
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
+\toprule
+                    & Koa    & Moeda   &  Terminalizer \\
+\midrule
+ Size (KB)          & 41M    &  29M    &   262M        \\
+ LoC                & 127K   &  79K    &   39K         \\
+ Top-level modules  &  24    &  7      &    33         \\
+ Total Modules      &  432   &  260    &    1084       \\
+ Lya detects:       &  1507  &   729   &     2355      \\
+ Baseline           &  xx    &         &               \\
+ A1 (TF)            &        &         &               \\
+ A3 (HF)            &        &         &               \\
+ A8 (Types)         &        &         &               \\     
+\bottomrule
+\end{tabular*}
+\label{tab:macro}
+\vspace{-5mm}
+\end{table}
+
+Highly popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
+Applying \sys to these applications generates much larger analayses
+For example, the performance diagnosis analysis hooks reports timing characteristics for
+
+The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few different reasons.
+One is that an analysis does not report accesses if a 
+\sys analyzes modules that are part of the standard library too (some of which have themselves internal dependencies), which are not shown by \ttt{npm}.
+Our post-processing counts by module name (\ie squashes duplicate reports by 
+This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
+For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
+It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{cache}).
+Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
+
+\section{Discussion}
 \label{diss}
@@
 \end{tabular*}
-\label{tab:compatibility}
+\label{tab:compat}
 \vspace{-5mm}
@@
 
-\heading{Dynamic Language Interpretation}
+The techniques presented in this paper are applicable to any programming language.
+We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
+  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
+	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
+In this section, we discuss the requirements for building \sys over other runtime environments.
+% FIXME: All these features have to have been discussed earlier
+
+By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
+All major programming languages can support these five features in a variety of ways, as described below.
+
+First, \sys replaces the implementation of the import statement (\eg \ttt{require});
+  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
+If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+% This is simplified by the fact that the import syntax is trivial.
+
+Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).
+
 Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.

### 2020-01-13 tst/nodejs_apps/moeda/bin/helpers.js
Updates to get times

@@ -10,7 +10,9 @@ const helpers = (argv) => {
 
   // help
   if (argv.indexOf('--help') !== -1 || argv.indexOf('-h') !== -1 || !argv.length) {
-    help()
+    //for ( var i=0; i<2000; i++) {
+        help()
+    //}
   }
 
   // currencies
@@ -25,7 +27,8 @@ const version = () => {
 }
 
 const help = () => {
-  console.log(`
+for (var i=0; i<50000; i++) {	 
+ console.log(`
   Usage
     $ moeda <amount> <currency> [<...currencies>]
 
@@ -38,7 +41,7 @@ const help = () => {
     or
 
     $ moeda 1 usd eur rub aud
-  `)
+  `)}
   process.exit(1)
 }
 

### 2020-01-13 tst/not working/lodash/t2/main.js
Updates

@@ -2,7 +2,7 @@ lyaConfig = {
   SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
   analysisCh: 1,
 };
-let lya = require("../../../src/txfm.js");
+let lya = require("../../../../src/txfm.js");
 require = lya.configRequire(require, lyaConfig);
 
 const _ = require("lodash");

### 2020-01-13 run_all.sh
Updated test

@@ -1,6 +1,52 @@
 cd ./tst/working/repos
 
-cd ./classnames
+cd ./colorette
+[ -e timebind.txt ] && rm timebind.txt
+
+npm --key=0 test > /dev/null
+npm --key=1 test > /dev/null
+npm --key=5 test > /dev/null
+npm --key=2 test > /dev/null
+npm --key=3 test > /dev/null
+npm --key=4 test > /dev/null
+npm --key=6 test > /dev/null
+npm --key=7 test > /dev/null
+npm --key=8 test > /dev/null
+npm --key=9 test > /dev/null
+echo "We all test for colorette"
+
+cd ../mkdirp/repo/
+[ -e timebind.txt ] && rm timebind.txt
+
+npm --key=0 test > /dev/null 2>> /dev/null
+npm --key=1 test > /dev/null 2>> /dev/null
+npm --key=5 test > /dev/null 2>> /dev/null
+npm --key=2 test > /dev/null 2>> /dev/null
+npm --key=3 test > /dev/null 2>> /dev/null
+npm --key=4 test > /dev/null 2>> /dev/null
+npm --key=6 test > /dev/null 2>> /dev/null
+npm --key=7 test > /dev/null 2>> /dev/null
+npm --key=8 test > /dev/null 2>> /dev/null
+npm --key=9 test > /dev/null 2>> /dev/null
+echo "We all test for colorette"
+
+cd ../../chalk/repo
+[ -e timebind.txt ] && rm timebind.txt
+
+npm --key=0 test > /dev/null
+npm --key=1 test > /dev/null
+npm --key=5 test > /dev/null
+npm --key=2 test > /dev/null
+npm --key=3 test > /dev/null
+npm --key=4 test > /dev/null
+npm --key=6 test > /dev/null
+npm --key=7 test > /dev/null
+npm --key=8 test > /dev/null
+npm --key=9 test > /dev/null
+echo "We all test for chalk"
+
+
+cd ../../classnames
 [ -e timebind.txt ] && rm timebind.txt
 
 npm --key=0 test > /dev/null
@@ -11,6 +57,8 @@ npm --key=3 test > /dev/null
 npm --key=4 test > /dev/null
 npm --key=6 test > /dev/null
 npm --key=7 test > /dev/null
+npm --key=8 test > /dev/null
+npm --key=9 test > /dev/null
 echo "We all test for classnames"
 
 cd ../debug/debug-master/
@@ -24,6 +72,8 @@ npm --key=3  test > /dev/null
[…]

### 2020-01-13 tst/working/repos/colorette/test/index.js
Updated tests

@@ -1,9 +1,15 @@
-lyaConfig = {
-    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
-};
-let lya = require("../lya/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+if (parseInt(process.env.npm_config_key) != 0) {
+  lyaConfig = {
+  SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+  analysisCh: parseInt(process.env.npm_config_key),
+  POLICY: '../tst/working/repos/classnames/tests/dynamic.json'
+  };
+  let lya = require("../../../../../src/txfm.js");
+  require = lya.configRequire(require, lyaConfig);
+}
+// We start to count time for the tests
+const time = process.hrtime();
+const fs = require('fs');
 
 const c = require("..")
 const equal = require("testmatrix").equal
@@ -83,3 +89,11 @@ exports.default = {
     }
   ]
 }
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timebind.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.npm_config_key) + ' is ' + thisTime + ' \n', 'utf-8');
+console.log('HAAAAAAAAAAAAAA')

### 2020-01-13 tst/working/repos/mkdirp/repo/test/chmod.js

@@ -1,11 +1,14 @@
-lyaConfig = {
-    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+if (parseInt(process.env.npm_config_key) != 0) {
+	global.lyaConfig = {
+	SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+	analysisCh: parseInt(process.env.npm_config_key),
+ 	POLICY: '../tst/working/repos/classnames/tests/dynamic.json',
     removejson: ['Buffer','hasOwnProperty','Promise'],
-};
-let lya = require("../../../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
-
+	};
+	let lya = require("../../../../../../src/txfm.js");
+	require = lya.configRequire(require, lyaConfig);
+}
+// We start to count time for the tests
 const time = process.hrtime();
 
 var mkdirp = require('../').mkdirp;

### 2020-01-13 run_all.sh
Updates

@@ -5,13 +5,7 @@ cd ./colorette
 
 npm --key=0 test > /dev/null
 npm --key=1 test > /dev/null
-npm --key=5 test > /dev/null
-npm --key=2 test > /dev/null
-npm --key=3 test > /dev/null
 npm --key=4 test > /dev/null
-npm --key=6 test > /dev/null
-npm --key=7 test > /dev/null
-npm --key=8 test > /dev/null
 npm --key=9 test > /dev/null
 echo "We all test for colorette"
 
@@ -20,13 +14,7 @@ cd ../mkdirp/repo/
 
 npm --key=0 test > /dev/null 2>> /dev/null
 npm --key=1 test > /dev/null 2>> /dev/null
-npm --key=5 test > /dev/null 2>> /dev/null
-npm --key=2 test > /dev/null 2>> /dev/null
-npm --key=3 test > /dev/null 2>> /dev/null
 npm --key=4 test > /dev/null 2>> /dev/null
-npm --key=6 test > /dev/null 2>> /dev/null
-npm --key=7 test > /dev/null 2>> /dev/null
-npm --key=8 test > /dev/null 2>> /dev/null
 npm --key=9 test > /dev/null 2>> /dev/null
 echo "We all test for colorette"
 
@@ -35,13 +23,7 @@ cd ../../chalk/repo
 
 npm --key=0 test > /dev/null
 npm --key=1 test > /dev/null
-npm --key=5 test > /dev/null
-npm --key=2 test > /dev/null
-npm --key=3 test > /dev/null
 npm --key=4 test > /dev/null
-npm --key=6 test > /dev/null
-npm --key=7 test > /dev/null
-npm --key=8 test > /dev/null
 npm --key=9 test > /dev/null
 echo "We all test for chalk"
 

### 2020-01-13 tst/tools.sh
Add scripts for adding and counting numbers

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+grep -o -E ':[[:blank:]]*[[:digit:]]+,?' ./dynamic.json |
+  grep -o -E '[[:digit:]]+' |
+  tr '\n' '+' |
+  sed 's/$/0/' |
+  bc | sed 's/^/sum of calls for all functions: /'
+
+grep -o -E ':[[:blank:]]*[[:digit:]]+,?' ./dynamic.json |
+  grep -o -E '[[:digit:]]+' |
+  wc -l |
+  sed 's/^/number of functions accessed: /'

### 2020-01-13 tst/nodejs_apps/moeda/bin/index.js
Updates

@@ -1,7 +1,7 @@
 #!/usr/bin/env node
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+    analysisCh: 9,
     removejson: ["unescape","Buffer"],	
 };
 let lya = require("../lya/txfm.js");
@@ -21,6 +21,6 @@ const command = {
   to: ['USD', 'EUR', 'GBP', 'BRL']
 }
 
-//for (var i=0; i<2000; i++) {
+for (var i=0; i<200; i++) {
 moeda(command)
-//}
+}

### 2020-01-13 paper/draft.tex
Added time for moeda,terminalizer

@@
 yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
+chalk~\cite{} 	    & 17.37  & 24.42 &  26.01 &  26.32  & 0.00    \\
+colorette~\cite{}   & 08.10  & 13.85 &  13.41 &  13.16  & 0.00    \\
+mkdirp~\cite{}      & 116.37 & 1959.52 & 1392.64 & 1252 & 0.00    \\
 \bottomrule
@@
  Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  xx    &         &               \\
- A1 (TF)            &        &         &               \\
- A3 (HF)            &        &         &               \\
- A8 (Types)         &        &         &               \\     
+ Baseline           &  xx    &  1.27   &    0.754      \\
+ A1 (TF)            &        &  2.00   &    3.346      \\
+ A3 (HF)            &        &  2.684  &    2.684      \\
+ A8 (Types)         &        &  2.036  &    2.615      \\     
 \bottomrule

### 2020-01-13 tst/nodejs_apps/terminalizer-master/app.js
Updates

@@ -5,7 +5,7 @@
  */
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+    analysisCh: 2,
     removejson: ['unescape','Buffer','toString'],
 };
 let lya = require("./lya/txfm.js");

### 2020-01-13 paper/draft.tex
Update section 2

--- 2020-01-13 paper/draft.tex
@@
 
+\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue
+
 \newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
@@
   a profiling analysis showing bottlenecked modules,
-  a synthesis-oriented analysis on input-output data, and
-  an analysis enforcing a static union-based type system at runtime.
+% a synthesis-oriented analysis on input-output data,
+  and an analysis extracting union-based type invariants.
 This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
@@
 
-\subsection{Background on Modules and Module Systems}
+\subsection{Background on Module Systems}
 \label{bg1}
 
-languages provide module systems
-
-closely coupled with the runtime
-
-A module uses a \ttt{import} function and returns an export .
-Intuitively a map
-
-Several details:
-  same module at multiple levels, and the module cache
-  sometime it's the same, some times it;s not
-  module resolution algorithm
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
+\caption{
+  \textbf{Example of a library import.}
+  \textmd{
+    The program on the left imports the \ttt{simple-math} library, shown right, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
+    Several names resolve to functionality provided by the programming language:
+      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
+  }
+}
+\label{fig:ex1}
+\end{figure}
+
+A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
+This functionality falls into two categories:
+  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
+  or (ii) provided by other developers sharing code others might find useful.
+Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).
+
+From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
+% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
+This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
+The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
+% , as shown on line \fixme{XX},
+% closely coupled with the runtime
+% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.
+
+From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
+Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
+Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
+This process starts by locating the library in the file system % or across the network,\footnote{
+%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
+% }
+by resolving relative or absolute identifiers.
+% The library is assigned a unique identifier.
+The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
+The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
+Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.
+
+There is significant variation, but a few features are common across many implementations.
+A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
+The cache serves a dual purpose:
+  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
+Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
+An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
+As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
+The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
+These features complicate library-level analysis, especially in interpreted programming languages.
+
+% Several details:
+%   same module at multiple levels, and the module cache
+%   sometime it's the same, some times it;s not
+%   module resolution algorithm
 
@@
   (i) an allow/deny security analysis,
-  (ii) a profiling analysis showing hot modules,
-  (iii) a synthesis-oriented analysis on input-output data, and
-  (iv) an analysis enforcing a static union-based type system at runtime.
+  (ii) a performance-profiling analysis showing bottlenecked libraries, and
+% (iii) a synthesis-oriented analysis on input-output data, and
+  (iii) an analysis extracting runtime type invariants.
 These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
@@
 \heading{Security Analysis}
-Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
-Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
-As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
-The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
+The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
+Both bugs and malicious code in libraries create attack vectors, exploitable long after libraries reach their end-users.
+As library boundaries disappear at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
+Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
 Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
-Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.
-
-Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
-The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
-% and is exploitable.
-Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
-Other functionality is \emph{implicitly} provided by the programming language;
-  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
-Both explicitly and implicitly provided functionality is exploitable by third-party code.
-While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
-% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
-MLC shows great promise, as it can
-(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
-(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
-(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).
-
-To make this concrete, we are introducing
+Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.
+
+As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
+Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
+Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
+Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.
+
+Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
+Analyzing the behavior \emph{within} the library itself is not critical:
+  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
+Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
+Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
+% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
+
+ %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
+ %% % FIXME more about the policy, tracking arguments too
+ %%  indicating the resources touched by that library 
+ %% it seems critical to be able to toggle analysis on/off on production.
+% \emph{
+% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
+% }
 
 \heading{Performance Diagnosis}
-Developers use various techniques to understand such problems.
-For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
-These techniques, however, require some degree of \emph{manual} effort:
-  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
-Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.
-
-Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
-A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
-This allows viewing a series of calls as a stream of messages. % that 
-% at each module boundary 
-Module boundaries can be viewed as (virtual) queues of messages that await processing.
-% and applying windowed average operations on a 
-Overwhelming a module causes its ingress queue to grow.
-% MM: related to the sync vs. async
-% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
-At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
-% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.
-
-To make this concrete, we are introducing
-
-\heading{Type and Invariant Checking}
-Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
-Dynamic analysis can be used to generate type assertions or invariants
-For example
-
-To make this concrete, we are using
+Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
+Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
+  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{cheapcomplexity}.
+Maintenance and rewriting can also cause performance regressions between two versions of a library;
+% FIXME: Garbage collection
+  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, performance characteristics can change dramatically~\cite{jest}.
+
+As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
+Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain that can also affect other parts competing for the same resource~\cite{evp}.
+Developers use various techniques to understand such problems---for example, they collect and replay traces against off-line versions of the system, or use statistical profiling to identify hot code-paths.
+These techniques, however, require significant \emph{manual} effort:
+  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.
+
+Having the ability to quickly detect a slowdown and attribute it to a bottlenecked component is key, by toggling on/off a profiling analysis that operates at library boundaries.
+The analysis would wrap library interfaces with logic that generates a model of the current workload.
+Profiling can operate at a high resolution in time and space:
+  (i) at every function call entering a library, and (ii) on hundreds of libraries across an application.
+but does not need to track detailed operations such as direct variable accesses.
+% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
+% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
+Each library wrapper would collect profiling statistics at its own boundary, updating a global structure ordering the libraries' overall needs.
+
+% \emph{
+% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
+% }
+
+\heading{Type Invariant Discovery}
+Extracting typing information is helpful in a variety of ways, as type safety is an important property helpful in variety of scenarios. 
+%and types are lightweight annotations that can be quickly and efficiently checked.
+For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (ii) guide program synthesis and regeneration~\cite{daikon}.
+This is especially problematic in dynamic programming languages:
+  in the absence of static type signatures, there is not much one can say about a object \ttt{o} without executing it and introspecting its properties.
+
+As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
+Given a value returned from a library call---say, a bignum or crypto library---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
+if the type changes, because of a library version change or because of changes in the .
+
+Dynamic analysis can be used to generate type assertions or invariants.
 The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
-
-\heading{Learning, Synthesis, and Regeneration}
-Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
-Dynamic analysis can be used to generate type assertions or invariants
-For example
-The approach has been pioneered by systems such as
-
-To make this concrete, we are using
-The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
+A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
+The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
+The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
+
+% would need to be able 
+% to capture structural subtitling---that is the piecewise
+
+% \heading{Learning, Synthesis, and Regeneration}
 
@@
 
-Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
-
-% , such as an object returned from a module or an exception about to be sent across the network.
-Transformations can be applied to any value in the language. 
-The most general value is an object, a bag of records holding key-value fields;
-  other value types include primitives, functions, and booleans.
-% Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
-More specifically,
-  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
-  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
-  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
-
-The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
-These skeletons provide hooks for end-developers writing analyses.
-Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
-These hooks are then extended or rewritten by developers to
-
-For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
-\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
-The wrappers depend on the intended goal:
-  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.
-
-\subsection{Disassembly}
+% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
+
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
+\caption{
+  \textbf{Base transformation.}
+  \textmd{
+  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
+The meta-function $\alpha$ stands for the locations of analysis hooks.
+  }
+}
+\label{fig:base}
+\end{figure}
+
+% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
+% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
+% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
+% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
+% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
+% The following subsections detail these steps.
+
+\subsection{Dismantling}
 \label{one}
+
+When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
+Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
+For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
+For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
+
+It then dynamically replaces the implementation of\ttt{import}:
+  rather than simply locating and loading a library, the function yields to \sys.
+
+\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
+If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
+If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
+% \omit{---the common case---}
+Otherwise, \sys first invokes the built-in library loader to locate the library.
+
+The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
+Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
+A series of transformations is applied before and after interpretation~\sx{two}.
+
+Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
+\sys must note not to include these constructs in the ones 
+% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
+Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
+To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
+The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
+  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
+
+\begin{figure}[t]
+\centering 
+\includegraphics[width=0.45\textwidth]{./figs/lya_shadowing.pdf}
+\caption{
+  \textbf{Shadowing segments.}
+  \textmd{
+  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
+  }
+  \vspace{-4mm}
+}
+\label{fig:shadowing}
+\end{figure}
 
@@
 
-\subsection{Reassembly}
+For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
+This is achieved in three logical steps:
+(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
+(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
+(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
+Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
+
+\heading{Transformations}
+% , such as an object returned from a module or an exception about to be sent across the network.
+Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
+% Listing~\ref{core-tx} presents a simplified core of the language.
+Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
+More specifically,
+  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
+  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
+  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
+To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
+% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
+
+% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
+% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
+% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
+% At runtime, $f'$ checks $\sigma$:
+%  if the access is allowed, it forwards the call to $f$;
+%  otherwise, it raises an exception.
+% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
+% 
+% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
+% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
+% 
+% % Listing~\ref{core-tx} presents a simplified core of the language.
+% 
+% \begin{itemize}
+% \item
+%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
+% \item
+%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
+% \item
+%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
+% \end{itemize}
+
+Direct field accesses, such as assignments, require custom detection upon dereference.
+To achieve this, \sys wraps fields with an interposition mechanism;
+  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
+% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
+\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
+For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
+
+\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
+To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
+  the unprocessed value is used to create objects, at runtime, that run a different analysis;
+  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
+
+\heading{Context Transformation}
+To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
+
+To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
+Semantically, the context is a map from variable names to their values.
+Thus, \sys creates an auxiliary hash table mapping names to transformed values.
+Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
+Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
+
+%% FIXME: 
+%% While user-defined global variables are stored in well-known locations,\footnote{
+%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
+%% } traversing the global scope for built-in values is generally not possible.
+%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
+%%   different lists exist for different environments and versions of the language.
+%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.
+
+Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
+These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
+Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
+Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
+\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).
+
+\heading{Context Linking}
+To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
+The closure's body starts with a prologue of the form:
+\begin{verbatim}
+  local pint = ctx.print
+  local error = ctx.error
+  ...
+\end{verbatim}
+These statements shadow global variable names by redefining them as local ones.
+The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
+The prologue executes before everything else in the library.
+% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
+This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
+Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
+
+Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
+  these names are now bound to the correct library-local values.
+
+\heading{Library Interface Transformation}
+Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
+% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
+The goal of the final transformation is to track activity at the boundary;
+  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
+
+The final transformation is applied for every new consumer of the library.
+This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
+
+\subsection{Re-assembly}
 \label{three}
 
-% \section{Applications of Analysis}
-% \label{apps}
-
-\section{Implementation: Lya}
+To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
+The central mechanism for resolution is the library cache.
+
+To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
+The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
+A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
+Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
+% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
+For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
+Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
+  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.
+
+% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
+A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
+When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
+It then applies a transformation to the library's return value.
+New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
+
+\section{Implementation of Dialysis for SSJ}
 \label{impl}
 
-We implemented \sys for version 8.9.4 of the Node.js runtime.
-Node.js is a runtime that bun
-
-in about 1.5K lines of JavaScript.
-We summarize where other implementations would diverge in table 1
-
-Individual analysis are implemented using a set of templates that provide initial constructs (see below).
-The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.
-
-The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
-It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
+\vspace{-2mm}
+\caption{
+  \textbf{Example transformations.}
+   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
+\fixme{No UX!}
+}
+\label{fig:tx2}
+\vspace{-2mm}
+\end{figure*}
+
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
+We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
+We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
 
 In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is as a modified version of the runtime, where 
-No-op analyses correspond to the default execution
-  either 
-It is introduced as a backward-compatible, drop-in replacement of the language's module system.
-It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
-
-We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
-However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-  we expand on these at the end of this section~\sx{opportunities}.
-% get second argument, no need to pass arguments around, tricky to 
-% carefull hardcoding of paths, because \sys's code itself is split into modules
-% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
-% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
-% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
-% This is useful, for example, when...
-% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
-
-(1) why node.js
-(2) Create a table of compatibility and show individual aspects
-
-\heading{Module System}
+The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
+The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
+It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
+  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
+  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
+% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
+%   we expand on in the discussion section~\sx{reqs}.
+
+% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+
+\subsection{System Implementation}
+\label{impl1}
+
 Node.js' module system is implemented entirely in JavaScript.
 It exposes \ttt{require}, a global-looking function for importing modules.
-\fixme{Figure} above demonstrates the use of \ttt{require}.
-
-% \begin{lstlisting}[language=js,mathescape,upquote=true]
-% // -------------- [./main.js] -------------
-% // importing point
-% let Point = require("./point.js");
-% Point.create(1, 1).print(); // => [1, 1]
-% 
-% // -------------- [./point.js] ------------
-% let Point = function Point (x, y) {
-%     this.x = x; this.y = y;
-% };
-% Point.prototype.print = function print () {
-%   console.log([this.x, this.y]);
-% };
-% module.exports = {
-%     create:  function create (x, y) {
-%         return new Point(x, y);
-%     }
-% };
-% \end{lstlisting}
-
-In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
-Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
-  the rest is module-private functionality.
-Files and modules are in one-to-one correspondence (each file is treated as a separate module).
-Method \ttt{require} is synchronous (\ie blocking):
-  it will block execution until the module specified is loaded.
-% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
-The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.
-
-\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).
-
-\subsection{Implementation of the Module System}
-\label{c}
-
-At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
-
-\begin{enumerate}
-% \def\labelenumi{\arabic{enumi}.}
-\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
-\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
-\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
-\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
-\end{enumerate}
+At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
 
@@
 \subsection{Applying to Other Environments}
-
-\begin{table}[t]
+\label{reqs}
+
+\begin{table*}[t]
 \center
@@
 }
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
+\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
 \toprule
-                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
+             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
 \midrule
-Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
-Walk objects                    &         &             &        &      &      &      &      &         \\
-Shadow variables                &         &             &        &      &      &      &      &         \\
-Wrap values                     &         &             &        &      &      &      &      &         \\
-Global names                    &         &             &        &      &      &      &      &         \\
+Lua          &                              &                       &                     &                   &                       \\
+JavaScript   &                              &                       &                     &                   &                       \\
+Python       &                              &                       &                     &                   &                       \\
+Ruby         &                              &                       &                     &                   &                       \\
+Haskell      &                              &                       &                     &                   &                       \\
+OCaml        &                              &                       &                     &                   &                       \\
+Rust         &                              &                       &                     &                   &                       \\
+Java         &                              &                       &                     &                   &                       \\
 \bottomrule
@@
 
-First, \sys replaces the implementation of the import statement (\eg \ttt{require});
-  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
-If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
-If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
+% This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
+If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
 % This is simplified by the fact that the import syntax is trivial.
 
-Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).
-
-Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
-They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
+\sys also needs the ability to interpose on values and transform their components.
+This is relatively easy in languages that provide meta-programming capabilities.
+Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
+Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
+Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
+And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
+% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
+% Static programming languages provide different types of support for
+
+\sys makes extensive use of weak maps to support to check for object equality.
+Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
+Hash tables that are indexed by reference are supported in virtually all programming languages.
+An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
+Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
+
+Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
+This is a feature that is universally available in programming languages;\footnote{
+  A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
+}
+Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
+
+To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
+Runtime transformations conveniently unify module identification with interposition:
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-
-Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
-% used for performance monitoring and replica construction:
-  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
-% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.
-
-Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
-Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
-Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
-  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
-Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
-Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
+Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
+Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
+  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 
@@
 \label{principles}
-Dynamic analysis is a general analysis technique that discovering facts about programs;
-  dialysis can be thought as a specif
+Dynamic analysis is a general analysis technique that discovering facts about programs.
 While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
-
+Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
+Which are these cases exactly?
+
+The first class of  
+It is really a quick-and-dirty 
+As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
+Its availability as a global module makes this trivial.
+% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
+
+The second is when the goal is to understand the behavior of third-party code.
+Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
 Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
+Examples include the 
+N-version programming ---all of which would require a custom tool.
 By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
 
-Another use is in the existence of multi-language applications---wrappers and FFI.
+Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
+These limitations is due to several reasons.
+First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
+An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
+Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
+A related problem is the inability to traverse and wrap objects, due to lack of bounds.
+It is unclear how to wrap values without any kind of size information.\footnote{
+  Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
+}
+% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}
+
+That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
+Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
+Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
 

### 2020-01-13 paper/draft.tex
[Minor] corrections
Add times for koa

--- 2020-01-13 paper/draft.tex
@@
  Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  xx    &  1.27   &    0.754      \\
- A1 (TF)            &        &  2.00   &    3.346      \\
- A3 (HF)            &        &  2.684  &    2.684      \\
- A8 (Types)         &        &  2.036  &    2.615      \\     
+ Baseline           &  0.97  &  1.27   &    0.754      \\
+ A1 (TF)            &  1.48  &  2.00   &    3.346      \\
+ A3 (HF)            &  1.30  &  2.684  &    2.684      \\
+ A8 (Types)         &  1.32  &  2.036  &    2.615      \\     
 \bottomrule

### 2020-01-13 paper/draft.tex
Pass over section 2

--- 2020-01-13 paper/draft.tex
@@
 Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
-Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
-  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{cheapcomplexity}.
+Libraries are written by authors with different education, backgrounds, quality standards, and, most importantly, needs:
+  it is not unusual for a weekend project solving a local need to end up as a critical dependency among several open-source projects~\cite{cheapcomplexity}.
 Maintenance and rewriting can also cause performance regressions between two versions of a library;
 % FIXME: Garbage collection
-  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, performance characteristics can change dramatically~\cite{jest}.
+  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, its performance can change dramatically~\cite{jest}.
 
 As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
-Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain that can also affect other parts competing for the same resource~\cite{evp}.
-Developers use various techniques to understand such problems---for example, they collect and replay traces against off-line versions of the system, or use statistical profiling to identify hot code-paths.
+Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain, affecting also other parts of the program competing for the same resources~\cite{evp}.
+Developers use various techniques to understand such problems---\eg collecting and replaying traces against off-line versions of the system, or using statistical profiling to identify hot code-paths.
 These techniques, however, require significant \emph{manual} effort:
-  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.
-
-Having the ability to quickly detect a slowdown and attribute it to a bottlenecked component is key, by toggling on/off a profiling analysis that operates at library boundaries.
-The analysis would wrap library interfaces with logic that generates a model of the current workload.
-Profiling can operate at a high resolution in time and space:
-  (i) at every function call entering a library, and (ii) on hundreds of libraries across an application.
-but does not need to track detailed operations such as direct variable accesses.
+  capturing traces, setting up test-beds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.
+
+Switching on a library-level profiling analysis % that operates at library boundaries
+  would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
+Wrapping library interfaces with profiling logic would collectively construct a model of the current workload.
+Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
 % An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
 % At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
-Each library wrapper would collect profiling statistics at its own boundary, updating a global structure ordering the libraries' overall needs.
+Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.
 
@@
 \heading{Type Invariant Discovery}
-Extracting typing information is helpful in a variety of ways, as type safety is an important property helpful in variety of scenarios. 
+Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
 %and types are lightweight annotations that can be quickly and efficiently checked.
-For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (ii) guide program synthesis and regeneration~\cite{daikon}.
-This is especially problematic in dynamic programming languages:
-  in the absence of static type signatures, there is not much one can say about a object \ttt{o} without executing it and introspecting its properties.
+For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
+This is especially important in dynamic programming languages:
+  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.
 
 As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
-Given a value returned from a library call---say, a bignum or crypto library---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
-if the type changes, because of a library version change or because of changes in the .
-
-Dynamic analysis can be used to generate type assertions or invariants.
-The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
-A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
-The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
-The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
+To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
+Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec. %, common in distributed systems
+This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.
+
+Dynamic analysis can be used to discover such type assertions or invariants.
+The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the library boundaries by observing the execution of the program.
+%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
+Additionally, it would need to support expressions of type unions, for when it witnesses variables holding values of different types, and the decomposing of complex types to their elementary building blocks.
+The former would be captured by sum types---although, in practice, a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
+For the latter, the analysis would perform ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
 
@@
   these frameworks either require highly specialized solutions often outside the core language,
-  do not leverage or offer semantic information at the level of module boundaries, or
+  do not leverage or offer semantic information at the level of library boundaries, or
   lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
@@
 \begin{itemize}
-  \item \textbf{(G1)} Operates at the level of modules, leveraging both the semantics and performance potential that this level of granularity potentially offers.
-  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses on the same language as the program.
-  \item \textbf{(G3)} Can be implemented as a library that bolts onto an existing language runtime environment.
+  \item \textbf{(G1)} Operates at the level of libraries, leveraging both the semantics and performance potential that this level of granularity can potentially offer.
+  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses in the same language as the program.
+  \item \textbf{(G3)} Can be implemented as a library that bolts analyses onto an existing language runtime environment.
+% \item \textbf{(G4)} It does not incur prohibitive overheads, such that it can be switched on and off selectively during runtime execution.
 \end{itemize}
 
-The next section describes program dialysis, a new program analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
+The next section describes program dialysis, a new analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
   the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.
@@
 \centering
-\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
+\includegraphics[width=0.99\textwidth]{./figs/lya_ex2.pdf}
 \vspace{-2mm}
@@
 }
-\label{fig:tx2}
+\label{fig:ex2}
 \vspace{-2mm}
@@
 
-Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
+Fig.~\ref{fig:ex2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
 \sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.

### 2020-01-13 paper/draft.tex

--- 2020-01-13 paper/draft.tex
@@
 \newcommand{\tcn}[1]{}
+
+\definecolor{cdb}{rgb}{0.37, 0.62, 0.63} % cadet blue
 
@@
 
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
+\caption{
+  \textbf{Base transformation.}
+  \textmd{
+  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
+  }
+}
+\label{fig:base}
+\end{figure}
+
 The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
@@
 yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
-chalk~\cite{} 	    & 17.37  & 24.42 &  26.01 &  26.32  & 0.00    \\
-colorette~\cite{}   & 08.10  & 13.85 &  13.41 &  13.16  & 0.00    \\
-mkdirp~\cite{}      & 116.37 & 1959.52 & 1392.64 & 1252 & 0.00    \\
 \bottomrule
@@
  Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  0.97  &  1.27   &    0.754      \\
- A1 (TF)            &  1.48  &  2.00   &    3.346      \\
- A3 (HF)            &  1.30  &  2.684  &    2.684      \\
- A8 (Types)         &  1.32  &  2.036  &    2.615      \\     
+ Baseline           &  xx    &         &               \\
+ A1 (TF)            &        &         &               \\
+ A3 (HF)            &        &         &               \\
+ A8 (Types)         &        &         &               \\     
 \bottomrule
@@
 
-First, \sys replaces the implementation of the import statement (\eg \ttt{require});
-  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
-If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
-If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
+% This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
+If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
 % This is simplified by the fact that the import syntax is trivial.
 
-Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).
+\sys also needs the ability to interpose on values and transform their components.
+This is relatively easy in languages that provide meta-programming capabilities.
+Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
+Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
+Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
+And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
+% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
+% Static programming languages provide different types of support for
 
-Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
-They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
+\sys makes extensive use of weak maps to support to check for object equality.
+Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
+Hash tables that are indexed by reference are supported in virtually all programming languages.
+An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
+Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
+
+Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
+This is a feature that is universally available in programming languages;\footnote{
+  A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
+}
+Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
+
+To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
+Runtime transformations conveniently unify module identification with interposition:
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-
-Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
-% used for performance monitoring and replica construction:
-  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
-% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.
-
-Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
-Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
-Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
-  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
-Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
-Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
+Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
+Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
+  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 

### 2020-01-13 paper/draft.tex

@@
  Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  xx    &         &               \\
- A1 (TF)            &        &         &               \\
- A3 (HF)            &        &         &               \\
- A8 (Types)         &        &         &               \\     
+ Baseline           &  0.97  &  1.27   &    0.754      \\
+ A1 (TF)            &  1.48  &  2.00   &    3.346      \\
+ A3 (HF)            &  1.30  &  2.684  &    2.684      \\
+ A8 (Types)         &  1.32  &  2.036  &    2.615      \\     
 \bottomrule

### 2020-01-13 tst/nodejs_apps/koajsExamples/blog/app.js
Run analysis2

@@ -1,6 +1,6 @@
 lyaConfig = {
     SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 1,
+    analysisCh: 2,
     removejson: ["Promise","toString","unescape","Buffer"],
 };
 let lya = require("../lya/txfm.js");

### 2020-01-14 paper/draft.tex
Pass over design

--- 2020-01-13 paper/draft.tex
@@
 } and implemented in \sys.
-Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
+Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
 It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
@@
 These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
-Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.
+Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
+  internals of module systems~\sx{bg1}.
 
@@
   \textmd{
-    The program on the left imports the \ttt{simple-math} library, shown right, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
-    Several names resolve to functionality provided by the programming language:
-      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
-  }
+    The program on the left imports the \ttt{simple-math} library, shown right, which imports \ttt{log} and exports a \ttt{Math} object.
+    Several names are provided by the programming language:
+      \ttt{import} and \ttt{exports} resolve to library-local values; \ttt{print} resolves to a global value.
+  }
+  \vspace{-8mm}
 }
@@
 % FIXME: add user data
-At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
- In more detail:
+Program dialysis operates by
+  dismantling the program at the boundaries of libraries,
+  applying transformations that insert analysis-specific machinery, and then carefully 
+  reassembling individual components to maintain the original semantics:
 
@@
 Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
-This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
-During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.
+This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
+During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map th provided analysis hooks to the corresponding libraries.
 
@@
 
-  \item \textbf{Re-assembly}
-Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
-The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
-  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
+  \item \textbf{Reassembly}
+Finally, dialysis reassembles individual modified libraries back into the program's original structure.
+The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
+The cache needs to be augmented to support multiple wrappers per library, each capturing a small fragment of the overall analysis.
+% without breaking the program's semantics.
+% ensure every fragment finds its place during dependency reassembly,
 
@@
   \textmd{
-  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
-The meta-function $\alpha$ stands for the locations of analysis hooks.
-  }
+  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{two}.
+The functions $\alpha_1$, $\alpha_2$, and $\alpha_3$ stand for the locations of analysis hooks.
+  }
+  \vspace{-4mm}
 }
@@
 
-When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
-Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
-For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
-For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
-
-It then dynamically replaces the implementation of\ttt{import}:
-  rather than simply locating and loading a library, the function yields to \sys.
-
-\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
+When a dialysis-augmented program starts, it first loads the analysis file provided by the developer. 
+The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
+Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
+To do this, it extracts a static approximation of the dependency graph by traversing library files.
+Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
+It also checks for constructs not associated with libraries---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
+\sys then proceeds to dynamically replace the implementation of \ttt{import} and launch the program:
+  rather than simply locating and loading a library, calls to \ttt{import} now yield to \sys.
+
+For every invocation of \ttt{import} \sys checks the cache~\sx{three} to determine
+  (i) if the library has already been loaded, and
+  (ii) whether it has been loaded with the same analysis hooks.
 If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
@@
 
-The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
-Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
-A series of transformations is applied before and after interpretation~\sx{two}.
-
+The process of loading new libraries includes (i) a phase of reading the necessary source files and (ii) a phase of interpreting them, interspersed by applications of transformations~\sx{two}.
+Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code into an in-memory object.
+% A series of transformations is applied before and after interpretation~\sx{two}.
+
+%FIXME: Need to start with both problems
 Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
-\sys must note not to include these constructs in the ones 
+As these will be part of the same execution context, \sys must note to avoid transforming and wrapping these constructs as part of the analysis.
 % The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
-Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
-To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
+Dialysis frameworks may also want to add analysis-specific keywords not provided by the language.
+To achieve this, \sys wraps each analysis hook with a function whose body starts by defining the expected keywords.
 The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
-  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
+  the key point to remember is that analyses are initially represented as source strings, similar to libraries.
 
@@
 
+%FIXME: Needs examples, especially the context
 For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
 This is achieved in three logical steps:
-(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
+(i) transforming library's context, a mapping from names to values that are available from outside library,
 (ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
 (iii) transforming the return value, \ie the library interface, once the interpretation is complete.
-Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
+Before discussing \emph{where} each transformation is applied, however, we show \emph{how} they are applied.
 
@@
 % , such as an object returned from a module or an exception about to be sent across the network.
-Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
+\sys's transformations boil down to a base transform \ttt{wrap} that traverses and augments values with runtime analysis monitors.
+At a high level, \ttt{wrap} takes a value $v$ and an analysis fragment $\alpha$ and returns a new value $v'$ that has every one of its fields $f$ wrapped:
+   every $f$ is replaced with a method $f'$ that returns the result of calling $f$ after applying the analysis segment corresponding to $v$.
+
+More specifically, \ttt{wrap} can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
 % Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
-More specifically,
+Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}):
+% More specifically,
   (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
@@
   (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
+To avoid cycles during the walk, values are added to a map that is consulted at the beginning of each recursive call.
 % Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
@@
 
-Direct field accesses, such as assignments, require custom detection upon dereference.
+Direct field accesses, such as assignments, require detection upon access.
 To achieve this, \sys wraps fields with an interposition mechanism;
@@
 % Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
-\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
-For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
+Extending a transformed object with a value will start with the value's transformation.
+% \sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
+For example, if a field in a transformed object is assigned a new value, that value has to be be transformed before its to the object.
 
@@
 To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
-  the unprocessed value is used to create objects, at runtime, that run a different analysis;
-  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
+  the unprocessed value is used to create objects, at runtime, that run different analyses;
+  the new value is used to revoke or chain analyses together.
 
 \heading{Context Transformation}
-To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
+To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names to which a library has access.
 
@@
 Thus, \sys creates an auxiliary hash table mapping names to transformed values.
-Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
-Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
+Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc
+Transformed values are created by applying \ttt{wrap} to values in the context, adding the provided analysis hooks.
 
@@
 These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
-Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
+Examples include the library's absolute filename as \ttt{\_\_name\_\_}, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
 Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
@@
 These statements shadow global variable names by redefining them as local ones.
-The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
+The closure accepts an argument \ttt{ctx} that will hold the customized context (see above), assigning its entries to their respective variable names.
 The prologue executes before everything else in the library.
 % When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
-This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
-Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
-
-Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
+This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process:
+  instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
+
+Late-bound, \emph{library}-local variables, such as the absolute filename mentioned during context creation, are the result of applying \ttt{wrap} over variable names in the current scope;
   these names are now bound to the correct library-local values.
@@
 \heading{Library Interface Transformation}
-Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
+Returning the library's value to its consumer amounts to interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
 % TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
-The goal of the final transformation is to track activity at the boundary;
-  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
-
-The final transformation is applied for every new consumer of the library.
-This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
-
-\subsection{Re-assembly}
+The goal of the final transformation is to track activity at the boundary;\footnote{
+  For some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.}
+This final transformation is applied for every new consumer of the library, returning a fresh analysis wrapper.
+This is due to the need for distinguishing between different boundaries of the same library.
+
+The treatment of this feature during reassembly is explained in the next section~\sx{three}.
+
+\subsection{Reassembly}
 \label{three}
@@
 To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
-The central mechanism for resolution is the library cache.
-
-To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
+The central mechanism for this resolution is the library cache.
+
+To support multiple wrappers for a single cached library, the cache is extended by two levels (for a total of three).
 The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
@@
 % A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
-A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
-When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
-It then applies a transformation to the library's return value.
-New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
+A special entry is reserved for the original library value as a string~\sx{two}, so that subsequent transformations can skip loading the library from disk.
+When a new analysis is applied to a library, \sys indexes the cache by library identifier and applies the analysis-specific \ttt{wrap} to the library's context.
+It then adds that result to a slot in the next layer of the cache, indexed by the analysis identifier.
+When a library is already loaded, \sys indexes by analysis to retrieve the (mostly) transformed library corresponding to this analysis.
+It then applies a transformation to the library's return value, and inserts the (finalized) transformed library to the third layer of the cache.
+% New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
 
@@
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4.
+We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses developed with \sys~\sx{impl2}.
+We postpone discussion of how other environments diverge from JavaScript for later~\sx{reqs}.
 

### 2020-01-14 paper/draft.tex
Update implementation

@@
 \newcommand{\dia}{\fra, \ana, and \ass}
+
+\newcommand{\R}{\ttt{R}\xspace}
+\newcommand{\W}{\ttt{W}\xspace}
+\newcommand{\X}{\ttt{X}\xspace}
+\newcommand{\E}{\ttt{X}\xspace}
+\newcommand{\rwx}{\ttt{RWX}\xspace}
 
@@
 %% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
-Additionally, it would need to support expressions of type unions, for when it witnesses variables holding values of different types, and the decomposing of complex types to their elementary building blocks.
-The former would be captured by sum types---although, in practice, a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
-For the latter, the analysis would perform ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
 
@@
    Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
-\fixme{No UX!}
 }
 \label{fig:ex2}
-\vspace{-2mm}
+\vspace{-4mm}
 \end{figure*}
+
+% Fixme switch from libraries to modules?
 
@@
 
-In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
-The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
-
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
-It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
-  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
-  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
-% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-%   we expand on in the discussion section~\sx{reqs}.
+The aforementioned dialysis design can be implemented in either of two ways.
+The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place.
+% with the techniques described earlier.
+The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system;
+  we went with the second approach, as avoiding tight coupling has several benefits:
+  it does not require \sys's users to have a second Node copy only for running analyses;
+  it removes \sys's developers from the critical path of updates between the Node developers and its users; 
+  and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
+The primary drawback was missing a few  opportunities for runtime-performance and development-effort.
 
@@
 
-Node.js' module system is implemented entirely in JavaScript.
-It exposes \ttt{require}, a global-looking function for importing modules.
-At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
-(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
-(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
-(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
-(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+Node's module system is implemented entirely in JavaScript, exposing a library-local \ttt{require} function for importing modules.
+Loading a fresh module with \ttt{require("foo");} corresponds to the following five stages, all of which are augmented by \sys:
+(R) Resolution: identify the file to which the module specified corresponds, locate it in the file-system, and assign its absolute path as a module identifier.
+(L) Loading: depending on the file type, identify the corresponding loader---\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc
+% Identifiers are absolute paths.
+(W) Wrapping: wrap the module so local names do not escape the module's scope and Node's module-local names get resolved.
+(E) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+(C) Caching: add the module to a handful of module-related caches, for purposes of consistency and performance.
 
@@
 \sys interposes on all of these steps to facilitate transformations.
-Wrapping (3) and evaluation (4) are particularly interesting, because they allow \sys to interpose at the module boundary during runtime.
-Before a module's code is evaluated, the Node.js module loader wraps the module so that
-  (i) it keeps top-level variables (defined with \ttt{var}, \ttt{const} or \ttt{let}) scoped to the module rather than the global object; and
-  (ii) it provides some global-looking variables that are actually specific to the module, such as the \ttt{module} and \ttt{exports} objects that the implementor can use to export values from the module and convenience variables---such as \ttt{\_\_filename} and \ttt{\_\_dirname}  containing the module's absolute filename and directory path, respectively.
-True globals remaining are
-  (i) the global objects as defined by the EcmaScript standard (\eg \ttt{Object}, \ttt{Function}, \ttt{Math}); and
-  (ii) Node.js-specific globals (\eg \ttt{console}, \ttt{process}, \ttt{timer}).
-These globals require further interposition.
+Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
+If the module's type is one \sys can analyze, it fetches the corresponding analysis during loading (L).
+Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
+\sys replaces Node's wrapper function in order to add a last variable in the function definition, \ttt{CTX}.
+\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.js:
+  (i) identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit;
+  (ii) Node's global names are described at various parts of the documentation; and
+  (iii) library-local required close inspection of Node's internals; fortunately, these were only five names.
+
+% Before a module's code is evaluated, the Node.js module loader wraps the module so that
+%   (i) it keeps top-level variables (declared with \ttt{var}, \ttt{const} or \ttt{let}) scoped to the module rather than the global object; and
+%   (ii) it provides some global-looking variables that are actually specific to the module, such as the \ttt{module} and \ttt{exports} objects that the implementor can use to export values from the module and convenience variables---such as \ttt{\_\_filename} and \ttt{\_\_dirname}  containing the module's absolute filename and directory path, respectively.
+% True globals remaining are
+%   (i) the global objects as defined by the EcmaScript standard (\eg \ttt{Object}, \ttt{Function}, \ttt{Math}); and
+%   (ii) Node.js-specific globals (\eg \ttt{console}, \ttt{process}, \ttt{timer}).
+% These globals require further interposition.
+
+% TODO: Talk about recipe file, that could be kept along with the module identifier
 
@@
 
-\sys hooks into the wrapper function (the last variable in the function definition, \ttt{CTX}).
-This trivial source-to-source transformation re-defines global variables as module-locals and initializes them with \sys-augmented values.
-For example, \ttt{console} in the context of the module will be an \sys-created object that allows \sys to interpose on it.
-Evaluation of the module passes an additional value to this function, which is the modified context.
-As a result, any changes to the top-level objects and any global variables are accessible from the within the module.
+We found it useful to add an option for white- and black-listing libraries.
+The configuration object accepts \ttt{only} and \ttt{not} expressions that indicate whether a module identifier will be part of the analysis.
+These expressions contain sets of sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
+Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose them to users.
+Examples of use include blacklisting built-in libraries or white-listing only the newest-imported library.
+% This is useful, for example, when...
 
@@
 % carefull hardcoding of paths, because \sys's code itself is split into modules
-% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
-% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
-% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
-% This is useful, for example, when...
-% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
 
 %% TODO: implementation
-%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
+
+Fig.~\ref{fig:ex2} exemplifies \sys's transformation techniques in the context of JavaScript.
+\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
+
+\subsection{Individual Analyses}
+\label{impl2}
+
+Individual analysis are implemented using a set of templates that provide initial constructs.
+%% Individual transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
 %% These skeletons provide hooks for end-developers writing analyses.
@@
 %% These hooks are then extended or rewritten by developers to
-
-Fig.~\ref{fig:ex2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
-\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
-The precise wrappers depend on the intended analysis, reviewed next.
-
-\subsection{Individual Analyses}
-\label{impl2}
-
-Individual analysis are implemented using a set of templates that provide initial constructs (see below).
 \sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
-As a result, code that is specific to individual analyses averages about 20--30 lines.
+Individual analyses are between 100--200 lines of code, but a significant part of this code is common across analyses.
+
+As the three analyses are quite complex to be shown in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
+
+\begin{verbatim}
+let fs = require('fs');
+let count = {};
+forevery.global.in(/serial/) = {
+  pre: (name, path, _) => {
+    let id = resolve(name, path);
+    count[id] = count[id]?  count[id] + 1 : 1;
+  }
+};
+process.on('exit', () => {
+  fs.writeFileSync('acl.json',
+                   'utf-8',
+                   JSON.stringify(count));
+});
+\end{verbatim}
+
+\noindent
+\sys-provided \ttt{forevery} generates sets of names succinctly.
+The \ttt{in} field is a method that takes a regular expression matching module identifiers.
+If not empty, \ttt{pre} and \ttt{post} hooks are called before and after each access of the elements specified in the set.
+Finally, \ttt{resolve} is a method for traversing an object given a path within that object.
+Upon program exit, the results are written to disk, all using the expected Node APIs.
 
 \heading{Security Analysis}
-To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
-The language of the analysis is given in the following grammar:
-
-\begin{alltt}
-  str:  <identifier in JS>
-  libs: [ str ]
-  path: str `.` path
-  mode: P{ R | W | X }
-  body: { [ path: mode ]: path \(\in\) mods}
-  analysis:  mods body
-\end{alltt}
+To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
+The analysis treats built-in libraries and global variables as modules,
+% and generates a list of permissions for each of their fields.
+and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
+ (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
+ (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
+ (iii)  an execute permission (\X) indicates that a consumer to executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).
+
+The resulting permission sets are organized as a collection of maps, one per library, each indexed by object-paths such as \ttt{Math.add: RX}.
+% that correspond to values of other modules or global-like language names.
 
 \heading{Performance Diagnosis}
-
-\begin{equation}
-\label{eq:2}
-R_{new} =
-\begin{cases}
-  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
-  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
-\end{cases}
-\end{equation}
-
-Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
-However, after scale-in, the system often ends up just scaling out the same module.
-To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.
-
-% ATTRIBUTION
-Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
-For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
-% \eat{ is \ttt{A}-internal and how much}
-comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
-
-\heading{Invariant Discovery}
-Describe specific type system
+To conduct performance diagnosis, we develop a profiling analysis that operates at two levels:
+ (i) module-boundary wrappers that collecting profiling statistics for calls between modules by wrapping module interfaces; and
+ (ii) an aggregator function that collects statistics from all boundary wrappers and generates a model of library load under the current workload.
+
+Boundary wrappers operate at a higher-frequency intervals than the aggregator, which operates on summaries.
+Their analysis focuses on function values (\eg functions, methods, constructors), skipping all other direct field accesses.
+Functions are wrapped with prologue and epilogue wrappers that record statistics from the Node.js runtime---for now, a frequency counter and a timer between prologue-to-epilogue invocations.
+% Many statistics are available by the Node.js runtime, including memory and garbage-collection statistics, 
+Boundary wrappers summarize these statistics by periodically sending a windowed, weighted average of call latencies to the aggregator function.
+
+% Wrappers record statistics about the their encapsulated functions as well as queue characteristics of outstanding calls.
+% The wrapper epilogue has access to several raw metrics related to profiling (Tab.~\ref{tab:metrics}).
+% These metrics are viewed as a windowed average that priori
+
+Interestingly, profiling functions at the boundary cannot ``see through'' libraries to correctly attribute load among a library and its dependencies.
+For example, a boundary wrapper \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency comes from \ttt{B}.
+Fortunately, the aggregator understands the dependency structure and can approximate how much of the latency comes from each module.
+% Such a approximation is more complicated than a simple subtraction, as a module may invoke interfaces from multiple modules at the same time.
+% Having an analysis fragment per library consumer, however, alleviates much of the problem.
+
+% FIXME: Snapshot results
+% [serial , whatever, pizza, ...]
+
+\heading{Type Invariant Discovery}
+To infer type invariants for serialization specifications, we develop a simple type system and use our analysis to map values to types.
+
+The type system is modeled after the simply-typed lambda calculus augmented with:
+  (i) unions (sum types), such as \ttt{a | b | c}; 
+  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}; and
+  (iii) a \ttt{native} type for values that cannot be serialized, like \ttt{console.log}.
+Support for union types is useful for when our analysis witnesses variables holding values of different types---although, in practice,  programs tend to make calls of the same type across their entire lifetime~\cite{daikon}.
+
+Our implementation also uses a base set of JavaScript types and rules to deconstruct complex types into their elementary building blocks.
+% Knowing how to deconstruct a type to its structural primitives allows walking values---
+For example, the analysis extracts that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
+% To achieve this, the analysis makes use of introspection to identify
+
+% leftpad: (string | number) -> number -> (string | null) -> string
 

### 2020-01-14 paper/draft.tex
Update discussion

@@
 {\rm Anonymous Author(s)}\\
-\normalsize{Submission \#225, 12 pages}\\
+\normalsize{Submission \#225, 11 + 2 pages}\\
 % \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
@@
 A single application today often incorporates multiple libraries written and published by several different authors.
-To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
-These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
+To make the difficulties of analyzing such library-overreliant software more concrete, we describe three example analyses~\sx{examples}.
+These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules~\sx{goals}.
 Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
@@
 \subsection{Motivating Examples}
+\label{examples}
 
@@
 \subsection{Design Goals}
+\label{goals}
 
@@
 
-Library dialysis, as implemented in \sys, depends on a few features available in the programming language.
-In this section we describe how to develop the same solution on other environments.
-In the second part of this section, we reflect on some of the current limitations of the system.
-
-\subsection{Applying to Other Environments}
+Program dialysis depends on a few features provided by the programming language.
+In this section, we start by describing its requirements~\sx{reqs} and then reflect on some of its strengths and weaknesses~\sx{principles}.
+
+\subsection{Applying \sys to Other Environments}
 \label{reqs}
 
-\begin{table*}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{Language features used and their availability in other languages}.
-    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
-  }
-}
-\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
-\toprule
-             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
-\midrule
-Lua          &                              &                       &                     &                   &                       \\
-JavaScript   &                              &                       &                     &                   &                       \\
-Python       &                              &                       &                     &                   &                       \\
-Ruby         &                              &                       &                     &                   &                       \\
-Haskell      &                              &                       &                     &                   &                       \\
-OCaml        &                              &                       &                     &                   &                       \\
-Rust         &                              &                       &                     &                   &                       \\
-Java         &                              &                       &                     &                   &                       \\
-\bottomrule
-\end{tabular*}
-\label{tab:compat}
-\vspace{-5mm}
-\end{table*}
+% \begin{table*}[t]
+% \center
+% \footnotesize
+% \setlength\tabcolsep{3pt}
+% \caption{
+%   \footnotesize{
+%     \textbf{Language features used and their availability in other languages}.
+%     Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
+%   }
+% }
+% \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
+% \toprule
+%              &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
+% \midrule
+% Lua          &                              &                       &                     &                   &                       \\
+% JavaScript   &                              &                       &                     &                   &                       \\
+% Python       &                              &                       &                     &                   &                       \\
+% Ruby         &                              &                       &                     &                   &                       \\
+% Haskell      &                              &                       &                     &                   &                       \\
+% OCaml        &                              &                       &                     &                   &                       \\
+% Rust         &                              &                       &                     &                   &                       \\
+% Java         &                              &                       &                     &                   &                       \\
+% \bottomrule
+% \end{tabular*}
+% \label{tab:compat}
+% \vspace{-5mm}
+% \end{table*}
 
 The techniques presented in this paper are applicable to any programming language.
-We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
-  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
-	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
-In this section, we discuss the requirements for building \sys over other runtime environments.
+We chose the JavaScript ecosystem % to evaluate the feasibility of our approach,
+primarily because
+  (i) it boasts the largest collection of libraries~\cite{modulecounts} and
+	(ii) we had prior experience developing more sophisticated version of the security and performance analyses.
+We now expand on the requirements for developing dialysis over other runtime environments.
 % FIXME: All these features have to have been discussed earlier
 
-By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
-All major programming languages can support these five features in a variety of ways, as described below.
-
-First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
+By operating on library boundaries, dialysis uses a few special language features, supported by all major programming languages.
+First, \sys needs to re-wire the \ttt{import} keyword:
 % This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
-If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
-If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
+  if it is a function (\eg JavaScript, Scheme, Racket), rewiring amounts to an overwrite;
+  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (at module-loading).
 % This is simplified by the fact that the import syntax is trivial.
 
-\sys also needs the ability to interpose on values and transform their components.
-This is relatively easy in languages that provide meta-programming capabilities.
+It also needs the ability to interpose on values and transform their components.
+% This is relatively easy in languages that provide meta-programming capabilities.
 Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
-Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
-Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
-And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
+Compiled languages would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
+Examples include templates and macro expansions such as Haskell's Template and Rust's macro system.
+% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities. %, allowing considerable freedom in the choice of implementation.
 % Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
@@
 
-\sys makes extensive use of weak maps to support to check for object equality.
-Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
-Hash tables that are indexed by reference are supported in virtually all programming languages.
-An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
-Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
-
-Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
-This is a feature that is universally available in programming languages;\footnote{
+\sys makes extensive use of hash-maps---to check for object equality, for cycles during traversal, and for prior wrapping.
+Hash-maps are supported by every programming language; many support storing weak references, which avoid affecting object reclamation in garbage-collected environments, and can be created either explicitly (\eg Python) or implicitly by using a ``weak'' structure (\eg JavaScript).
+% An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
+% Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
+
+Finally, \sys makes use of variable shadowing to hide the original, unmodified versions of values---a universal feature.\footnote{
   A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
 }
-Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
-
-To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
+% Differences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
+
+To conclude, all major languages provide facilities to support dialysis---albeit with a different level of convenience.
 Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
@@
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
-Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
-  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
+Compiled languages have other benefits, namely that applying transformations statically ameliorates their runtime overhead.
+% and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 

### 2020-01-14 paper/draft.tex
Opinions

@@
 \label{principles}
-Dynamic analysis is a general analysis technique that discovering facts about programs.
-While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
-Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
-Which are these cases exactly?
-
-The first class of  
-It is really a quick-and-dirty 
-As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
-Its availability as a global module makes this trivial.
-% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
-
-The second is when the goal is to understand the behavior of third-party code.
-Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
-Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
-Examples include the 
-N-version programming ---all of which would require a custom tool.
-By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
+% Dynamic analysis is a general technique for discovering facts about programs.
+While heavy-weight dynamic analysis provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand.
+% Dialysis can be thought as a coarser version of analysis stemming from natural library boundaries---a level of granularity that seems just right for certain problems.
+% Which are these cases exactly?
+
+% pressing need, lightweight, 
+% multiplies lyas power
+Dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
+It can help identify (or narrow down) the source of a problem quickly, by swiftly isolating homegrown code from standard and third-party libraries, by requiring a few lines of analysis-specific code inlined, and by leveraging the developer's expertise in their language of choice.
+By operating at coarser granularity, using the vanilla optimized runtime, and by toggling parts of the analysis on and off, it provides the ability to perform the analysis online.
+Finally, dialysis deconstructs programs only at library boundaries, a naturally coarser granularity that is just the right level for certain problems.
+% a granularity that is well-suited for several tasks.
+% libraries are a convenient level of abstraction---or the point where abstractions 
+% monitors all around a library
+
+% The first class of problems where dialysis shines is quick-and-dirty insights;
+% Even if dialysis doesn't solve the problem, it can quickly narrow it down to a certain corner of the application, at which point the cost of a heavy-weight solution is lower.
+% % This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
+% 
+% The second is when the goal is to understand the behavior of third-party code.
+% Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
+% Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
+% Examples include the 
+% N-version programming ---all of which would require a custom tool.
+% By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
 
 Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
-These limitations is due to several reasons.
+These limitations are due to several reasons.
 First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
-An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
-Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
-A related problem is the inability to traverse and wrap objects, due to lack of bounds.
-It is unclear how to wrap values without any kind of size information.\footnote{
+An important feature of the wrapping techniques presented in this paper is that they can track a library's full observable behavior.
+Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in the program's address space.
+A related problem is C's inability to traverse and wrap objects;
+  due to lack of runtime information about size and structure, it is unclear how to traverse and transform them.\footnote{
   Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
@@
 
-That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
-Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
-Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
+% That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
+% Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
+% Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
 

### 2020-01-14 paper/draft.tex
Update related work

@@
 
-In this section, we compare \sys to previously proposed systems in several categories.
-For a comparison between dialysis and dynamic analysis, we refer the reader to the previous section~\sx{principles}.
+The previous section~\sx{principles} offers a principles-comparison between dynamic analysis and dialysis.
+This section we turn to a technical comparison of \sys to prior systems.
 
@@
 There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
-The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
-On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
-This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
-  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
-They are also not embeddable in existing applications in a runtime-agnostic manner.
-These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.
-
-NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
-NodeProf stands at a different point in the analysis design space---more powerful than \sys, but with significantly more effort.
-It statically instruments the program's AST (rather than the code), making it easier to maintain compared to source changes but assuming some knowledge of the Graal and Truffle APIs and requiring recompilation of the Java hooks.
-Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
-Nevertheless, NodeProf's approach shares similarities with \sys, including decoupling from the source code, overheads lower than code instrumentation, and can on/off toggling during execution.
+Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot} are the most popular and feature fine-grained code-level instrumentation powerful enough to record and replay entire program executions.
+This power comes at a significant inconvenience: % as they need to virtualize the entire execution environment.
+  they incur 2--3 order-of-magnitude slowdown and are not embeddable in a runtime-agnostic manner.
+% source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
+These features are antithetical to \sys, which leverages basic programming-language primitives to insert high-performance analysis hooks completely transparently to the runtime environment.
+
+NodeProf~\cite{javascript3} is a fine-grained dynamic analysis % atop Truffle~\cite{} and running on top of Graal.js~\cite{graal}, a Node.js-compatible runtime.
+  standing at a different point in the analysis design space---more powerful than \sys, but with a significantly higher effort to use.
+It instruments a program's AST (rather than the code) statically, % making it easier to maintain compared to source changes but
+  limiting the use of dynamic features, assuming knowledge of the underlying Graal~\cite{graal} and Truffle~\cite{truffle} APIs, and requiring recompilation of the Java hooks.
+% Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
+Nevertheless, some of NodeProf's goals are similar to \sys such as lowering overheads and toggling analysis during execution.
 %FIXME: Lya is also limited (i) by dynamic features such as reflection, because they're gonna hit the wrapper and (ii) the equality and other primitive operators
 
-Aran~\cite{javascript1}, an implementation sketch of proxy-based analysis, leverages JavaScript's \ttt{with} primitive to wrap custom contexts.
-\sys works at the module boundaries (at a potentially coarser granularity) without any special language constructs.
-
-JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
-It allows users to write access control contracts, policies that execute at runtime.
-It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
-Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.
-
-\heading{Dynamic Analysis for WebAssembly}
-Related to JavaScript is WebAssembly, a standardized subset of JavaScript target, designed to serve as a compilation target.
-The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of the same goals with \sys---\eg lowering the effort required to write analyses, and providing hooks for observation rather than manipulation.
-Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
-  Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
-  whereas our explicit goal is to write analysis in the same language as the program~\sx{goals}---that is, dialysis implemented for Python would be using Python abstractions.
-Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.
-
-\heading{Dynamic Instrumentation}
-Dialysis is related to dynamic instrumentation frameworks~\cite{pin, valgrind} that wrap incrementally parts of the program to extract information.
-Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
-  \sys starts by wrapping a library during import, adding a small overhead on its loading time.
-This overhead is only a small fraction of the time required to locate and load the module from disk.
-However, these systems operate at a much lower level (binary) than \sys, and are not available to high-level runtime environments as a pluggable library.
-
-DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} are systems for instrumenting JVM byte code.
-These too work at a lower level than \sys,
-
-\heading{Program Transformations}
+The Aran sketch~\cite{javascript1} proposes proxy-based analysis coupled with JavaScript's unusual \ttt{with} primitive for wrapping custom contexts.
+\sys works at the module boundaries, a potentially coarser granularity, without any unusual language constructs.
+
+JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework;
+\fixme{Rather than extracting accesses, it arms developers with the ability to write access control contracts (\ie executable partial specifications)}.
+This capability is complimentary to \sys's security analysis model~\sx{examples}, illustrating a need for a general-purpose online analysis framework.
+% \ie their analysis can be implemented on top of \sys with significantly less effort.
+% build around proxies.
+
+JavaScript is related to WebAssembly, a standardized subset of JavaScript target designed to serve as a compilation target.
+The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of \sys' goals---\eg low-effort analysis and API for observation rather than manipulation.
+% Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
+%   Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
+%   whereas \sys's partial goal is supporting analysis in the same language as the program~\sx{goals}. % ---that is, dialysis implemented for Python would be using Python abstractions.
+Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims for heavyweight instrumentation.
+
+\sys has some resemblance to dynamic instrumentation frameworks~\cite{pin, valgrind, disl, roadrunner}.
+These wrap basic blocks of a program incrementally and right before execution, similar in vein to how \sys wraps libraries.
+% Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
+%   \sys starts by wrapping a library during import, adding a small overhead on its loading time.
+However, they operate at a much lower level (binary) than \sys, are much more detailed and heavy-weight, and are not available to high-level runtime environments as a language-aware library.
+
 % Add our work
@@
 More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
-While \sys makes extensive use of metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
+While \sys uses metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
 % self element
 
-\heading{Fracture and Recombination}
 Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
@@
 Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
-Applications today routinely pull together hundreds of libraries, making their analysis difficult
-
-due to the very same abstraction and modularity principles that have benefited software engineering for decades.
-
-security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.
-
-This paper introduces \emph{module dialysis}, an approach 
-corser
-approach towards coarse-grained
-This is achieved using a set of programmatic \emph{transformations} parametrizable by optional \emph{distribution recipes}.
-These operate at module boundaries during runtime to collect profiling information, detect bottlenecked components, and dynamically separate and coalesce parts of the application.
-
-We want to emphasize that \sys is open source, available to experiment with more applications and analyses
+Applications today routinely pull together hundreds of libraries, making their analysis difficult.
+To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
+Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
+% is a general technique that
+Contrary to heavy-weight dynamic analysis that provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand, dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
+
+We note that \sys is open source, available for experimentation with other applications and analyses.
 

### 2020-01-14 paper/draft.tex

--- 2020-01-14 paper/draft.tex
@@
 
-\newcommand{\R}{\ttt{R}\xspace}
-\newcommand{\W}{\ttt{W}\xspace}
-\newcommand{\X}{\ttt{X}\xspace}
-\newcommand{\E}{\ttt{X}\xspace}
-\newcommand{\rwx}{\ttt{RWX}\xspace}
-
 % FIXME:
@@
 {\rm Anonymous Author(s)}\\
-\normalsize{Submission \#225, 11 + 2 pages}\\
+\normalsize{Submission \#225, 12 pages}\\
 % \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
@@
 } and implemented in \sys.
-Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
+Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
 It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
@@
   a profiling analysis showing bottlenecked modules,
-% a synthesis-oriented analysis on input-output data,
-  and an analysis extracting union-based type invariants.
+  a synthesis-oriented analysis on input-output data, and
+  an analysis enforcing a static union-based type system at runtime.
 This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
@@
 \begin{itemize}
-\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
-\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
-\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
+\item \S\ref{bg} characterizes the shared needs of four case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
+\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
+\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
 \item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
@@
 A single application today often incorporates multiple libraries written and published by several different authors.
-To make the difficulties of analyzing such library-overreliant software more concrete, we describe three example analyses~\sx{examples}.
-These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules~\sx{goals}.
-Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
-  internals of module systems~\sx{bg1}.
+To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
+These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
+Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.
 
@@
 
-\begin{figure}[t]
-\raggedleft 
-\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
-\caption{
-  \textbf{Example of a library import.}
-  \textmd{
-    The program on the left imports the \ttt{simple-math} library, shown right, which imports \ttt{log} and exports a \ttt{Math} object.
-    Several names are provided by the programming language:
-      \ttt{import} and \ttt{exports} resolve to library-local values; \ttt{print} resolves to a global value.
-  }
-  \vspace{-8mm}
-}
-\label{fig:ex1}
-\end{figure}
-
-A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
+A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
 This functionality falls into two categories:
-  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) provided by other developers sharing code others might find useful.
-Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).
-
-From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
-% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
-This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
-The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
-Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
+  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
+  or (ii) is provided by other developers sharing code others might find useful.
+Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
+
+From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
+What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
+This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
+The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
 % , as shown on line \fixme{XX},
@@
 
-From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
-Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
-Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
-This process starts by locating the library in the file system % or across the network,\footnote{
-%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
-% }
+From the language's perspective, the loading process is achieved in several steps. 
+In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
+Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
+This process starts by locating the library in the file system or across the network,\footnote{
+  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
+}
 by resolving relative or absolute identifiers.
@@
 The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
-The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
-Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.
+The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
+Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.
 
 There is significant variation, but a few features are common across many implementations.
-A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
-The cache serves a dual purpose:
-  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
-Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
+A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
+The library cache serves a dual purpose:
+  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
+Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
 An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
-The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
+As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
+The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
 These features complicate library-level analysis, especially in interpreted programming languages.
@@
 \subsection{Motivating Examples}
-\label{examples}
 
@@
   (i) an allow/deny security analysis,
-  (ii) a performance-profiling analysis showing bottlenecked libraries, and
-% (iii) a synthesis-oriented analysis on input-output data, and
-  (iii) an analysis extracting runtime type invariants.
+  (ii) a profiling analysis showing hot libraries,
+  (iii) a synthesis-oriented analysis on input-output data, and
+  (iv) an analysis enforcing a static union-based type system at runtime.
 These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
@@
 The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
-Both bugs and malicious code in libraries create attack vectors, exploitable long after libraries reach their end-users.
-As library boundaries disappear at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
+Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
+As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
 Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
@@
 
-As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
-Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
-Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
-Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.
-
-Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
-Analyzing the behavior \emph{within} the library itself is not critical:
-  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
-Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
-Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
+As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
+As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
+At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
+  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
+Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
 % The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
 
- %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
- %% % FIXME more about the policy, tracking arguments too
- %%  indicating the resources touched by that library 
- %% it seems critical to be able to toggle analysis on/off on production.
+To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
+% FIXME more about the policy, tracking arguments too
+A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
+Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.
+
 % \emph{
@@
 Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
-Libraries are written by authors with different education, backgrounds, quality standards, and, most importantly, needs:
-  it is not unusual for a weekend project solving a local need to end up as a critical dependency among several open-source projects~\cite{cheapcomplexity}.
-Maintenance and rewriting can also cause performance regressions between two versions of a library;
+Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
+  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
+Maintenance and rewriting can cause performance regressions between two versions of a library.
 % FIXME: Garbage collection
-  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, its performance can change dramatically~\cite{jest}.
-
-As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
-Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain, affecting also other parts of the program competing for the same resources~\cite{evp}.
-Developers use various techniques to understand such problems---\eg collecting and replaying traces against off-line versions of the system, or using statistical profiling to identify hot code-paths.
-These techniques, however, require significant \emph{manual} effort:
-  capturing traces, setting up test-beds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.
-
-Switching on a library-level profiling analysis % that operates at library boundaries
-  would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
-Wrapping library interfaces with profiling logic would collectively construct a model of the current workload.
-Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
-% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
-% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
-Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.
+Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.
+
+As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
+Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
+The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).
+
+The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
+An analysis 
+% A key observation is the semantic isomorphism between calling a function and passing a message
+% This allows viewing a series of calls as a stream of messages.
+% Module boundaries can be viewed as (virtual) queues of messages that await processing.
+treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
+Overwhelming a module causes its ingress queue to grow.
+At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
+Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
+Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
+Profile generation can operate at a high resolution in time and space:
+  (i) at every function call entering a module, and (ii) on thousands of modules across an application.
 
@@
 
-\heading{Type Invariant Discovery}
-Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
-%and types are lightweight annotations that can be quickly and efficiently checked.
-For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
-This is especially important in dynamic programming languages:
-  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.
-
-As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
-To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
-Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec. %, common in distributed systems
-This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.
-
-Dynamic analysis can be used to discover such type assertions or invariants.
-The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the library boundaries by observing the execution of the program.
-%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
+\heading{Invariant Discovery}
+Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
+Dynamic analysis can be used to generate type assertions or invariants
+For example
+e.
+For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
+This is especially problematic in dynamic programming languages:
+  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.
+
+To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
+Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
+if the type changes, because of a library version change or because of changes in the .
+
+The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
+A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
+The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
+The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
 
@@
 \subsection{Design Goals}
-\label{goals}
-
-We have briefly introduced three motivating analyses for extracting information about an application's dependencies.
+
+We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
 While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
   these frameworks either require highly specialized solutions often outside the core language,
-  do not leverage or offer semantic information at the level of library boundaries, or
+  do not leverage or offer semantic information at the level of module boundaries, or
   lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
@@
 \begin{itemize}
-  \item \textbf{(G1)} Operates at the level of libraries, leveraging both the semantics and performance potential that this level of granularity can potentially offer.
-  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses in the same language as the program.
-  \item \textbf{(G3)} Can be implemented as a library that bolts analyses onto an existing language runtime environment.
-% \item \textbf{(G4)} It does not incur prohibitive overheads, such that it can be switched on and off selectively during runtime execution.
+  \item \textbf{(G1)} Operates at the level of modules, leveraging both the semantics and performance potential that this level of granularity potentially offers.
+  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses on the same language as the program.
+  \item \textbf{(G3)} Can be implemented as a library that bolts onto an existing language runtime environment.
 \end{itemize}
 
-The next section describes program dialysis, a new analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
+The next section describes program dialysis, a new program analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
   the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.
@@
 % FIXME: add user data
-Program dialysis operates by
-  dismantling the program at the boundaries of libraries,
-  applying transformations that insert analysis-specific machinery, and then carefully 
-  reassembling individual components to maintain the original semantics:
+At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
+ In more detail:
 
@@
 Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
-This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
-During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map th provided analysis hooks to the corresponding libraries.
+This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
+During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.
 
@@
 
-  \item \textbf{Reassembly}
-Finally, dialysis reassembles individual modified libraries back into the program's original structure.
-The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
-The cache needs to be augmented to support multiple wrappers per library, each capturing a small fragment of the overall analysis.
-% without breaking the program's semantics.
-% ensure every fragment finds its place during dependency reassembly,
+  \item \textbf{Re-assembly}
+Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
+The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
+  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
 
@@
   \textmd{
-  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{two}.
-The functions $\alpha_1$, $\alpha_2$, and $\alpha_3$ stand for the locations of analysis hooks.
-  }
-  \vspace{-4mm}
+  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
+The meta-function $\alpha$ stands for the locations of analysis hooks.
+  }
 }
@@
 
-When a dialysis-augmented program starts, it first loads the analysis file provided by the developer. 
-The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
-Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
-To do this, it extracts a static approximation of the dependency graph by traversing library files.
-Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
-It also checks for constructs not associated with libraries---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
-\sys then proceeds to dynamically replace the implementation of \ttt{import} and launch the program:
-  rather than simply locating and loading a library, calls to \ttt{import} now yield to \sys.
-
-For every invocation of \ttt{import} \sys checks the cache~\sx{three} to determine
-  (i) if the library has already been loaded, and
-  (ii) whether it has been loaded with the same analysis hooks.
+When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
+Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
+For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
+For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
+
+It then dynamically replaces the implementation of\ttt{import}:
+  rather than simply locating and loading a library, the function yields to \sys.
+
+\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
 If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
@@
 
-The process of loading new libraries includes (i) a phase of reading the necessary source files and (ii) a phase of interpreting them, interspersed by applications of transformations~\sx{two}.
-Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code into an in-memory object.
-% A series of transformations is applied before and after interpretation~\sx{two}.
-
-%FIXME: Need to start with both problems
+The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
+Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
+A series of transformations is applied before and after interpretation~\sx{two}.
+
 Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
-As these will be part of the same execution context, \sys must note to avoid transforming and wrapping these constructs as part of the analysis.
+\sys must note not to include these constructs in the ones 
 % The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
-Dialysis frameworks may also want to add analysis-specific keywords not provided by the language.
-To achieve this, \sys wraps each analysis hook with a function whose body starts by defining the expected keywords.
+Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
+To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
 The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
-  the key point to remember is that analyses are initially represented as source strings, similar to libraries.
+  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
 
@@
 
-%FIXME: Needs examples, especially the context
 For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
 This is achieved in three logical steps:
-(i) transforming library's context, a mapping from names to values that are available from outside library,
+(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
 (ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
 (iii) transforming the return value, \ie the library interface, once the interpretation is complete.
-Before discussing \emph{where} each transformation is applied, however, we show \emph{how} they are applied.
+Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
 
@@
 % , such as an object returned from a module or an exception about to be sent across the network.
-\sys's transformations boil down to a base transform \ttt{wrap} that traverses and augments values with runtime analysis monitors.
-At a high level, \ttt{wrap} takes a value $v$ and an analysis fragment $\alpha$ and returns a new value $v'$ that has every one of its fields $f$ wrapped:
-   every $f$ is replaced with a method $f'$ that returns the result of calling $f$ after applying the analysis segment corresponding to $v$.
-
-More specifically, \ttt{wrap} can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
+Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
 % Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}):
-% More specifically,
+Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
+More specifically,
   (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
@@
   (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-To avoid cycles during the walk, values are added to a map that is consulted at the beginning of each recursive call.
+To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
 % Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
@@
 
-Direct field accesses, such as assignments, require detection upon access.
+Direct field accesses, such as assignments, require custom detection upon dereference.
 To achieve this, \sys wraps fields with an interposition mechanism;
@@
 % Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
-Extending a transformed object with a value will start with the value's transformation.
-% \sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
-For example, if a field in a transformed object is assigned a new value, that value has to be be transformed before its to the object.
+\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
+For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
 
@@
 To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
-  the unprocessed value is used to create objects, at runtime, that run different analyses;
-  the new value is used to revoke or chain analyses together.
+  the unprocessed value is used to create objects, at runtime, that run a different analysis;
+  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
 
 \heading{Context Transformation}
-To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names to which a library has access.
+To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
 
@@
 Thus, \sys creates an auxiliary hash table mapping names to transformed values.
-Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc
-Transformed values are created by applying \ttt{wrap} to values in the context, adding the provided analysis hooks.
+Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
+Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
 
@@
 These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
-Examples include the library's absolute filename as \ttt{\_\_name\_\_}, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
+Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
 Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
@@
 These statements shadow global variable names by redefining them as local ones.
-The closure accepts an argument \ttt{ctx} that will hold the customized context (see above), assigning its entries to their respective variable names.
+The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
 The prologue executes before everything else in the library.
 % When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
-This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process:
-  instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
-
-Late-bound, \emph{library}-local variables, such as the absolute filename mentioned during context creation, are the result of applying \ttt{wrap} over variable names in the current scope;
+This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
+Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
+
+Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
   these names are now bound to the correct library-local values.
@@
 \heading{Library Interface Transformation}
-Returning the library's value to its consumer amounts to interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
+Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
 % TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
-The goal of the final transformation is to track activity at the boundary;\footnote{
-  For some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.}
-This final transformation is applied for every new consumer of the library, returning a fresh analysis wrapper.
-This is due to the need for distinguishing between different boundaries of the same library.
-
-The treatment of this feature during reassembly is explained in the next section~\sx{three}.
-
-\subsection{Reassembly}
+The goal of the final transformation is to track activity at the boundary;
+  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
+
+The final transformation is applied for every new consumer of the library.
+This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
+
+\subsection{Re-assembly}
 \label{three}
@@
 To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
-The central mechanism for this resolution is the library cache.
-
-To support multiple wrappers for a single cached library, the cache is extended by two levels (for a total of three).
+The central mechanism for resolution is the library cache.
+
+To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
 The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
@@
 % A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
-A special entry is reserved for the original library value as a string~\sx{two}, so that subsequent transformations can skip loading the library from disk.
-When a new analysis is applied to a library, \sys indexes the cache by library identifier and applies the analysis-specific \ttt{wrap} to the library's context.
-It then adds that result to a slot in the next layer of the cache, indexed by the analysis identifier.
-When a library is already loaded, \sys indexes by analysis to retrieve the (mostly) transformed library corresponding to this analysis.
-It then applies a transformation to the library's return value, and inserts the (finalized) transformed library to the third layer of the cache.
-% New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
+A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
+When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
+It then applies a transformation to the library's return value.
+New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
 
@@
 \centering
-\includegraphics[width=0.99\textwidth]{./figs/lya_ex2.pdf}
+\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
 \vspace{-2mm}
@@
    Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
-}
-\label{fig:ex2}
-\vspace{-4mm}
+\fixme{No UX!}
+}
+\label{fig:tx2}
+\vspace{-2mm}
 \end{figure*}
 
-% Fixme switch from libraries to modules?
-
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses developed with \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\sx{reqs}.
-
-The aforementioned dialysis design can be implemented in either of two ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place.
-% with the techniques described earlier.
-The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
-
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system;
-  we went with the second approach, as avoiding tight coupling has several benefits:
-  it does not require \sys's users to have a second Node copy only for running analyses;
-  it removes \sys's developers from the critical path of updates between the Node developers and its users; 
-  and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
-The primary drawback was missing a few  opportunities for runtime-performance and development-effort.
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
+We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
+We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
+
+In practice, the aforementioned dialysis stages can be implemented in two different ways.
+The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
+The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
+It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
+  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
+  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
+% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
+%   we expand on in the discussion section~\sx{reqs}.
 
@@
 
-Node's module system is implemented entirely in JavaScript, exposing a library-local \ttt{require} function for importing modules.
-Loading a fresh module with \ttt{require("foo");} corresponds to the following five stages, all of which are augmented by \sys:
-(R) Resolution: identify the file to which the module specified corresponds, locate it in the file-system, and assign its absolute path as a module identifier.
-(L) Loading: depending on the file type, identify the corresponding loader---\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc
-% Identifiers are absolute paths.
-(W) Wrapping: wrap the module so local names do not escape the module's scope and Node's module-local names get resolved.
-(E) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-(C) Caching: add the module to a handful of module-related caches, for purposes of consistency and performance.
+Node.js' module system is implemented entirely in JavaScript.
+It exposes \ttt{require}, a global-looking function for importing modules.
+At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
 
@@
 \sys interposes on all of these steps to facilitate transformations.
-Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
-If the module's type is one \sys can analyze, it fetches the corresponding analysis during loading (L).
-Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
-\sys replaces Node's wrapper function in order to add a last variable in the function definition, \ttt{CTX}.
-\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.js:
-  (i) identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit;
-  (ii) Node's global names are described at various parts of the documentation; and
-  (iii) library-local required close inspection of Node's internals; fortunately, these were only five names.
-
-% Before a module's code is evaluated, the Node.js module loader wraps the module so that
-%   (i) it keeps top-level variables (declared with \ttt{var}, \ttt{const} or \ttt{let}) scoped to the module rather than the global object; and
-%   (ii) it provides some global-looking variables that are actually specific to the module, such as the \ttt{module} and \ttt{exports} objects that the implementor can use to export values from the module and convenience variables---such as \ttt{\_\_filename} and \ttt{\_\_dirname}  containing the module's absolute filename and directory path, respectively.
-% True globals remaining are
-%   (i) the global objects as defined by the EcmaScript standard (\eg \ttt{Object}, \ttt{Function}, \ttt{Math}); and
-%   (ii) Node.js-specific globals (\eg \ttt{console}, \ttt{process}, \ttt{timer}).
-% These globals require further interposition.
-
-% TODO: Talk about recipe file, that could be kept along with the module identifier
+Wrapping (3) and evaluation (4) are particularly interesting, because they allow \sys to interpose at the module boundary during runtime.
+Before a module's code is evaluated, the Node.js module loader wraps the module so that
+  (i) it keeps top-level variables (defined with \ttt{var}, \ttt{const} or \ttt{let}) scoped to the module rather than the global object; and
+  (ii) it provides some global-looking variables that are actually specific to the module, such as the \ttt{module} and \ttt{exports} objects that the implementor can use to export values from the module and convenience variables---such as \ttt{\_\_filename} and \ttt{\_\_dirname}  containing the module's absolute filename and directory path, respectively.
+True globals remaining are
+  (i) the global objects as defined by the EcmaScript standard (\eg \ttt{Object}, \ttt{Function}, \ttt{Math}); and
+  (ii) Node.js-specific globals (\eg \ttt{console}, \ttt{process}, \ttt{timer}).
+These globals require further interposition.
 
@@
 
-We found it useful to add an option for white- and black-listing libraries.
-The configuration object accepts \ttt{only} and \ttt{not} expressions that indicate whether a module identifier will be part of the analysis.
-These expressions contain sets of sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
-Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose them to users.
-Examples of use include blacklisting built-in libraries or white-listing only the newest-imported library.
-% This is useful, for example, when...
+\sys hooks into the wrapper function (the last variable in the function definition, \ttt{CTX}).
+This trivial source-to-source transformation re-defines global variables as module-locals and initializes them with \sys-augmented values.
+For example, \ttt{console} in the context of the module will be an \sys-created object that allows \sys to interpose on it.
+Evaluation of the module passes an additional value to this function, which is the modified context.
+As a result, any changes to the top-level objects and any global variables are accessible from the within the module.
 
@@
 % carefull hardcoding of paths, because \sys's code itself is split into modules
+% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
+% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
+% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
+% This is useful, for example, when...
+% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
 
 %% TODO: implementation
-
-Fig.~\ref{fig:ex2} exemplifies \sys's transformation techniques in the context of JavaScript.
-\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
-
-\subsection{Individual Analyses}
-\label{impl2}
-
-Individual analysis are implemented using a set of templates that provide initial constructs.
-%% Individual transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
+%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
 %% These skeletons provide hooks for end-developers writing analyses.
@@
 %% These hooks are then extended or rewritten by developers to
+
+Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
+\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
+The precise wrappers depend on the intended analysis, reviewed next.
+
+\subsection{Individual Analyses}
+\label{impl2}
+
+Individual analysis are implemented using a set of templates that provide initial constructs (see below).
 \sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
-Individual analyses are between 100--200 lines of code, but a significant part of this code is common across analyses.
-
-As the three analyses are quite complex to be shown in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
-
-\begin{verbatim}
-let fs = require('fs');
-let count = {};
-forevery.global.in(/serial/) = {
-  pre: (name, path, _) => {
-    let id = resolve(name, path);
-    count[id] = count[id]?  count[id] + 1 : 1;
-  }
-};
-process.on('exit', () => {
-  fs.writeFileSync('acl.json',
-                   'utf-8',
-                   JSON.stringify(count));
-});
-\end{verbatim}
-
-\noindent
-\sys-provided \ttt{forevery} generates sets of names succinctly.
-The \ttt{in} field is a method that takes a regular expression matching module identifiers.
-If not empty, \ttt{pre} and \ttt{post} hooks are called before and after each access of the elements specified in the set.
-Finally, \ttt{resolve} is a method for traversing an object given a path within that object.
-Upon program exit, the results are written to disk, all using the expected Node APIs.
+As a result, code that is specific to individual analyses averages about 20--30 lines.
 
 \heading{Security Analysis}
-To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
-The analysis treats built-in libraries and global variables as modules,
-% and generates a list of permissions for each of their fields.
-and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
- (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
- (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
- (iii)  an execute permission (\X) indicates that a consumer to executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).
-
-The resulting permission sets are organized as a collection of maps, one per library, each indexed by object-paths such as \ttt{Math.add: RX}.
-% that correspond to values of other modules or global-like language names.
+To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
+The language of the analysis is given in the following grammar:
+
+\begin{alltt}
+  str:  <identifier in JS>
+  libs: [ str ]
+  path: str `.` path
+  mode: P{ R | W | X }
+  body: { [ path: mode ]: path \(\in\) mods}
+  analysis:  mods body
+\end{alltt}
 
 \heading{Performance Diagnosis}
-To conduct performance diagnosis, we develop a profiling analysis that operates at two levels:
- (i) module-boundary wrappers that collecting profiling statistics for calls between modules by wrapping module interfaces; and
- (ii) an aggregator function that collects statistics from all boundary wrappers and generates a model of library load under the current workload.
-
-Boundary wrappers operate at a higher-frequency intervals than the aggregator, which operates on summaries.
-Their analysis focuses on function values (\eg functions, methods, constructors), skipping all other direct field accesses.
-Functions are wrapped with prologue and epilogue wrappers that record statistics from the Node.js runtime---for now, a frequency counter and a timer between prologue-to-epilogue invocations.
-% Many statistics are available by the Node.js runtime, including memory and garbage-collection statistics, 
-Boundary wrappers summarize these statistics by periodically sending a windowed, weighted average of call latencies to the aggregator function.
-
-% Wrappers record statistics about the their encapsulated functions as well as queue characteristics of outstanding calls.
-% The wrapper epilogue has access to several raw metrics related to profiling (Tab.~\ref{tab:metrics}).
-% These metrics are viewed as a windowed average that priori
-
-Interestingly, profiling functions at the boundary cannot ``see through'' libraries to correctly attribute load among a library and its dependencies.
-For example, a boundary wrapper \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency comes from \ttt{B}.
-Fortunately, the aggregator understands the dependency structure and can approximate how much of the latency comes from each module.
-% Such a approximation is more complicated than a simple subtraction, as a module may invoke interfaces from multiple modules at the same time.
-% Having an analysis fragment per library consumer, however, alleviates much of the problem.
-
-% FIXME: Snapshot results
-% [serial , whatever, pizza, ...]
-
-\heading{Type Invariant Discovery}
-To infer type invariants for serialization specifications, we develop a simple type system and use our analysis to map values to types.
-
-The type system is modeled after the simply-typed lambda calculus augmented with:
-  (i) unions (sum types), such as \ttt{a | b | c}; 
-  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}; and
-  (iii) a \ttt{native} type for values that cannot be serialized, like \ttt{console.log}.
-Support for union types is useful for when our analysis witnesses variables holding values of different types---although, in practice,  programs tend to make calls of the same type across their entire lifetime~\cite{daikon}.
-
-Our implementation also uses a base set of JavaScript types and rules to deconstruct complex types into their elementary building blocks.
-% Knowing how to deconstruct a type to its structural primitives allows walking values---
-For example, the analysis extracts that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
-% To achieve this, the analysis makes use of introspection to identify
-
-% leftpad: (string | number) -> number -> (string | null) -> string
+
+\begin{equation}
+\label{eq:2}
+R_{new} =
+\begin{cases}
+  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
+  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
+\end{cases}
+\end{equation}
+
+Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
+However, after scale-in, the system often ends up just scaling out the same module.
+To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.
+
+% ATTRIBUTION
+Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
+For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
+% \eat{ is \ttt{A}-internal and how much}
+comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
+
+\heading{Invariant Discovery}
+Describe specific type system
 
@@
     \textbf{Synthetic Micro-benchmarks}.
-		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
+		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
   }
@@
     \textbf{Applying \sys to single-library programs}.
-		\fixme{Execution time of eight test suites against }
+		\fixme{Execution time of four test suites against }
   }
@@
 
-Table~\ref{} depicts the results of the three analysis applied to these benchmarks.
+Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
 We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
@@
 
-Program dialysis depends on a few features provided by the programming language.
-In this section, we start by describing its requirements~\sx{reqs} and then reflect on some of its strengths and weaknesses~\sx{principles}.
-
-\subsection{Applying \sys to Other Environments}
+Library dialysis, as implemented in \sys, depends on a few features available in the programming language.
+In this section we describe how to develop the same solution on other environments.
+In the second part of this section, we reflect on some of the current limitations of the system.
+
+\subsection{Applying to Other Environments}
 \label{reqs}
 
-% \begin{table*}[t]
-% \center
-% \footnotesize
-% \setlength\tabcolsep{3pt}
-% \caption{
-%   \footnotesize{
-%     \textbf{Language features used and their availability in other languages}.
-%     Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
-%   }
-% }
-% \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
-% \toprule
-%              &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
-% \midrule
-% Lua          &                              &                       &                     &                   &                       \\
-% JavaScript   &                              &                       &                     &                   &                       \\
-% Python       &                              &                       &                     &                   &                       \\
-% Ruby         &                              &                       &                     &                   &                       \\
-% Haskell      &                              &                       &                     &                   &                       \\
-% OCaml        &                              &                       &                     &                   &                       \\
-% Rust         &                              &                       &                     &                   &                       \\
-% Java         &                              &                       &                     &                   &                       \\
-% \bottomrule
-% \end{tabular*}
-% \label{tab:compat}
-% \vspace{-5mm}
-% \end{table*}
+\begin{table*}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Language features used and their availability in other languages}.
+    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
+  }
+}
+\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
+\toprule
+             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
+\midrule
+Lua          &                              &                       &                     &                   &                       \\
+JavaScript   &                              &                       &                     &                   &                       \\
+Python       &                              &                       &                     &                   &                       \\
+Ruby         &                              &                       &                     &                   &                       \\
+Haskell      &                              &                       &                     &                   &                       \\
+OCaml        &                              &                       &                     &                   &                       \\
+Rust         &                              &                       &                     &                   &                       \\
+Java         &                              &                       &                     &                   &                       \\
+\bottomrule
+\end{tabular*}
+\label{tab:compat}
+\vspace{-5mm}
+\end{table*}
 
 The techniques presented in this paper are applicable to any programming language.
-We chose the JavaScript ecosystem % to evaluate the feasibility of our approach,
-primarily because
-  (i) it boasts the largest collection of libraries~\cite{modulecounts} and
-	(ii) we had prior experience developing more sophisticated version of the security and performance analyses.
-We now expand on the requirements for developing dialysis over other runtime environments.
+We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
+  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
+	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
+In this section, we discuss the requirements for building \sys over other runtime environments.
 % FIXME: All these features have to have been discussed earlier
 
-By operating on library boundaries, dialysis uses a few special language features, supported by all major programming languages.
-First, \sys needs to re-wire the \ttt{import} keyword:
+By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
+All major programming languages can support these five features in a variety of ways, as described below.
+
+First, \sys replaces the implementation of the import statement (\eg \ttt{require}).
 % This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
-  if it is a function (\eg JavaScript, Scheme, Racket), rewiring amounts to an overwrite;
-  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (at module-loading).
+If this statement is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
+If this statement is a special non-function keyword such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
 % This is simplified by the fact that the import syntax is trivial.
 
-It also needs the ability to interpose on values and transform their components.
-% This is relatively easy in languages that provide meta-programming capabilities.
+\sys also needs the ability to interpose on values and transform their components.
+This is relatively easy in languages that provide meta-programming capabilities.
 Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
-Compiled languages would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
-Examples include templates and macro expansions such as Haskell's Template and Rust's macro system.
-% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities. %, allowing considerable freedom in the choice of implementation.
+Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
+Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
+And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
 % Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
@@
 
-\sys makes extensive use of hash-maps---to check for object equality, for cycles during traversal, and for prior wrapping.
-Hash-maps are supported by every programming language; many support storing weak references, which avoid affecting object reclamation in garbage-collected environments, and can be created either explicitly (\eg Python) or implicitly by using a ``weak'' structure (\eg JavaScript).
-% An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
-% Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
-
-Finally, \sys makes use of variable shadowing to hide the original, unmodified versions of values---a universal feature.\footnote{
+\sys makes extensive use of weak maps to support to check for object equality.
+Examples of uses include checking for cycles during object traversal and checking whether an object has already been wrapped.
+Hash tables that are indexed by reference are supported in virtually all programming languages.
+An additional feature useful in garbage-collected languages would be for these (copies of) references to not affect the reclamation of original objects.
+Languages either support the ability to create such a weak reference from a normal reference (\eg Python's weak references), or provide structures that automatically hold weak versions of these references (\eg JavaScript's Weak Map).
+
+Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
+This is a feature that is universally available in programming languages;\footnote{
   A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
 }
-% Differences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
-
-To conclude, all major languages provide facilities to support dialysis---albeit with a different level of convenience.
+Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.
+
+To conclude, all major languages provide enough facilities to support the dialysis---albeit with a different level of convenience.
 Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
@@
   a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-Compiled languages have other benefits, namely that applying transformations statically ameliorates their runtime overhead.
-% and type checking could further aid developers by issuing warnings of incompatible privilege settings.
+Compiled languages such as Haskell, OCaml, and Rust apply transformations using compile-time metaprogramming facilities.
+Compile time transformations alleviate much of the runtime overhead of transformations, improving program startup times;
+  and type checking could further aid developers by issuing warnings of incompatible privilege settings.
 
@@
 It is unclear how to wrap values without any kind of size information.\footnote{
-  Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
+  Recent advances show promise: C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} provide type-aware heap traversal for C programs.
 }

### 2020-01-14 paper/draft.tex
Added ubuntu version and jalangi version

@@
 \newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
-\newcommand{\rf}[1]{\ref{#1}}
-\newcommand{\se}[1]{\S\ref{#1}}
-\newcommand{\fg}[1]{Fig.~\ref{#1}}
-
 \newcommand{\sys}{{\scshape Lya}\xspace}
@@
 \newcommand{\dia}{\fra, \ana, and \ass}
-
-% FIXME:
-\newcommand{\pc}{PIC\xspace}
-\newcommand{\pcs}{\pc{}s\xspace}
 
@@
 
-\subsection{Background on Module Systems}
+\subsection{Background on Modules and Module Systems}
 \label{bg1}
 
-A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
-This functionality falls into two categories:
-  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) is provided by other developers sharing code others might find useful.
-Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
-
-From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
-What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
-This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
-The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
-Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
-% , as shown on line \fixme{XX},
-% closely coupled with the runtime
-% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.
-
-From the language's perspective, the loading process is achieved in several steps. 
-In compiled programming languages libraries might be used to enable separate compilation, in which case an additional linking phase connects the resulting object files.
-Interpreted languages involve a somewhat convoluted process that combines loading, interpretation, and linking.
-This process starts by locating the library in the file system or across the network,\footnote{
-  Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
-}
-by resolving relative or absolute identifiers.
-% The library is assigned a unique identifier.
-The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
-The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit} in the library's top-level scope will exit the entire program.
-Finally, the value returned bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) will be made available to the scope of code calling \ttt{import}.
-
-There is significant variation, but a few features are common across many implementations.
-A library cache maintains a mapping from library identifiers---often absolute paths---to returned \ttt{export} values.
-The library cache serves a dual purpose:
-  by avoiding to locate already loaded libraries, it improves performance and maintains the consistency of stateful libraries.
-Recursive imports are handled in depth-first way, and if cyclical dependencies are possible they are resolved by pointing to the cache.
-An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \ttt{lib} does not necessarily resolve to the same (version of the) library \ttt{lib} every time.
-The dual of this situation is also possible, in which two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
-These features complicate library-level analysis, especially in interpreted programming languages.
-
-% Several details:
-%   same module at multiple levels, and the module cache
-%   sometime it's the same, some times it;s not
-%   module resolution algorithm
+languages provide module systems
+
+closely coupled with the runtime
+
+A module uses a \ttt{import} function and returns an export .
+Intuitively a map
+
+Several details:
+  same module at multiple levels, and the module cache
+  sometime it's the same, some times it;s not
+  module resolution algorithm
 
@@
 \heading{Security Analysis}
-The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
-Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
-As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
-Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
+Today's ubiquitous reliance on third-party modules has led to an explosion of supply-chain attacks~\cite{maass2016theory, lauinger2017thou, long2015owasp, cadariu2015tracking, breakapp:plos:2017, snyk}.
+Both bugs and malicious code in imported modules provide attack vectors that are exploitable long after modules reach their end-users.
+As development-time module boundaries do not exist at runtime, modules end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of an application.
+The popularity of certain libraries---depended upon by tens of thousands of other libraries or applications---allows vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{kuppusamy2016diplomat, leftpad, npmstudy:19}.
 Discovered vulnerabilities are becoming harder to eradicate, as updates are fetched automatically~\cite{npmFailure} and module unpublishing is becoming a multi-step process to avoid breaking applications~\cite{npmUnpublish}.
-Worst of all, leaked publishing tokens allow attackers to update packages with code that will eventually reach end-users via package updates~\cite{eslint1}.
-
-As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
-As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
-At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
-  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
-Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
-% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
-
-To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
-% FIXME more about the policy, tracking arguments too
-A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
-Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.
-
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
+Worst of all,\omit{package developers accidentally publishing their security} leaked publishing tokens allow anyone to update packages with code that will eventually reach end-users via package updates~\cite{eslint1, eslint2}.
+
+Recent work~\cite{dld:08, sandcrust, tsampas2017towards, breakapp:ndss:2018} has shown that 
+The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
+% and is exploitable.
+Some of this functionality is \emph{explicitly} provided by other libraries such as \ttt{fs} and \ttt{http}.
+Other functionality is \emph{implicitly} provided by the programming language;
+  examples include the ability to use global variables, import modules, and access the cache of the loaded modules.
+Both explicitly and implicitly provided functionality is exploitable by third-party code.
+While it may be needed for the application to function as a whole, it is not necessarily needed by \ttt{event-stream}.
+% However, not \emph{all} of this capability is needed by \emph{all} of the modules during \emph{all} of the time.
+MLC shows great promise, as it can
+(i) retrofit security into \emph{legacy} systems not designed with security as their primary concern,
+(ii) protect against a plethora of \emph{real} attacks stemming from defective, subverted, and malicious elements, and
+(iii) shield against attacker-controlled components with \emph{unknown} vulnerabilities and powerful \emph{runtime} code evaluation. % (\eg \texttt{eval}).
+
+To make this concrete, we are introducing
 
 \heading{Performance Diagnosis}
-Diagnosing performance problems is a difficult task, exacerbated by the heavy use of third-party libraries.
-Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
-  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
-Maintenance and rewriting can cause performance regressions between two versions of a library.
-% FIXME: Garbage collection
-Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.
-
-As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
-Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
-The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).
-
-The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
-An analysis 
-% A key observation is the semantic isomorphism between calling a function and passing a message
-% This allows viewing a series of calls as a stream of messages.
-% Module boundaries can be viewed as (virtual) queues of messages that await processing.
-treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
+Developers use various techniques to understand such problems.
+For example, collected traces can be replayed against off-line versions of the system and statistical profiling can identify hot code-paths.
+These techniques, however, require some degree of \emph{manual} effort:
+  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks.
+Pervasiveness of third-party modules and heavy code reuse in modern applications compound the challenge, as the causes may lie deep in the dependency chain.
+
+Once provided with a few recipes, \sys starts monitoring the performance of the corresponding modules in order to detect bottlenecked modules.
+A key observation is the semantic isomorphism between calling a function and passing a message~\cite{scheme:98, duality:79}.
+This allows viewing a series of calls as a stream of messages. % that 
+% at each module boundary 
+Module boundaries can be viewed as (virtual) queues of messages that await processing.
+% and applying windowed average operations on a 
 Overwhelming a module causes its ingress queue to grow.
-At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
-Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
-Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
-Profile generation can operate at a high resolution in time and space:
-  (i) at every function call entering a module, and (ii) on thousands of modules across an application.
-
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
-
-\heading{Invariant Discovery}
+% MM: related to the sync vs. async
+% As the queue grows due to module overloading, new messages will be processed only after all other messages have been processed.
+At some point, the waiting time of newly-arrived messages becomes longer than the time to send the messages to a remote copy of the module, run the call there, and return the results back to their intended recipient.
+% Intuitively, it makes sense to schedule a queue on a remote processor when the wait time at the end of the queue becomes longer than scheduling the message to a remote queue.
+
+To make this concrete, we are introducing
+
+\heading{Type and Invariant Checking}
 Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
@@
 For example
-e.
-For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
-This is especially problematic in dynamic programming languages:
-  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.
-
-To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
-Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
-if the type changes, because of a library version change or because of changes in the .
-
+
+To make this concrete, we are using
 The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
-A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
-The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
-The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
-
-% would need to be able 
-% to capture structural subtitling---that is the piecewise
-
-% \heading{Learning, Synthesis, and Regeneration}
+
+\heading{Learning, Synthesis, and Regeneration}
+Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
+Dynamic analysis can be used to generate type assertions or invariants
+For example
+The approach has been pioneered by systems such as
+
+To make this concrete, we are using
+The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
 
@@
 Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
-  instead of simply locating and loading a library from the file-system, it yields control to \sys, which applies a series of transformations to libraries with the goal of interposing at their boundaries.
-We start with an overview of dialysis~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).
+  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
+We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
+We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).
 
@@
 % FIXME: add user data
-At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
- In more detail:
+At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
+ In more detail, these three phases are as follows:
 
@@
 
-  \item \textbf{Dismantling:}
-Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
-This is achieved by re-wiring the language's \ttt{import} functionality to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
-During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and mapping provided analysis hooks to the corresponding libraries.
-
-  \item \textbf{Transformation:}
-It then sets up the provided analysis, by transforming each library interface, its surrounding environment, and possibly the values passing through the library boundary.
-Programmatic transformations walk and wrap each one of these values based on their type.
-% the library interface is usually a complex (but singular) object;
-% the surrounding environment provides names to multiple ``implicitely'' imported libraries, functionality provided by the language.
-This phase requires solving several challenges, including enumerating all points of entry into and exit out of a library, 
-and swapping original values externally available to a library with ones that are wrapped with interposition mechanisms.
-
-  \item \textbf{Re-assembly}
-Finally, dialysis re-assembles individual modified libraries back into the program's original structure.
-The most important challenge during this phase the treatment of the library cache~\sx{bg1}:
-  since a single library can now correspond to many different wrappers, each modified to capture a small fragment of the overall analysis, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
+  \item \Fra:
+    It first starts by recursively dis-assembling programs into their library dependencies---pieces of software implement a computation or functionality.
+    This is essentially achieved by instrumenting the import statements and walking the program's recursive dependency structure.
+    Different analysis can operate at different granularities, and has to solve challenges such as multi-module and dedublication.
+
+  \item \Ana:
+    It then sets a specific analysis up by wrapping and transforming each module interface, its surrounding environment, as well as the values passing through the module boundary.
+    Programmatic transformations walk and transform each one of these values based on their type:
+      the module interface is usually a complex (but singular) object; the surrounding environment treats 
+    This phase requires solving several challenges, including enumerating and tracking all points of entry into and exit out of a library.
+    It also requires providing 
+     in a backwards compatible fashion.
+
+  \item \Ass:
+    Finally, it re-assembles individual modified modules back into the original structure.
+    This creates several challenges, the most important of which is the treatment of the module cache---a mechanism for avoiding multiple loads of the same module .
+    Since a single library can now correspond to many different wrappers, each modified to capture different  analysis fragments, the cache needs to be augmented to ensure the right analysis fragment clicks at the right place during the re-assembly of the dependency tree.
 
@@
 
-% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
+Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
+
+% , such as an object returned from a module or an exception about to be sent across the network.
+Transformations can be applied to any value in the language. 
+The most general value is an object, a bag of records holding key-value fields;
+  other value types include primitives, functions, and booleans.
+% Listing~\ref{core-tx} presents a simplified core of the language.
+Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
+More specifically,
+  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
+  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
+  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
+% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
 
@@
   The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
-The meta-function $\alpha$ stands for the locations of analysis hooks.
   }
@@
 
-% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
-% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
-% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
-% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
-% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
-% The following subsections detail these steps.
-
-\subsection{Dismantling}
+The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
+These skeletons provide hooks for end-developers writing analyses.
+Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
+These hooks are then extended or rewritten by developers to
+
+For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
+\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
+The wrappers depend on the intended goal:
+  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.
+
+\subsection{Disassembly}
 \label{one}
-
-When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
-Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
-For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
-For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
-
-It then dynamically replaces the implementation of\ttt{import}:
-  rather than simply locating and loading a library, the function yields to \sys.
-
-\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
-If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
-If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
-% \omit{---the common case---}
-Otherwise, \sys first invokes the built-in library loader to locate the library.
-
-The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
-Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
-A series of transformations is applied before and after interpretation~\sx{two}.
-
-Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
-\sys must note not to include these constructs in the ones 
-% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
-Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
-To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
-The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
-  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
 
@@
 
-\subsection{Transformation}
-\label{two}
-
-For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
-This is achieved in three logical steps:
-(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
-(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
-(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
-Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.
-
-\heading{Transformations}
-% , such as an object returned from a module or an exception about to be sent across the network.
-Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
-% Listing~\ref{core-tx} presents a simplified core of the language.
-Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
-More specifically,
-  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
-  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
-  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
-To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
-% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
-
-% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
-% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
-% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
-% At runtime, $f'$ checks $\sigma$:
-%  if the access is allowed, it forwards the call to $f$;
-%  otherwise, it raises an exception.
-% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
+\subsection{Reassembly}
+\label{three}
+
+% \section{Applications of Analysis}
+% \label{apps}
+
+\section{Implementation: Lya}
+\label{impl}
+
+We implemented \sys for version 8.9.4 of the Node.js runtime.
+Node.js is a runtime that bun
+
+in about 1.5K lines of JavaScript.
+We summarize where other implementations would diverge in table 1
+
+Individual analysis are implemented using a set of templates that provide initial constructs (see below).
+The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.
+
+The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
+It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+
+In practice, the aforementioned dialysis stages can be implemented in two different ways.
+The first is as a modified version of the runtime, where 
+No-op analyses correspond to the default execution
+  either 
+It is introduced as a backward-compatible, drop-in replacement of the language's module system.
+It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
+
+We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
+However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
+  we expand on these at the end of this section~\sx{opportunities}.
+% get second argument, no need to pass arguments around, tricky to 
+% carefull hardcoding of paths, because \sys's code itself is split into modules
+% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
+% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
+% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
+% This is useful, for example, when...
+% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
+
+(1) why node.js
+(2) Create a table of compatibility and show individual aspects
+
+\heading{Module System}
+Node.js' module system is implemented entirely in JavaScript.
+It exposes \ttt{require}, a global-looking function for importing modules.
+\fixme{Figure} above demonstrates the use of \ttt{require}.
+
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% // -------------- [./main.js] -------------
+% // importing point
+% let Point = require("./point.js");
+% Point.create(1, 1).print(); // => [1, 1]
 % 
-% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
-% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
-% 
-% % Listing~\ref{core-tx} presents a simplified core of the language.
-% 
-% \begin{itemize}
-% \item
-%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
-% \item
-%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
-% \item
-%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
-% \end{itemize}
-
-Direct field accesses, such as assignments, require custom detection upon dereference.
-To achieve this, \sys wraps fields with an interposition mechanism;
-  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
-% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
-\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
-For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.
-
-\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
-To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
-  the unprocessed value is used to create objects, at runtime, that run a different analysis;
-  the new value is used to revoke or chain analyses, a feature not explored further in this paper.
-
-\heading{Context Transformation}
-To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.
-
-To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
-Semantically, the context is a map from variable names to their values.
-Thus, \sys creates an auxiliary hash table mapping names to transformed values.
-Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
-Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.
-
-%% FIXME: 
-%% While user-defined global variables are stored in well-known locations,\footnote{
-%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
-%% } traversing the global scope for built-in values is generally not possible.
-%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
-%%   different lists exist for different environments and versions of the language.
-%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.
-
-Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
-These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
-Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
-Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
-\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).
-
-\heading{Context Linking}
-To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
-The closure's body starts with a prologue of the form:
-\begin{verbatim}
-  local pint = ctx.print
-  local error = ctx.error
-  ...
-\end{verbatim}
-These statements shadow global variable names by redefining them as local ones.
-The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
-The prologue executes before everything else in the library.
-% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
-This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
-Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.
-
-Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
-  these names are now bound to the correct library-local values.
-
-\heading{Library Interface Transformation}
-Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
-% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
-The goal of the final transformation is to track activity at the boundary;
-  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
-
-The final transformation is applied for every new consumer of the library.
-This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.
-
-\subsection{Re-assembly}
-\label{three}
-
-To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
-The central mechanism for resolution is the library cache.
-
-To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
-The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
-A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
-Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
-% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
-For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
-Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
-  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.
-
-% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
-A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
-When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
-It then applies a transformation to the library's return value.
-New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
-
-\section{Implementation of Dialysis for SSJ}
-\label{impl}
+% // -------------- [./point.js] ------------
+% let Point = function Point (x, y) {
+%     this.x = x; this.y = y;
+% };
+% Point.prototype.print = function print () {
+%   console.log([this.x, this.y]);
+% };
+% module.exports = {
+%     create:  function create (x, y) {
+%         return new Point(x, y);
+%     }
+% };
+% \end{lstlisting}
+
+In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
+Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
+  the rest is module-private functionality.
+Files and modules are in one-to-one correspondence (each file is treated as a separate module).
+Method \ttt{require} is synchronous (\ie blocking):
+  it will block execution until the module specified is loaded.
+% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
+The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.
+
+\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).
+
+\subsection{Implementation of the Module System}
+\label{c}
 
@@
    Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
-\fixme{No UX!}
 }
@@
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
-
-In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
-The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
-
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
-It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
-  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
-  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
-% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-%   we expand on in the discussion section~\sx{reqs}.
-
-% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
-
-\subsection{System Implementation}
-\label{impl1}
-
-Node.js' module system is implemented entirely in JavaScript.
-It exposes \ttt{require}, a global-looking function for importing modules.
-At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
-(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
-(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
-(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
-(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
-(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
+
+\begin{enumerate}
+% \def\labelenumi{\arabic{enumi}.}
+\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
+\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
+\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
+\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
+\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
+\end{enumerate}
 
@@
 
-% get second argument, no need to pass arguments around, tricky to 
-% carefull hardcoding of paths, because \sys's code itself is split into modules
-% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
-% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
-% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
-% This is useful, for example, when...
-% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;
-
-%% TODO: implementation
-%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
-%% These skeletons provide hooks for end-developers writing analyses.
-%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
-%% These hooks are then extended or rewritten by developers to
-
-Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
-\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
-The precise wrappers depend on the intended analysis, reviewed next.
-
-\subsection{Individual Analyses}
-\label{impl2}
-
-Individual analysis are implemented using a set of templates that provide initial constructs (see below).
-\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
-As a result, code that is specific to individual analyses averages about 20--30 lines.
-
-\heading{Security Analysis}
-To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
-The language of the analysis is given in the following grammar:
-
-\begin{alltt}
-  str:  <identifier in JS>
-  libs: [ str ]
-  path: str `.` path
-  mode: P{ R | W | X }
-  body: { [ path: mode ]: path \(\in\) mods}
-  analysis:  mods body
-\end{alltt}
-
-\heading{Performance Diagnosis}
-
-\begin{equation}
-\label{eq:2}
-R_{new} =
-\begin{cases}
-  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
-  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
-\end{cases}
-\end{equation}
-
-Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
-However, after scale-in, the system often ends up just scaling out the same module.
-To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.
-
-% ATTRIBUTION
-Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
-For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
-% \eat{ is \ttt{A}-internal and how much}
-comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
-
-\heading{Invariant Discovery}
-Describe specific type system
-
-% \subsection{Limitations}
-% 
-% % FIXME: Talk about the inability to 
-% A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
-% This is because \sys cannot transform the context of that file
-% As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
-% The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
-
-\section{Evaluation}
+% \begin{lstlisting}[language=js,mathescape,upquote=true]
+% //Input: module ID e.g., absolute filepath
+% let load = function (ID) {
+%   if (cache[ID]) {
+%      return cache[ID];
+%   }
+%   let m = {
+%     exports: {}, id: ID, dir: path.resolve(ID)
+%   };
+%   let cm = v8.compile(wrapped);
+%   let ii = iris.getImplicit(ID);
+%   let c = iris.freshContext(ii);
+%   cm(m.exports, this.require, m, ID, m.dir, c);
+%   let ei = iris.getExplicit(ID);
+%   m.exports = iris.wrap(m.exports, [ei] );
+%   cache[ID] = m;
+%   return m.exports;
+% }
+% \end{lstlisting}
+
+The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
+After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
+\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
+Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
+Finally, the results of the entire process are placed into the module cache for later use.
+
+\subsection{Limitations}
+
+% FIXME: Talk about the inability to 
+A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
+This is because \sys cannot transform the context of that file
+As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
+The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).
+
+\section{Evaluation and Experience}
 \label{eval}
@@
 Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
-In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu XXX version}, Jalangi \fixme{vXXX}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
+In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu 14.04.6 version}, Jalangi \fixme{v2}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
 We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.

### 2020-01-14 paper/draft.tex

@@
 
-A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
+\begin{figure}[t]
+\raggedleft 
+\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
+\caption{
+  \textbf{Example of a library import.}
+  \textmd{
+    The program on the left imports the \ttt{simple-math} library, shown right, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
+    Several names resolve to functionality provided by the programming language:
+      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
+  }
+}
+\label{fig:ex1}
+\end{figure}
+
+A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
 This functionality falls into two categories:
-  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) is provided by other developers sharing code others might find useful.
-Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.
-
-From a developer's perspective, \ttt{import}ing a library makes its functionality usable by the calling code. 
-What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
-This is provided through a form of \ttt{export}ing, where the library developer expresses which values should become available to the importing code.
-The definition of a value depends on the semantics of the language, but for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
-Internally, the library might import other libraries, cause side-effects to the file-system and the network, or even be implemented in multiple languages.
+  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
+  or (ii) provided by other developers sharing code others might find useful.
+Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).
+
+From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
+% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
+This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
+The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
 % , as shown on line \fixme{XX},
@@
 The pervasive reliance on third-party libraries has led to an explosion of supply-chain attacks~\cite{long2015owasp, maass2016theory, snyk, lauinger2017thou}.
-Both bugs and malicious code in imported libraries create attack vectors, exploitable long after libraries reach their end-users.
-As library boundaries do not exist at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
+Both bugs and malicious code in libraries create attack vectors, exploitable long after libraries reach their end-users.
+As library boundaries disappear at runtime, libraries end up executing with no meaningful isolation or privilege separation guarantees between each other and the trusted portions of a program.
 Popular libraries, depended upon by tens of thousands of other libraries or applications, allow vulnerabilities deep in the dependency graph to affect a great number of applications~\cite{leftpad, npmstudy:19}.
@@
 
-As a concrete example, consider the recent event-stream incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code for stealing Bitcoin wallet credentials from a program using that library.
-As event-stream activated its malicious behavior only on production---\ie not during testing or development---it is critical to be able to toggle the behavior of the system
-At the same time, it is not critical to analyze behavior \emph{within} the event-stream library itself:
-  if any data exfiltration is happening, this will require calling out of the library and into the network---in event-stream's case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
-Both \ttt{fs} and \ttt{http} are libraries part of the standard library and built into the runtime environment.
+As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
+Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
+Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
+Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.
+
+Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
+Analyzing the behavior \emph{within} the library itself is not critical:
+  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
+Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
+Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
 % The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
 
-To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
-% FIXME more about the policy, tracking arguments too
-A simple ``allow-deny'' security analysis indicating the resources touched by that library would have revealed access to the and access .
-Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are easily available to any third-party that is part of an application.
-
+ %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
+ %% % FIXME more about the policy, tracking arguments too
+ %%  indicating the resources touched by that library 
+ %% it seems critical to be able to toggle analysis on/off on production.
 % \emph{
@@
 Libraries are written by authors with different education backgrounds, quality standards, and, most importantly, needs:
-  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{}.
-Maintenance and rewriting can cause performance regressions between two versions of a library.
+  it's not unusual for a weekend project solving a local need to end up as a critical dependency among several open source projects~\cite{cheapcomplexity}.
+Maintenance and rewriting can also cause performance regressions between two versions of a library;
 % FIXME: Garbage collection
-Worse even, the fact that one library changes a dependency to a different implementation can cause severe performance pathologies to upstream projects---that is, while the interface remains the same due to an intermediate layer of abstraction, performance characteristics change dramatically~\cite{evhaus}.
-
-As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays because of pathological regular expressions that involve backtracking.
-Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation.
-The source of this degradation can lie deep in the dependency chain of the application~\cite{crosby2003denial}, but also affect logically unrelated parts competing for the same resource (\ie CPU).
-
-The research community has proposed several possible mitigations~\cite{}, all critically depending on detecting and attributing the slowdown to the bottlenecked component.
-An analysis 
-% A key observation is the semantic isomorphism between calling a function and passing a message
-% This allows viewing a series of calls as a stream of messages.
-% Module boundaries can be viewed as (virtual) queues of messages that await processing.
-treating library invocation boundaries as message queues~\cite{scheme:98, duality:79}.
-Overwhelming a module causes its ingress queue to grow.
-At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
-Profiling is accomplished by wrapping module interfaces with logic that generates a model of the current workload.
-Each module boundary collects its own statistics based on a combination of recipes and instructions from the coordinator.
-Profile generation can operate at a high resolution in time and space:
-  (i) at every function call entering a module, and (ii) on thousands of modules across an application.
+  worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, performance characteristics can change dramatically~\cite{jest}.
+
+As a concrete example, consider the \ttt{minimatch} library, a regular-expression-based file-matching utility susceptible to long delays due to regular expressions that involve backtracking~\cite{minimatch}.
+Pathological inputs reaching \ttt{minimatch}, even if benign, can cause significant performance degradation~\cite{redos} deep in the dependency chain that can also affect other parts competing for the same resource~\cite{evp}.
+Developers use various techniques to understand such problems---for example, they collect and replay traces against off-line versions of the system, or use statistical profiling to identify hot code-paths.
+These techniques, however, require significant \emph{manual} effort:
+  capturing traces, setting up testbeds, replaying traces, analyzing statistics, and debugging performance are all tedious and time-consuming tasks, compounded by the difficulties of mapping the results to the right third-party libraries.
+
+Having the ability to quickly detect a slowdown and attribute it to a bottlenecked component is key, by toggling on/off a profiling analysis that operates at library boundaries.
+The analysis would wrap library interfaces with logic that generates a model of the current workload.
+Profiling can operate at a high resolution in time and space:
+  (i) at every function call entering a library, and (ii) on hundreds of libraries across an application.
+but does not need to track detailed operations such as direct variable accesses.
+% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
+% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
+Each library wrapper would collect profiling statistics at its own boundary, updating a global structure ordering the libraries' overall needs.
 
@@
 
-\heading{Invariant Discovery}
-Extracting type invariants is helpful in a variety of ways---type safety is an important property and types are lightweight annotations that can be quickly and efficiently checked.
-Dynamic analysis can be used to generate type assertions or invariants
-For example
-e.
-For example, types identify program invariants to be preserved during code modifications, to generate marshalling and marshalling wrappers, or even to guide library synthesis and regeneration.
+\heading{Type Invariant Discovery}
+Extracting typing information is helpful in a variety of ways, as type safety is an important property helpful in variety of scenarios. 
+%and types are lightweight annotations that can be quickly and efficiently checked.
+For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (ii) guide program synthesis and regeneration~\cite{daikon}.
 This is especially problematic in dynamic programming languages:
-  in the absence of type signatures, there is not much one can say about a \ttt{http.request} object.
-
-To make this concrete, consider the case of the \ttt{gRPC} library for serializing and de-serializing objects.
-Given a ---say, a simple bignum library or a crypto---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
+  in the absence of static type signatures, there is not much one can say about a object \ttt{o} without executing it and introspecting its properties.
+
+As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
+Given a value returned from a library call---say, a bignum or crypto library---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
 if the type changes, because of a library version change or because of changes in the .
 
+Dynamic analysis can be used to generate type assertions or invariants.
 The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
@@
 It is unclear how to wrap values without any kind of size information.\footnote{
-  Recent advances show promise: C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} provide type-aware heap traversal for C programs.
+  Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
 }

### 2020-01-14 tst/working/synthetic/t6/main.js
Created script to run sythetic -- rerun tests

@@ -1,11 +1,23 @@
-lyaConfig = {
-    SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
-    analysisCh: 9,
-};
-let lya = require("../../../../src/txfm.js");
-require = lya.configRequire(require, lyaConfig);
+if (parseInt(process.env.key) != 0) {
+        lyaConfig = {
+        SAVE_RESULTS: require("path").join(__dirname, "dynamic.json"),
+        analysisCh: parseInt(process.env.key),
+        };
+        let lya = require("../../../../src/txfm.js");
+        require = lya.configRequire(require, lyaConfig);
+}
+const time = process.hrtime();
+const fs = require('fs');
 
 
 let x = require("./m1.js");
 console.log(x);
 let y = x + 1;
+
+const diff = process.hrtime(time);
+const thisTime = (diff[0] * 1e9 + diff[1]) * 1e-6;
+var logger = fs.createWriteStream('timetest.txt', {
+  flags: 'a' // 'a' means appending (old data will be preserved)
+})
+logger.write('The time of ' + parseInt(process.env.key) + ' is ' + thisTime + ' \n', 'utf-8');
+

### 2020-01-14 paper/draft.tex
Added meso2.pdf times *1000
Add times for all synthetic

--- 2020-01-14 paper/draft.tex
@@
 \midrule
-something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
-something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
-something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
-something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
-something5    &           &  24214  &   24721  &   24574  &   24502   \\
+something1    &   0.90    &  4.70   &  4.54   &  4.30   &  -   \\
+something2    &   1.44    &  6.46   &  6.24   &  5.96   &  -   \\
+something3    &   3.37    &  6.26   &  6.32   &  5.72   &  -   \\
+something4    &   7.79    &  13.54  &  13.31  &  12.8   &  -   \\
+something5    &   24661   &  24848  &  24754  &  24760  &  -   \\
+something6    &   4.06    &  7.24   &  7.16   &  6.79   &  -   \\
+something7    &   4.11    &  7.25   &  7.23   &  6.86   &  -   \\
+something8    &   4.32    &  8.32   &  8.19   &  7.73   &  -   \\
 \bottomrule
@@
   \centering
-   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
+   \includegraphics[width=0.95\textwidth]{./figs/meso2.pdf}
   \caption{

### 2020-01-15 paper/draft.tex

--- 2020-01-14 paper/draft.tex
@@
 
+\newcommand{\R}{\ttt{R}\xspace}
+\newcommand{\W}{\ttt{W}\xspace}
+\newcommand{\X}{\ttt{X}\xspace}
+\newcommand{\E}{\ttt{X}\xspace}
+\newcommand{\rwx}{\ttt{RWX}\xspace}
+
 % FIXME:
@@
 A single application today often incorporates multiple libraries written and published by several different authors.
-To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
-These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
-Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.
+To make the difficulties of analyzing such library-overreliant software more concrete, we describe three example analyses~\sx{examples}.
+These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules~\sx{goals}.
+Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
+  internals of module systems~\sx{bg1}.
 
@@
 \heading{Type Invariant Discovery}
-Extracting typing information is helpful in a variety of ways, as type safety is an important property helpful in variety of scenarios. 
+Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
 %and types are lightweight annotations that can be quickly and efficiently checked.
-For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (ii) guide program synthesis and regeneration~\cite{daikon}.
-This is especially problematic in dynamic programming languages:
-  in the absence of static type signatures, there is not much one can say about a object \ttt{o} without executing it and introspecting its properties.
+For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
+This is especially important in dynamic programming languages:
+  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.
 
 As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
-Given a value returned from a library call---say, a bignum or crypto library---a developer has to first run the library manually, take note of the result, and then write a protocol buffer specification file declaring the type; %, common in distributed systems
-if the type changes, because of a library version change or because of changes in the .
-
-Dynamic analysis can be used to generate type assertions or invariants.
-The static type system is defined as a variant of a simply-typed lambda calculus augmented with union types.
-A simple approach would be to define a very simple type system that captures the type of a value by observing the execution of the program---after all, the types are dynamically checked!
-The analysis could also capture union types, for cases where it observes that a variable is at times witnessed to hold values of different types---although a single program tends to make calls of the same type signature across its entire lifetime~\cite{daikon}.
-The analysis could also do some type ``unpacking'' to deconstruct a type to its structural primitives---for example, noting that an object of type user is comprised of two strings (first and last name) and a number (age).
+To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
+Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec. %, common in distributed systems
+This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.
+
+Dynamic analysis can be used to discover such type assertions or invariants.
+The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the library boundaries by observing the execution of the program.
+%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
 
@@
    Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
-\fixme{No UX!}
 }
 \label{fig:ex2}
-\vspace{-2mm}
+\vspace{-4mm}
 \end{figure*}
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.
-
-In practice, the aforementioned dialysis stages can be implemented in two different ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
-The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
-
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
-It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
-  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
-  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
-% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
-%   we expand on in the discussion section~\sx{reqs}.
+% Fixme switch from libraries to modules?
+
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4.
+We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses developed with \sys~\sx{impl2}.
+We postpone discussion of how other environments diverge from JavaScript for later~\sx{reqs}.
+
+The aforementioned dialysis design can be implemented in either of two ways.
+The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place.
+% with the techniques described earlier.
+The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
+
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system;
+  we went with the second approach, as avoiding tight coupling has several benefits:
+  it does not require \sys's users to have a second Node copy only for running analyses;
+  it removes \sys's developers from the critical path of updates between the Node developers and its users; 
+  and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
+The primary drawback was missing a few  opportunities for runtime-performance and development-effort.
 

### 2020-01-15 tst/jalangi_test/simpleAnalysis/analysis.js
Add jalangi analysis

@@ -1,0 +1,68 @@
+/*
+ * Copyright 2014 Samsung Information Systems America, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *        http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+// Author: Koushik Sen
+
+// do not remove the following comment
+// JALANGI DO NOT INSTRUMENT
+
+/**
+ * @file A template for writing a Jalangi 2 analysis
+ * @author  Koushik Sen
+ *
+ */
+
+(function (sandbox) {
+    var globalsDecl = {};
+
+    function MyAnalysis() {
+	/**
+         * This callback is called after a variable is read.
+         *
+         * @param {number} iid - Static unique instruction identifier of this callback
+         * @param {string} name - Name of the variable being read
+         * @param {*} val - Value read from the variable
+         * @param {boolean} isGlobal - True if the variable is not declared using <tt>var</tt> (e.g. <tt>console</tt>)
+         * @param {boolean} isScriptLocal - True if the variable is declared in the global scope using <tt>var</tt>
+         * @returns {{result: *} | undefined} - If an object is returned, the result of the read operation is
+         * replaced with the value stored in the <tt>result</tt> property of the object.
+         */
+	
+        this.read = function (iid, name, val, isGlobal, isScriptLocal) {
+	    if (isGlobal) {
+	        if (globalsDecl[name] === undefined) {
+		    globalsDecl[name] = true;
+		}
+ 	    }
+	    return {result: val};
+        };
+        /**
+         * This callback is called when an execution terminates in node.js.  In a browser environment, the callback is
+         * called if ChainedAnalyses.js or ChainedAnalysesNoCheck.js is used and Alt-Shift-T is pressed.
+         *
+         * @returns {undefined} - Any return value is ignored
+         */
+        this.endExecution = function () {
+	    console.log(globalsDecl);
+        };
+    }
+
+    sandbox.analysis = new MyAnalysis();
+})(J$);
+
+
+
+

### 2020-01-15 tst/jalangi_test/simpleAnalysis/example_jalangi_.js

@@ -1,0 +1,69 @@
+J$.iids = {"8":[36,25,36,31],"9":[26,13,26,15],"10":[31,17,31,28],"16":[35,21,35,27],"17":[26,13,26,15],"18":[31,17,31,31],"24":[44,15,44,26],"25":[26,13,26,15],"26":[33,26,33,35],"32":[47,17,47,26],"33":[27,10,27,13],"34":[33,26,33,37],"40":[52,17,52,23],"41":[27,10,27,13],"42":[33,17,33,38],"49":[27,10,27,13],"50":[33,15,33,39],"57":[28,10,28,13],"58":[35,21,35,27],"65":[28,10,28,13],"66":[35,29,35,32],"73":[28,10,28,13],"81":[31,17,31,21],"82":[36,25,36,31],"89":[31,17,31,24],"90":[36,33,36,36],"97":[31,27,31,28],"105":[31,29,31,31],"106":[37,18,37,22],"113":[31,17,31,31],"114":[37,18,37,24],"121":[31,17,31,31],"122":[37,15,37,25],"129":[32,15,32,19],"130":[37,15,37,27],"137":[32,15,32,23],"138":[37,39,37,42],"145":[32,15,32,23],"146":[37,38,37,51],"153":[32,15,32,23],"154":[37,56,37,60],"161":[33,17,33,19],"162":[37,34,37,60],"169":[33,22,33,25],"170":[44,19,44,24],"177":[33,26,33,27],"178":[44,19,44,26],"185":[33,28,33,32],"186":[44,15,44,26],"193":[33,28,33,35],"194":[44,28,44,31],"201":[33,36,33,37],"209":[33,22,33,38],"210":[47,17,47,26],"217":[33,15,33,39],"218":[47,28,47,31],"225":[33,15,33,39],"233":[35,18,35,19],"234":[48,14,48,21],"241":[35,18,35,19],"242":[52,17,52,23],"249":[35,18,35,19],"250":[52,25,52,28],"257":[35,21,35,22],"265":[35,25,35,27],"266":[52,25,52,28],"274":[53,24,53,28],"281":[35,31,35,32],"282":[53,24,53,30],"289":[35,29,35,32],"290":[53,21,53,31],"297":[36,22,36,23],"298":[53,21,53,33],"305":[36,22,36,23],"306":[53,19,53,34],"313":[36,22,36,23],"321":[36,25,36,26],"329":[36,29,36,31],"345":[36,35,36,36]
[…]

### 2020-01-15 tst/jalangi_test/simpleAnalysis/run.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+
+set -e
+
+[ -e timeResultsJalangiEns.txt ] && rm timeResultsJalangiEns.txt
+[ -e timeResultsJalangiDir.txt ] && rm timeResultsJalangiDir.txt
+[ -e timeResultsJalangi.txt    ] && rm timeResultsJalangi.txt
+
+input="../tests/sunspider1/LIST"
+while IFS= read -r line
+do
+        name=$line.js
+        echo "******************************"
+        echo "We are processing this: $name"
+	echo "The name of file $name" >> timeResultsJalangiEns.txt
+        echo "The name of file $name" >> timeResultsJalangiDir.txt
+        echo "The name of file $name" >> timeResultsJalangi.txt
+
+        (time node ../src/js/commands/esnstrument_cli.js --inlineIID --inlineSource  ../tests/sunspider1/$name) > /dev/null 2>> "timeResultsJalangiEns.txt"
+        (time node ../src/js/commands/direct.js --analysis analysis.js ../tests/sunspider1/$name) > /dev/null 2>> "timeResultsJalangiDir.txt"
+        (time node ../src/js/commands/jalangi.js --inlineIID --inlineSource --analysis analysis.js ../tests/sunspider1/$name) > /dev/null 2>> "timeResultsJalangi.txt"
+done < "$input"
+

### 2020-01-15 paper/draft.tex
Update evaluation

--- 2020-01-15 paper/draft.tex
@@
 The type system is modeled after the simply-typed lambda calculus augmented with:
-  (i) unions (sum types), such as \ttt{a | b | c}; 
-  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}; and
+  (i) unions (sum types), such as \ttt{a | b | c}, 
+  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}, and
   (iii) a \ttt{native} type for values that cannot be serialized, like \ttt{console.log}.
@@
 
-\sys's  development achieves goals~\goal{1--3}~\sx{goals}, demonstrating that it is indeed feasible to construct a framework that operates at the level of modules, 
-does not force developers to learn a new language, and that it can be implemented as a library around an existing runtime.
-Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
-
-In this section, we are interested in zooming into \sys's performance characteristics~\goal{4}.
-At a high level, we are interested in three questions:
+\sys's  development achieves goals~\sx{goals}, demonstrating that it is indeed feasible to build a frameworks that 
+  operates as a library around an existing runtime,
+  does not require learning a new language and tools, and 
+  gets meaningful information by operating only at library boundaries, 
+% Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
+In this section, we report on \sys's performance characteristics:
+% At a high level, we are interested in three questions:
   (i) the overheads of the \sys's underlying building blocks;
-(ii) the overhead of different analysis on real libraries and how this compares with production dynamic analysis frameworks; and
-(iii) evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
+  (ii) the overhead of different analysis on real libraries, and how this compares with production dynamic analysis frameworks; and
+  (iii) an evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
 % For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
@@
 Several takeaways are worth highlighting.
-\fixme{TODO after we have the results.}
-
-Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
-In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu 14.04.6 version}, Jalangi \fixme{v2}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
-We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.
+Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation frameworks.
+\sys supports high-performance analysis at the boundaries of individual libraries, adding on average less than \fixme{2$\times$}.
+Finally, \sys seems to scale well to large applications with hundreds of libraries while interposing on several thousands of objects.
+
+Experiments were conducted on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
+In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
+All times reported are in \textbf{ms}, averaged over 1K runs;
+  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type-invariant discovery.
 
@@
 
-\sys's micro-benchmark suite was designed with two goals in mind.
-
-The first goal was to test key properties of each analysis and confirm it outputs the expected results.
-For example, to better understand performance diagnosis policy and confirm it works correctly, we craft a library that contains four other libraries with pre-defined bottlenecks.
-The library can perform one of three operations, depending on its current state:
-  (i) invoke a call to a module it imports,
-  (ii) busy-wait, or
-  (iii) respond to calls by returning a value.
-
-The second goal was to identify understand \sys bottlenecks in a controlled environment, 
-Both of these goals would have been difficult to achieve outside a synthetic environment, as we do not fully understand applications we haven't written ourselves.
+\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
+For example, to better understand PD and confirm it works correctly, we craft a micro-benchmark with four dependencies of known static bottlenecks.
+% Each dependency can perform one of three operations, depending on its current state:
+%   (i) invoke a call to a module it imports,
+%   (ii) busy-wait for a specific amount of time, or
+%   (iii) respond to calls by returning a value.
+A second goal was to understand \sys's internal overheads in a controlled environment.
+% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.
 
@@
 		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
+    All timings are in $ms$.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
 \toprule
-              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
+	            &   Base    &  SA     & PD      &  TID    \\
 \midrule
-something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
-something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
-something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
-something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
-something5    &           &  24214  &   24721  &   24574  &   24502   \\
+globals.js    &   0.90    &  4.70   &  4.54   &  4.30   \\
+something2    &   1.44    &  6.46   &  6.24   &  5.96   \\
+counter.js    &   3.37    &  6.26   &  6.32   &  5.72   \\
+something4    &   7.79    &  13.54  &  13.31  &  12.8   \\
+delay.js      &   24661   &  24848  &  24754  &  24760  \\
+something6    &   4.06    &  7.24   &  7.16   &  6.79   \\
+something7    &   4.11    &  7.25   &  7.23   &  6.86   \\
+cycles.js     &   4.32    &  8.32   &  8.19   &  7.73   \\
 \bottomrule
@@
 \end{table}
+
+Table~\ref{tab:synthetic} depicts the results of the three analysis applied to a subset of our benchmarks.
+Not all analysis-benchmark combinations are useful---\ie some modules do not feature interesting access or performance patterns.
+Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
+The \ttt{delay.js} is the PD benchmark mentioned earlier, with static bottlenecks.
+Initial loading time, affected by transformations altering the environment, is not affected (delta is under 1ms).
+
+To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
+  unmodified and proxy-wrapped.
+Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
+We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
+The proxy-wrapped version introduces interposition at every level.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+
+We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
 
@@
   \footnotesize{
-    \textbf{Applying \sys to single-library programs}.
-		\fixme{Execution time of eight test suites against }
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
+    \textbf{\sys-augmented single-library programs}.
+    The table shows the overheads of applying the three analyses to the test suites of eight libraries (with Minimist involving five test cases).
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
 \toprule
-                    & Base   &  SA   & PD     &   TIC   & LSR     \\
+                               & Base   &  SA   & PD     &   TID   \\
 \midrule
-Classnames~\cite{}  &  2.72  & 6.62  &  6.61  &  6.10   & 5.94    \\
-Debug~\cite{}       & 31.39  & 33.54 &  33.94 &  33.96  & 33.04   \\
-% Minimist\\
-~~~-t1              & 31.46  & 60.13 &  60.00 &  56.62  & 56.72   \\
-~~~-t2              & 19.17  & 59.77 &  60.75 &  57.15  & 57.79   \\
-~~~-t3              & 21.64  & 205.2 &  205.53&  132.25 & 137.84  \\
-~~~-t4              & 20.69  & 59.70 &  60.75 &  59.92  & 56.60   \\
-~~~-t5              & 20.49  & 70.48 &  72.20 &  64.71  & 66.03   \\
-Moment~\cite{}      & 31.73  & 48.04 &  49.23 &  44.95  & 46.12   \\
-yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
-chalk~\cite{} 	    & 17.37  & 24.42 &  26.01 &  26.32  & 0.00    \\
-colorette~\cite{}   & 08.10  & 13.85 &  13.41 &  13.16  & 0.00    \\
-mkdirp~\cite{}      & 116.37 & 1959.52 & 1392.64 & 1252 & 0.00    \\
+Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
+Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
+Minimist~\cite{minimist}       &        &       &        &         \\
+~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
+~~~-t2                         & 19.17  & 59.77 &  60.75 &  57.15  \\
+~~~-t3                         & 21.64  & 205.2 &  205.53&  132.25 \\
+~~~-t4                         & 20.69  & 59.70 &  60.75 &  59.92  \\
+~~~-t5                         & 20.49  & 70.48 &  72.20 &  64.71  \\
+Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
+yargs~\cite{yargs}             & 13.42  & 13.00 &  14.41 &  13.47  \\
+chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
+colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
+mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
 \bottomrule
@@
 
-Table~\ref{} depicts the results of the three analysis applied to these benchmarks.
-We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
-Currently, these benchmarks return the results we expect, but they did help with the identification of problems such as 
-These be
-Load is visible at the application level (left), but the lack of detail does not help determine which modules must be scaled out.
-Module-level data, collected by \sys' coordinator (right), reveal that \ttt{m3} receives the majority of the load.
-
-To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
-  unmodified and proxy-wrapped.
-Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
-We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
-The proxy-wrapped version introduces interposition at every level.
-Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
-
-We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
-  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
-The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
-
-\subsection{Single-module Benchmarks}
+\subsection{Single-Library Benchmarks}
 \label{meso}
@@
 
+To understand \sys's performance characteristics at the level of individual modules, we perform two experiments.
+
+In the first experiment, we collect a diverse set of eight popular libraries from npm, 
+% used by thousands of other projects,
+on the order of hundreds of lines of code.
+As a workload, we use the project-internal test suite that comes bundled with each library (invocable by \ttt{npm test});
+  \ttt{minimist} involves several distinct test harnesses, which we 
+These tests stress functionality as expected by the authors of the library, and confirms compatibility with all of its functionality.
+We apply \sys using the three analyses we developed, and compare the results with their baseline performance (Tab.~\ref{tab:meso}).
+The results show that executions augmented with analyses are within 2$\times$, averaging \fixme{XX\%}.
+Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as \fixme{XXX} wrappers, as shown by the resulting analysis output on disk.
+
+In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
+To be fair in our comparison, we design a simple analysis from scratch that both frameworks can support---namely, one for tracking counts of global variable accesses~\sx{impl2}.
+The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
+  the effort of employing \sys as a library was significantly lower than Jalangi2, for which we \fixme{relied} on a Docker container to simplify the framework's setup.
+The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
+We note here that Jalangi2 has a runtime performance that is significantly faster than the classic Jalangi, as it eschews record/replay capabilities.
+Jalangi2 is more powerful, expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.
+
 \subsection{End-to-End Benchmarks}
@@
 
-\begin{table}[t]
+\begin{table}[b]
 \center
@@
     \textbf{Applying \sys to three large applications}.
-		\fixme{Highlight some things}
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
+    The table shows the overheads of applying the three analyses to three large applications.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ccc}
 \toprule
-                    & Koa    & Moeda   &  Terminalizer \\
+                                     & KoaBlog~\cite{koa}    & Moeda~\cite{moeda}   &  Term/zr~\cite{terminalizer} \\
 \midrule
- Size (KB)          & 41M    &  29M    &   262M        \\
- LoC                & 127K   &  79K    &   39K         \\
- Top-level modules  &  24    &  7      &    33         \\
- Total Modules      &  432   &  260    &    1084       \\
- Lya detects:       &  1507  &   729   &     2355      \\
- Baseline           &  0.97  &  1.27   &    0.754      \\
- A1 (TF)            &  1.48  &  2.00   &    3.346      \\
- A3 (HF)            &  1.30  &  2.684  &    2.684      \\
- A8 (Types)         &  1.32  &  2.036  &    2.615      \\     
+Structure                            &                   &                      &              \\
+~~Size (MB)                          & 41                &  29                  &   262        \\
+~~Code Size (KLoC)                   & 127               &  79                  &   39         \\
+~~Top-level Modules, statically      &  24               &  7                   &    33         \\
+~~Total Modules, statically (npm)    &  432              &  260                 &    1084       \\
+~~Total Modules, dynamically (\sys)  &  1507             &   729                &     2355      \\
+%                                     &                   &                      &              \\
+Performance                          &                   &                      &              \\
+~~Baseline                           &  0.97             &  1.27                &    0.754      \\
+~~Security Analysis                  &  1.48             &  2.00                &    3.346      \\
+~~Performance Diagnosis              &  1.30             &  2.684               &    2.684      \\
+~~Type Invariant Discovery           &  1.32             &  2.036               &    2.615      \\     
 \bottomrule
@@
 
-Highly popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
-Applying \sys to these applications generates much larger analayses
-For example, the performance diagnosis analysis hooks reports timing characteristics for
-
-The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few different reasons.
-One is that an analysis does not report accesses if a 
-\sys analyzes modules that are part of the standard library too (some of which have themselves internal dependencies), which are not shown by \ttt{npm}.
-Our post-processing counts by module name (\ie squashes duplicate reports by 
+Finally, we perform end-to-end program dialysis  on three large, popular applications:
+  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework,
+  Modeda~\cite{moeda}, a CLI converter that, among other features, uses online currency exchange rates to convert currencies from the terminal, and
+  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generating animated gif images and shareable a web player links.
+These are popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
+Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.
+
+The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few reasons.
+One is that \sys does not report accesses if a library has not been accessed, whereas \ttt{npm} traverses reports on the static library structure.
+Additionally, \sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
+
+Applying \sys to these applications generates much larger analysis results, while the performance of analyzed code is on average still within 2--3$\times$ over the baseline.
+The size of the resulting JSON files raises the challenge of analysis interpretability---surprisingly, just running Terminalizer with \ttt{--help} returns more than 6K entries from several libraries.
+Our routines for post-processes \sys's results also counts by module name---\ie squashes duplicate reports by human-name, not module identifier.
 This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
 For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
-It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{cache}).
+It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
 Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
@@
 
-JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework;
-\fixme{Rather than extracting accesses, it arms developers with the ability to write access control contracts (\ie executable partial specifications)}.
-This capability is complimentary to \sys's security analysis model~\sx{examples}, illustrating a need for a general-purpose online analysis framework.
-% \ie their analysis can be implemented on top of \sys with significantly less effort.
-% build around proxies.
+%% JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework;
+%% \fixme{Rather than extracting accesses, it arms developers with the ability to write access control contracts (\ie executable partial specifications)}.
+%% This capability is complimentary to \sys's security analysis model~\sx{examples}, illustrating a need for a general-purpose online analysis framework.
+%% % \ie their analysis can be implemented on top of \sys with significantly less effort.
+%% % build around proxies.
 

### 2020-01-15 paper/draft.tex
Updated table 2

@@
 ~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
-~~~-t2                         & 19.17  & 59.77 &  60.75 &  57.15  \\
-~~~-t3                         & 21.64  & 205.2 &  205.53&  132.25 \\
-~~~-t4                         & 20.69  & 59.70 &  60.75 &  59.92  \\
-~~~-t5                         & 20.49  & 70.48 &  72.20 &  64.71  \\
+~~~-t2                         & 29.35  & 56.30 &  53.98 &  53.17  \\
+~~~-t3                         & 30.34  & 59.13 &  55.76 &  55.34  \\
+~~~-t4                         & 30.04  & 56.40 &  53.68 &  53.27  \\
+~~~-t5                         & 30.24  & 58.17 &  55.07 &  54.76  \\
 Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
-yargs~\cite{yargs}             & 13.42  & 13.00 &  14.41 &  13.47  \\
+yargs~\cite{yargs}             & 14.59  & 15.68 &  15.49 &  15.54  \\
 chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\

### 2020-01-15 paper/draft.tex
Fixes

--- 2020-01-15 paper/draft.tex
@@
 \usepackage{amsmath}
+\usepackage{listings}
+
+\lstdefinelanguage{js}{
+  morekeywords={typeof, let, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+  keywordstyle=\color{purple}\ttfamily,
+  keywordstyle=[3]\color{orange},
+  keywords=[3]{SBX, PROC},
+  ndkeywords={class, export, require, boolean, throw, implements, import, this},
+  ndkeywordstyle=\color{cyan}\ttfamily, %bfseries
+  identifierstyle=\color{black},
+  sensitive=false,
+  comment=[l]{//},
+  commentstyle=\color{lightgray},
+% morecomment=[s]{/\\*\\*, \\*/},
+  stringstyle=\color{blue}\ttfamily,
+  basicstyle=\footnotesize\ttfamily,  % the size of the fonts that are used for the code
+  numberstyle=\tiny\color{gray},   % the style that is used for the line-numbers
+  morestring=[b]',
+  morestring=[b]",
+% moredelim=[s][\color{gray}]{c:}{>},
+% moredelim=[s][\color{orange}]{/*}{/}
+}
+
+\lstdefinelanguage{es}{
+  morekeywords={string, number, bool, p, v, e, x},
+  keywordstyle=\color{darkgray},
+  keywordstyle=[3]\color{orange},
+  keywords=[3]{SBX, PROC},
+  ndkeywords={undefined, null, delete},
+  ndkeywordstyle=\color{black}\ttfamily\bfseries,
+  identifierstyle=\color{black},
+  sensitive=false,
+  comment=[l]{//},
+  commentstyle=\color{lightgray},
+% morecomment=[s]{/\\*\\*, \\*/},
+  stringstyle=\color{darkgray}\ttfamily,
+  morestring=[b]',
+  morestring=[b]",
+% numbersep=1pt,
+% numberstyle=\footnotesize\bf\color{gray},   % the style that is used for the line-numbers
+  abovecaptionskip=0em,
+  aboveskip=0em,
+  belowcaptionskip=0em,
+  belowskip=0em,
+  frame=none,                     % adds a frame around the code
+% moredelim=[s][\color{gray}]{c:}{>},
+% moredelim=[s][\color{orange}]{/*}{/}
+}
+
+\lstset{ %
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  basicstyle=\small\ttfamily,  % the size of the fonts that are used for the code
+  upquote=true,
+  captionpos=b,                    % sets the caption-position to bottom
+% frame=B,                    % adds a frame around the code
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=3pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{gray},   % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+}
 
@@
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4.
-We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses developed with \sys~\sx{impl2}.
-We postpone discussion of how other environments diverge from JavaScript for later~\sx{reqs}.
+This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
+% We start with the internals of \sys's implementation, and then describe
+including the three analyses developed atop \sys~\sx{impl2}.
+Discussion of how other environments diverge from JavaScript is left for the next section~\sx{reqs}.
 
 The aforementioned dialysis design can be implemented in either of two ways.
-The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place.
-% with the techniques described earlier.
+The first is to implement \sys as a modified version of the runtime, in which several stages of its library-loading facility have been augmented in-place. % with the techniques described earlier.
 The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
-
-With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system;
-  we went with the second approach, as avoiding tight coupling has several benefits:
+% 
+With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system.
+We went with the second approach, as looser coupling seems to have several benefits:
   it does not require \sys's users to have a second Node copy only for running analyses;
@@
   and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
-The primary drawback was missing a few  opportunities for runtime-performance and development-effort.
-
-% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
+The primary drawback was missing a few opportunities for lowering runtime-performance and development-effort.
+
+% It sketches the Node runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
 
@@
 Node's module system is implemented entirely in JavaScript, exposing a library-local \ttt{require} function for importing modules.
-Loading a fresh module with \ttt{require("foo");} corresponds to the following five stages, all of which are augmented by \sys:
+Loading a fresh module % with \ttt{require("foo")}
+  corresponds to the following five stages, all of which are augmented by \sys:
 (R) Resolution: identify the file to which the module specified corresponds, locate it in the file-system, and assign its absolute path as a module identifier.
@@
 % Identifiers are absolute paths.
-(W) Wrapping: wrap the module so local names do not escape the module's scope and Node's module-local names get resolved.
+(W) Wrapping: wrap the module so that local names do not escape the module's scope and Node's module-local names get resolved.
 (E) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
@@
 Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
-\sys replaces Node's wrapper function in order to add a last variable in the function definition, \ttt{CTX}.
-\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.js:
-  (i) identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit;
-  (ii) Node's global names are described at various parts of the documentation; and
-  (iii) library-local required close inspection of Node's internals; fortunately, these were only five names.
+\sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
+\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.
+Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
+Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, these were only five names.
 
@@
 
-% \begin{verbatim}
+% \begin{lstlisting}
 % let lib = `
@@
 %  });`;
-% \end{verbatim}
+% \end{lstlisting}
 
@@
 The configuration object accepts \ttt{only} and \ttt{not} expressions that indicate whether a module identifier will be part of the analysis.
-These expressions contain sets of sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
-Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose them to users.
-Examples of use include blacklisting built-in libraries or white-listing only the newest-imported library.
+These expressions contain sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
+Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose it to \sys's users.
+Examples of its use include blacklisting built-in libraries or white-listing only the library imported most recently.
 % This is useful, for example, when...
@@
 Fig.~\ref{fig:ex2} exemplifies \sys's transformation techniques in the context of JavaScript.
-\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
+\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers, creates a modified version of the surrounding context, and binds it to the library.
 
@@
 \sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
-Individual analyses are between 100--200 lines of code, but a significant part of this code is common across analyses.
+Individual analyses are about 60 lines of code, but a significant part of this code is common across them.
 
@@
 
-\begin{verbatim}
-let fs = require('fs');
+\begin{lstlisting}
+let fs = require("fs");
 let count = {};
@@
 };
-process.on('exit', () => {
-  fs.writeFileSync('acl.json',
-                   'utf-8',
+process.on("exit", () => {
+  fs.writeFileSync("acl.json",
+                   "utf-8",
                    JSON.stringify(count));
 });
-\end{verbatim}
+\end{lstlisting}
 
@@
 \heading{Security Analysis}
-To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
+To address the security concerns of third-party libraries, we developed a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
 The analysis treats built-in libraries and global variables as modules,
@@
  (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
- (iii)  an execute permission (\X) indicates that a consumer to executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).
-
-The resulting permission sets are organized as a collection of maps, one per library, each indexed by object-paths such as \ttt{Math.add: RX}.
+ (iii)  an execute permission (\X) indicates that a consumer executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).
+
+The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{Math.add: RX}.
 % that correspond to values of other modules or global-like language names.
@@
 \heading{Performance Diagnosis}
-To conduct performance diagnosis, we develop a profiling analysis that operates at two levels:
- (i) module-boundary wrappers that collecting profiling statistics for calls between modules by wrapping module interfaces; and
+We develop a profiling analysis that operates at two levels:
+ (i) module-boundary wrappers that collect profiling statistics for calls between modules by wrapping module interfaces; and
  (ii) an aggregator function that collects statistics from all boundary wrappers and generates a model of library load under the current workload.
@@
 Boundary wrappers operate at a higher-frequency intervals than the aggregator, which operates on summaries.
-Their analysis focuses on function values (\eg functions, methods, constructors), skipping all other direct field accesses.
+Their analysis focuses on function calls, skipping all other direct field accesses.
 Functions are wrapped with prologue and epilogue wrappers that record statistics from the Node.js runtime---for now, a frequency counter and a timer between prologue-to-epilogue invocations.
@@
 \heading{Type Invariant Discovery}
-To infer type invariants for serialization specifications, we develop a simple type system and use our analysis to map values to types.
-
-The type system is modeled after the simply-typed lambda calculus augmented with:
+To infer type invariants for serialization specifications, we base our analysis on a simple type system modeled after the simply-typed lambda calculus augmented with:
   (i) unions (sum types), such as \ttt{a | b | c}, 
   (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}, and
-  (iii) a \ttt{native} type for values that cannot be serialized, like \ttt{console.log}.
+  (iii) a \ttt{native} type for values that cannot be serialized, such as \ttt{console.log}.
 Support for union types is useful for when our analysis witnesses variables holding values of different types---although, in practice,  programs tend to make calls of the same type across their entire lifetime~\cite{daikon}.
@@
 % Knowing how to deconstruct a type to its structural primitives allows walking values---
-For example, the analysis extracts that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
+For example, it unpacks a type \ttt{user} into two \ttt{string}s (first and last name) and a \ttt{number} (age).
 % To achieve this, the analysis makes use of introspection to identify
@@
 
-\sys's  development achieves goals~\sx{goals}, demonstrating that it is indeed feasible to build a frameworks that 
+\sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
   operates as a library around an existing runtime,
-  does not require learning a new language and tools, and 
-  gets meaningful information by operating only at library boundaries, 
+  does not require learning a new language, and 
+  gets meaningful information while operating only at library boundaries.
 % Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
@@
 % At a high level, we are interested in three questions:
-  (i) the overheads of the \sys's underlying building blocks;
-  (ii) the overhead of different analysis on real libraries, and how this compares with production dynamic analysis frameworks; and
-  (iii) an evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
+  (i) the overheads of its underlying building blocks;
+  (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
+  (iii) \sys's behavior on realistic  multi-library applications.
 % For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
@@
 Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation frameworks.
-\sys supports high-performance analysis at the boundaries of individual libraries, adding on average less than \fixme{2$\times$}.
-Finally, \sys seems to scale well to large applications with hundreds of libraries while interposing on several thousands of objects.
+\sys's library-level analysis adds a small overhead, less than $2\times$ for the vast majority of libraries and often less than $5ms$.
+Finally, \sys scales to large applications with hundreds of libraries while interposing on several thousands of objects.
 
@@
 All times reported are in \textbf{ms}, averaged over 1K runs;
-  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type-invariant discovery.
+  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type invariant discovery.
 
@@
 \midrule
-globals.js    &   0.90    &  4.70   &  4.54   &  4.30   \\
-something2    &   1.44    &  6.46   &  6.24   &  5.96   \\
-counter.js    &   3.37    &  6.26   &  6.32   &  5.72   \\
-something4    &   7.79    &  13.54  &  13.31  &  12.8   \\
-delay.js      &   24661   &  24848  &  24754  &  24760  \\
-something6    &   4.06    &  7.24   &  7.16   &  6.79   \\
-something7    &   4.11    &  7.25   &  7.23   &  6.86   \\
-cycles.js     &   4.32    &  8.32   &  8.19   &  7.73   \\
+globals vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
+built-in fields  &   1.44    &  6.46   &  6.24   &  5.96   \\
+counter          &   3.37    &  6.26   &  6.32   &  5.72   \\
+all names        &   7.79    &  13.54  &  13.31  &  12.8   \\
+custom delays    &   24661   &  24848  &  24754  &  24760  \\
+direct-access    &   4.06    &  7.24   &  7.16   &  6.79   \\
+timple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
+cycles           &   4.32    &  8.32   &  8.19   &  7.73   \\
 \bottomrule
@@
 
-Table~\ref{tab:synthetic} depicts the results of the three analysis applied to a subset of our benchmarks.
-Not all analysis-benchmark combinations are useful---\ie some modules do not feature interesting access or performance patterns.
-Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
-The \ttt{delay.js} is the PD benchmark mentioned earlier, with static bottlenecks.
-Initial loading time, affected by transformations altering the environment, is not affected (delta is under 1ms).
+Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
+The first column indicates the focus of the benchmark; not all analysis-benchmark combinations are useful.
+% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
+For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
+The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
+Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
+  most of these benchmarks feature artificially tight loops with high-frequency accesses.
+Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
+% is not affected significantly % by transformations altering a library's context
 
@@
 Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
-
+% 
 We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
-  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
-The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
+  what is likely to be the overhead is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
 
@@
     \textbf{\sys-augmented single-library programs}.
-    The table shows the overheads of applying the three analyses to the test suites of eight libraries (with Minimist involving five test cases).
+    The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
   }
@@
     \textbf{Analysis overheads.}
-    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
-		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
-    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
+    The plot compares single-library programs taken from Jalangi2 between three setups:
+		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi2, (iii) global-use analysis with \sys.
+    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
   }
@@
 on the order of hundreds of lines of code.
-As a workload, we use the project-internal test suite that comes bundled with each library (invocable by \ttt{npm test});
-  \ttt{minimist} involves several distinct test harnesses, which we 
-These tests stress functionality as expected by the authors of the library, and confirms compatibility with all of its functionality.
+As a workload, we use each library's internal test suite, with \ttt{minimist} includes several distinct test harnesses.
+These tests stress functionality as expected by the library's authors and confirm that \sys does not break it.
 We apply \sys using the three analyses we developed, and compare the results with their baseline performance (Tab.~\ref{tab:meso}).
-The results show that executions augmented with analyses are within 2$\times$, averaging \fixme{XX\%}.
-Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as \fixme{XXX} wrappers, as shown by the resulting analysis output on disk.
+The results show that executions augmented with analyses are within 2--3$\times$, averaging a 80\% slowdown for the largest libraries.
+Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as 257 wrappers. % (shown by the analysis output).
 
 In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
-To be fair in our comparison, we design a simple analysis from scratch that both frameworks can support---namely, one for tracking counts of global variable accesses~\sx{impl2}.
+We note that Jalangi2 improves significantly over Jalangi's performance~\cite{jalangi}, as it eschews record/replay capabilities.
+To be fair in our comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
 The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
-  the effort of employing \sys as a library was significantly lower than Jalangi2, for which we \fixme{relied} on a Docker container to simplify the framework's setup.
+  the effort of employing \sys as a library was significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
 The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
-We note here that Jalangi2 has a runtime performance that is significantly faster than the classic Jalangi, as it eschews record/replay capabilities.
-Jalangi2 is more powerful, expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.
+Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.
 
@@
 
-Finally, we perform end-to-end program dialysis  on three large, popular applications:
+Finally, we perform end-to-end program dialysis on three large applications:
   KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework,
-  Modeda~\cite{moeda}, a CLI converter that, among other features, uses online currency exchange rates to convert currencies from the terminal, and
-  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generating animated gif images and shareable a web player links.
-These are popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
+  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates, and
+  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
+These applications are highly popular, with Koa.js and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
 Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.
 
-The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few reasons.
-One is that \sys does not report accesses if a library has not been accessed, whereas \ttt{npm} traverses reports on the static library structure.
-Additionally, \sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
-
-Applying \sys to these applications generates much larger analysis results, while the performance of analyzed code is on average still within 2--3$\times$ over the baseline.
-The size of the resulting JSON files raises the challenge of analysis interpretability---surprisingly, just running Terminalizer with \ttt{--help} returns more than 6K entries from several libraries.
-Our routines for post-processes \sys's results also counts by module name---\ie squashes duplicate reports by human-name, not module identifier.
-This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
-For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
-It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
+The differences between the number of sub-modules detected statically (by \ttt{npm ls}) and the ones observed by \sys are due to a few reasons.
+One is that \sys does not report accesses if a library has not been accessed at runtime, whereas \ttt{npm} traverses and reports on the entire dependency structure.
+\sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
+Finally, \sys generates several different return wrapped objects for the same libraries~\sx{three}.
+
+Applying \sys to these applications generates analysis results that are 9--132$\times$ larger than the ones for single libraries.
+However, the performance of analyzed code is on average still within 2--3$\times$ over the baseline performance.
+The size of the resulting JSON files raises the challenge of analysis interpretability---surprisingly, just running Terminalizer with \ttt{--help} still returns more than 6K fragments from several libraries.
+Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-name, not module identifier.
+This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries
+% For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
+We also squash cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but results in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
 Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
@@
 
-Program dialysis depends on a few features provided by the programming language.
-In this section, we start by describing its requirements~\sx{reqs} and then reflect on some of its strengths and weaknesses~\sx{principles}.
+In this section, we start by reflecting on the requirements of dialysis from the programming language~\sx{reqs} and then on some of its strengths and weaknesses~\sx{principles}.
+% Program dialysis depends on a few features provided by the programming language.
 
@@
   (i) it boasts the largest collection of libraries~\cite{modulecounts} and
-	(ii) we had prior experience developing more sophisticated version of the security and performance analyses.
-We now expand on the requirements for developing dialysis over other runtime environments.
+	(ii) we had prior experience developing more sophisticated versions of SA and PD.
+We now expand on the requirements bolting dialysis on other runtime environments.
 % FIXME: All these features have to have been discussed earlier
@@
 % This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
-  if it is a function (\eg JavaScript, Scheme, Racket), rewiring amounts to an overwrite;
-  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (at module-loading).
+  if it is a function (\eg JavaScript, Scheme, Racket), re-wiring amounts to an overwrite;
+  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (during module loading).
 % This is simplified by the fact that the import syntax is trivial.
@@
 
-\sys makes extensive use of hash-maps---to check for object equality, for cycles during traversal, and for prior wrapping.
+\sys makes extensive use of hash-maps to check for object equality, for cycles during traversal, and for prior wrapping.
 Hash-maps are supported by every programming language; many support storing weak references, which avoid affecting object reclamation in garbage-collected environments, and can be created either explicitly (\eg Python) or implicitly by using a ``weak'' structure (\eg JavaScript).
@@
 
-To conclude, all major languages provide facilities to support dialysis---albeit with a different level of convenience.
-Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations.
-Runtime transformations conveniently unify module identification with interposition:
-  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
-Compiled languages have other benefits, namely that applying transformations statically ameliorates their runtime overhead.
+To conclude, all major languages provide facilities to support dialysis, albeit with a different level of convenience.
+Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations, which conveniently unify module identification with interposition:
+  a single function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
+Static languages have other benefits, such as avoiding the runtime overheads of transformations by applying them at compile-time.
 % and type checking could further aid developers by issuing warnings of incompatible privilege settings.
@@
 By operating at coarser granularity, using the vanilla optimized runtime, and by toggling parts of the analysis on and off, it provides the ability to perform the analysis online.
-Finally, dialysis deconstructs programs only at library boundaries, a naturally coarser granularity that is just the right level for certain problems.
+Finally, it deconstructs programs only at library boundaries, a naturally coarser granularity that is just right for certain classes of problems.
 % a granularity that is well-suited for several tasks.

### 2020-01-16 paper/draft.tex
Minor corrections to paper

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Dynamic Program Dialysis with Lya}
+\title{\Large \bf Multi-library Program Dialysis with Lya}
 
@@
 {\rm Anonymous Author(s)}\\
-\normalsize{Submission \#225, 11 + 2 pages}\\
+\normalsize{Submission \#225, 11 + 3 pages}\\
 % \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
@@
 
-% Such library over-reliance is a recent trend: % in software engineering:
 Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
-% On the surface, such reliance is beneficial, 
-Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge of and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
-
-To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
-Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
-% is a general technique that
+Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
+
+To address these challenges, we present \emph{program dialysis}, a dynamic analysis technique specifically tailored to applications with many third-party libraries.
+Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
 It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
-Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries used on the web, server, and mobile.
-We develop a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-libraries application programs with low developer effort and performance overhead:
-  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual libraries, and scale to real applications with hundreds of libraries.
+Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries for the web, server, and mobile.
+We develop a series of case-studies that motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
+  insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
 
@@
 
-Dynamic analysis is a type of program analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
+Dynamic analysis is a type of analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
 Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
 Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
-  (i) current runtime information, such as profiling information, in view of changing load patterns~\cite{staticdynamic},
+  (i) current runtime information, such as profiling data, in view of changing load patterns~\cite{staticdynamic},
   (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
-  (iii) Turing-complete policies, where policies themselves are programs~\cite{contracts1, contracts2, contracts3},
+  (iii) Turing-complete policies, where monitors themselves are programs~\cite{contracts1, contracts2, contracts3},
   (iv) dynamic or runtime-reflection features, such as the ones present in Python and JavaScript~\cite{jsanalysis1, jsanalysis2}.
@@
   language-specific package repositories eliminate the cost of publishing and using a library.
-As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each often only a few lines long~\cite{leftpad, npmstudy:19}.
+As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each one often only a few lines long~\cite{leftpad, npmstudy:19}.
 % how to say thousands of them depend on a 11-line lib?
@@
 Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
-It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
+%                                                   !! sosto!!------.
+%                                                                   \/
+It operates during program execution, automating the wrapping and transformation of a program's dependency graph, and allows developers to extract meaningful insights with only a few lines of analysis-specific code.
 By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
-  (i) it allows bolting library dialysis itself as a library onto existing runtime environments with no dynamic analysis,
+  (i) it allows bolting analysis, itself as a library, onto unmodified runtime environments, % with no dynamic analysis,
   (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
@@
 We develop a diverse set of analyses that target practical information about a program:
-  an allow/deny security analysis,
+  a read-write-execute security analysis,
   a profiling analysis showing bottlenecked modules,
@@
   and an analysis extracting union-based type invariants.
-This set of analyses drives the design requirements for \sys, and highlights dialysis as a middle ground between coarse- and fine-grained analysis.
+These analyses drive the design requirements for \sys, and highlight dialysis as a middle ground between coarse- and fine-grained analysis.
 We evaluate \sys at three different levels:
@@
   (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
-  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
+  (iii) end-to-end full-application macro-benchmarks that showcase \sys's behavior on realistic workloads. 
 \S\ref{bg}--\ref{eval} present our key contributions:
@@
 \item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
-\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
+\item \S\ref{design} presents the design of dialysis, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
 \item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
-\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
+\item \S\ref{eval} evaluates \sys, showing that it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundred-library programs.
 \end{itemize}
@@
   it compares with related prior work in the literature~\sx{rw};
-  and closes with appropriate conclusions~\sx{end}.
+  and draws appropriate conclusions~\sx{end}.
 
@@
 Before describing these examples, however, we offer a brief refresher on the %abstractions and corresponding
-  internals of module systems~\sx{bg1}.
+  internals of a module system~\sx{bg1}.
 
@@
   it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
-  or (ii) provided by other developers sharing code others might find useful.
+  or (ii) is provided by other developers sharing code others might find useful.
 Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).
@@
 This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
-The definition of a value depends on the semantics of the language; for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+The definition of a value depends on the semantics of the language. % for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
 Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
@@
 Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
-This process starts by locating the library in the file system % or across the network,\footnote{
+This process starts by locating the library in the file system, % or across the network,\footnote{
 %   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
 % }
-by resolving relative or absolute identifiers.
+by resolving code-relative module identifiers.
 % The library is assigned a unique identifier.
-The content of the library is then read and wrapped in a way that resolves library-local names such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript to meaningful values.
+The content of the library is then read and wrapped in a way that resolves library-local names, such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript, to meaningful values.
 The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
@@
   by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
-Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible they are resolved by pointing to the cache.
+Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible, they are resolved by pointing to the cache.
 An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
-As a result, a single \ttt{import} \ttt{l} does not necessarily resolve to the same (version of the) library \ttt{l} every time.
+As a result, a single \ttt{import} $l$ does not necessarily resolve to the same (version of the) library $l$ every time.
 The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
@@
 Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
-  (i) an allow/deny security analysis,
+  (i) a read-write-execute security analysis,
   (ii) a performance-profiling analysis showing bottlenecked libraries, and
@@
   (iii) an analysis extracting runtime type invariants.
-These examples illuminate key design requirements for \sys's implementation of module-level dynamic analysis.
+These examples illuminate key design requirements for dialysis in general and \sys in particular.
+% \sys's implementation of module-level dynamic analysis.
 
@@
 Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
-Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its source code.
+Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its malicious payload.
 
@@
 Analyzing the behavior \emph{within} the library itself is not critical:
-  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then use \ttt{http} from the second library.
+  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then call \ttt{http} from the second library.
 Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
@@
 
-Switching on a library-level profiling analysis % that operates at library boundaries
+Switching-on a library-level profiling analysis % that operates at library boundaries
   would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
@@
 
-Dynamic analysis can be used to discover such type assertions or invariants.
-The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the library boundaries by observing the execution of the program.
+Library-level dynamic analysis can be used to discover such type assertions or invariants.
+The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the boundaries of libraries by observing their arguments during the execution of the program.
 %% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
@@
 We have briefly introduced three motivating analyses for extracting information about an application's dependencies.
-While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
+While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analysis frameworks due to a combination of factors:
   these frameworks either require highly specialized solutions often outside the core language,
-  do not leverage or offer semantic information at the level of library boundaries, or
+  do not leverage nor offer semantic information at the level of library boundaries, or
   lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
@@
 
-  \item \textbf{Dismantling:}
+  \item \textbf{Fragmentation:}
 Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
 This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
-During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map th provided analysis hooks to the corresponding libraries.
+During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map the provided analysis hooks to the corresponding libraries.
 
@@
 This phase requires solving several challenges, including enumerating all points of entry into and exit out of a library, 
-and swapping original values externally available to a library with ones that are wrapped with interposition mechanisms.
+and swapping all original values externally-available to a library with ones that are wrapped with interposition mechanisms.
 
@@
 
-\subsection{Dismantling}
+\subsection{Fragmentation}
 \label{one}
@@
   \textmd{
-  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
+  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import)~\cf{two}.
   }
@@
 %FIXME: Needs examples, especially the context
-For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
+For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface (Fig.~\ref{fig:shadowing}).
 This is achieved in three logical steps:
 (i) transforming library's context, a mapping from names to values that are available from outside library,
-(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
-(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
+(ii) interpreting the library within this context, so that all names bind and resolve to \sys-augmented values, and
+(iii) transforming the library's \ttt{export} value, \ie the library interface, once the interpretation is complete.
 Before discussing \emph{where} each transformation is applied, however, we show \emph{how} they are applied.
@@
 \sys's transformations boil down to a base transform \ttt{wrap} that traverses and augments values with runtime analysis monitors.
-At a high level, \ttt{wrap} takes a value $v$ and an analysis fragment $\alpha$ and returns a new value $v'$ that has every one of its fields $f$ wrapped:
-   every $f$ is replaced with a method $f'$ that returns the result of calling $f$ after applying the analysis segment corresponding to $v$.
+At a high level, \ttt{wrap} takes a value $v$ and analysis fragments $(\alpha_1, \alpha_2)$ and returns a new value $v'$ that has every one of its fields $f$ wrapped:
+   every $f$ is replaced with a method $f'$ that calls fragment $\alpha_1$, calls $f$, calls fragments $\alpha_2$, and returns the result of the call to $f$.
 
@@
 % \sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
-For example, if a field in a transformed object is assigned a new value, that value has to be be transformed before its to the object.
-
-\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
+For example, if a field in a transformed object is assigned a new value, that value has to be transformed before it is attached to the object.
+
+\sys allows toggling analyses on/off, changing analyses, or chaining multiple analyses during the execution of the program.
 To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
@@
 To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names to which a library has access.
+This includes global and pseudo-global\footnote{
+  For example, Node introduces objects that are not part of the EcmaScript specification into the global scope, such as \ttiny{process} and \ttiny{console};
+  similarly, Lua's Luvit introduces its own globals such as \ttiny{p()} and \ttiny{exports}.
+} names provided by the language and its runtime.
 
@@
 
-\heading{Context Linking}
+\heading{Context Binding}
 To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
@@
 \begin{verbatim}
-  local pint = ctx.print
+  local print = ctx.print
   local error = ctx.error
@@
 \end{verbatim}
-These statements shadow global variable names by redefining them as local ones.
+These statements shadow global variable names by redefining them as function-local ones.
 The closure accepts an argument \ttt{ctx} that will hold the customized context (see above), assigning its entries to their respective variable names.
@@
 % TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
-The goal of the final transformation is to track activity at the boundary;\footnote{
+The goal of the final transformation is to track activity at the boundary.\footnote{
   For some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.}
@@
 We went with the second approach, as looser coupling seems to have several benefits:
-  it does not require \sys's users to have a second Node copy only for running analyses;
+  it does not force \sys's users to have a Node copy only for running analyses;
   it removes \sys's developers from the critical path of updates between the Node developers and its users; 
@@
 % It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
-\sys interposes on all of these steps to facilitate transformations.
+% \sys interposes on all of these steps to facilitate transformations.
+\sys augments all of these steps.
 Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
-If the module's type is one \sys can analyze, it fetches the corresponding analysis during loading (L).
+If the module's type corresponds to a module that can be analyzed by \sys, \sys fetches the corresponding analysis during loading (L).
 Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
 \sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
-\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.
+\sys comes with a hard-coded list of names corresponding to the specific versions of EcmaScript and Node.
 Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
-Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, these were only five names.
+Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, they were only five names.
 
@@
 
-As the three analyses are quite complex to be shown in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
+As the three analyses are quite complex to include in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
 
@@
 let count = {};
-forevery.global.in(/serial/) = {
+forevery.global.in(/serial/).do({
   pre: (name, path, _) => {
-    let id = resolve(name, path);
-    count[id] = count[id]?  count[id] + 1 : 1;
-  }
-};
+    let o = resolve(name, path);
+    count[o] = count[o]?  count[o] + 1 : 1;
+  } });
 process.on("exit", () => {
@@
                    "utf-8",
-                   JSON.stringify(count));
-});
+                   JSON.stringify(count)); });
 \end{lstlisting}
@@
 
-The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{Math.add: RX}.
+The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{require("Math").add: RX}.
 % that correspond to values of other modules or global-like language names.
@@
 \heading{Performance Diagnosis}
-We develop a profiling analysis that operates at two levels:
+We developed a profiling analysis that operates at two levels:
  (i) module-boundary wrappers that collect profiling statistics for calls between modules by wrapping module interfaces; and
@@
 \heading{Type Invariant Discovery}
-To infer type invariants for serialization specifications, we base our analysis on a simple type system modeled after the simply-typed lambda calculus augmented with:
-  (i) unions (sum types), such as \ttt{a | b | c}, 
+To infer type invariants for serialization specifications, we based our analysis on a simple type system modeled after the simply-typed lambda calculus augmented with:
+  (i) unions (sum types), such as \ttt{string | number}, 
   (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}, and
@@
 Several takeaways are worth highlighting.
-Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation frameworks.
+Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.
 \sys's library-level analysis adds a small overhead, less than $2\times$ for the vast majority of libraries and often less than $5ms$.
@@
 \sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
-For example, to better understand PD and confirm it works correctly, we craft a micro-benchmark with four dependencies of known static bottlenecks.
+For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
 % Each dependency can perform one of three operations, depending on its current state:
@@
 		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
-    All timings are in $ms$.
+    All timings are in $ms$~\cf{micro}.
   }
@@
 Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
-The first column indicates the focus of the benchmark; not all analysis-benchmark combinations are useful.
+The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful.
 % Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
@@
 The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
-  what is likely to be the overhead is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
+  what is likely to be is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
 
@@
 
-To understand \sys's performance characteristics at the level of individual modules, we perform two experiments.
-
-In the first experiment, we collect a diverse set of eight popular libraries from npm, 
+To understand \sys's performance characteristics at the level of individual modules, we performed two experiments.
+
+In the first experiment, we collected a diverse set of eight popular libraries from npm, 
 % used by thousands of other projects,
 on the order of hundreds of lines of code.
-As a workload, we use each library's internal test suite, with \ttt{minimist} includes several distinct test harnesses.
+As a workload, we used each library's internal test suite (one library, \ttt{minimist}, includes several test harnesses).
 These tests stress functionality as expected by the library's authors and confirm that \sys does not break it.
-We apply \sys using the three analyses we developed, and compare the results with their baseline performance (Tab.~\ref{tab:meso}).
+We applied our three analyses, and compare their performance with the baseline (Tab.~\ref{tab:meso}).
 The results show that executions augmented with analyses are within 2--3$\times$, averaging a 80\% slowdown for the largest libraries.
-Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as 257 wrappers. % (shown by the analysis output).
+Different benchmarks put a different pressure on \sys's wrappers, which range between 23--257. % (shown by the analysis output).
 
@@
 We note that Jalangi2 improves significantly over Jalangi's performance~\cite{jalangi}, as it eschews record/replay capabilities.
-To be fair in our comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
+To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
 The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
-  the effort of employing \sys as a library was significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
+  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
 The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
@@
     \textbf{Applying \sys to three large applications}.
-    The table shows the overheads of applying the three analyses to three large applications.
+    The table shows the overheads of applying the three analyses to three large applications~\cf{macro}.
   }
@@
 Finally, we perform end-to-end program dialysis on three large applications:
-  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework,
-  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates, and
+  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
+  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates; and
   Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
@@
 Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-name, not module identifier.
-This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries
+This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
 % For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
@@
 
-Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
-Applications today routinely pull together hundreds of libraries, making their analysis difficult.
-To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
-Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
+Recent trends in software engineering have led to unprecedented levels of third-party code (re-)use.
+% Applications today routinely pull together hundreds of libraries, making meaningful analysis difficult.
+We present \emph{program dialysis}, a novel library-aware analysis technique for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
 % is a general technique that
-Contrary to heavy-weight dynamic analysis that provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand, dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
-
-We note that \sys is open source, available for experimentation with other applications and analyses.
+Contrary to heavy-weight dynamic analysis, dialysis lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
+% it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand, dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
+Our dialysis prototype for JavaScript, \sys, is available as an open-source library for experimentation with other applications and analyses.
 

### 2020-04-06 core/src/rwx.js
Fix get stacking

@@ -1,4 +1,5 @@
 let locEnv;
+const pattern = /require[(](.*)[)]/;
 
 // We add the R or W or E to the existing string
 const addEvent = (event, values, index) => {
@@ -32,7 +33,6 @@ const updateAnalysisData = (storedCalls, truename, modeGrid) => {
 // onRead <~ is called before every object is read
 const onRead = (target, name, nameToStore, currentModule, typeClass) => {
   if (nameToStore !== 'global') {
-    const pattern = /require[(](.*)[)]/;
     if (pattern.test(nameToStore)) {
       updateAnalysisData(locEnv.analysisResult[currentModule],
           nameToStore.match(pattern)[0], ['r']);
@@ -46,7 +46,7 @@ const onRead = (target, name, nameToStore, currentModule, typeClass) => {
 };
 
 // onWrite <~ is called before every write of an object
-const onWrite = (target, name, value, currentModule, parentName, 
+const onWrite = (target, name, value, currentModule, parentName,
     nameToStore) => {
   updateAnalysisData(locEnv.analysisResult[currentModule], parentName, ['r']);
   updateAnalysisData(locEnv.analysisResult[currentModule], nameToStore, ['w']);
@@ -67,6 +67,10 @@ const onCallPre = (target, thisArg, argumentsList, name, nameToStore,
     }
     updateAnalysisData(locEnv.analysisResult[declareModule],
         nameToStore, ['r', 'x']);
+    if (pattern.test(nameToStore)) {
+      updateAnalysisData(locEnv.analysisResult[currentModule],
+        nameToStore.match(pattern)[0], ['r']);
+    }
   }
 };
 

### 2020-04-06 core/src/txfm.js

@@ -47,8 +47,9 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
   const objectPath = new WeakMap();
   const methodNames = new WeakMap();
   const storePureFunctions = new WeakMap();
-  const withProxy = new WeakMap();
   const globalNames = new Map();
+  const withProxy = new WeakMap();
+  const passedOver = new Map();
 
   // We read and store the data of the json file
   const defaultNames = require('./default-names.json');
@@ -476,11 +477,11 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
             });
             storePureFunctions.set(target[name], currFunction);
             namePathSet(currFunction, parentName, currModule);
+            policy.onRead(target, name, nameToStore, currModule);
           } else {
             const key = storePureFunctions.get(currFunction);
             namePathSet(key, parentName, currModule);
           }
-          policy.onRead(target, name, nameToStore, currModule);
 
           const result = Reflect.get(target, name);
           withProxy.set(result, true);
@@ -491,7 +492,11 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           const parentName = objectName.get(target);
           const nameToStore = parentName + '.' + name;
           const currModule = moduleName[env.requireLevel];
-          policy.onRead(target, name, nameToStore, currModule);
+          // Stacking fix
+          if (!passedOver.has(nameToStore + currModule)) {
+            policy.onRead(target, name, nameToStore, currModule);
+            passedOver.set(nameToStore + currModule, true);
+          }
         }
       }
 

### 2020-04-06 core/src/txfm.js
Add debug-flag

@@ -24,6 +24,7 @@ const preset = {
 const systemPreset = {
   WITH_ENABLE : true,
   INPUT_STRING: true,
+  DEBUG_FLAG: false,
 }
 
 const lyaStartUp = (callerRequire, lyaConfig) => {
@@ -378,8 +379,11 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
   Module.wrap = (script) => {
     script = lyaConfig.withEnable ? getPrologue() + script + '}' :
       getPrologue() + script;
-    let wrappedScript = originalWrap(script);
-    wrappedScript = wrappedScript.replace('dirname)', 'dirname, localGlobal, withGlobal)');
+    const wrappedScript = originalWrap(script).replace('dirname)',
+      'dirname, localGlobal, withGlobal)');
+    if (lyaConfig.debugFlag) {
+      console.log(wrappedScript);
+    }
     return wrappedScript;
   };
 
@@ -447,7 +451,6 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           if (withProxy.has(target[name])) {
             return Reflect.get(target, name);
           }
-          // FIXME: Problem here stacking
           if (Object.entries(target[name]).length) {
             const currObject = target[name];
             const currModule = moduleName[env.requireLevel];
@@ -502,6 +505,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
 
       return Reflect.get(target, name);
     },
+    // TODO: here is stacking
     set: function(target, name, value) {
       const parentName = objectName.get(target);
       const nameToStore = parentName + '.' + name;
@@ -535,6 +539,8 @@ module.exports = {
       systemPreset.WITH_ENABLE;
     conf.inputString = conf.inputString === false ? conf.inputString:
       systemPreset.INPUT_STRING;
+    conf.debugFlag = conf.debugFlag ? conf.debugFlag :
+      systemPreset.DEBUG_FLAG;
     return lyaStartUp(origRequire, conf);
   },
 };

### 2020-04-06 core/src/txfm.js
Add tracking flag

@@ -25,6 +25,13 @@ const systemPreset = {
   WITH_ENABLE : true,
   INPUT_STRING: true,
   DEBUG_FLAG: false,
+  TRACKING: [
+    'user-globals',
+    'es-globals',
+    'node-globals',
+    'module-locals',
+    'module-returns'
+  ]
 }
 
 const lyaStartUp = (callerRequire, lyaConfig) => {
@@ -170,6 +177,10 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
 
   // We wrap the global variable in a proxy
   const createGlobalPr = () => {
+    if (!lyaConfig.track.includes('user-globals')) {
+      return global;
+    }
+
     const tempGlobal = new Proxy(global, {});
     methodNames.set(tempGlobal, 'global');
     objectPath.set(tempGlobal, moduleName[env.requireLevel]);
@@ -199,6 +210,9 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
     }
     methodNames.set(localCopy, moduleInputNames[count]);
     objectPath.set(localCopy, moduleName[env.requireLevel]);
+    if (!lyaConfig.track.includes('module-locals')) {
+      return localCopy;
+    }
     const handler = createHandler('module-locals');
     return new Proxy(localCopy, {
       apply: handler.apply,
@@ -210,7 +224,9 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
   const setLocalGlobal = () => {
     let localGlobal = {};
     localGlobal = passJSONFile(createGlobal, defaultNames.globals);
-    localGlobal['proxyExportHandler'] = createHandler('es-globals');
+    if (lyaConfig.track.includes('es-globals')) {
+      localGlobal['proxyExportHandler'] = createHandler('es-globals');
+    }
     //const noProxyOrig = new Proxy(global['process']['env'], {});
     //localGlobal['process.env'] = new Proxy(noProxyOrig, exportHandler);
     localGlobal['proxyGlobal'] = createGlobalPr();
@@ -293,6 +309,9 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
 
   const createGlobal = (name) => {
     if (global[name] !== undefined) {
+      if (!lyaConfig.track.includes('node-globals')) {
+        return global[name];
+      }
       const proxyObj = proxyWrap(createHandler('node-globals'), global[name], name);
       objectPath.set(proxyObj, moduleName[env.requireLevel]);
[…]

### 2020-04-06 core/tst/repoExamples/chalk/main.js
Error on chalk even with Lya options disabled

@@ -5,13 +5,13 @@ console.log(chalk.blue('Hello world!'));
 
 // Combine styled and normal strings
 log(chalk.blue('Hello') + ' World' + chalk.red('!'));
- 
+
 // Compose multiple styles using the chainable API
 log(chalk.blue.bgRed.bold('Hello world!'));
- 
+
 // Pass in multiple arguments
 log(chalk.blue('Hello', 'World!', 'Foo', 'bar', 'biz', 'baz'));
- 
+
 // Nest styles
 log(chalk.red('Hello', chalk.underline.bgBlue('world') + '!'));
  
@@ -21,15 +21,15 @@ log(chalk.green(
     chalk.blue.underline.bold('with a blue substring') +
     ' that becomes green again!'
 ));
- 
+
 // ES2015 template literal
 log(`
 CPU: ${chalk.red('90%')}
 RAM: ${chalk.green('40%')}
 DISK: ${chalk.yellow('70%')}
 `);
- 
- 
+
+
 // Use RGB colors in terminal emulators that support it.
 log(chalk.keyword('orange')('Yay for orange colored text!'));
 log(chalk.rgb(123, 45, 67).underline('Underlined reddish color'));

### 2020-04-06 core/src/txfm.js
Stacking place

@@ -111,7 +111,6 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           policy.onCallPre(target, thisArg, argumentsList, target.name, nameToStore,
             currentModule, currentName, moduleClass);
         };
-
         const result = Reflect.apply(target, thisArg, argumentsList);
 
         if (nameToStore) {
@@ -467,7 +466,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
       return Reflect.apply(target, thisArg, argumentsList);
     },
     get: function(target, name, receiver) {
-      const exportType = typeof(target[name]);
+      const exportType = typeof target[name];
       if (exportType !== 'undefined' && target[name] != null &&
           typeof name === 'string' && (!(target[name] instanceof RegExp))) {
         if (exportType === 'object') {
@@ -518,7 +517,6 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           const parentName = objectName.get(target);
           const nameToStore = parentName + '.' + name;
           const currModule = moduleName[env.requireLevel];
-          // Stacking fix
           if (!passedOver.has(nameToStore + currModule)) {
             policy.onRead(target, name, nameToStore, currModule);
             passedOver.set(nameToStore + currModule, true);
@@ -528,13 +526,12 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
 
       return Reflect.get(target, name);
     },
-    // TODO: here is stacking
+    // TODO: here is stacking -- remove set for fix
     set: function(target, name, value) {
       const parentName = objectName.get(target);
       const nameToStore = parentName + '.' + name;
       const currModule = moduleName[env.requireLevel];
       policy.onWrite(target, name, value, currModule, parentName, nameToStore);
-
       return Reflect.set(target, name, value);
     },
   };

### 2020-04-06 core/src/wrapGlobals.js
Assorted notes

@@ -1,3 +1,58 @@
+let RW = {
+   apply: function(target, thisArg, argumentsList) {
+     console.log("apply", target, thisArg, argumentsList);
+     Reflect.apply(...arguments);
+   },
+   construct: function(target, argumentsList, newTarget) {
+     console.log("construct", target, argumentsList);
+     Reflect.construct(...arguments);
+   },
+   defineProperty: function(target, property, descriptor){
+     console.log("defineProperty", target, property, descriptor);
+     Reflect.defineProperty(...arguments);
+   },
+   getOwnPropertyDescriptor: function(target, prop){
+     console.log("getOwnPropertyDescriptor", target, prop);
+     Reflect.getOwnPropertyDescriptor(...arguments);
+   },
+   deleteProperty: function(target, property){
+     console.log("deleteProperty", target, property);
+     Reflect.deleteProperty(...arguments);
+   },
+   getPrototypeOf: function(target){
+     console.log("getPrototypeOf", target);
+     Reflect.getPrototypeOf(...arguments);
+   },
+   setPrototypeOf: function(target, prototype){
+     console.log("setPrototypeOf", target, prototype);
+     Reflect.setPrototypeOf(...arguments);
+   },
+   isExtensible: function(){
+     console.log("isExtensible", ...arguments);
+     Reflect.isExtensible(...arguments);
+   },
+   preventExtensions: function(target){
+     console.log("preventExtensions", ...arguments);
+     Reflect.preventExtensions(...arguments);
+   },
+   get: function(target, prop, receiver) {
+     console.log("get", target, prop);
+     Reflect.get(...arguments);
+   },
+   set: function(target, prop, value, receiver) {
+     console.log("set", target, prop, value);
+     Reflect.set(...arguments);
+   },
+  has: function(target, prop){
+    console.log("has", target, prop);
+    Reflect.has(...arguments);
+  },
+  ownKeys: function(target){
+    console.log("ownKeys", target);
+    Reflect.ownKeys(...arguments);
+  },
+};
+
 function sandboxJS(js) {
   const whitelist = ['alert', 'console', 'navigator', 'location'];
   const handlers = {
@@ -14,7 +69,7 @@ function sandboxJS(js) {
       return Reflect.has(target, propKey, context);
     },
   };
-  const proxy = new Proxy(global, handlers);
[…]

### 2020-04-06 core/src/txfm.js
Switch to ...arguments

@@ -31,7 +31,7 @@ const systemPreset = {
     'node-globals',
     'module-locals',
     'module-returns'
-  ]
+  ],
 }
 
 const lyaStartUp = (callerRequire, lyaConfig) => {
@@ -111,7 +111,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           policy.onCallPre(target, thisArg, argumentsList, target.name, nameToStore,
             currentModule, currentName, moduleClass);
         };
-        const result = Reflect.apply(target, thisArg, argumentsList);
+        const result = Reflect.apply(...arguments);
 
         if (nameToStore) {
           policy.onCallPost(target, thisArg, argumentsList, target.name, nameToStore,
@@ -131,7 +131,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           policy.onRead(target, name, storeName, currentModule, moduleClass);
         }
 
-        return Reflect.get(target, name);
+        return Reflect.get(...arguments);
       },
       set: function(target, name, value) {
         const currentModule = objectPath.get(target);
@@ -145,16 +145,16 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
           }
         }
 
-        return Reflect.set(target, name, value);
+        return Reflect.set(...arguments);
       },
       has: function(target, prop) {
         const currentName = env.moduleName[env.requireLevel];
         const parentObject = methodNames.get(target);
-        const result =  Reflect.has(target, prop);
+        const result =  Reflect.has(...arguments);
         const nameToStore = parentObject + '.' + prop;
         if (parentObject === 'global' && !result &&
           prop !== 'localGlobal') {
-          policy.onHas(target, prop, currentName, nameToStore);
+          policy.onHas(...arguments);
         }
 
         return result;
@@ -242,7 +242,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
       }
       argumentsList[5] = setLocalGlobal();
       argumentsList[6] = createGlobalPr();
-      return Reflect.apply( ...arguments);
+      return Reflect.apply(...arguments);
     },
   };
 
@@ -463,7 +463,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
       policy.onCallPre(target, thisArg, argumentsList, target.name,
           nameToStore, currModule, declareModule);
 
-      return Reflect.apply(target, thisArg, argumentsList);
+      return Reflect.apply(...arguments);
     },
     get: function(target, name, receiver) {
       const exportType = typeof target[name];
[…]

### 2020-05-05 paper/tst/jalangi_test/run.sh
Small update

@@ -33,6 +33,22 @@ do
 	name=$line.js
 	echo "******************************"
   	echo "We are processing this: $name"
+  	sed -i "s/${prevname}/${name}/" noWith.js
+  	echo "The name of file $name" >> timeResultsLyaNOWITH.txt
+  	(time node noWith.js) >>  /dev/null 2>> "timeResultsLyaNOWITH.txt"
+  	prevname=$name
+
+done < "$input"
+
+sed -i "s/${prevname}/replaceme.js/" noWith.js
+
+prevname="replaceme.js"
+input="./sunspider/LIST"
+while IFS= read -r line
+do
+	name=$line.js
+	echo "******************************"
+  	echo "We are processing this: $name"
   	sed -i "s/${prevname}/${name}/" main.js
   	echo "The name of file $name" >> timeResultsLya.txt
   	(time node main.js) >>  /dev/null 2>> "timeResultsLya.txt"
@@ -46,18 +62,4 @@ echo "******************************"
 echo "******************************"
 echo "We are going to run the test for programs with lya but noWith"
 
-prevname="replaceme.js"
-input="./sunspider/LIST"
-while IFS= read -r line
-do
-	name=$line.js
-	echo "******************************"
-  	echo "We are processing this: $name"
-  	sed -i "s/${prevname}/${name}/" noWith.js
-  	echo "The name of file $name" >> timeResultsLyaNOWITH.txt
-  	(time node noWith.js) >>  /dev/null 2>> "timeResultsLyaNOWITH.txt"
-  	prevname=$name
 
-done < "$input"
-
-sed -i "s/${prevname}/replaceme.js/" noWith.js

### 2020-05-05 paper/draft.tex
Updates

@@
 {\rm Anonymous Author(s)}\\
-\normalsize{Submission \#225, 11 + 3 pages}\\
-% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
+% \normalsize{Submission \#225, 11 + 3 pages}\\
+% \normalsize{Anonymous Author(s)}\\
+\normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
 % {\rm Grigoris Ntousakis}\\
@@
 To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
-  A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
-  From ancient Greek {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
+  A method of deconstruction into elements often for the purposes of altering piecewise components or removing waste products.
+  From % ancient Greek 
+  {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
 } and implemented in \sys.
@@
   (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.
+
+% \heading{Is it Useful?}
+% First question
+% 
+% \heading{Is it Usable?}
+% Example 
+% 
+% \heading{Is it Performant?}
+% Highlight results
 

### 2020-05-05 core/src/rwx.js

@@ -112,6 +112,9 @@ const onExit = (intersection, candidateModule) => {
     fs.writeFileSync(env.conf.SAVE_RESULTS,
       JSON.stringify(env.analysisResult, null, 2), 'utf-8');
   }
+  if (env.conf.print) {
+    console.log(JSON.stringify(env.analysisResult, null, 2))
+  }
 }
 
 module.exports = (e) => {

### 2020-05-05 core/src/txfm.js

@@ -59,7 +59,7 @@ const lyaStartUp = (callerRequire, lyaConfig) => {
   const requireLevel = 0;
   const analysisResult = {};
 
-  moduleName[0] = process.cwd() + '/' + 'main.js';
+  moduleName[0] = process.cwd() + '/' + 'main.js'; // FIXME: What is this?
   analysisResult[moduleName[0]] = {};
 
   // This holds the string of the transformations inside modules

### 2020-05-05 paper/tst/jalangi_test/run.sh
Add some perf results

@@ -24,7 +24,7 @@ cd ../
 
 echo "******************************"
 echo "******************************"
-echo "We are going to run the test for programs with lya"
+echo "We are going to run the test for programs with lya but noWith"
 
 prevname="replaceme.js"
 input="./sunspider/LIST"
@@ -42,6 +42,10 @@ done < "$input"
 
 sed -i "s/${prevname}/replaceme.js/" noWith.js
 
+echo "******************************"
+echo "******************************"
+echo "We are going to run the test for programs with lya"
+
 prevname="replaceme.js"
 input="./sunspider/LIST"
 while IFS= read -r line
@@ -58,8 +62,6 @@ done < "$input"
 
 sed -i "s/${prevname}/replaceme.js/" main.js
 
-echo "******************************"
-echo "******************************"
-echo "We are going to run the test for programs with lya but noWith"
+
 
 

### 2020-05-20 paper/draft.tex
New abstract

@@
 
-Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
-Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
-
-To address these challenges, we present \emph{program dialysis}, a dynamic analysis technique specifically tailored to applications with many third-party libraries.
-Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
-It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
-Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries for the web, server, and mobile.
-We develop a series of case-studies that motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
-  insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
+% Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
+% Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
+% 
+% To address these challenges, we present \emph{program dialysis}, a dynamic analysis technique specifically tailored to applications with many third-party libraries.
+% Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
+% It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
+% Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries for the web, server, and mobile.
+% We develop a series of case-studies that motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
+%   insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
+%
+
+This paper introduces \emph{program dialysis}, a process for analyzing programs at the level of third-party libraries.
+Motivated by today's library ubiquity, dialysis exposes hooks for observing and modifying program behavior at the boundaries between libraries.
+These hooks are exposed through a series of program transformations that dismantle a program, wrap a subset of its libraries, and carefully reassemble the program to maintain its original execution while calling into developer-provided handlers.
+These handlers are called when certain interactions between a library and its environment occur, and are provided additional contextual information about each interaction.
+As dialysis operates at a coarse granularity and without modifying the runtime environment, it has a potential for low runtime overheads, increased compatibility, and succinct analyses.
+To evaluate this potential, we implement dialysis in \sys and apply it on targets drawn from the JavaScript ecosystem.
+Our results show $9.6\times$ performance improvements over state-of-the-art dynamic analysis, compatibility with over 50 libraries and applications,
+and analyses expressed in under 100LoC---all while offering insights in three realistic use-case analyses
+
+% ---\eg access to a specific global variable or invocation of a specific method.
+% library method calls 
+% property value .
+
+% An important advantage is increased performance and backwards compatibility executes on the unmodified runtime and performs at a coarse granularity.
+ % , and coordinate to get the full view of the workings of one or more libraries.
+% The level at which dialysis operates offer improved performance, backwards-compatibility
+
+% Handlers are stateful 
+% 
+% compute over information associated with these events.
+% written in the same language as the program
+% 
+% During its execution, the modified program calls 
+% 
+% perform on the unmodified language runtime
+% thus offer performance and compatibility advantages over conventional, finer-grained analysis.
+% 
+% An important advantage is increased performance and backwards compatibility 
+% executes on the unmodified runtime and performs at a coarse granularity.
+% Despite its coarse granularity, dialysis still offers insightful information whose 
+% 
+% as demonstrated by three analysis use-cases whose needs are largely unmet by conventional analysis frameworks.
+% 
+% We implement program dialysis in \sys and evaluate it against libraries and programs drawn from the JavaScript ecosystem.
+% The results show significant performance improvements over state-of-the-art dynamic analysis framework, comparable analysis scripts,
+% 
+% when certain events occur.
+% Analysis scripts provide handlers for certain classes of events,
+% 
+% Developers provide handlers that are called when certain events occur,
+% by providing handlers to events.
+% 
+% These handlers are short, operate on the unmodified language runtime, thus offering performance benefits,
+% 
+% To expose these hooks, dialysis performs 
+% 
+% This is achieved by augmenting the library loader, but without necessarily modifying the language runtime 
+% 
+% Compared to dynamic analysis, dialysis
+% (i) operates at a coarser granularity (performance) and on the same runtime getting full support for the language (compatible with the semantics of the langauge)
+% but on the original runtime 
+% (ii) at the same level as the program, which means it can manipulate semantic information 
+% (iii)
+% 
+% Despite the fact that it operates at the same level as program
+% 
+% \sys 
+% 
+% can capture the library's full observable behavior.
+% 
+%   a dynamic analysis technique specifically tailored to applications with many third-party libraries.
+% Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
+% It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
+% 
+% Our dialysis prototype, \sys, targets the JavaScript ecosystem.
+% demonstrates significant 
+% (i) performance benefits over conventional dynamic analysis, to the point that it can be toggled on/off online
+% Expressing analyses is comparable with 
+% succinct script in the same language and ecosystem as the dialysis target,
+% (iii) and its usefullness is 
+% 
+% 
+% A series of case-studies motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
+%   insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
+%
 

### 2020-05-20 core/tst/micro-packages/getInfo.sh
Update script that get info

@@ -23,10 +23,16 @@ getInfo() {
   # Get the number of lines from the tests of the package
   if test -f "test.js"; then
     wc -l test.js >> ../info.txt
+  elif test -f "tests.js"; then
+    wc -l tests.js >> ../info.txt
   else 
     if [ -d "test" ]; then
       cd test
         (find . -maxdepth 1 -name '*.js') | xargs wc -l | grep total >> ../../info.txt
+      cd ..
+    elif [ -d "tests" ]; then
+      cd tests
+      (find . -maxdepth 1 -name '*.js') | xargs wc -l | grep total >> ../../info.txt
       cd ..
     else 
       echo "no test found" >> ../info.txt

### 2020-05-20 paper/draft.tex
Update abstract

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Multi-library Program Dialysis with Lya}
+\title{\Large \bf \sys: Library-Oriented Program Analysis}
 
@@
 
-% Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
-% Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.
-% 
-% To address these challenges, we present \emph{program dialysis}, a dynamic analysis technique specifically tailored to applications with many third-party libraries.
-% Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
-% It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
-% Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries for the web, server, and mobile.
-% We develop a series of case-studies that motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
-%   insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
-%
-
-This paper introduces \emph{program dialysis}, a process for analyzing programs at the level of third-party libraries.
-Motivated by today's library ubiquity, dialysis exposes hooks for observing and modifying program behavior at the boundaries between libraries.
-These hooks are exposed through a series of program transformations that dismantle a program, wrap a subset of its libraries, and carefully reassemble the program to maintain its original execution while calling into developer-provided handlers.
-These handlers are called when certain interactions between a library and its environment occur, and are provided additional contextual information about each interaction.
-As dialysis operates at a coarse granularity and without modifying the runtime environment, it has a potential for low runtime overheads, increased compatibility, and succinct analyses.
-To evaluate this potential, we implement dialysis in \sys and apply it on targets drawn from the JavaScript ecosystem.
-Our results show $9.6\times$ performance improvements over state-of-the-art dynamic analysis, compatibility with over 50 libraries and applications,
-and analyses expressed in under 100LoC---all while offering insights in three realistic use-case analyses
-
+Dynamic program analysis is a long-standing technique for getting insights into the execution of a program.
+This paper presents a new form of dynamic analysis, termed \emph{dialysis}, enabled by the fact that modern dynamic languages feature an import mechanism that loads code at runtime as a string.
+Dialysis works by coupling light static transformations with more substantial dynamic ones, inserting hooks for capturing a library's full observable behavior.
+% transform and bind their context prior to their evaluation.
+% expose instrumentation opportunities to developers.
+% This mechanism enables a new lightweight instrumentation technique.
+Dialysis offers a new point in the dynamic-analysis trade-off space:
+  as it operates at a coarse granularity and does not modify the language runtime environment, it offers better performance and compatibility but foregoes expression-level visibility.
+To evaluate its potential, we implement dialysis in LYA and apply it on targets drawn from the JavaScript ecosystem.
+Our results show $9.6\times$ performance improvements over state-of-the-art dynamic analysis, compatibility with over 50 libraries and applications, and analyses expressed in under 100LoC---all while offering useful insights on three realistic use-case analyses.
+
+% 
+% 
+% 
+% different
+% dynamic interposition techniques
+% 
+% We show how to exploit the technique to deliver very efficient interposition schemes
+% 
+%   the new technique operates at a finer granularity, 
+%   coarse granularity
+% 
+% we can exploit our characteristics.
+% Allows us to do X. This in turn has the following benefits for the developer Y:
+% 
+% the results show a way faster
+% 
+% What are the benefits
+% we present a library-oriented dynamic analysis technique and system
+% technique the functionality for interposing at library boundaries
+% 
+% 
+% We do dynamic analys 10 times faster and has
+% 
 % ---\eg access to a specific global variable or invocation of a specific method.

### 2020-05-22 paper/draft.tex
Update abstract

@@
 
-Dynamic program analysis is a long-standing technique for getting insights into the execution of a program.
-This paper presents a new form of dynamic analysis, termed \emph{dialysis}, enabled by the fact that modern dynamic languages feature an import mechanism that loads code at runtime as a string.
-Dialysis works by coupling light static transformations with more substantial dynamic ones, inserting hooks for capturing a library's full observable behavior.
+Dynamic program analysis is a long-standing technique for obtaining information about program execution.
+We present a set of new dynamic analysis techniques that target modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that modern dynamic languages feature a module-import mechanism that loads code at runtime as a string.
+These techniques use lightweight load-time code transformations that operate on the string representation of the module,
+as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
+This code implements the dynamic analysis, enabling these techniques to capture all interactions around the library in unmodified production language runtime environments.
+We implement these techniques in \sys, a system targeting the JavaScript ecosystem. 
+Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.
+
+% operate at the library  interface level  
+% This approach occupies an new point in the design trade-off space, enabling lya to operates at the library interface level in unmodified production..
+
 % transform and bind their context prior to their evaluation.
@@
 % This mechanism enables a new lightweight instrumentation technique.
-Dialysis offers a new point in the dynamic-analysis trade-off space:
-  as it operates at a coarse granularity and does not modify the language runtime environment, it offers better performance and compatibility but foregoes expression-level visibility.
-To evaluate its potential, we implement dialysis in LYA and apply it on targets drawn from the JavaScript ecosystem.
-Our results show $9.6\times$ performance improvements over state-of-the-art dynamic analysis, compatibility with over 50 libraries and applications, and analyses expressed in under 100LoC---all while offering useful insights on three realistic use-case analyses.
 

### 2020-05-26 paper/draft.tex
Massive edits

@@
 Dynamic program analysis is a long-standing technique for obtaining information about program execution.
-We present a set of new dynamic analysis techniques that target modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that modern dynamic languages feature a module-import mechanism that loads code at runtime as a string.
-These techniques use lightweight load-time code transformations that operate on the string representation of the module,
-as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
-This code implements the dynamic analysis, enabling these techniques to capture all interactions around the library in unmodified production language runtime environments.
-We implement these techniques in \sys, a system targeting the JavaScript ecosystem. 
+We present a new dynamic analysis approach that targets modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that they feature a module-import mechanism that loads code at runtime as a string.
+This approach uses lightweight load-time code transformations that operate on the string representation of the module, as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
+This code implements the dynamic analysis, enabling this approach to capture all interactions around the library in unmodified production language runtime environments.
+We implement this approach in \sys, a system targeting the JavaScript ecosystem. 
 Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.
@@
 
-\section{Implementation of Dialysis for SSJ}
+\section{Implementation: Server-Side JavaScript}
 \label{impl}
@@
 
-\sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
-  operates as a library around an existing runtime,
-  does not require learning a new language, and 
-  gets meaningful information while operating only at library boundaries.
-% Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
-In this section, we report on \sys's performance characteristics:
-% At a high level, we are interested in three questions:
-  (i) the overheads of its underlying building blocks;
-  (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
-  (iii) \sys's behavior on realistic  multi-library applications.
-% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
-% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
-% For the third question, we use a combination of real applications~\sx{macro}.
-
-Several takeaways are worth highlighting.
-Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.
-\sys's library-level analysis adds a small overhead, less than $2\times$ for the vast majority of libraries and often less than $5ms$.
-Finally, \sys scales to large applications with hundreds of libraries while interposing on several thousands of objects.
-
-Experiments were conducted on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
+At a high level, we are interested in three main questions:
+
+\begin{itemize}
+  \item \textbf{Q1} Given its coarse granularity, is \sys useful?
+    We answer this question in \S\ref{bg}, which shows three case-study multi-module analyses with practical implications.
+    \sys operates at the right level of abstraction for answering important questions raised by today's software engineering practices.
+
+  \item \textbf{Q2} Is it usable?
+     We answer this question in \S\ref{impl}, by implementing these and other analyses.
+    \sys operates as a library around a unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
+    % Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.
+
+  \item \textbf{Q3} How does it perform? We answer this question here.
+  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
+  \sys is about $22\times$ \todo{faster} than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
+  By executing on unmodified runtimes, \sys has significantly better compatibility:
+    to execute, Jalangi requires significant library modifications~\sx{meso}.
+  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
+  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
+  % The majority of the overheads come from the use of \ttt{with}, a
+
+\end{itemize}
+
+% \sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
+%   operates as a library around an existing runtime,
+%   does not require learning a new language, and 
+%   gets meaningful information while operating only at library boundaries.
+% % Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
+% In this section, we report on \sys's performance characteristics:
+% % At a high level, we are interested in three questions:
+%   (i) the overheads of its underlying building blocks;
+%   (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
+%   (iii) \sys's behavior on realistic  multi-library applications.
+% % For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
+% % For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
+% % For the third question, we use a combination of real applications~\sx{macro}.
+
+Experiments were conducted on a modest server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
 In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
@@
 
-\subsection{Micro-benchmarks}
-\label{micro}
-
-\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
-For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
-% Each dependency can perform one of three operations, depending on its current state:
-%   (i) invoke a call to a module it imports,
-%   (ii) busy-wait for a specific amount of time, or
-%   (iii) respond to calls by returning a value.
-A second goal was to understand \sys's internal overheads in a controlled environment.
-% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.
-
-\begin{table}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{Synthetic Micro-benchmarks}.
-		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
-    All timings are in $ms$~\cf{micro}.
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
-\toprule
-	               &   Base    &  SA     & PD      &  TID    \\
-\midrule
-globals vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
-built-in fields  &   1.44    &  6.46   &  6.24   &  5.96   \\
-counter          &   3.37    &  6.26   &  6.32   &  5.72   \\
-all names        &   7.79    &  13.54  &  13.31  &  12.8   \\
-custom delays    &   24661   &  24848  &  24754  &  24760  \\
-direct-access    &   4.06    &  7.24   &  7.16   &  6.79   \\
-timple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
-cycles           &   4.32    &  8.32   &  8.19   &  7.73   \\
-\bottomrule
-\end{tabular*}
-\label{tab:synthetic}
-\vspace{-5mm}
-\end{table}
-
-Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
-The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful.
-% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
-For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
-The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
-Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
-  most of these benchmarks feature artificially tight loops with high-frequency accesses.
-Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
-% is not affected significantly % by transformations altering a library's context
-
-To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
-  unmodified and proxy-wrapped.
-Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
-We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
-The proxy-wrapped version introduces interposition at every level.
-Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
-% 
-We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
-  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
-The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
-  what is likely to be is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
-
-\begin{table}[t]
-\center
-\footnotesize
-\setlength\tabcolsep{3pt}
-\caption{
-  \footnotesize{
-    \textbf{\sys-augmented single-library programs}.
-    The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
-  }
-}
-\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
-\toprule
-                               & Base   &  SA   & PD     &   TID   \\
-\midrule
-Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
-Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
-Minimist~\cite{minimist}       &        &       &        &         \\
-~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
-~~~-t2                         & 29.35  & 56.30 &  53.98 &  53.17  \\
-~~~-t3                         & 30.34  & 59.13 &  55.76 &  55.34  \\
-~~~-t4                         & 30.04  & 56.40 &  53.68 &  53.27  \\
-~~~-t5                         & 30.24  & 58.17 &  55.07 &  54.76  \\
-Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
-yargs~\cite{yargs}             & 14.59  & 15.68 &  15.49 &  15.54  \\
-chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
-colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
-mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
-\bottomrule
-\end{tabular*}
-\label{tab:meso}
-\vspace{-5mm}
-\end{table}
+% \begin{table}[t]
+% \center
+% \footnotesize
+% \setlength\tabcolsep{3pt}
+% \caption{
+%   \footnotesize{
+%     \textbf{Analysis results for the largest libraries.}.
+%     The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
+%   }
+% }
+% \begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
+% \toprule
+%                                & Base   &  SA   & PD     &   TID   \\
+% \midrule
+% Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
+% Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
+% Minimist~\cite{minimist}       &        &       &        &         \\
+% ~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
+% ~~~-t2                         & 29.35  & 56.30 &  53.98 &  53.17  \\
+% ~~~-t3                         & 30.34  & 59.13 &  55.76 &  55.34  \\
+% ~~~-t4                         & 30.04  & 56.40 &  53.68 &  53.27  \\
+% ~~~-t5                         & 30.24  & 58.17 &  55.07 &  54.76  \\
+% Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
+% yargs~\cite{yargs}             & 14.59  & 15.68 &  15.49 &  15.54  \\
+% chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
+% colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
+% mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
+% \bottomrule
+% \end{tabular*}
+% \label{tab:meso}
+% \vspace{-5mm}
+% \end{table}
 
@@
   \centering
-   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
+   \includegraphics[width=\textwidth]{./figs/micro-packages.pdf}
   \caption{
-    \textbf{Analysis overheads.}
-    The plot compares single-library programs taken from Jalangi2 between three setups:
-		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi2, (iii) global-use analysis with \sys.
-    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
-  }
-  \label{fig:meso}
+    \textbf{Analysis performance overhead.}
+    The plot shows the performance overhead of the three analyses for 45 libraries~\cf{meso}.
+  }
+  \label{fig:micro-packages}
   \vspace{-3mm}
@@
 
-In the first experiment, we collected a diverse set of eight popular libraries from npm, 
-% used by thousands of other projects,
-on the order of hundreds of lines of code.
-As a workload, we used each library's internal test suite (one library, \ttt{minimist}, includes several test harnesses).
-These tests stress functionality as expected by the library's authors and confirm that \sys does not break it.
-We applied our three analyses, and compare their performance with the baseline (Tab.~\ref{tab:meso}).
-The results show that executions augmented with analyses are within 2--3$\times$, averaging a 80\% slowdown for the largest libraries.
-Different benchmarks put a different pressure on \sys's wrappers, which range between 23--257. % (shown by the analysis output).
-
-In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
-We note that Jalangi2 improves significantly over Jalangi's performance~\cite{jalangi}, as it eschews record/replay capabilities.
+\heading{\sys on Popular Libraries}
+For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
+These libraries are highly popular, averaging \todo{xx-xx} weekly downloads (total: \todo{X}) and are depended upon by about \todo{XX} other packages or applications on average (total: \todo{X}).
+These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.
+
+Each library was run against the test suite provided by its nominal developers, via \ttt{npm test}.
+As these libraries are quite popular, they have received significant investment in their testing infrastructure, resulting into two main benefits for \sys's evaluation:
+  (i) different tests stress different parts of the library and corresponding analysis primitives;
+  (ii) even if most applications that import these libraries use only a fraction of their functionality, tests still cover the majority of provided functionality---\eg we observed test suites that were $10\times$ the size of the corresponding library.
+
+Fig.~\ref{fig:micro-packages} shows the performance overhead of applying \sys on these libraries.
+Overheads report on running each library's entire test suite under the three analyses and comparing against the non-\sys version.
+On average, \sys's analyses add about 3.3ms per library causing 1.93\% slowdown;
+  relative overheads between analyses are negligible (avg: $<$0.1ms).
+For the largest of these libraries, we perform a lighter global-access analysis (not shown in Fig.~\ref{fig:micro-packages}).
+This is slightly faster, adding a 3.2ms causing a 1.62\% slowdown.
+We zoom into the sources of these overheads later~\sx{micro}.
+
+\heading{\sys vs. Jalangi}
+For the second experiment, we compare the performance of \sys to that of Jalangi.
+Jalangi is a popular dynamic analysis framework for JavaScript;
+  it provides fine-grained instrumentation by executing the program using a custom interpreter.
+We note our use of Jalangi's v2.2.5 version:
+  the v2 branch improves significantly over the performance of the original framework~\cite{jalangi}, as it eschews record/replay capabilities.
+
+In terms of programs, we use Jalangi's extensive test suite.
+This is not entirely by choice:
+  Jalangi's interaction with the bare-bones libraries was hitting important parsing issues, and was further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
+It is important
+
+(Fig.~\ref{fig:meso}).
+We compare with and compare \sys's performance to that of Jalangi2.
 To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
@@
 Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.
+
+\begin{figure*}[t]
+  \centering
+   \includegraphics[width=\textwidth]{./figs/meso.pdf}
+  \caption{
+    \textbf{\sys vs. Jalangi.}
+    The plot compares single-library programs taken from Jalangi between three setups:
+		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi, (iii) global-use analysis with \sys.
+    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
+  }
+  \label{fig:meso}
+  \vspace{-3mm}
+\end{figure*}
 
@@
 However, the performance of analyzed code is on average still within 2--3$\times$ over the baseline performance.
-The size of the resulting JSON files raises the challenge of analysis interpretability---surprisingly, just running Terminalizer with \ttt{--help} still returns more than 6K fragments from several libraries.
-Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-name, not module identifier.
+The size of the resulting JSON files raises the challenge of analysis interpretability---just by running Terminalizer with \ttt{--help} returns more than 6K fragments from several (hundreds of) libraries.
+Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-readable name, not file-system module identifier.
 This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
@@
 Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
+
+\subsection{Micro-benchmarks}
+\label{micro}
+
+\todo{Two types: zooming into prior benchmarks, and targeted micro packages}
+\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
+For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
+% Each dependency can perform one of three operations, depending on its current state:
+%   (i) invoke a call to a module it imports,
+%   (ii) busy-wait for a specific amount of time, or
+%   (iii) respond to calls by returning a value.
+A second goal was to understand \sys's internal overheads in a controlled environment.
+% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.
+
+\heading{Sources of Overbred}
+To understand the sources of these overheads, we perform a series of micro-benchmarks with tight loops calling several ES-internal libraries without any I/O.
+The primary source of overhead seems to be the use of JavaScript's \ttt{with} construct~\sx{}, 
+The \ttt{with} construct dominates overheads, as it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards~\cite{}.
+% Proxy objects exhibit a much lower cost.
+% \TODO{Add some numbers from \ttt{t19} for different configs}.
+
+\begin{table}[t]
+\center
+\footnotesize
+\setlength\tabcolsep{3pt}
+\caption{
+  \footnotesize{
+    \textbf{Synthetic Micro-benchmarks}.
+		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
+    All timings are in $ms$~\cf{micro}.
+  }
+}
+\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
+\toprule
+	               &   Base    &  SA     & PD      &  TID    \\
+\midrule
+globals vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
+built-in fields  &   1.44    &  6.46   &  6.24   &  5.96   \\
+counter          &   3.37    &  6.26   &  6.32   &  5.72   \\
+all names        &   7.79    &  13.54  &  13.31  &  12.8   \\
+custom delays    &   24661   &  24848  &  24754  &  24760  \\
+direct-access    &   4.06    &  7.24   &  7.16   &  6.79   \\
+timple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
+cycles           &   4.32    &  8.32   &  8.19   &  7.73   \\
+\bottomrule
+\end{tabular*}
+\label{tab:synthetic}
+\vspace{-5mm}
+\end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.05\textwidth]{./figs/lya_donut_index}
+  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_obj}
+  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_unique_valid}
+  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_total_valid}
+
+  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_unique_invalid}
+  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_total_invalid}
+  \caption{
+    \textbf{Access characteristics.}
+    \todo{Explain}
+  }
+  \label{fig:objects}
+\end{figure}
+
+\begin{figure}[b!]
+  \centering
+  \includegraphics[width=\columnwidth]{./figs/lya_n_obj}
+  \includegraphics[width=\columnwidth]{./figs/lya_unique_valid}
+  % \includegraphics[width=\columnwidth]{./figs/lya_unique_invalid}
+  \includegraphics[width=\columnwidth]{./figs/lya_total_valid}
+  % \includegraphics[width=\columnwidth]{./figs/lya_total_invalid}
+  \caption{
+    \textbf{Depth vs. permissiveness.}
+    From the top:
+    (a) number of \sys wrappers,
+    (b) unique valid accesses,
+    (c) unique invalid accesses,
+    (d) total valid accesses, and
+    (e) total invalid accesses---all as a function of \todo{enforcement} depth.
+  }
+  \label{fig:objects}
+\end{figure}
+
+Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
+The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful.
+% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
+For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
+The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
+Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
+  most of these benchmarks feature artificially tight loops with high-frequency accesses.
+Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
+% is not affected significantly % by transformations altering a library's context
+
+To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
+  unmodified and proxy-wrapped.
+Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
+We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
+The proxy-wrapped version introduces interposition at every level.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+% 
+We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
+  what is likely to be is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
 

### 2020-05-26 paper/draft.tex
Add total, average numbers of downloads per week and dependencies

@@
 For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
-These libraries are highly popular, averaging \todo{xx-xx} weekly downloads (total: \todo{X}) and are depended upon by about \todo{XX} other packages or applications on average (total: \todo{X}).
+These libraries are highly popular, averaging \todo{4842488} weekly downloads (total: \todo{227596957}) and are depended upon by about \todo{2} other packages or applications on average (total: \todo{75}).
+% More results about the javascript packages here: https://docs.google.com/spreadsheets/d/18xKjCgj1phODbNi6_IT-y3vP3oVaaY5oA-Wux2avvGY/edit#gid=2071117281
 These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.

### 2020-05-26 paper/draft.tex
Major rewrite

--- 2020-05-26 paper/draft.tex
@@
 For the second experiment, we compare the performance of \sys to that of Jalangi.
-Jalangi is a popular dynamic analysis framework for JavaScript;
-  it provides fine-grained instrumentation by executing the program using a custom interpreter.
+Jalangi is a popular dynamic analysis framework for JavaScript, providing fine-grained instrumentation by executing on a custom interpreter.
 We note our use of Jalangi's v2.2.5 version:
@@
 
-In terms of programs, we use Jalangi's extensive test suite.
+In terms of programs, we use Jalangi's extensive test suite within a Jalangi-provided docker container~\cite{jaladocker}
+(For these experiments, \sys is also run in the same container.)
 This is not entirely by choice:
-  Jalangi's interaction with the bare-bones libraries was hitting important parsing issues, and was further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
-It is important
-
-(Fig.~\ref{fig:meso}).
-We compare with and compare \sys's performance to that of Jalangi2.
-To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
+  Jalangi's interaction with the bare-bones libraries was hitting EcmaScript 6 parsing challenges, further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
+Contrary to Jalangi, \sys executes all programs, demonstrating the compatibility benefits of operating on an unmodified runtime.
+
+% FIXME OSDI
+% This is an important practical difference with \sys approach:
+%   if \sys does not understand, it will simply not wrap it---deferring silently to the default semantics implemented by the runtime rather than
+
+In terms of analysis, both systems are configured to perform dynamic frequency analysis of accesses to global variables.
+The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a fair and meaningful comparison between the two frameworks.
+Such analyses are useful for understanding how programs with third-party libraries interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.
+
+Fig.~\ref{fig:meso} presents the comparison between \sys and Jalangi.
 The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
@@
 
-\subsection{End-to-End Benchmarks}
+\subsection{Application Benchmarks}
 \label{macro}
@@
 
-Finally, we perform end-to-end program dialysis on three large applications:
+We perform end-to-end program dialysis on three large applications:
   KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
@@
 
-\todo{Two types: zooming into prior benchmarks, and targeted micro packages}
-\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
-For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
+\sys's micro-benchmarks zoom into \sys's sources of overheads.
+%  from \sys and confirm it does not affect the correctness of the program with respect to its sequential execution.
+The key results are that
+  (i) the majority of the overhead comes from the JavaScript's \ttt{with} expression, which \sys uses to wrap the context of libraries;
+  (ii) interposition overhead is negligible in practice;
+  (iii) while wrapped and accessed fields increase exponentially as a function of depth (as objects have many fields), object explosion quickly plateaus around level four with under 400 fields; and
+  (iv) the majority of wrapped and accessed fields come from Node and EcmaScript names rather than imports or global values.
+% We use two broad classes of micro-benchmarks.
+% In the first class, we use the same 50 libraries that were the focus of a previous section~\sx{meso} to understand the characteristics of access patterns and \sys-internal overheads in a controlled environment.
+% In the second class, we use synthetic micro-benchmarks to test key properties of each analysis and confirm it outputs the expected results.
+% For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
+
 % Each dependency can perform one of three operations, depending on its current state:
@@
 %   (iii) respond to calls by returning a value.
-A second goal was to understand \sys's internal overheads in a controlled environment.
 % Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.
 
-\heading{Sources of Overbred}
+\heading{Sources of Overhead}
 To understand the sources of these overheads, we perform a series of micro-benchmarks with tight loops calling several ES-internal libraries without any I/O.
-The primary source of overhead seems to be the use of JavaScript's \ttt{with} construct~\sx{}, 
-The \ttt{with} construct dominates overheads, as it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards~\cite{}.
+By enabling different parts of \sys, we discover that the primary source of overhead comes from JavaScript's \ttt{with} construct:
+  disabling \ttt{with} makes 95\% of the overheads disappear.
+The reason \ttt{with} dominates overheads is twofold: it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards.
 % Proxy objects exhibit a much lower cost.
@@
 
+\heading{Interposition Overheads}
+Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of the aforementioned synthetic benchmarks.
+%  (tight loops with no I/O).
+The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful:
+% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
+  for example, the ``custom-delay'' benchmark features static bottlenecks across its dependency tree but does not involve interesting access patterns.
+\sys-induced slowdown is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
+Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses.
+  these benchmarks feature artificially tight loops with high-frequency accesses.
+Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under $1ms$.
+% is not affected significantly % by transformations altering a library's context
+
+To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
+  unmodified and proxy-wrapped.
+Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
+We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
+The proxy-wrapped version introduces interposition at every level.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+% 
+We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
+  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
+The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
+  what is likely to be is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
+
+\heading{Analysis Depth}
+To understand the effect of depth in practice, Fig.~\ref{fig:objects} presents the number of wrapped object, unique accesses, and total accesses as a function of depth for all 50 libraries~\sx{meso}.
+Depth is explained in the previous paragraph:
+   it is about how deep \sys traverses references starting starting from the names in scope---\eg the access \ttt{global.obj.x} is two levels deep and \ttt{fs.readFile} is one level deep.
+
+There are a few highlights worth noting.
+While the number of objects wrapped by\sys starts growing exponentially, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
+Accesses grow quickly for the first couple of levels---objects for some of these libraries are hit several thousand times---but then remain stable.
+This is usually because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.
+
 \begin{figure}
@@
   \caption{
-    \textbf{Access characteristics.}
-    \todo{Explain}
+    \textbf{Access characteristics as a function of context.}
+    Clockwise from top-left:
+    (i) number of \sys wrappers,
+    (ii) unique valid accesses (\ie counting each access once),
+    (iii) total valid accesses~\cf{micro}.
   }
@@
 
-\begin{figure}[b!]
+\heading{Context}
+Context refers to the broad source of names that are available in the current scope---ones
+  defined by the EcmaScript standard (es), 
+  through an explicit import (exports),
+  by the Node.js runtime (node), or
+  via global variables (globs).
+A few names seem globally available but are in fact module-locals (\ttt{require}).
+User-defined global variables are not prefixed with \ttt{global} thus requiring special interposition (\ttt{with}).
+
+Fig.~\ref{fig:objects} shows \sys's context characteristics on all 50 libraries~\sx{meso}. % as a function of context.
+In terms of the number of objects wrapped, the vast majority comes from Node which accounts for 91.1\% of all wrappers.
+In terms of unique number of accesses, for both invalid and invalid ones the majority comes from \ttt{require};
+  taking their number into account, the majority comes from ES and Node names, whereas the majority of invalid ones comes from \ttt{export}s.
+
+\begin{figure}[t]
   \centering
@@
   \caption{
-    \textbf{Depth vs. permissiveness.}
+    \textbf{Analysis characteristics as a function of the analysis depth.}
     From the top:
-    (a) number of \sys wrappers,
-    (b) unique valid accesses,
-    (c) unique invalid accesses,
-    (d) total valid accesses, and
-    (e) total invalid accesses---all as a function of \todo{enforcement} depth.
+    (i) number of \sys wrappers applied,
+    (ii) number of unique accesses (\ie counting each access once),
+    (iii) total number of accesses~\cf{micro}.
   }
@@
 \end{figure}
-
-Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
-The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful.
-% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
-For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
-The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
-Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
-  most of these benchmarks feature artificially tight loops with high-frequency accesses.
-Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
-% is not affected significantly % by transformations altering a library's context
-
-To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
-  unmodified and proxy-wrapped.
-Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
-We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
-The proxy-wrapped version introduces interposition at every level.
-Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
-% 
-We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
-  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
-The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
-  what is likely to be is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.
 

### 2020-05-26 paper/draft.tex
Fix dependents problem

--- 2020-05-26 paper/draft.tex
@@
 For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
-These libraries are highly popular, averaging \todo{4842488} weekly downloads (total: \todo{227596957}) and are depended upon by about \todo{2} other packages or applications on average (total: \todo{75}).
+These libraries are highly popular, averaging \todo{4842488} weekly downloads (total: \todo{227596957}) and are depended upon by about \todo{656} other packages or applications on average (total: \todo{30812}).
 % More results about the javascript packages here: https://docs.google.com/spreadsheets/d/18xKjCgj1phODbNi6_IT-y3vP3oVaaY5oA-Wux2avvGY/edit#gid=2071117281

### 2020-05-26 paper/draft.tex
Massive cleanup

--- 2020-05-26 paper/draft.tex
@@
-% TODO: tempted to term this "Module-aware dynamic fragmentation, analysis, and reassembly" as Dialysis or refracture
 % CFP: https://www.usenix.org/conference/atc20/call-for-papers
@@
 
-\newcommand{\fra}{fragmentation\xspace} % fracture
+\newcommand{\fra}{fragmentation\xspace} % fracture?
 \newcommand{\ana}{analysis\xspace}      % 
 \newcommand{\ass}{reassembly\xspace}    % 
-\newcommand{\Fra}{Fragmentation\xspace} % fracture
+\newcommand{\Fra}{Fragmentation\xspace} % fracture?
 \newcommand{\Ana}{Analysis\xspace}      % 
@@
 
-%don't want date printed
 \date{}
 
-% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
 \title{\Large \bf \sys: Library-Oriented Program Analysis}
 
-%for single author (just remove % characters)
 \author{
 {\rm Anonymous Author(s)}\\
-% \normalsize{Submission \#225, 11 + 3 pages}\\
-% \normalsize{Anonymous Author(s)}\\
 \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
-% {\rm Grigoris Ntousakis}\\
-% Technical University of Crete
-% \and
-% {\rm Nikos Vasilakis}\\
-% Massachusetts Institute of Technology
 }
@@
 Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.
-
-% operate at the library  interface level  
-% This approach occupies an new point in the design trade-off space, enabling lya to operates at the library interface level in unmodified production..
-
-% transform and bind their context prior to their evaluation.
-% expose instrumentation opportunities to developers.
-% This mechanism enables a new lightweight instrumentation technique.
-
-% 
-% 
-% 
-% different
-% dynamic interposition techniques
-% 
-% We show how to exploit the technique to deliver very efficient interposition schemes
-% 
-%   the new technique operates at a finer granularity, 
-%   coarse granularity
-% 
-% we can exploit our characteristics.
-% Allows us to do X. This in turn has the following benefits for the developer Y:
-% 
-% the results show a way faster
-% 
-% What are the benefits
-% we present a library-oriented dynamic analysis technique and system
-% technique the functionality for interposing at library boundaries
-% 
-% 
-% We do dynamic analys 10 times faster and has
-% 
-% ---\eg access to a specific global variable or invocation of a specific method.
-% library method calls 
-% property value .
-
-% An important advantage is increased performance and backwards compatibility executes on the unmodified runtime and performs at a coarse granularity.
- % , and coordinate to get the full view of the workings of one or more libraries.
-% The level at which dialysis operates offer improved performance, backwards-compatibility
-
-% Handlers are stateful 
-% 
-% compute over information associated with these events.
-% written in the same language as the program
-% 
-% During its execution, the modified program calls 
-% 
-% perform on the unmodified language runtime
-% thus offer performance and compatibility advantages over conventional, finer-grained analysis.
-% 
-% An important advantage is increased performance and backwards compatibility 
-% executes on the unmodified runtime and performs at a coarse granularity.
-% Despite its coarse granularity, dialysis still offers insightful information whose 
-% 
-% as demonstrated by three analysis use-cases whose needs are largely unmet by conventional analysis frameworks.
-% 
-% We implement program dialysis in \sys and evaluate it against libraries and programs drawn from the JavaScript ecosystem.
-% The results show significant performance improvements over state-of-the-art dynamic analysis framework, comparable analysis scripts,
-% 
-% when certain events occur.
-% Analysis scripts provide handlers for certain classes of events,
-% 
-% Developers provide handlers that are called when certain events occur,
-% by providing handlers to events.
-% 
-% These handlers are short, operate on the unmodified language runtime, thus offering performance benefits,
-% 
-% To expose these hooks, dialysis performs 
-% 
-% This is achieved by augmenting the library loader, but without necessarily modifying the language runtime 
-% 
-% Compared to dynamic analysis, dialysis
-% (i) operates at a coarser granularity (performance) and on the same runtime getting full support for the language (compatible with the semantics of the langauge)
-% but on the original runtime 
-% (ii) at the same level as the program, which means it can manipulate semantic information 
-% (iii)
-% 
-% Despite the fact that it operates at the same level as program
-% 
-% \sys 
-% 
-% can capture the library's full observable behavior.
-% 
-%   a dynamic analysis technique specifically tailored to applications with many third-party libraries.
-% Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic fragmentation, analysis, and reassembly of programs at the level of individual libraries during program execution.
-% It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
-% 
-% Our dialysis prototype, \sys, targets the JavaScript ecosystem.
-% demonstrates significant 
-% (i) performance benefits over conventional dynamic analysis, to the point that it can be toggled on/off online
-% Expressing analyses is comparable with 
-% succinct script in the same language and ecosystem as the dialysis target,
-% (iii) and its usefullness is 
-% 
-% 
-% A series of case-studies motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-library programs with low developer effort and performance overhead:
-%   insightful analyses can be expressed in a few lines of code, add a minimal increase in the load latency of individual libraries, and scale to large programs with hundreds of libraries.
-%
-
-% Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
-% % By leveraging the ubiquity of third-party modules in today's applications
-% Such modules can be part of third-party packages or of the language's standard library;
-%   the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
-
-% Operating at this level of granularity has several benefits:
-%   (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
-%   (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and %developers can use their tools
-%   (iii) it features low performance overheads, to the point that has the potential to be used online.
-% % FIXME: It depends on the analysis
-% % Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis 
-% % Operating at the granularity of library has several benefits: (i) ease (ii) performance (iii) while still getting 
-% %In a sense, modules are the right level of abstraction 
 \end{abstract}
@@
 
-% Where dynamic analysis shines is
-% Dynamic analysis occupies a clear spot in the space of analysis has clear strengths and weaknesses.
-% Examples of information not analyzable statically include runtime code evaluation, runtime introspection and reflection, as well as multi-lingual support.
-% Dynamic analysis is a particularly good fit for the analysis of dynamic languages.
-
 Unfortunately, reaping these benefits comes with significant costs in terms of developer effort or runtime performance.
-Manually instrumenting a program requires a good understanding of its internals. % instruction sets?
+Manually instrumenting a program requires a good understanding of its internals. 
 External tools such as instrumentation frameworks~\cite{pin, valgrind} and performance tracing tools~\cite{perf, dtrace} only add to the curve, as they feature their own language for specifying analyses.
-% usually different from the application's language.
 Modifying the application's runtime environment such as the interpreter is cumbersome, error-prone, and requires development in a language that is different than that of the program.
@@
 This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
-% Libraries are used pervasively today to lower development costs and improve software quality, 
-% This over-reliance to third-party libraries is a recent phenomenon, 
   language-specific package repositories eliminate the cost of publishing and using a library.
@@
 
-To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
-  A method of deconstruction into elements often for the purposes of altering piecewise components or removing waste products.
-  From % ancient Greek 
-  {\scriptsize $\delta\iota\acute{\alpha}$} (di\'{a}, ``inter-, through'') and {\scriptsize $\lambda\acute{\tilde{\upsilon}}\epsilon\iota\nu$} (lúein, ``to loosen'').
-} and implemented in \sys.
+To address these challenges, we propose a novel approach to dynamic analysis,
+\todo{implemented in} \sys.
 Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
-%                                                   !! sosto!!------.
-%                                                                   \/
 It operates during program execution, automating the wrapping and transformation of a program's dependency graph, and allows developers to extract meaningful insights with only a few lines of analysis-specific code.
-By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
-  (i) it allows bolting analysis, itself as a library, onto unmodified runtime environments, % with no dynamic analysis,
+By operating at the granularity of libraries, dialysis has several benefits over prior work:
+  (i) it allows bolting analysis, itself as a library, onto unmodified runtime environments,
   (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
@@
 
-% (i) at a somewhat coarser granularity, but still offering insights---and in a semantics-aware way tailored to the programming language.
-% (ii) bolt on
-% Our approach is applicable to any language that supports some notion of modularity, runtime introspection, and .
-% It plugs into the module-loading capability of the runtime system to insert key hooks for inserting 
-% After the parsing and interpretation phases of module loading complete, 
-%  which are then parsed and interpreted and 
-% Surprisingly, as we show in this paper, this architecture requires \emph{no} modifications to the language runtime---that is, it is backward-compatible with vanilla unmodified language runtime environments.
-% 
-% Its key strategy is to fracture applications at the boundaries of modules, instrument their interfaces (including direct accesses) using meta-programming capabilities, and recombine them 
-% By combining visiiblity into both built-in and third-party modules, \sys can get gather important information for 
-% at a much lower cost---both in terms of runtime performance and developer effort.
-% 
-% % to enable module-aware dynamic analysis are general
-% To achieve this, module-aware dynamic analysis leverages several techniques.
-% It plugs into the module manager;
-% wraps interfaces
-% (i) bolt on, meaning
-% (ii) high-performance, and 
-% (iii) low effort 
-% 
-% As shown later, these capabilities are generally available in all dynamic programming languages---\eg
-
 To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). 
-% and unusually high code-reuse~\cite{npmstudy:19}.
-%, and a pressing need for usable dynamic analysis~\cite{}.
 We develop a diverse set of analyses that target practical information about a program:
@@
   a profiling analysis showing bottlenecked modules,
-% a synthesis-oriented analysis on input-output data,
   and an analysis extracting union-based type invariants.
@@
 
-% The emerging development process should (and to a certain extent, does) simplify the development and testing process;
-%   unfortunately, good abstractions are sealed (\ie they do not leak between abstraction layers), which makes the inspection of a library difficult.
-
 \subsection{Background on Module Systems}
@@
 From a developer's perspective, \ttt{import}ing a library makes its functionality available to the calling code by means of binding its functionality to a name in the caller's scope.
-% What this means is that some of the library's functionality is bound to a variable name that becomes available in the scope of the caller.
 This is achieved by some form of \ttt{export}ing, where the library developer expresses which values should become available to the \ttt{import}ing code.
-The definition of a value depends on the semantics of the language. % for now we can assume it's either a primitive value, a list of values, a function, or an object mapping string keys to values.
+The definition of a value depends on the semantics of the language. 
 Internally, the library may \ttt{import} other libraries, cause side-effects to the file-system or the network, or even be implemented in multiple languages.
-% , as shown on line \fixme{XX},
-% closely coupled with the runtime
-% and in some cases features its own mini-language, as is the case in Scheme and Standard ML.
 
@@
 Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
-This process starts by locating the library in the file system, % or across the network,\footnote{
+This process starts by locating the library in the file system,
+% or across the network,\footnote{
 %   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
@@
 by resolving code-relative module identifiers.
-% The library is assigned a unique identifier.
 The content of the library is then read and wrapped in a way that resolves library-local names, such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript, to meaningful values.
@@
 
-% Several details:
+\subsection{Motivating Examples}
+\label{examples}
+
+% Could add several details:
 %   same module at multiple levels, and the module cache
@@
 
-\subsection{Motivating Examples}
-\label{examples}
-
 Having reviewed the building blocks and underlying techniques that power modularity, we now turn to examples of dynamic analysis that today are difficult or require specialized solutions:
@@
   (ii) a performance-profiling analysis showing bottlenecked libraries, and
-% (iii) a synthesis-oriented analysis on input-output data, and
   (iii) an analysis extracting runtime type invariants.
 These examples illuminate key design requirements for dialysis in general and \sys in particular.
-% \sys's implementation of module-level dynamic analysis.
 
@@
 
- %% To address such problems, several recent proposals suggest analyzing third-party modules dynamically to identify malicious behavior~\cite{}.
- %% % FIXME more about the policy, tracking arguments too
- %%  indicating the resources touched by that library 
- %% it seems critical to be able to toggle analysis on/off on production.
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
-
 \heading{Performance Diagnosis}
@@
 Maintenance and rewriting can also cause performance regressions between two versions of a library;
-% FIXME: Garbage collection
   worse even, the fact that a library changes one of its dependencies can cause severe performance pathologies to upstream projects---that is, while an interface remains the same due to an intermediate layer of abstraction, its performance can change dramatically~\cite{jest}.
@@
 
-Switching-on a library-level profiling analysis % that operates at library boundaries
+Switching-on a library-level profiling analysis 
   would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
@@
 Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
-% An analysis could treat library invocation boundaries as message queues~\cite{scheme:98, duality:79} growing when a library gets overwhelmed.
-% At some point, the waiting time of newly-arrived messages becomes longer than sending messages to a library replica.
 Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.
-
-% \emph{
-% This case highlights the need to \fixme{analyze} all the observable behavior \emph{around} a library, without necessarily caring about fine-grained library-internal analysis.
-% }
 
@@
 Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
-%and types are lightweight annotations that can be quickly and efficiently checked.
 For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
@@
 To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
-Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec. %, common in distributed systems
+Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec.
 This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.
@@
 %% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
-
-% would need to be able 
-% to capture structural subtitling---that is the piecewise
-
-% \heading{Learning, Synthesis, and Regeneration}
 
@@
 % the library interface is usually a complex (but singular) object;
-% the surrounding environment provides names to multiple ``implicitely'' imported libraries, functionality provided by the language.
+% the surrounding environment provides names to multiple ``implicitly'' imported libraries, functionality provided by the language.
 This phase requires solving several challenges, including enumerating all points of entry into and exit out of a library, 
@@
 \end{itemize}
-
-% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.
 
@@
 
-% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
-% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
-% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
-% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
-% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
-% The following subsections detail these steps.
-
 \subsection{Fragmentation}
@@
 If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
-% \omit{---the common case---}
 Otherwise, \sys first invokes the built-in library loader to locate the library.
@@
 Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code into an in-memory object.
-% A series of transformations is applied before and after interpretation~\sx{two}.
 
@@
 \heading{Transformations}
-% , such as an object returned from a module or an exception about to be sent across the network.
 \sys's transformations boil down to a base transform \ttt{wrap} that traverses and augments values with runtime analysis monitors.
@@
 To avoid cycles during the walk, values are added to a map that is consulted at the beginning of each recursive call.
-% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
-
-% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
-% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
-% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
-% At runtime, $f'$ checks $\sigma$:
-%  if the access is allowed, it forwards the call to $f$;
-%  otherwise, it raises an exception.
-% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
-% 
-% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
-% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
-% 
-% % Listing~\ref{core-tx} presents a simplified core of the language.
-% 
-% \begin{itemize}
-% \item
-%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
-% \item
-%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
-% \item
-%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
-% \end{itemize}
 
@@
 The prologue executes before everything else in the library.
-% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
 This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process:
@@
 Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
-% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
 For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
@@
 
-% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
 A special entry is reserved for the original library value as a string~\sx{two}, so that subsequent transformations can skip loading the library from disk.
@@
 \end{figure*}
-
-% Fixme switch from libraries to modules?
 
@@
 
-% It sketches the Node runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.
-
 \subsection{System Implementation}
@@
 (L) Loading: depending on the file type, identify the corresponding loader---\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc
-% Identifiers are absolute paths.
 (W) Wrapping: wrap the module so that local names do not escape the module's scope and Node's module-local names get resolved.
@@
 
-% TODO: Talk about recipe file, that could be kept along with the module identifier
-
-% \begin{lstlisting}
-% let lib = `
-%  function (exports, require, module,
-%            __filename, __dirname, CTX) {
-%    let Math = CTX.Math
-%    let console = CTX.console
-%    //...[more definitions]
-%    ${moduleSource}
-%  });`;
-% \end{lstlisting}
-
 We found it useful to add an option for white- and black-listing libraries.
@@
 Examples of its use include blacklisting built-in libraries or white-listing only the library imported most recently.
-% This is useful, for example, when...
-
-% get second argument, no need to pass arguments around, tricky to 
-% carefull hardcoding of paths, because \sys's code itself is split into modules
-
-%% TODO: implementation
 
@@
 Individual analysis are implemented using a set of templates that provide initial constructs.
-%% Individual transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
-%% These skeletons provide hooks for end-developers writing analyses.
-%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
-%% These hooks are then extended or rewritten by developers to
 \sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
@@
 
-% FIXME: Snapshot results
-% [serial , whatever, pizza, ...]
-
 \heading{Type Invariant Discovery}
@@
 % \subsection{Limitations}
-% 
-% % FIXME: Talk about the inability to 
 % A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
@@
 \sys's micro-benchmarks zoom into \sys's sources of overheads.
-%  from \sys and confirm it does not affect the correctness of the program with respect to its sequential execution.
 The key results are that
@@
   (iv) the majority of wrapped and accessed fields come from Node and EcmaScript names rather than imports or global values.
-% We use two broad classes of micro-benchmarks.
-% In the first class, we use the same 50 libraries that were the focus of a previous section~\sx{meso} to understand the characteristics of access patterns and \sys-internal overheads in a controlled environment.
-% In the second class, we use synthetic micro-benchmarks to test key properties of each analysis and confirm it outputs the expected results.
-% For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
-
-% Each dependency can perform one of three operations, depending on its current state:
-%   (i) invoke a call to a module it imports,
-%   (ii) busy-wait for a specific amount of time, or
-%   (iii) respond to calls by returning a value.
-% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.
 
@@
 The reason \ttt{with} dominates overheads is twofold: it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards.
-% Proxy objects exhibit a much lower cost.
-% \TODO{Add some numbers from \ttt{t19} for different configs}.
 
@@
 Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of the aforementioned synthetic benchmarks.
-%  (tight loops with no I/O).
 The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful:
-% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
   for example, the ``custom-delay'' benchmark features static bottlenecks across its dependency tree but does not involve interesting access patterns.
@@
 Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under $1ms$.
-% is not affected significantly % by transformations altering a library's context
 
@@
   \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_total_valid}
-
-  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_unique_invalid}
-  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_total_invalid}
   \caption{
@@
   \includegraphics[width=\columnwidth]{./figs/lya_unique_valid}
-  % \includegraphics[width=\columnwidth]{./figs/lya_unique_invalid}
   \includegraphics[width=\columnwidth]{./figs/lya_total_valid}
-  % \includegraphics[width=\columnwidth]{./figs/lya_total_invalid}
   \caption{
@@
 
-% \begin{table*}[t]
-% \center
-% \footnotesize
-% \setlength\tabcolsep{3pt}
-% \caption{
-%   \footnotesize{
-%     \textbf{Language features used and their availability in other languages}.
-%     Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
-%   }
-% }
-% \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
-% \toprule
-%              &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
-% \midrule
-% Lua          &                              &                       &                     &                   &                       \\
-% JavaScript   &                              &                       &                     &                   &                       \\
-% Python       &                              &                       &                     &                   &                       \\
-% Ruby         &                              &                       &                     &                   &                       \\
-% Haskell      &                              &                       &                     &                   &                       \\
-% OCaml        &                              &                       &                     &                   &                       \\
-% Rust         &                              &                       &                     &                   &                       \\
-% Java         &                              &                       &                     &                   &                       \\
-% \bottomrule
-% \end{tabular*}
-% \label{tab:compat}
-% \vspace{-5mm}
-% \end{table*}
-
 The techniques presented in this paper are applicable to any programming language.
@@
 We now expand on the requirements bolting dialysis on other runtime environments.
-% FIXME: All these features have to have been discussed earlier
 
@@
 First, \sys needs to re-wire the \ttt{import} keyword:
-% This feature is important for compatibility reasons---otherwise developers would have to replace all import statements in their applications.
   if it is a function (\eg JavaScript, Scheme, Racket), re-wiring amounts to an overwrite;
@@
 Examples include templates and macro expansions such as Haskell's Template and Rust's macro system.
-% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities. %, allowing considerable freedom in the choice of implementation.
+% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
 % Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
@@
 \label{principles}
-% Dynamic analysis is a general technique for discovering facts about programs.
 While heavy-weight dynamic analysis provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand.
-% Dialysis can be thought as a coarser version of analysis stemming from natural library boundaries---a level of granularity that seems just right for certain problems.
-% Which are these cases exactly?
-
-% pressing need, lightweight, 
-% multiplies lyas power
+
 Dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
@@
 Finally, it deconstructs programs only at library boundaries, a naturally coarser granularity that is just right for certain classes of problems.
-% a granularity that is well-suited for several tasks.
-% libraries are a convenient level of abstraction---or the point where abstractions 
-% monitors all around a library
-
-% The first class of problems where dialysis shines is quick-and-dirty insights;
-% Even if dialysis doesn't solve the problem, it can quickly narrow it down to a certain corner of the application, at which point the cost of a heavy-weight solution is lower.
-% % This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
-% 
-% The second is when the goal is to understand the behavior of third-party code.
-% Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
-% Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
-% Examples include the 
-% N-version programming ---all of which would require a custom tool.
-% By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.
 
@@
 }
-% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}
-
-% That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
-% Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
-% Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
 
@@
 
-% Add our work
 Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
@@
 Recent trends in software engineering have led to unprecedented levels of third-party code (re-)use.
-% Applications today routinely pull together hundreds of libraries, making meaningful analysis difficult.
 We present \emph{program dialysis}, a novel library-aware analysis technique for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
-% is a general technique that
 Contrary to heavy-weight dynamic analysis, dialysis lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
-% it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand, dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
 Our dialysis prototype for JavaScript, \sys, is available as an open-source library for experimentation with other applications and analyses.
-
-% \section*{Acknowledgments}
-% Martin
-% \section*{Availability}
 

### 2020-05-27 paper/draft.tex
Dialysis -> Lya

--- 2020-05-26 paper/draft.tex
@@
 We implement this approach in \sys, a system targeting the JavaScript ecosystem. 
-Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.
+Results show that \sys delivers over an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.
 \end{abstract}
@@
 
-To address these challenges, we propose a novel approach to dynamic analysis,
-\todo{implemented in} \sys.
-Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and reassembly of applications at the level of individual libraries. 
-It operates during program execution, automating the wrapping and transformation of a program's dependency graph, and allows developers to extract meaningful insights with only a few lines of analysis-specific code.
-By operating at the granularity of libraries, dialysis has several benefits over prior work:
-  (i) it allows bolting analysis, itself as a library, onto unmodified runtime environments,
-  (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
-  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.
+To address these challenges, we propose a novel approach to dynamic analysis, targeting dynamic programming languages---and implemented in \sys for the server-side JavaScript ecosystem (>1.3M libraries~\cite{modulecounts}).
+\sys leverages the ability of these languages to import code at runtime as a string in order to apply transformations that wrap the module about to be imported with developer-provided, analysis-specific code.
+More specifically, \sys inserts a series of steps in the module-loading process result in wrapping a library's full observable behavior---rather than just its interface---and exposing it to developers for runtime analysis.
+\sys effectively fragments, transforms, and reassembles the application at the level of individual libraries. 
+The overall approach has several practical benefits over prior work:
+  (i) it allows bolting the dynamic analysis as a library  onto unmodified runtime environments,
+  (ii) it supports analyses expressed using the same language, tools, and abstractions as the program language,
+  (iii) it features low runtime performance overheads, enabling the potential for toggling its use in production environments.
 
@@
 
-To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem (>1.2M libraries~\cite{modulecounts}). 
-We develop a diverse set of analyses that target practical information about a program:
+To demonstrate that \sys can be useful in practice, despite its coarse granularity, we develop a diverse set of analyses:
   a read-write-execute security analysis,
-  a profiling analysis showing bottlenecked modules,
+  a profiling analysis for identifying bottlenecked modules,
   and an analysis extracting union-based type invariants.
-These analyses drive the design requirements for \sys, and highlight dialysis as a middle ground between coarse- and fine-grained analysis.
-We evaluate \sys at three different levels:
-  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
-  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
-  (iii) end-to-end full-application macro-benchmarks that showcase \sys's behavior on realistic workloads. 
+% These analyses drive \sys's design requirements, and highlight the decisions behind its design.
+Each of these analyses takes about 100 LoC in JavaScript;
+  this integration between the code being analyzed and the one implementing the analysis has significant usability implications.
+Finally, \sys's performance is evaluated extensively, using
+  (i) over 50 popular libraries and scripts, highlighting compatibility and performance improvements over state-of-the-art frameworks;
+  (ii) three full applications, demonstrating that \sys scales to large and complex programs; and
+  (iii) a series of micro-benchmarks that zoom into a few specific characteristics of \sys.
 \S\ref{bg}--\ref{eval} present our key contributions:
 \begin{itemize}
-\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly unmet by general-purpose analysis frameworks.
-\item \S\ref{design} presents the design of dialysis, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
+\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly by general-purpose analysis frameworks.
+\item \S\ref{design} presents the design of \sys, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
 \item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
@@
 
-Aside from the aforementioned sections (\S\ref{bg}--\ref{impl}), the paper discusses \sys's limitations and its application to other languages~\sx{diss};
-  it compares with related prior work in the literature~\sx{rw};
+The paper then discusses \sys's limitations and its application to other languages~\sx{diss};
+  it compares with related prior work~\sx{rw};
   and draws appropriate conclusions~\sx{end}.
@@
   (i) a read-write-execute security analysis,
-  (ii) a performance-profiling analysis showing bottlenecked libraries, and
+  (ii) a performance-profiling analysis, and %  for identifying bottlenecked libraries, and
   (iii) an analysis extracting runtime type invariants.
-These examples illuminate key design requirements for dialysis in general and \sys in particular.
+These examples illustrate key design requirements for \sys.
 
@@
 
-The next section describes program dialysis, a new analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
-  the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.
-
-\section{The Design of Program Dialysis}
+The next section describes the design of \sys, a new dynamic analysis framework that satisfies these goals, in a language-agnostic manner~\sx{design};
+  the section following that describes \sys's concrete implementation for server-side JavaScript~\sx{impl}.
+
+\section{The Design of \sys}
 \label{design}
 
-Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
+\sys starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
   instead of simply locating and loading a library from the file-system, it yields control to \sys, which applies a series of transformations to libraries with the goal of interposing at their boundaries.
-We start with an overview of dialysis~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).
+We start with an overview of \sys~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).
 
@@
 % FIXME: add user data
-Program dialysis operates by
+\sys operates by
   dismantling the program at the boundaries of libraries,
@@
   \item \textbf{Fragmentation:}
-Dialysis starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
+\sys starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
 This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
@@
   \item \textbf{Reassembly}
-Finally, dialysis reassembles individual modified libraries back into the program's original structure.
+Finally, \sys reassembles individual modified libraries back into the program's original structure.
 The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
@@
 
-When a dialysis-augmented program starts, it first loads the analysis file provided by the developer. 
+When a \sys-augmented program starts, it first loads the analysis file provided by the developer. 
 The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
@@
 % The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
-Dialysis frameworks may also want to add analysis-specific keywords not provided by the language.
+\sys frameworks may also want to add analysis-specific keywords not provided by the language.
 To achieve this, \sys wraps each analysis hook with a function whose body starts by defining the expected keywords.
@@
 
-This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
+This section details our implementation of \sys for server-side JavaScript in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
 % We start with the internals of \sys's implementation, and then describe
@@
 
-The aforementioned dialysis design can be implemented in either of two ways.
+The aforementioned \sys design can be implemented in either of two ways.
 The first is to implement \sys as a modified version of the runtime, in which several stages of its library-loading facility have been augmented in-place. % with the techniques described earlier.
@@
 %   (i) the overheads of its underlying building blocks;
-%   (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
+%   (ii) \sys on real libraries, and how they compare to a production-grade dynamic analysis; and
 %   (iii) \sys's behavior on realistic  multi-library applications.
@@
 \heading{\sys on Popular Libraries}
-For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
-These libraries are highly popular, averaging \todo{4842488} weekly downloads (total: \todo{227596957}) and are depended upon by about \todo{2} other packages or applications on average (total: \todo{75}).
+For the first experiment, we evaluate \sys on 50 JavaScript packages from the npm ecosystem.
+These libraries are highly popular, averaging 4.8M weekly downloads (total: 227M) and are depended upon by about 656 other packages or applications on average (total: 30K).
 % More results about the javascript packages here: https://docs.google.com/spreadsheets/d/18xKjCgj1phODbNi6_IT-y3vP3oVaaY5oA-Wux2avvGY/edit#gid=2071117281
-These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.
+These libraries are relatively small---adhering to known ecosystem trends~\cite{npmstudy:19}---simplifying compatibility inspection.
 
@@
 
-We perform end-to-end program dialysis on three large applications:
+We apply \sys on three large applications:
   KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
@@
 
-In this section, we start by reflecting on the requirements of dialysis from the programming language~\sx{reqs} and then on some of its strengths and weaknesses~\sx{principles}.
-% Program dialysis depends on a few features provided by the programming language.
+This section starts by discussing \sys's requirements from the programming language~\sx{reqs}. It then reflects on its strengths and weaknesses~\sx{principles}.
 
@@
 	(ii) we had prior experience developing more sophisticated versions of SA and PD.
-We now expand on the requirements bolting dialysis on other runtime environments.
-
-By operating on library boundaries, dialysis uses a few special language features, supported by all major programming languages.
+We now expand on the requirements bolting our techniques on other runtime environments.
+
+By operating on library boundaries, \sys uses a few special language features, supported by all major programming languages.
 First, \sys needs to re-wire the \ttt{import} keyword:
@@
 
-To conclude, all major languages provide facilities to support dialysis, albeit with a different level of convenience.
+To conclude, all major languages provide facilities to support a \sys-like framework, albeit with a different level of convenience.
 Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations, which conveniently unify module identification with interposition:
@@
 
-\subsection{When to Use Dialysis}
+\subsection{When to Use \sys-like Analysis}
 \label{principles}
@@
 
-Dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
+The set of techniques presented in this paper shines when there is a need for urgency, select online analysis, and a high level of abstraction.
 It can help identify (or narrow down) the source of a problem quickly, by swiftly isolating homegrown code from standard and third-party libraries, by requiring a few lines of analysis-specific code inlined, and by leveraging the developer's expertise in their language of choice.
@@
 
-Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
+\sys's set of techniques is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
 These limitations are due to several reasons.
@@
 
-The previous section~\sx{principles} offers a principles-comparison between dynamic analysis and dialysis.
+The previous section~\sx{principles} offers a theoretical comparison between conventional dynamic analysis and \sys.
 This section we turn to a technical comparison of \sys to prior systems.
@@
 %   Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
-%   whereas \sys's partial goal is supporting analysis in the same language as the program~\sx{goals}. % ---that is, dialysis implemented for Python would be using Python abstractions.
+%   whereas \sys's partial goal is supporting analysis in the same language as the program~\sx{goals}. % ---that is, \sys implemented for Python would be using Python abstractions.
 Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims for heavyweight instrumentation.
@@
 
-Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
-Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
-Moreover, AOP works on languages that were already designed to support it, whereas module dialysis is explicitly designed to bolt onto existing languages.
+\nv{
+\sys builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
+Both approaches lower complexity by mapping multiple points across the program to the same actions, but \sys does not alter the program's control flow.
+Moreover, AOP works on languages that were already designed to support it, whereas \sys is explicitly designed to bolt onto existing languages.
+}
 
@@
 
-Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
+\sys draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
 PFR breaks up multiple programs into many components with the goal of exchanging functionality between donor-donee pairs of programs.
-Contrary to PFR, dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.
+Contrary to PFR, \sys operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.
 
@@
 Recent trends in software engineering have led to unprecedented levels of third-party code (re-)use.
-We present \emph{program dialysis}, a novel library-aware analysis technique for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
-Contrary to heavy-weight dynamic analysis, dialysis lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
-Our dialysis prototype for JavaScript, \sys, is available as an open-source library for experimentation with other applications and analyses.
+We present \sys, a novel library-aware analysis framework for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
+Contrary to heavy-weight dynamic analysis, \sys lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
+
+\sys is  available as an open-source library for experimentation with other applications and analyses.
 

### 2020-05-27 paper/draft.tex
Massive rewrite

@@
 
-\newcommand{\fra}{fragmentation\xspace} % fracture?
+\newcommand{\fra}{fracture\xspace} % fracture?
 \newcommand{\ana}{analysis\xspace}      % 
 \newcommand{\ass}{reassembly\xspace}    % 
-\newcommand{\Fra}{Fragmentation\xspace} % fracture?
+\newcommand{\Fra}{Fracture\xspace} % fracture?
 \newcommand{\Ana}{Analysis\xspace}      % 
@@
 
-Effort and performance costs are severely compounded by the use of third-party libraries, usually glued together without a full understanding of their internals.
-This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
-  language-specific package repositories eliminate the cost of publishing and using a library.
-As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each one often only a few lines long~\cite{leftpad, npmstudy:19}.
-% how to say thousands of them depend on a 11-line lib?
+Effort and performance costs are severely compounded by the use of third-party libraries,\footnote{
+  The terms library, package, and module are used interchangeably.
+}
+often glued together without full understanding of their internals~\cite{libs}.
+% This is a recent phenomenon enabled by zero-cost code sharing
+%   language-specific package repositories eliminate the cost of publishing and using a library.
+Applications frequently count hundreds of libraries~\cite{npmstudy:19}, each one often only a few lines long~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
 Library-oriented analysis adds to the challenges of prior tools as
@@
 
-To address these challenges, we propose a novel approach to dynamic analysis, targeting dynamic programming languages---and implemented in \sys for the server-side JavaScript ecosystem (>1.3M libraries~\cite{modulecounts}).
+This paper presents a novel approach to dynamic analysis, targeting dynamic programming languages---and implemented in \sys for the server-side JavaScript ecosystem (>1.3M libraries~\cite{modulecounts}).
 \sys leverages the ability of these languages to import code at runtime as a string in order to apply transformations that wrap the module about to be imported with developer-provided, analysis-specific code.
@@
   (ii) it supports analyses expressed using the same language, tools, and abstractions as the program language,
-  (iii) it features low runtime performance overheads, enabling the potential for toggling its use in production environments.
+  (iii) it features low runtime performance overheads, enabling toggling its use in production environments.
 
@@
 \end{itemize}
-
+\noindent
 The paper then discusses \sys's limitations and its application to other languages~\sx{diss};
@@
 
-A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
+Libraries are development-time construct encapsulating reusable functionality.
 This functionality falls into two categories:
@@
 The content of the library is then read and wrapped in a way that resolves library-local names, such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript, to meaningful values.
-The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
+The wrapper is then interpreted and evaluated using the language's interpreter, which might result in side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
 Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.
@@
 As a result, a single \ttt{import} $l$ does not necessarily resolve to the same (version of the) library $l$ every time.
-The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
+The dual of this is also possible:
+   two different library names may resolve to the same identifier (\ie point to the same cache entry).
 These features complicate library-level analysis, especially in interpreted programming languages.
@@
 As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
-Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
-Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
+Heavy-weight runtime instrumentation~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
+Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either as the programs importing \ttt{event-stream} already made use of system calls to access the disk and network.
 Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its malicious payload.
@@
 Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
-Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
+Other examples of interfaces that are available to the entire program include global variables, library importing, and the module cache---all of which are accessible by any third-party library.
 % The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.
@@
   would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
-Wrapping library interfaces with profiling logic would collectively construct a model of the current workload.
+Wrapping library interfaces with profiling logic can be of aid to constructing a model of the current workload.
 Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
@@
 \heading{Type Invariant Discovery}
-Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
-For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
+Extracting type information in at the library boundary is helpful in a variety of scenarios. %, as type safety is an important property helpful in variety of scenarios. 
+Types can be used to
+  (i) identify library invariants to be preserved during code modifications,
+  (ii) generate (machine-checkable) library documentation, or 
+  (iii) guide library synthesis and regeneration~\cite{daikon}.
 This is especially important in dynamic programming languages:
-  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.
+  in the absence of static type signatures, there is not much one can say about a library without executing it and inspecting its properties.
 
@@
 To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
-Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec.
+Given a library---\eg \ttt{bignum}, \ttt{crypto}---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec.
 This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.
@@
 Library-level dynamic analysis can be used to discover such type assertions or invariants.
-The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the boundaries of libraries by observing their arguments during the execution of the program.
+The analysis would consult the (static) definition of a type system, capturing the type of values at the boundaries of libraries by observing their arguments during the execution of the program.
 %% TODO: such as the simply-typed lambda calculus augmented with objects and union types.
@@
 
-  \item \textbf{Fragmentation:}
+  \item \textbf{Fracture:}
 \sys starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
@@
 The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
-The cache needs to be augmented to support multiple wrappers per library, each capturing a small fragment of the overall analysis.
+The cache needs to be augmented to support multiple wrappers per library, each capturing a part of the overall analysis.
 % without breaking the program's semantics.
@@
 
-\subsection{Fragmentation}
+\subsection{Fracture}
 \label{one}
@@
 Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
-To do this, it extracts a static approximation of the dependency graph by traversing library files.
+To do this, it extracts an approximation of the dependency graph by traversing library files.
 Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
@@
 This is achieved in three logical steps:
-(i) transforming library's context, a mapping from names to values that are available from outside library,
+(i) transforming the library's context, a mapping from names to values that are available from outside library,
 (ii) interpreting the library within this context, so that all names bind and resolve to \sys-augmented values, and
@@
 
-To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
-Semantically, the context is a map from variable names to their values.
-Thus, \sys creates an auxiliary hash table mapping names to transformed values.
+To achieve this, \sys first needs to prepare a transformed copy of the library's context---a map from variable names that are (expected to be) in scope to their values.
+\sys creates an auxiliary hash table mapping names to transformed values.
 Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc
@@
 
-This section details our implementation of \sys for server-side JavaScript in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
+This section details the implementation of \sys for server-side JavaScript (Node.js v8.9.4) in about 1.5K LoC~\sx{impl1},
+and the three analyses developed atop \sys~\sx{impl2}.
 % We start with the internals of \sys's implementation, and then describe
-including the three analyses developed atop \sys~\sx{impl2}.
-Discussion of how other environments diverge from JavaScript is left for the next section~\sx{reqs}.
+The differences between JavaScript and other languages are left for \S\ref{reqs}. 
+% How other environments diverge from JavaScript is discussed in a later section~\sx{reqs}.
 
@@
 \sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
-\sys comes with a hard-coded list of names corresponding to the specific versions of EcmaScript and Node.
+\sys comes with a hard-coded list of variable names available to the code of a module, such as \ttt{require} and \ttt{Array};
+  the list contains about 150 entries and corresponds to the specific versions of EcmaScript and Node.
 Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
@@
 
-As the three analyses are quite complex to include in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
+As the three analyses are too complex to include in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:
 
@@
 \heading{Security Analysis}
-To address the security concerns of third-party libraries, we developed a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
+To address the security concerns of third-party libraries, we developed an on-off policy that analyzes accesses for every library-to-library combination.
 The analysis treats built-in libraries and global variables as modules,
 % and generates a list of permissions for each of their fields.
-and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
- (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
- (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
- (iii)  an execute permission (\X) indicates that a consumer executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).
-
-The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{require("Math").add: RX}.
+and develops a permission-like model where individual fields are governed by permission sets containing combinations of on and off permissions.
+At the start of the analysis all permissions are set to off (\ie default-deny), and gradually turn on based on the accesses they detect.
+Example accesses include:
+ (i) reading a value, including assigning it to a variable and passing it around to other modules;
+ (ii) modifying or deleting a value; and
+ (iii)  executing a value---\eg a function or a method---or invoking a constructor (usually prefixed by \ttt{new}).
+
+The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{require("Math").add: ON}.
 % that correspond to values of other modules or global-like language names.
@@
   For the most libraries, \sys overheads are under 5\%~\sx{meso}.
-  \sys is about $22\times$ \todo{faster} than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
+  \sys is over an order-of-magnitude faster than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
   By executing on unmodified runtimes, \sys has significantly better compatibility:
@@
   \caption{
-    \textbf{Analysis performance overhead.}
-    The plot shows the performance overhead of the three analyses for 45 libraries~\cf{meso}.
+    \textbf{Runtime overhead.}
+    The plot shows the runtime overhead of the three analyses for 50 libraries against normal (vanilla) execution~\cf{meso}.
   }
@@
 In terms of analysis, both systems are configured to perform dynamic frequency analysis of accesses to global variables.
-The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a fair and meaningful comparison between the two frameworks.
-Such analyses are useful for understanding how programs with third-party libraries interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.
+The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a % fair and 
+  meaningful comparison between the two frameworks.
+Such analyses are useful for understanding program components interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.
 
 Fig.~\ref{fig:meso} presents the comparison between \sys and Jalangi.
-The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
-  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
-The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
-Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.
+The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code.
+% the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
+The performance results show that \sys performs better than Jalangi, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
+
+Implemented as a custom interpreter, Jalangi exists at a different point in the trade-off space than \sys.
+On the one hand, it is significantly more fine-grained than \sys, capable of expressing and executing analyses at the granularity of individual expressions.
+On the other hand, it results in significantly higher incompatibility and runtime overhead---even when the analysis does not make use of its features.
 
@@
     \textbf{Applying \sys to three large applications}.
-    The table shows the overheads of applying the three analyses to three large applications~\cf{macro}.
+    The table shows the characteristics and runtime overheads of applying the three analyses to three large applications~\cf{macro}.
   }
@@
 %                                     &                   &                      &              \\
-Performance                          &                   &                      &              \\
+Performance (s)                      &                   &                      &              \\
 ~~Baseline                           &  0.97             &  1.27                &    0.754      \\
@@
 The differences between the number of sub-modules detected statically (by \ttt{npm ls}) and the ones observed by \sys are due to a few reasons.
-One is that \sys does not report accesses if a library has not been accessed at runtime, whereas \ttt{npm} traverses and reports on the entire dependency structure.
+One is that \sys does not report accesses if a library is not accessed at runtime, whereas \ttt{npm} traverses and reports on the entire dependency structure.
 \sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
@@
 The size of the resulting JSON files raises the challenge of analysis interpretability---just by running Terminalizer with \ttt{--help} returns more than 6K fragments from several (hundreds of) libraries.
-Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-readable name, not file-system module identifier.
+Custom \ttt{onExit} analysis routines post-process \sys's results to compress by module name---\ie squashing duplicate reports by human-readable name, not file-system module identifier.
 This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
@@
 \midrule
-globals vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
+global  vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
 built-in fields  &   1.44    &  6.46   &  6.24   &  5.96   \\
@@
 direct-access    &   4.06    &  7.24   &  7.16   &  6.79   \\
-timple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
+simple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
 cycles           &   4.32    &  8.32   &  8.19   &  7.73   \\
@@
 \sys-induced slowdown is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
-Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses.
+Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses:
   these benchmarks feature artificially tight loops with high-frequency accesses.
@@
 The proxy-wrapped version introduces interposition at every level.
-Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
+Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms ($3.5\times$) for the unmodified and proxy-wrapped versions, respectively.
 % 
@@
 	(ii) we had prior experience developing more sophisticated versions of SA and PD.
-We now expand on the requirements bolting our techniques on other runtime environments.
+We now expand on the requirements for bolting our techniques on other runtime environments.
 
@@
 
+It is worth noting that \sys does not require the entire source code of the library to be available.
+While this is common in dynamic languages, \sys can operate on language-aware wrappers as is common, for example, with Python wrappers around C libraries.
+
 To conclude, all major languages provide facilities to support a \sys-like framework, albeit with a different level of convenience.
@@
 
-The set of techniques presented in this paper shines when there is a need for urgency, select online analysis, and a high level of abstraction.
-It can help identify (or narrow down) the source of a problem quickly, by swiftly isolating homegrown code from standard and third-party libraries, by requiring a few lines of analysis-specific code inlined, and by leveraging the developer's expertise in their language of choice.
+The set of techniques presented in this paper shines at a need for urgency, select online analysis, and a high level of abstraction.
+It can help identify quickly the source of a problem by swiftly isolating homegrown code from standard and third-party libraries, by requiring a few lines of analysis-specific code to be inlined, and by leveraging the developer's expertise in their language of choice.
 By operating at coarser granularity, using the vanilla optimized runtime, and by toggling parts of the analysis on and off, it provides the ability to perform the analysis online.
-Finally, it deconstructs programs only at library boundaries, a naturally coarser granularity that is just right for certain classes of problems.
-
-\sys's set of techniques is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
-These limitations are due to several reasons.
-First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
-An important feature of the wrapping techniques presented in this paper is that they can track a library's full observable behavior.
-Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in the program's address space.
-A related problem is C's inability to traverse and wrap objects;
+Finally, it deconstructs programs only at library boundaries, a naturally coarser granularity that is ideal for certain classes of problems.
+
+\sys's set of techniques is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C, due to several reasons.
+C neither features import/export keywords and runtime code evaluation,
+% Dependencies often lack \emph{any} source code.
+  nor clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
+C libraries can forge pointers and access arbitrary locations in the program's address space, a feature that breaks a key hypothesis in \sys---namely, that the wrapping mechanism can track a library's full observable behavior.
+A final problem is C's inability to traverse and wrap objects;
   due to lack of runtime information about size and structure, it is unclear how to traverse and transform them.\footnote{
@@
 
-\nv{
-\sys builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
-Both approaches lower complexity by mapping multiple points across the program to the same actions, but \sys does not alter the program's control flow.
-Moreover, AOP works on languages that were already designed to support it, whereas \sys is explicitly designed to bolt onto existing languages.
-}
-
-More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
-While \sys uses metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
+Aspect-oriented programming (AOP) is a programming model where program points map to actions taken at these points~\cite{aop}.
+A part of \sys is genetically related to AOP, drawing from proxies, wrappers, mirrors and other related mechanisms up to  metaobjects~\cite{metaobject},
+While aspects are a powerful---and indeed more cross-cutting than \sys's localized transformations---adding support for aspects in a language is not trivial;
+  while AspectJ and AspectC++ are indeed extensions of popular languages, they do require modifications to the language and runtime system.
+This is antithetical to \sys, which operates on a completely unmodified language and runtime environment.
+% Key ingredients of \sys's approach include variable shadowing, runtime loading,
+
+% \sys piggy-backs on a common  mechanism of existing (dynamic) languages---runtime module loading---to enable dynamic analysis.
+% More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
+% While \sys uses metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
 % self element
@@
 Recent trends in software engineering have led to unprecedented levels of third-party code (re-)use.
-We present \sys, a novel library-aware analysis framework for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
-Contrary to heavy-weight dynamic analysis, \sys lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
-
-\sys is  available as an open-source library for experimentation with other applications and analyses.
+We present \sys, a novel library-oriented dynamic analysis framework for dismantling, analyzing, and reassembling programs by combining name shadowing, context wrapping, and transformation of the underlying dependency graph.
+% Contrary to heavy-weight dynamic analysis, \sys lowers developer effort in writing and deploying analysis, improves runtime performance, and operates at a high level of abstraction.
+\sys delivers better performance  than conventional analysis systems, improved compatibility, and support for a range of dynamic analyses.
+
+% \sys is  available as an open-source library for experimentation with other applications and analyses.
 

### 2020-05-27 paper/draft.tex
Update

@@
   (i) current runtime information, such as profiling data, in view of changing load patterns~\cite{staticdynamic},
-  (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
+  (ii) accurate visibility into the execution, devoid of imprecision or approximation~\cite{staticdynamic},
   (iii) Turing-complete policies, where monitors themselves are programs~\cite{contracts1, contracts2, contracts3},
@@
      We answer this question in \S\ref{impl}, by implementing these and other analyses.
-    \sys operates as a library around a unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
+    \sys operates as a library around unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
     % Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.
@@
   \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
-  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
+    Most of the overheads ($>95\%$)come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
   % The majority of the overheads come from the use of \ttt{with}, a
@@
   Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
-These applications are highly popular, with Koa.js and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
+These applications are highly popular, with Koa and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
 Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.
@@
   these benchmarks feature artificially tight loops with high-frequency accesses.
-Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under $1ms$.
+Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under 1ms.
 
@@
 There are a few highlights worth noting.
-While the number of objects wrapped by\sys starts growing exponentially, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
-Accesses grow quickly for the first couple of levels---objects for some of these libraries are hit several thousand times---but then remain stable.
-This is usually because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.
+While the number of objects wrapped by \sys starts growing rapidly, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
+Accesses grow exponentially for the first couple of levels---as objects at levels have multiple fields, many of which are accessed several thousand times---but then stabilize around level 5.
+This is because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.
 
@@
 
-By operating on library boundaries, \sys uses a few special language features, supported by all major programming languages.
+By operating on library boundaries, \sys uses a few special language features supported by all dynamic programming languages.
 First, \sys needs to re-wire the \ttt{import} keyword:
@@
 Compiled languages would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
-Examples include templates and macro expansions such as Haskell's Template and Rust's macro system.
+Examples include templates and macro expansions such as Template Haskell and Rust's macro system.
 % Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.

### 2020-06-22 paper/draft.tex
Minor updates/corrections

@@
 \author{
-{\rm Anonymous Author(s)}\\
-\normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
+% {\rm Anonymous Author(s)}\\
+% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
+% {\rm Nikos Vasilakis \quad Grigorios Ntousakis\textsuperscript{$*$} \quad Martin Rinard}\\
+% MIT, CSAIL \quad \quad \quad \textsuperscript{$*$}TU Crete, ECE
 }
@@
 \item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly by general-purpose analysis frameworks.
-\item \S\ref{design} presents the design of \sys, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
+\item \S\ref{design} presents the design of \sys, bolt-on library-oriented dynamic analysis, which meets the requirements of the three case-study analyses.
 \item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
@@
     (iii) total valid accesses~\cf{micro}.
+    \vspace{-4mm}
   }
@@
 Fig.~\ref{fig:objects} shows \sys's context characteristics on all 50 libraries~\sx{meso}. % as a function of context.
-In terms of the number of objects wrapped, the vast majority comes from Node which accounts for 91.1\% of all wrappers.
-In terms of unique number of accesses, for both invalid and invalid ones the majority comes from \ttt{require};
-  taking their number into account, the majority comes from ES and Node names, whereas the majority of invalid ones comes from \ttt{export}s.
+In terms of the number of objects wrapped, the majority comes from Node (91.1\% of all wrappers).
+In terms of unique number of accesses, for both invalid and invalid the majority comes from \ttt{require};
+  taking their number into account, valid accesses concentrate on ES and Node, whereas invalid ones concentrate on \ttt{export}s.
 
@@
     (iii) total number of accesses~\cf{micro}.
+    \vspace{-5mm}
   }
@@
 
-This section starts by discussing \sys's requirements from the programming language~\sx{reqs}. It then reflects on its strengths and weaknesses~\sx{principles}.
+This section discusses \sys's minimum requirements~\sx{reqs} and reflects on its strengths and weaknesses~\sx{principles}.
 
@@
 The techniques presented in this paper are applicable to any programming language.
-We chose the JavaScript ecosystem % to evaluate the feasibility of our approach,
+We chose JavaScript % to evaluate the feasibility of our approach,
 primarily because
@@
 %   \sys starts by wrapping a library during import, adding a small overhead on its loading time.
-However, they operate at a much lower level (binary) than \sys, are much more detailed and heavy-weight, and are not available to high-level runtime environments as a language-aware library.
+However, they operate at a much lower level (binary) than \sys, are much more detailed and heavy-weight, and are usually not available to high-level languages as a language-aware library.
 
 Aspect-oriented programming (AOP) is a programming model where program points map to actions taken at these points~\cite{aop}.
-A part of \sys is genetically related to AOP, drawing from proxies, wrappers, mirrors and other related mechanisms up to  metaobjects~\cite{metaobject},
-While aspects are a powerful---and indeed more cross-cutting than \sys's localized transformations---adding support for aspects in a language is not trivial;
-  while AspectJ and AspectC++ are indeed extensions of popular languages, they do require modifications to the language and runtime system.
-This is antithetical to \sys, which operates on a completely unmodified language and runtime environment.
+A part of \sys is genetically related to AOP, drawing from proxies, wrappers, mirrors and other related mechanisms up to  metaobjects~\cite{metaobject}.
+While aspects are more powerful than \sys's localized transformations, adding support for them in a language is not trivial:
+  for example, AspectJ and AspectC++, while extensions of popular languages, require modifications to the original language and/or runtime system.
+\sys operates on a completely unmodified language and runtime environment.
 % Key ingredients of \sys's approach include variable shadowing, runtime loading,
@@
 
+% \subsection*{Acknowledgments}
+% 
+% We thank Ben Karel, Jeff Perkins, and the MIT PAC group for their valuable thoughts. 
+% Much of \sys's design was informed through interactions with the community---we are particularly thankful to Isaac Z.
+Schlueter and CJ Silverio from npm and Daniel Katz, Petros Efstathopoulos, Kevin Roundy, and Daniel Marino from Symantec/NortonLifeLock Research Group.
+% This work was partly supported by DARPA contract no. HR00112020013 (ALRSCC).
+
 \bibliographystyle{plain}
